%------------------------------------------------------------------------------%
\begingroup
    \ifcsname\PATH\endcsname
        \newcommand{\PATH}{books/Algebra/Group_Theory}
        \newcommand{\OLDPATH}{\PATH}
    \else
        \newcommand{\OLDPATH}{\PATH}
        \renewcommand{\PATH}{books/Algebra/Group_Theory}
    \fi
    \chapter{Elementary Group Theory}
        One of the most fundamental structures studied in algebra, and more
        generally in mathematics, is that of a \gls{group}\index{Group}.
        Recalling some notions from Book~\ref{book:Foundations}, we define a
        group to be a \gls{set}\index{Set} $G$ together with a
        \gls{binary operation}\index{Binary Operation} $*$ that satisfies a few
        properties. There are three properties $*$ must satisfy,
        \glslink{associative operation}{associativity}%
        \index{Binary Operation!Associative},
        \glslink{unital element}{identity}\index{Unital Element}, and
        \glslink{invertible element}{invertibility}\index{Invertible Element},
        all of which were briefly discussed in
        Chapt.~\ref{chapt:Function_Theory}. Groups then seem to be very simple
        objects, and indeed the standard arithmetic that one is
        familiar with in \gls{mathbbR} has far more structure (it is a
        \gls{field}\index{Field}). However, in another sense, perhaps groups
        have too much structure. We can certainly strip away the requirement of
        invertibility, leaving associativity and identity in tact, and this
        results in a \gls{monoid}\index{Monoid}. We can further rid of the
        existence of an identity, maintaining only associativity, and it may be
        reasonable that such an object has its uses. Furthermore we can take
        away the requirement that we have a binary operation, and replace this
        with a partial function\index{Partial Function}. This latter object
        gives rise to the notion of a groupoid\index{Groupoid}, which has
        applications in geometry and analysis. We'll begin by considering
        ordinary binary operations, but only require the operation to be
        associative. Such a structure is called a
        \gls{semigroup}\index{Semigroup}.
        \input{\PATH/Elementary_Group_Theory/Group_Like_Structures.tex}
        \input{\PATH/Elementary_Group_Theory/Groups.tex}
        \input{\PATH/Elementary_Group_Theory/Group_Morphisms.tex}
    \chapter{Finite Groups}
        Finite groups are of fundamental interest not only to mathematicians,
        but throughout many of the other sciences. Indeed, chemists and
        physicists make regular use of the theory of finite groups, and its
        application can be found in general relativity, quantum mechanics, and
        studying the lattice structure of organic molecules. A finite group is
        exactly what it sounds like: A group $(G,*)$ where $G$ is a finite set.
        \begin{fdefinition}{Finite Group}{Finite_Group}
            A finite group is a \gls{group} $(G,*)$ such that $G$ is a
            finite set.
        \end{fdefinition}
        One of the fundamental problems of group theory is a combinatorial one.
        Given an integer $n\in\mathbb{N}$, how many groups with $n$ elements are
        there (up to isomorphism)? This challenging problem can be aided by the
        theorems of Cayley, Cauchy, Lagrange, and Sylow, and it is our aim to
        develop this theory.
        \input{\PATH/Finite_Groups/Permutation_Groups.tex}
        \input{\PATH/Finite_Groups/Dihedral_Groups.tex}
    \renewcommand{\PATH}{\OLDPATH}
\endgroup