\documentclass[crop=false,class=book]{standalone}
%---------------PREAMBLE------------%
\input{../../../preamble.tex}
%--------------Title Page-----------%
\begin{document}
\chapter{Miscellaneous Materials}
    \section{Naif Toolkit}
        \subimport{./NAIF_Toolkit/}{Tutorials}
    \section{Miscellaneous Notes}
        \subimport{./Notes/}{Miscellaneous}
        \subimport{./Notes/}{Ryans_Progress_Report}
    \subsection{Meeting Minutes}
        \subsubsection{2017/05/30}
            \subsubsection{Goals}
            \begin{enumerate}
                \begin{multicols}{2}
                    \item Overview of Cassini Mission.
                    \item Overview of Team Goals.
                    \item Team responsibilities.
                    \item How we'll do our work.
                    \item Familiarize with key resources.
                    \item Procedures and skills needed.
                    \item Analyze, preserve, and document
                          \par
                          RSS observations.
                    \item Design data archive for PDS.
                    \item Design open-source software for
                          \par
                          going from raw data to optical depth.
                    \item Develop User's Guide.
                \end{multicols}
            \end{enumerate}
            Jolene:
            \begin{enumerate}[nolistsep]
                \begin{multicols}{2}
                    \item Download entire set of RSS raw data.
                    \item Design format of data and software.
                    \item Test Dick Simpson's MATLAB program.
                    \item Reproduce "Browse" products for Rev007E.
                    \item Design and produce "Browse" for each data set.
                    \item Edit Revised RSS User's Guide.
                \end{multicols}
            \end{enumerate}
            Glenn:
            \begin{enumerate}[nolistsep]
                \begin{multicols}{2}
                    \item Convert data from raw to DLP.
                    \item Develop expertise in DSP.
                    \item Learn to use NAIF toolkit.
                \end{multicols}
            \end{enumerate}
\end{document}