\section{Integration}
    The integral of a constant function on an interval
    $[a,b]$ is defined by the signed area under the
    rectangle formed by the function. That is, if
    $f(x)=C$, we define the integral on $[a,b]$ to
    be $C(b-a)$. Given a piece-wise constant function,
    we can define the integral as the sum over the
    various regions. Given an arbitrary function, the
    only reasonable way to define the integral is to
    take a limit of approximations using piece-wise
    constant functions. This is how the Riemann integral
    is defined. The Riemann integral makes sense if
    the given function is continuous. By making the
    partition small enough, approximating a continuous
    function on a small interval by a constant can be
    reasonable. But consider the function:
    \begin{equation}
        f(x)=
        \begin{cases}
            0,&x\notin\mathbb{Q}\\
            1,&x\in\mathbb{Q}
        \end{cases}
    \end{equation}
    Given any interval $(a,b)$, $f$ takes on the values
    0 and 1 and thus it is not reasonable to approximate
    this function by a constant anywhere. However,
    the measure, or length, of $\mathbb{Q}$ is zero, and
    the height of the function on $\mathbb{Q}$ is 1.
    Thus it may be reasonable to define the area under
    this function as zero. While the Riemann integral
    cannot handle such function, the Lebesgue integral
    can. Given a measurable space
    $(\Omega,\mathcal{A},\mu)$, and a measurable
    function $f:\Omega\rightarrow\mathbb{R}$, where
    $f$ is $\mathcal{A}-\mathcal{B}$ measurable,
    $\mathcal{B}$ being the Borel
    $\sigma-\textrm{Algebra}$, it is possible to define
    the integral of $f$.
    \begin{ldefinition}{Support of a Real Valued Function}
          {Support_Real_Func}
        The support of a real-valued function
        $f:\Omega\rightarrow\mathbb{R}$ is the set:
        \begin{equation}
            \mathrm{supp}(f)=\{\omega\in\Omega:f(\omega)\ne{0}\}
        \end{equation}
    \end{ldefinition}
    \begin{ldefinition}{Simple Function}{Simple_Functions}
        A simple function from a measurable space
        $(\Omega,\mathcal{A},\mu)$ to the real line
        $\mathbb{R}$ is a function
        $f:\Omega\rightarrow\mathbb{R}$ such that
        $f$ is $\mathcal{A}-\mathcal{B}$ measurable,
        where $\mathcal{B}$ is the Borel
        $\sigma-\textrm{Algebra}$, the range of $f$,
        $f(\Omega)$, is finite, and the measure of the
        support of $f$ is finite.
    \end{ldefinition}
    \begin{lexample}{}{Measurable_Space}
        Let $(\Omega,\mathcal{A},\mu)$ be a measurable
        space, and let $E\subseteq\Omega$ be measurable
        and of finite measure. Define the following:
        \begin{equation}
            \chi_{E}(\omega)=
            \begin{cases}
                0,&\omega\notin{E}\\
                1,&\omega\in{E}
            \end{cases}
        \end{equation}
        This is called the indicator function of
        $E$. It is a simple function on the measurable
        space $(\Omega,\mathcal{A},\mu)$ since
        $\mu(E)<\infty$. To see that it is measurable,
        note that the pre-image is either
        $\emptyset$, $E$, $E^{C}$, or $\Omega$, and thus
        $\chi_{E}$ is measurable. Finally, it takes on
        only two values and thus it's range is finite.
    \end{lexample}
    \begin{lexample}{}{Another_Measurable_Space}
        Let $(\Omega,\mathcal{A},\mu)$ be a measurable
        space, and let $B_{1},\dots,B_{n}$ be measurable
        subsets of $\Omega$. Furthermore, let
        $a_{1},\dots,a_{n}$ be real numbers. If we let
        $\chi_{B_{i}}$ denote that indicator
        function of $B_{i}$, then we see that their sum
        is also a simple function. That is, define the
        following:
        \begin{equation}
            f(\omega)=\sum_{k=1}^{n}
                a_{k}\chi_{B_{k}}(\omega)
        \end{equation}
        THen $f:\Omega\rightarrow\mathbb{R}$ is a simple
        function. Since the sum of measurable functions
        is measurable, we see that $f$ is measurable.
        We also have that the support is finite since:
        \begin{equation}
            \mathrm{supp}(f)\subseteq\bigcup_{k=1}^{n}B_{k}
        \end{equation}
        Finally, there are $2^{n}$ ways, at most, to
        combine the various real numbers
        $a_{1},\dots,a_{n}$, and thus the range of
        $f$ has, at most, $2^{n}$ elements. Therefore
        $f$ is simple.
    \end{lexample}
    Now, let $(\Omega,\mathcal{A},\mu)$ be a
    measurable space, and let
    $f:\Omega\rightarrow\mathbb{R}$ be a simple function.
    If $f$ is simple than it's range is finite. Let
    $a_{1},\cdots,a_{n}$ be the distinct elements of
    $f(\Omega)$ and define the following:
    \begin{equation}
        E_{k}=f^{-1}\big(\{a_{k}\}\big)
    \end{equation}
    Since $f$ is simple, it is measurable, and thus
    $E_{k}\in\mathcal{A}$ for all $k\in\mathbb{Z}_{n}$.
    Moreover, for $i\ne{j}$,
    $E_{i}\cap{E}_{j}=\emptyset$. But, since $f$ is
    simple, the measure of its support is finite, and
    thus for all $k\in\mathbb{Z}_{n}$,
    the masure of $E_{k}$ is also finite.
    We can thus obtain the following for $f$:
    \begin{equation}
        f(\omega)=
            \sum_{k=1}^{n}a_{k}\chi_{E_{k}}(\omega)
    \end{equation}
    This is called the \textrm{Canonical Representation}
    of $f$.
    \begin{ldefinition}{Integral of a Simple Function}
          {Integral_Simple_Function}
        The integral of a simple function
        $f:\Omega\rightarrow\mathbb{R}$ on a measurable
        space $(\Omega,\mathcal{A},\mu)$ with canonical
        form:
        \begin{equation}
            f(\omega)=\sum_{k=1}^{n}
                a_{k}\chi_{E_{k}}(\omega)
        \end{equation}
        Is the real number $\int_{\Omega}f\diff{\mu}$
        define by:
        \begin{equation}
            \int_{\Omega}f\diff{\mu}=
                \sum_{k=1}^{n}a_{k}\mu(E_{k})
        \end{equation}
    \end{ldefinition}
    The first thing to check to ensure that this is
    a good definition of integration is that the
    sum of two integrals is the integral of the sum
    of the two functions. We first prove a result that
    will make this definition more flexible.
    \begin{theorem}
        If $(\Omega,\mathcal{A},\mu)$ is a measurable
        space, and if $B_{1},\dots,B_{n}$ are measurable
        subsets of $\Omega$ that are pairwise disjoint
        and such that, for all $k\in\mathbb{Z}_{n}$,
        $\mu(B_{k})<\infty$, if
        $\lambda_{1},\dots,\lambda_{n}$ are real
        numbers, and if $f:\Omega\rightarrow\mathbb{R}$
        is defined by:
        \begin{equation}
            f(\omega)=\sum_{k=1}^{n}
                \lambda_{k}\chi_{B_{k}}(\omega)
        \end{equation}
        Then the integral of $f$ is given by:
        \begin{equation}
            \int_{\Omega}f\diff{\mu}
                =\sum_{k=1}^{n}\lambda_{k}
                \mu(B_{k})
        \end{equation}
    \end{theorem}
    \begin{proof}
        For every $\omega\in\Omega$ falls in only
        one of the $B_{k}$. But if $\omega\in{B}_{k}$,
        then $f(\omega)=\lambda_{k}$. Let
        $a_{1},\hdots,a_{n}$ be the distinct values of
        $f$ and defin $\mathcal{J}_{k}$ as:
        \begin{equation}
            \mathcal{J}_{k}=\{j:\lambda_{j}=a_{k}\}
        \end{equation}
        Also, let $\mathcal{J}_{0}$ be defined as:
        \begin{equation}
            \mathcal{J}_{0}=\{j:\lambda_{j}=0\}
        \end{equation}
        If $E_{k}=f^{-1}(\{a_{k}\}$, then:
        \begin{equation}
            E_{k}=\bigcup_{j\in\mathcal{J}_{k}}B_{j}
        \end{equation}
        But since the $B_{j}$ are pair-wise disjoint,
        we have that:
        \begin{equation}
            \mu(E_{k})=\sum_{j\in\mathcal{J}_{k}}
                \mu(B_{j})
        \end{equation}
        But then:
        \begin{align}
            \int_{\Omega}f\diff{\mu}
            &=\sum_{k=1}^{n}a_{k}\mu(E_{k})\\
            &=\sum_{k=1}^{n}a_{k}\Big(
                    \sum_{j\in\mathcal{J}_{k}}\mu(B_{j})
                \Big)\\
            &=\sum_{k=1}^{n}\sum_{j\in\mathcal{J}_{k}}
                a_{k}\mu(B_{j})\\
            &=\sum_{k=1}^{n}\sum_{j\in\mathcal{J}_{k}}
                \lambda_{j}\mu(B_{j})\\
            &=\sum_{k=1}^{m}\lambda_{k}\mu(B_{k})
        \end{align}
    \end{proof}
    This theorem will make it easier to prove the
    additive property of integrals. We are still only
    talking about the integral of simple functions.
    \begin{theorem}
        If $(\Omega,\mathcal{A},\mu)$ is a measurable
        space and $f:\Omega\rightarrow\mathbb{R}$ and
        $g:\Omega\rightarrow\mathbb{R}$ are simple
        functions, then:
        \begin{equation}
            \int_{\Omega}(f+g)\diff{\mu}
            =\int_{\Omega}f\diff{\mu}
            +\int_{\Omega}g\diff{\mu}
        \end{equation}
    \end{theorem}
    \begin{proof}
        For let $f$ and $g$ have the following
        canonical representations:
        \begin{align}
            f(\omega)&=\sum_{k=1}^{n}\alpha_{k}
                \chi_{A_{k}}(\omega)\\
            g(\omega)&=\sum_{k=1}^{m}\beta_{k}
                \chi_{B_{k}}(\omega)
        \end{align}
        Define the following:
        \begin{align}
            A_{n+1}
            =\Big(\bigcup_{k=1}^{m}B_{k}\Big)\setminus
                \Big(\bigcup_{j=1}^{n}A_{j}\Big)\\
            B_{m+1}
            =\Big(\bigcup_{k=1}^{n}A_{k}\Big)\setminus
                \Big(\bigcup_{j=1}^{m}B_{j}\Big)
        \end{align}
        From this, we have the following:
        \begin{equation}
            \bigcup_{k=1}^{n+1}A_{k}=
            \bigcup_{j=1}^{m+1}B_{j}
        \end{equation}
        Let $\alpha_{n+1}=\beta_{m+1}=0$. Then we have:
        \begin{align}
            f(\omega)&=\sum_{k=1}^{n+1}\alpha_{k}
                \chi_{A_{k}}(\omega)\\
            g(\omega)&=\sum_{k=1}^{m+1}\beta_{k}
                \chi_{B_{k}}(\omega)
        \end{align}
        Then, for all $i$, we have:
        \begin{align}
            A_{i}&=A_{i}\bigcap
                \Big(\bigcup_{j=1}^{m+1}B_{j}\Big)\\
            &=\bigcup_{j=1}^{m+1}
                \Big(A_{i}\cap{B}_{j}\Big)\\
            B_{i}&=B_{i}\bigcap
                \Big(\bigcup_{k=1}^{n+1}A_{k}\Big)\\
            &=\bigcup_{k=1}^{n+1}
                \Big(A_{k}\cap{B}_{i}\Big)
        \end{align}
        And these are all pair-wise disjoint sets.
        So, we have:
        \begin{align}
            f(\omega)&=
            \sum_{i=1}^{n+1}\sum_{j=1}^{m+1}\alpha_{i}
                \chi_{A_{i}\cap{B}_{j}}(\Omega)\\
            g(\omega)&=
            \sum_{i=1}^{n+1}\sum_{j=1}^{m+1}\beta_{j}
                \chi_{A_{i}\cap{B}_{j}}(\Omega)
        \end{align}
        Summing these two functions, we get:
        \begin{equation}
            f(\omega)+g(\omega)=
            \sum_{i=1}^{n+1}\sum_{j=1}^{m+1}
                (\alpha_{i}+\beta_{j})
                \chi_{A_{i}\cap{B}_{j}}(\Omega)
        \end{equation}
        But by the previous theorem:
        \begin{align}
            \int_{\Omega}(f+g)\diff{\mu}
            &=\sum_{i=1}^{n+1}\sum_{j=1}^{m+1}
                (\alpha_{i}+\beta_{j})
                \mu(A_{i}\cap{B}_{j})\\
            &=\sum_{i=1}^{n+1}\sum_{j=1}^{m+1}
                \alpha_{i}\mu(A_{i}\cap{B}_{j})+
                \sum_{i=1}^{n+1}\sum_{j=1}^{m+1}
                \beta_{j}\mu(A_{i}\cap{B}_{j})\\
            &=\sum_{i=1}^{n+1}\alpha_{i}\mu(A_{i})+
                \sum_{j=1}^{m+1}\beta_{j}\mu(B_{j})\\
            &=\int_{\Omega}f\diff{\mu}+
                \int_{\Omega}g\diff{\mu}
        \end{align}
    \end{proof}
    The integrals of simple functions also have the
    property of homogeneity.
    \begin{theorem}
        If $(\Omega,\mathcal{A},\mu)$ is a measurable
        space, $f:\Omega\rightarrow\mathbb{R}$ is
        a simple function, and if $c\in\mathbb{R}$,
        then:
        \begin{equation}
            \int_{\Omega}cf\diff{\mu}=
            c\int_{\Omega}f\diff{\mu}
        \end{equation}
    \end{theorem}
    \begin{theorem}
        If $(\Omega,\mathcal{A},\mu)$ is a measurable
        space, $f:\omega\rightarrow\mathbb{R}$ is
        a simple function, if $A_{1},\dots,A_{n}$
        are measurable subsets of $\Omega$ with
        finite measure, and if $f$ is such that:
        \begin{equation}
            f(\omega)=\sum_{k=1}^{n}a_{k}
                \chi_(A_{k})(\omega)
        \end{equation}
        Then:
        \begin{equation}
            \int_{\Omega}f\diff{\mu}=
            \sum_{k=1}^{n}a_{k}\mu(A_{k})
        \end{equation}
    \end{theorem}
    \subsection{Further Properties of the Integral}
        So far we have defined the integral of a simple
        function over the entire of a given space
        $\Omega$. We often wish to evaluate the integral
        of a function on a subset of $\Omega$, rather
        than the entire of it. We can do this by defining
        the following:
        \begin{equation}
            f_{E}(\omega)=
            \begin{cases}
                f(\omega),&\omega\in{E}\\
                0,&\omega\notin{E}
            \end{cases}
        \end{equation}
        We need some properties of $f_{E}$.
        $f_{E}$ is measurable, has finite range, and
        has support of finite measure, and is therefore
        simple. $f_{E}$ can have only one more value
        (That is, zero) than $f$. Finally,
        $\mathrm{supp}(f_{E})\subseteq{\mathrm{supp}(f)}$. We define
        the integral on $E\in\mathcal{A}$ as follows:
        \begin{equation}
            \int_{E}f\diff{\mu}=
            \int_{\Omega}f_{E}\diff{\mu}
        \end{equation}
        Since $f_{E}$ is also simple, the right hand
        side of this equation is well defined.
        \begin{theorem}
            If $(\Omega,\mathcal{A},\mu)$ is a measurable
            space, if $E_{1},E_{2}$ are disjoint
            measurable subsets of $\Omega$, and if
            $f:\Omega\rightarrow\mathbb{R}$ is a simple
            function, then:
            \begin{equation}
                \int_{E_{1}\cup{E}_{2}}f\diff{\mu}=
                \int_{E_{1}}f\diff{\mu}+
                \int_{E_{2}}f\diff{\mu}
            \end{equation}
        \end{theorem}
        This is similar to a notion that is found when
        studying the Riemann integral. That is:
        \begin{equation}
            \int_{a}^{b}f(x)\diff{x}=
            \int_{a}^{c}f(x)\diff(x)+
            \int_{c}^{b}f(x)\diff{x}
        \end{equation}
        \begin{theorem}
            If if $f:\omega\rightarrow\mathbb{R}$
            is a simple function, and if
            $f(\omega)\geq{0}$ for all $\omega\in\Omega$,
            then:
            \begin{equation}
                \int_{\Omega}f\diff{\mu}\geq{0}
            \end{equation}
        \end{theorem}
        \begin{theorem}
            If $f:\Omega\rightarrow\mathbb{R}$ is
            simple, then:
            \begin{equation}
                \int_{\Omega}f\diff{\mu}=0
            \end{equation}
            If and only if $f=0$ $\mu$ almost everywhere.
        \end{theorem}
        \begin{ftheorem}
              {Triangle Inequality
               for Simple Functions}{}
            If $f$ is a simple function, then:
            \begin{equation}
                \Big|\int_{\Omega}f\diff{\mu}\Big|
                \leq\int_{\Omega}|f|\diff{\mu}
            \end{equation}
        \end{ftheorem}
    \subsection{Limit Theorems for Simple Functions}
        \begin{theorem}
            If $f_{n}:\Omega\rightarrow\mathbb{R}$ is
            a sequence of simple functions such that
            $f_{n}\rightarrow{f}$ uniformly,
            where $f$ is a simple function,
            and if there is a measurable set $E$
            such that $\mathrm{supp}(f_{n})\subseteq{E}$ and
            $\mathrm{supp}(f)\subseteq{E}$, and if
            $\mu(E)<\infty$, then:
            \begin{equation}
                \underset{n\rightarrow\infty}{\lim}
                \int_{\Omega}f_{n}\diff{\mu}
                =\int_{\Omega}f\diff{\mu}
            \end{equation}
        \end{theorem}
        \begin{proof}
            For:
            \begin{align}
                \Big|
                    \int_{\Omega}f_{n}\diff{\mu}-
                    \int_{\Omega}f\diff{\mu}
                \Big|
                &=\Big|\int_{\Omega}(f_{n}-f)\diff{\mu}
                    \Big|\\
                &\leq\int_{\Omega}|f_{n}-f|\diff{\mu}\\
                &=\int_{E}|f_{n}-f|\diff{\mu}\\
                &\leq\int_{E}\varepsilon\diff{\mu}\\
                &=\varepsilon\int_{E}\diff{\mu}\\
                &=\varepsilon\mu(E)
            \end{align}
            Since $\mu(E)<\infty$, this can be made
            arbitrarily small.
        \end{proof}
        \begin{theorem}
            If $f_{n}\rightarrow{f}$ uniformly, and if
            $f_{n}$ and $f$ are simple, then
            $f_{n}$ is uniformly bounded.
        \end{theorem}
        \begin{theorem}[Bounded Convergence Theorem]
            If $f_{n}\rightarrow{f}$, $f_{n}$ are
            simple and $f$ is simple, if
            $f_{n}$ are uniformly bounded, and if
            there is a measurable set $E$ of finite
            measure such that $\mathrm{supp}(f_{n})\subseteq{E}$
            and $\mathrm{supp}(f)\subseteq{E}$, then:
            \begin{equation}
                \underset{n\rightarrow\infty}{\lim}
                \int_{\Omega}f_{n}\diff{\mu}
                =\int_{\Omega}f\diff{\mu}
            \end{equation}
        \end{theorem}
        \begin{lexample}{}{Bounded_Convergence_Theorem}
            The additional assumptions are indeed
            necessary, and without them these results
            may not hold. For let $f_{n}$ be defined as:
            \begin{equation}
                f_{n}(\omega)=
                \begin{cases}
                    n,&0\leq\omega\leq\frac{1}{n}\\
                    0,&\textrm{Otherwise}
                \end{cases}
            \end{equation}
            Then $\int_{\mathbb{R}}f_{n}\diff{\mu}=1$
            for all $n$, but the limit function is
            $f=0$, and this has integral zero. It is
            also not guarenteed that the results
            fail, for let:
            \begin{equation}
                f_{n}(\omega)=
                \begin{cases}
                    n,&0\leq\omega\leq\frac{1}{n^{2}}\\
                    0,&\textrm{Otherwise}
                \end{cases}
            \end{equation}
            Then the limit function is zero, and the
            integral is $\frac{1}{n}$, which does indeed
            converge to zero. For the requirement that
            $\mathrm{supp}(f_{n})$ and $\mathrm{supp}(f)$ be contained in
            one set, consider the following function:
            \begin{equation}
                f_{n}(\omega)=
                \begin{cases}
                    1,&n\leq\omega\leq{n+1}\\
                    0,&\textrm{Otherwise}
                \end{cases}
            \end{equation}
            Then $f_{n}$ is uniformly bounded,
            converges to $0$, but the integral is
            1 for all $n$.
        \end{lexample}
        \begin{theorem}[Monotone Convergence Theorem]
            If $f_{n}$, $f$ are simple functions, if
            $f_{n}\rightarrow{f}$, if $f_{n}\leq{f}_{n+1}$,
            then:
            \begin{equation}
                \int_{\Omega}f_{n}\diff{\mu}
                \rightarrow\int_{\Omega}f\diff{\mu}
            \end{equation}
        \end{theorem}
        \begin{theorem}
            \label{thm:MEASURE_THEORY_LIM_INT_MONO_SIMPLE_FUNCS}
            If $f_{n}$ and $g_{n}$ are simple and monotonically
            increasing, and if:
            \begin{equation}
                \underset{n\rightarrow\infty}{\lim}f_{n}(\omega)
                =\underset{n\rightarrow\infty}{\lim}g_{n}(\omega)
            \end{equation}
            Then:
            \begin{equation}
                \underset{n\rightarrow\infty}{\lim}
                \int_{\Omega}f_{n}\diff\mu
                =\underset{n\rightarrow\infty}{\lim}
                \int_{\Omega}g_{n}\diff\mu
            \end{equation}
        \end{theorem}
        This theorem will allow us to extend the definition
        of the integral to a more general class of functions.
    \subsection{Integration of Non-Negative Measurable Functions}
        Consider a measure space $(\Omega,\mathcal{A},\mu)$ and
        let $f:\Omega\rightarrow\mathbb{R}$ be an
        $\mathcal{A}-\mathcal{B}$ measurable function, where
        $\mathcal{B}$ is the Borel $\sigma\textrm{-Algebra}$ on
        $\mathbb{R}$. If there exist a sequence of simple
        functions $f_{n}$ that are monotonically increasing
        and such that $f_{n}\rightarrow{f}$, then we define the
        integral of $f$ as follows:
        \begin{equation}
            \int_{\Omega}f\diff{\mu}=
            \underset{n\rightarrow\infty}{\lim}
            \int_{\Omega}f_{n}\diff{\mu}
        \end{equation}
        Because of
        Thm.~\ref{thm:MEASURE_THEORY_LIM_INT_MONO_SIMPLE_FUNCS}
        this is a well defined concept, since for any
        two sequences of simples functions that are monotonically
        increasing and converge to $f$, the limit of the
        integrals is the same, thus giving a consitent definition
        to the integral of $f$. The first question that then
        arises is which measurable functions can be approximated
        arbitrarily well by a sequence of monotonically
        increasing simple functions? From the definition we will
        need that $f$ is bounded below. For now we will discuss
        measurable functions that are non-negative. Let
        $f:\Omega\rightarrow\mathbb{R}$ be any non-negative
        function, it need not be measurable. We wish to construct
        a sequence of simple functions $f_{n}$ such that
        $f_{n}$ is monotonically increasing, and for all
        $\omega\in\Omega$, $f_{n}(\omega)\rightarrow{f}(\omega)$.
        We construct such a sequence as follows, dividing
        the $[0,n)$ into $n2^{n}-1$ parts
        $[\frac{i}{2^{n}},\frac{i+1}{2^{n}})$ and define the
        following sets:
        \begin{align}
            E_{n}^{C}
            &=\{\omega\in\Omega:f(\omega)\geq{n}\}\\
            E_{n,i}
            &=\{\omega:\frac{i}{2^{n}}\leq{f}(\omega)
                \leq\frac{i+1}{2^{n}}\}\\
            &=f^{-1}\big([\frac{i}{2^{n}},\frac{i+1}{2^{n}})\big)
        \end{align}
        Then, for every fixed $n\in\mathbb{N}$, the sets
        $E_{n,i}$ are pairwise disjoint. Defined $f_{n}$ as
        follows:
        \begin{equation}
            f_{n}(\omega)=
            \begin{cases}
                n,&f(\omega)\geq{n}\\
                \frac{i}{2^{n}},&\frac{i}{2^{n}}
                    \leq{f}(\omega)
                    \leq\frac{i+1}{2^{n}}
            \end{cases}
        \end{equation}
        Then, using the sets $E_{n,i}$ and $E_{n}^{C}$, we
        can rewrite $f_{n}$ as follows:
        \begin{equation}
            f_{n}(\omega)=
            n\chi_{E_{n}^{C}}(\omega)+
            \sum_{i=0}^{n2^{n}-1}
                \frac{i}{2^{n}}\chi_{E_{n,i}}(\omega)
        \end{equation}
        We now have that $f_{n}$ is monotonically increasing
        and tends to $f$. For is $f(\omega)=\infty$, then:
        \begin{equation}
            w\in\cap_{n=1}^{\infty}E_{n}^{C}
            \Rightarrow
            f_{n}(\omega)=n\rightarrow\infty
        \end{equation}
        If $f(\omega)\in\mathbb{R}$, then there is an
        $N\in\mathbb{N}$ such that $f(\omega)<N$. But then, for
        all $n>N$, $f(\omega)<n$ and thus there is an
        $i\in\mathbb{Z}_{n2^{n}-1}$ such that:
        \begin{equation}
            \frac{i}{2^{n}}\leq{f}(\omega)\leq\frac{i+1}{2^{n}}
        \end{equation}
        But $f_{n}(\omega)=\frac{i}{2^{n}}$ and thus:
        \begin{equation}
            0\leq{f}(\omega)-f_{n}(\omega)\leq\frac{1}{2^{n}}
        \end{equation}
        And therefore $f_{n}\rightarrow{f}$. Finally,
        $f_{n}$ is monotonically increasing. Now let's see what
        we can add to this if we know that $f$ is measurable.
        Since $f$ is measurable, the pre-image
        $f^{-1}([n,\infty))\in\mathcal{A}$, since
        $[n,\infty)$ is a Borel set for all $n\in\mathbb{N}$.
        Moreover, for all $n$ and $i$, $E_{n,i}\in\mathcal{A}$.
        Then all of the indicator functions $\chi_{E_{n,i}}$ are
        measurable, and thus $f_{n}$ is measurable for all
        $n$. However, the support of the $f_{n}$ may not be
        finite. Simply take $f(\omega)=1$ for all $\omega$, and
        let $\Omega=\mathbb{R}$. If the $\mu(\Omega)<\infty$,
        then $\mu(\mathrm{supp}(f_{n}))<\infty$. This case is particularly
        important when studying probability theory.
        \begin{ldefinition}{$\sigma\textrm{-Finite}$}
            A $\sigma\textrm{-Finite}$ measure on a
            $\sigma\textrm{-Algebra}$ $\mathcal{A}$ of a set
            $\Omega$ is a measure $\mu$ such that there is a
            sequence of sets $\Omega_{n}$ such that
            $\Omega_{n}\subseteq\Omega_{n+1}$,
            $\Omega=\cup_{n=1}^{\infty}\Omega_{n}$, and for all
            $n\in\mathbb{N}$, $\mu(\Omega_{n})<\infty$.
        \end{ldefinition}
        \begin{lexample}{}{Lebesgue_Stieljes}
            Let $\Omega=\mathbb{R}$ and consider the Borel
            $\sigma\textrm{-Algebra}$ $\mathcal{B}$ on
            $\mathbb{R}$. Then the standard Lebesgue-Measure
            is $\sigma\textrm{-finite}$ since we can write:
            \begin{equation}
                \mathbb{R}=\cup_{n=1}^{\infty}[-n,n]
            \end{equation}
            And $\mu([-n,n])=2n$, which is finite.
        \end{lexample}
        Define $\tilde{f}_{n}$ as follows:
        \begin{equation}
            f_{n}(\omega)
            =f_{n}(\omega)\cdot\chi_{\Omega_{n}}(\omega)
        \end{equation}
        Then we have that $\tilde{f}_{n}$ is simple, measurable,
        takes on finitely many values, and the measure of it's
        support is finite. Thus we have that if
        $(\Omega,\mathcal{A},\mu)$ is a measure space and if
        $\mu$ is $\sigma\textrm{-Finite}$, then for any
        non-negative measurable function
        $f:\Omega\rightarrow\mathbb{R}$, the integral of $f$ is
        well defined. We write:
        \begin{equation}
            \int_{\Omega}f\diff{\mu}=
            \underset{n\rightarrow\infty}{\lim}
            \int_{\Omega}f_{n}\diff{\mu}
        \end{equation}
    \subsection{Properties of the Integral
                of Non-Negative Functions}
    \begin{theorem}[Homogeneity of the Integral]
        If $f$ is a non-negative measurable function, and if
        $c>0$, then:
        \begin{equation}
            \int_{\Omega}(cf)\diff{\mu}=
            c\int_{\Omega}f\diff{\mu}
        \end{equation}
    \end{theorem}
    \begin{proof}
        For let $f_{n}$ be a sequence of simple functions such
        that $f_{n}\rightarrow{f}$ and $f_{n}$ is monotonically
        increasing. Then:
        \begin{equation}
            \int_{\Omega}(cf)\diff{\mu}
            =\underset{n\rightarrow\infty}{\lim}
            \int_{\Omega}(cf_{n})\diff{\mu}
            =c\underset{n\rightarrow\infty}{\lim}
            \int_{\Omega}f_{n}\diff{\mu}
            =c\int_{\Omega}f\diff{\mu}
        \end{equation}
    \end{proof}
    \begin{theorem}[Additivity of the Integral]
        If $f$ and $g$ are non-negative and measurable,
        then:
        \begin{equation}
            \int_{\Omega}(f+g)\diff{\mu}
            =\int_{\Omega}f\diff{\mu}
            +\int_{\Omega}g\diff{\mu}
        \end{equation}
    \end{theorem}
    \begin{proof}
        For let $f_{n}$ and $g_{n}$ be simple functions such
        that $f_{n}\rightarrow{f}$, $g_{n}\rightarrow{g}$, and
        such that $f_{n}$ and $g_{n}$ are monotonically
        increasing. Then:
        \begin{align}
            \int_{\Omega}(f+g)\diff{\mu}
            &=\underset{n\rightarrow\infty}{\lim}
            \int_{\Omega}(f_{n}+g_{n})\diff{\mu}\\
            &=\underset{n\rightarrow\infty}{\lim}
            \int_{\Omega}f_{n}\diff{\mu}+
            \underset{n\rightarrow\infty}{\lim}
            \int_{\Omega}g_{n}\diff{\mu}\\
            &=\int_{\Omega}f\diff{\mu}+\int_{\Omega}g\diff{\mu}
        \end{align}
    \end{proof}
    \begin{theorem}
        If $f$ is non-negative and measurable, and if
        $E_{1},E_{2}$ are disjoint sets, then:
        \begin{equation}
            \int_{E_{1}\cup{E}_{2}}f\diff{\mu}
            =\int_{E_{1}}f\diff{\mu}+\int_{E_{2}}f\diff{\mu}
        \end{equation}
    \end{theorem}
    \begin{theorem}
        If $f$ is a non-negative measurable function, then:
        \begin{equation}
            \int_{\Omega}f\diff{\mu}\geq{0}
        \end{equation}
    \end{theorem}
    \begin{theorem}
        If $f$ is a non-negative measurable function, then:
        \begin{equation}
            \int_{\Omega}f\diff{\mu}=0
            \Longleftrightarrow{f=0}
            \quad\mu\textrm{-almost everywhere}
        \end{equation}
    \end{theorem}
    \begin{ldefinition}{Summable Functions}
        A non-negative summable function is a non-negative
        and measurable function from
        a measure space $(\Omega,\mathcal{A},\mu)$ where
        $\mu$ is $\sigma\textrm{-Finite}$ to $\mathbb{R}$
        such that:
        \begin{equation}
            \int_{\Omega}f\diff{\mu}<\infty
        \end{equation}
    \end{ldefinition}
    \begin{ltheorem}{Chebyshev's Inequality}
        If $f$ is a non-negative measurable function, then for
        all $a\in\mathbb{R}^{+}$:
        \begin{equation}
            \mu\Big(\{\omega:f(\omega)\geq{a}\}\Big)
            <\frac{1}{a}\int_{\Omega}f\diff{\mu}
        \end{equation}
    \end{ltheorem}
    \begin{proof}
        For define the following:
        \begin{align}
            E_{1}&=\{\omega:f(\omega)\geq{a}\}\\
            E_{2}&=\{\omega:f(\omega)<a\}
        \end{align}
        Then $E_{1}$ and $E_{2}$ are disjoint, and therefore:
        \begin{equation}
            \int_{\Omega}f\diff{\mu}=
            \int_{E_{1}}f\diff{\mu}+
            \int_{E_{2}}f\diff{\mu}
            \geq\int_{E_{1}}f\diff{\mu}
            \geq\int_{\Omega}a\diff{\mu}
            =a\mu(E_{1})
        \end{equation}
        Dividing by $a$ completes the proof.
    \end{proof}
    \begin{theorem}
        If $f$ is a non-negative summable function, then
        for all $a\in\mathbb{R}^{+}$:
        \begin{equation}
            \underset{a\rightarrow\infty}{\lim}
            \mu\Big(\{\omega:f(\omega)\geq{a}\}\Big)=0
        \end{equation}
    \end{theorem}
    \begin{ltheorem}{Monotone Convergence Theorem}
        If $f$ is a non-negative measurable function and if
        $f_{n}$ is a sequence of non-negative measurable
        functions that are monotonically increasing and such
        that $f_{n}\rightarrow{f}$, then:
        \begin{equation}
            \underset{n\rightarrow\infty}{\lim}
            \int_{\Omega}f_{n}\diff{\mu}
            =\int_{\Omega}f\diff{\mu}
        \end{equation}
    \end{ltheorem}
    \begin{proof}
        For all $n\in\mathbb{N}$, there is a function
        $g_{n,k}$ such that $g_{n,k}$ is simple and:
        \begin{equation}
            \int_{\Omega}f_{n}\diff{\mu}=
            \underset{k\rightarrow\infty}{\lim}
            \int_{\Omega}g_{n,k}\diff{\mu}
        \end{equation}
        Define $F_{n}$ as follows:
        \begin{equation}
            F_{n}(\omega)=
            \max\{g_{j,n}(\omega):
                \omega\in\Omega,0\leq{j}\leq{n}\}
        \end{equation}
        Then, for all $n\in\mathbb{N}$, $F_{n}$ is simple.
        For it is the maximum of finitely many measurable
        functions, and is therefore measurable. Moreover:
        \begin{equation}
            \mathrm{supp}(F_{n})\subseteq
            \bigcup_{k=1}^{n}\mathrm{supp}(f_{k,n})
        \end{equation}
        And finally, $F_{n}$ is monotonically increasing from
        it's definition. Now we must show that
        $F_{n}\rightarrow{f}$. For:
        \begin{equation}
            g_{k,n}\leq{F}_{k}\leq{f}_{k}
        \end{equation}
        Since $g_{n,k}$ increases monotonically to $f_{n}$.
        Taking the limit as $k\rightarrow\infty$, we obtain:
        \begin{equation}
            f_{n}\leq\underset{k\rightarrow\infty}{\lim}F_{k}
            \leq{f}
        \end{equation}
        Then taking the limit on $n$, we see that
        $F_{n}\rightarrow{f}$. Integrating this inequality, we
        get:
        \begin{equation}
            \int_{\Omega}g_{k,n}\diff{\mu}
            \leq\int_{\Omega}F_{k}\diff{\mu}
            \leq\int_{\Omega}f\diff{\mu}
        \end{equation}
        Taking the limit as $k\rightarrow\infty$, we get:
        \begin{equation}
            \underset{k\rightarrow\infty}{\lim}
            \int_{\Omega}g_{k,n}\diff{\mu}
            \leq\int_{\Omega}f\diff{\mu}
            \leq\underset{k\rightarrow\infty}{\lim}
            \int_{\Omega}f_{k}\diff{\mu}
        \end{equation}
        Finally, taking the limit on $n$, we get:
        \begin{equation}
            \underset{n\rightarrow\infty}{\lim}
            \int_{\Omega}f_{n}\diff{\mu}
            \leq\int_{\Omega}f\diff{\mu}
            \leq\underset{k\rightarrow\infty}{\lim}
            \int_{\Omega}f_{k}\diff{\mu}
        \end{equation}
        This completes the proof.
    \end{proof}