\documentclass[crop=false,class=article,oneside]{standalone}
%----------------------------Preamble-------------------------------%
\input{../../../../preamble.tex}
%--------------------------Main Document----------------------------%
\begin{document}
    \ifx\ifphysicscourseselectromagnetismI\undefined
        \section*{Miscellaneous Materials}
        \setcounter{section}{1}
    \fi
    \subsection{Mathematica Seminar}
        Wolfram Alpha uses the same technologies as siri,
        little fun fact. Mathematica can use wolfram alpha.
        This allows for standard english input that can be
        translated into the wolfram languages.
        Non-mathematical inputs can also be used, such as
        'Current stock price of Google.'
        Mathematica notebook has a classroom assistant
        that allows for easy input of mathematical
        expressions. There is also extensive documentation
        in the Help drop menu. There are three rules to
        the Wolfram language:
        \begin{enumerate}
            \item Functions in Mathematica are capitalized.
            \item Use [] around function arguments.
            \item Use \{\} to denote lists and ranges.
        \end{enumerate}
        Manipulate is useful for making models interactive:
        Manipulate[Plot[Sin[yx],\{x,0,2$\pi$\}],\{y,0,2\}]
        Other examples such as Pascal's triangle are also
        possible. Image processing is also possible within
        the manipulate function. Manipulates can be nested
        inside of each other to create large and complex
        models. The wolfram demonstration project has 11,000
        premade models for demonstration. Wolframalpha can
        be used to teach math. C and Python can be run
        from inside of Mathematica.
\end{document}