\documentclass[crop=false,class=article,oneside]{standalone}
%----------------------------Preamble-------------------------------%
\input{../../../../preamble.tex}
%--------------------------Main Document----------------------------%
\begin{document}
    \ifx\ifmathcoursesalgebraicgeometry\undefined
        \section*{Algebraic Geometry}
        \setcounter{section}{1}
    \fi
    \subsection{\'{E}tale Cohomology}
        \subsubsection{Review of Schemes}
            \begin{remark}
                Limitations of Affine Varieties:
                \begin{enumerate}
                    \item One would like to construct spaces
                          by gluing together simpler pieces,
                          like in geometry and topology.
                    \item Difficult over non-algebraically
                          closed fields.
                    \item Keeping track of multiplicities.
                \end{enumerate}
            \end{remark}
            Grothendieck's Theory of Schemes gives solutions to
            these problems. Should $x^{2}+y^{2}=-1$ and
            $x^{2}+y^{2}=3$ be regarded as the same over
            $\mathbb{A}_{\mathbb{R}}^{2}$? They both have no
            solution. The answer is no. An isomorphism should
            be given by an invertible transformation. In general,
            the affine variety $X\subset\mathbb{A}_{R}^n$ is
            completely determined by the coordinate ring
            $S=\mathcal{O}(X)%
              =R[x_{1},\hdots,x_{n}]/(f_{1},\hdots,f_{N})$.
            Given a compact Hausdorff space $X$, let $C(X)$
            denote the set of continous complex valued functions.
            This is a commutative ring with identity. With the
            supremum norm, it becomes a unital $C^{*}-$algebra.
            \begin{theorem}
                The map $X\rightarrow\max\{C(X)\}$
                is a homeomorphism.
            \end{theorem}
            Given a continuous map of spaces $f:X\rightarrow Y$,
            we get a homomorphism $C(Y)\rightarrow C(X)$ given
            by $g\mapsto{g}\circ f$. Thus $C(X)$ can be
            regarded as a contravariant functor. 
            \begin{theorem}[Gelfand]
                The functor $X\mapsto C(X)$ induces an
                equivalence between the category of compact
                Hausdorff spaces and the opposite category of
                commutative unital $C^{*}-$algebras.
            \end{theorem}
            \begin{definition}
                The spectrum of $R$, denoted $\Spec(R)$,
                is the set of prime ideals of $R$.
            \end{definition}
            \begin{theorem}
                The Zariski topology on $\Spec(R)$
                contains open sets
                $D(f)=\{p\in\Spec(R):f\notin{p}\}$
            \end{theorem}
            A function $f:\mathbb{R}^{n}\rightarrow\mathbb{R}$
            is $C^{\infty}$ if and only if its restriction to
            the neighborhood of every point is $C^{\infty}$.
            That is, $f\in{C}^{\infty}(X)$ if and only if
            for any open cover
            $\{U_{i}\},f\big|_{U_{i}}\in{C}^{\infty}(U_i)$.
            \begin{definition}
                If $X$ is a topological space, a presheaf
                of sets $\mathcal{F}$ is a collection of
                sets $\mathcal{F}(U)$ for each open set
                $U\subset X$ together with maps
                $\rho_{UV}:\mathcal{F}(U)\rightarrow \mathcal{F}(V)$
                for each pair $U\subset V$ such that $\rho_{UU}=id$
                and $\rho_{WV}\circ\rho_{VU}=\rho_{WU}$
                whenever $U\subset{V}\subset{W}$.
            \end{definition}
            \begin{definition}
                A sheaf is a presheaf such that for any open
                cover $\{U_i\}$ of an open $U\subset{X}$ and
                section $f_{i}\in\mathcal{F}(U_{i})$ such that
                $F_{i}\big|_{U_{i}\cap I_{j}}%
                 =f_{j}\big|_{U_{i}\cap U_{j}}$,
                there is a unique $f\in\mathcal{F}(U)$
                such that $f_{i}=f\big|_{U_{i}}$.
            \end{definition}
            \begin{definition}
                A ringed space is a pair $(X,\mathcal{O}_{X})$,
                where $X$ is a topological space and
                $\mathcal{O}_{X}$ is a sheaf of commutative rings.
            \end{definition}
            The collection of presheaves of a topological space
            form a category, denoted $Sh(X)$. 
            \begin{definition}
                A scheme is a ringed space $(X,\mathcal{O}_X)$
                which is locally an affine space.
            \end{definition}
            \begin{theorem}
                A property of commutative rings extends
                to schemes if it is local.
            \end{theorem}
        \subsubsection{Differential Calculus of Schemes}
            \begin{definition}
                The tangent space of an affine variety
                $X=V(f_{1},\hdots,f_{N})\subset\mathbb{A}_{k}^{n}$,
                denoted $T_{X,p}$, is the set of points
                $v\in{k}^{n}$ such that
                $\sum\frac{\partial{f_{j}}}%
                          {\partial{x_{i}}}p)v_{i})%
                 =0$
            \end{definition}
            \begin{definition}
                A domain
                $R=k[x_{1},\hdots,x_{n}]/(f_{1},\hdots,f_{N})$
                or $\Spec(R)$ is smooth if and only if the rank of
                $\big(\frac{\partial{f_{j}}}{\partial{x_{i}}}(p)\big)$
                is $n=\dim(R)$ for all $p\in\max(R)$. 
            \end{definition}
            \begin{definition}
                An \'{e}tale $R$ algebra is smooth of relative
                dimension 0, where
                $\det(\frac{\partial{f_{i}}}{\partial{x_{j}}})$
                is a unit in $S$.
            \end{definition}
            \begin{theorem}
                If $k$ is a field, then an algebra over $k$
                is \'{e}tale if and only if it is a finite Cartesian
                product of separable field extensions. 
            \end{theorem}
            \begin{theorem}
                The tensor product of two
                \'{e}tale algebras is \'{e}tale.
            \end{theorem}
            \begin{theorem}
                If $S$ is \'{e}tale over $R$ and $T$ is
                \'{e}tale over $S$, then $T$ is \'{e}tale over $R$.
            \end{theorem}
            \begin{definition}
                If $R$ is a commutative ring and $S$ is an
                $R$ algebra and $M$ is an $S$ module,
                then an $R$ linear derivation from $S$ to $M$ is
                a map $\delta:S\rightarrow M$ such that
                $\delta(s_{1}+s_{2})=\delta(s_{1})+\delta(s_{2})$,
                $\delta(s_{1}s_{2})%
                 =s_{1}\delta(s_{2})+s_{2}\delta(s_{1})$,
                 and $\delta(r)=0$ for all $r\in{R}$.
            \end{definition}
            \begin{theorem}
                There exists an $S$ module $\Omega_{S/R}$
                with a universal $R$ linear derivation
                $d:S\rightarrow \Omega_{S/R}$.
            \end{theorem}
            \begin{theorem}
                If $M$ is a finitely generated module over a
                Noetherian ring $R$, then these are equivalent:
                \begin{enumerate}
                    \begin{multicols}{3}
                        \item $M$ is locally free.
                        \item $\forall_{p\in\Spec(R)},R_{p}\otimes M$
                              is free.
                        \item $M$ is projective.
                    \end{multicols}
                \end{enumerate}
            \end{theorem}
            \begin{definition}
                If $M$ is an $S-$module, then $M$ is called
                flat if $M\otimes{i}$ is injective for any $i$.
            \end{definition}
            \begin{theorem}
                If $S$ is an $R$ algebra and $M$ is an $S$ module,
                $f\in S$ is an element such that multiplication
                by $f$ is injective on $M\otimes k(m)$ for all
                $m\in\max(R)$, and if $M$ is flat over $R$,
                then $M/fM$ is flat over $R$.
            \end{theorem}
            \begin{theorem}
                A smooth algebra is flat.
            \end{theorem}
            \begin{theorem}
                If $R$ is a Noetherian ring, then a homomorphism
                $R\rightarrow S$ is \'{e}tale if and only if:
                \begin{enumerate}
                    \item $S$ is finitely generated as an algebra.
                    \item $S$ is flat as an $R$-module.
                    \item $\Omega_{S/R}=0$.
                \end{enumerate}
            \end{theorem}
            \begin{definition}
                A sheaf on a scheme is quasi-coherent if
                it is with respect to some affine open cover.
            \end{definition}
            \begin{theorem}
                If $f:X\rightarrow Y$ is a morphism, there
                exists a quasi-coherent sheaf $\Omega_{X/Y}$
                such that
                $\Omega_{X/Y}\big|_{\Spec(S_{ij})}=\Omega_{S_{ij}/R_i}$
                for open affine covers $\Spec(R_i)=U_{i}$.
            \end{theorem}
        \subsubsection{The Fundamental \'{E}tale Group}
            \begin{definition}
                A topological group is a topological space
                $(X,\tau)$ with a group structure $(X,*)$ such
                that $*:X\times X\rightarrow X$ is a continuous
                function with respect to the product topology.
            \end{definition}
            \begin{theorem}
                A topological space is profinite if and only
                if it is compact Hausdorff and totally disconnected.
            \end{theorem}
            \begin{definition}
                The topological fundamental group of a
                topological space $X$, denoted $\pi_1(X)$,
                is the group of homotopy classes of loops in $X$
                with a given base point.
            \end{definition}
            \begin{theorem}
                Any \'{e}tale morphism $Y\rightarrow X$ is
                a finite to one covering space of $X$ with
                the usual topology.
            \end{theorem}
            \begin{theorem}[Grothendieck's Theorem]
                If $X$ is a scheme of finite type of
                $\mathbb{C}$, then $\pi_{1}^{et}(X)$ is the
                profinite completion of $\pi_{1}{X}$.
            \end{theorem}
        \subsubsection{\'{E}tale Topology}
            \begin{remark}
                Given a topological space $(X,\tau)$,
                the topology $\tau$
                (That is, the collection of open sets) forms a
                partially ordered set with respect to set
                inclusion. There also exists a notion of
                open covering $U=\cup U_{i}$.
            \end{remark}
            \begin{definition}
                A Groethendieck Topology on a category $C$ with
                fibre products is a collection of families of
                morphisms $U_{i}\rightarrow U$ such that:
                \begin{enumerate}
                    \item The family consisting of a single
                          isomorphism $\{U\sim{U}\}$ is a covering.
                    \item If $\{U_{i}\rightarrow{U}\}$ and
                          $\{V_{ij}\rightarrow{U_{i}}\}$ are coverings,
                          then so is the composition
                          $\{V_{ij}\rightarrow{U}\}$.
                \end{enumerate}
            \end{definition}
            \begin{definition}
                A site is a category with a Grothendieck Topology.
            \end{definition}
\end{document}