\documentclass[crop=false,class=article,oneside]{standalone}
%----------------------------Preamble-------------------------------%
\input{../../../../preamble.tex}
%--------------------------Main Document----------------------------%
\begin{document}
    \ifx\ifmathcoursesalgebraicgeometry\undefined
        \section*{Algebraic Geometry}
        \setcounter{section}{1}
    \fi
    \subsection{Notes on Varieties}
        \subsubsection{Affine Varieties}
            Let $k$ denote an algebraically closed field.
            $\textbf{A}_{k}^n$ is the affine $k-$space in
            $n$ dimensions. An element $a=(a_1,\hdots, a_n)$
            is called a point, and $a_i$ is called a coordinate.
            \begin{definition}
                The zero set of a set of polynomials
                $T=\{f_{1},\hdots,f_{s}\}$ is the set
                $Z(T)%
                 =\{p\in\textbf{A}_{k}^{n}|f_{i}(p)=0,%
                    i=1,\hdots,s\}$.
            \end{definition}
            \begin{notation}
                The set of polynomials in $n$ variables
                over $\textbf{A}_{k}^{n}$ is denoted $A$.
            \end{notation}
            \begin{definition}
                A subset $Y\subset\textbf{A}_{k}^{n}$ is an
                algebraic set if there exists a subset
                $T\subset{A}$ such that $Z(T)=Y$.
            \end{definition}
            \begin{theorem}
                The union of two algebraic
                sets is algebraic.
            \end{theorem}
            \begin{theorem}
                The intersection of two algebraic
                sets is algebraic.
            \end{theorem}
            \begin{definition}
                The Zariski topology $\mathcal{Z}$ on
                $\textbf{A}_{k}^{n}$ is the set of compliments
                of algebraic sets. That is,
                algebraic sets are closed.
            \end{definition}
            \begin{definition}
                A non-empty subset $Y$ of a topological space
                $X$ is irreducible if it cannot be expressed
                as the union $Y={Y_{1}}\cup{Y_{2}}$ of
                two proper subsets, each on of which is
                closed in $Y$.
            \end{definition}
            \begin{definition}
                An affine algebraic variety is an irreducible
                subset of $\textbf{A}_{k}^{n}$ with respect
                to the induced topology.
            \end{definition}
            \begin{definition}
                An open subset of an affine variety
                is called a quasi-affine variety.
            \end{definition}
            \begin{notation}
                If $Y\subset\textbf{A}_{k}^{n}$,
                $I(Y)=\{f\in A:\forall_{p\in Y},f(p)=0\}$.
            \end{notation}
            \begin{theorem}
                \
                \begin{enumerate}
                    \item If $T_1\subset T_2$,
                          the $Z(T_2)\subset{Z}(T_1)$
                    \item If
                          $Y_{1}\subset{Y_{2}}\subset%
                          \textbf{A}_{k}^{n}$,
                          then $I(Y_{2})\subset{I}(Y_{1})$
                    \item $I(Y_{1}\cup{Y_{2}})%
                           =I(Y_{1})\cap{I}(Y_{2})$
                    \item If $a\subset A$,
                          then $I(Z(a))=\sqrt{a}$
                          (The radical of $a$)
                    \item If $Y\subset\textbf{A}_{k}^{n}$,
                          then $Z(I(Y))=\overline{Y}$
                          (The closure of $Y$)
                \end{enumerate}
            \end{theorem}
            \begin{theorem}[Hilbert's Nullstellensatz]
                If $k$ is an algebraically closed field,
                $a\subset{A}=k[x_{1},\hdots,x_{n}]$
                is an ideal, and if $f\in{A}$ is a polynomial
                which vanishes on $Z(a)$, then there is an
                $r\in\mathbb{N}$ such that $f^{r}\in{a}$.
            \end{theorem}
            \begin{definition}
                The affine coordinate ring of an affine
                algebraic set $Y\subset\textbf{A}_{k}^{n}$
                is $A/I(Y)$.
            \end{definition}
            \begin{definition}
                A topological space $X$ is called Noetherian
                if it satisfies the descending chain condition
                for closed subsets.
            \end{definition}
            \begin{theorem}
                A Noetherian Topological Space is compact.
            \end{theorem}
            \begin{definition}
                If $A$ is a ring, then height of a prime
                ideal $p$ is the supremum of all integers $n$
                such that there is a chain
                $p_{0}\subset\hdots\subset{p_{n}}=p$
                of distinct prime ideals.
            \end{definition}
            \begin{definition}
                The Krull dimension of a ring $A$ is the
                supremum of the height of all ideals.
            \end{definition}
            \begin{theorem}[Krull's Hauptidealsatz]
                If $A$ is a Noetherian Ring, and $f\in A$
                has neither a zero divisor nor a unit,
                then every minimal prime ideal $p$
                containing $f$ has height $1$.
            \end{theorem}
            \begin{theorem}
                The dimension of $\textbf{A}_{k}^{n}$ is $n$.
            \end{theorem}
        \subsubsection{Projective Varieties}
            \begin{definition}
                A subset $Y$ of $P^n$ is an algebraic
                set if there is a set $T$ of homogeneous
                elements of $S$ such that $Y=Z(T)$.
            \end{definition}
            \begin{definition}
                The Zariski Topology on $P^n$ is defined
                as the complements of algebraic sets.
                That is, algebraic sets are closed.
            \end{definition}
            \begin{definition}
                A projective algebraic variety is an
                irreducible algebraic set in $P^{n}$.
            \end{definition}
        \subsubsection{More Notes on Projective Varieties}
            \begin{definition}
                The projective $n-$space over $\mathbb{A}$,
                denoted $\mathbb{P}^{n}$, is the set of all
                one-dimensional linear subspaces of the vector
                space $\mathbb{A}^{n+1}$.
            \end{definition}
            \begin{remark}
                Equivalently, it is the set of all lines
                in $\mathbb{A}^{n+1}$ through the origin.
            \end{remark}
            \begin{definition}
                The projective $n$ space $\mathbb{P}^{n}$ over $k$
                is the set of all equivalence classes
                $\mathbb{A}^{n+1}/\{0\}$, where
                $(a_{1},\hdots,a_{n})\sim(b_{1},\hdots,b_{n})$
                if and only if there is a
                $\lambda\in\mathbb{A}\setminus\{0\}$
                such that $b_{i}=\lambda{a_{i}}$.
            \end{definition}
            \begin{remark}
                Elements of $\mathbb{P}^{n}$ are called points.
            \end{remark}
            \begin{definition}
                A homogenous polynomial of degree $d$
                is a polynomial $f$ such that
                $f(\lambda a_1,\hdots,\lambda a_n)%
                 =\lambda^d f(a_1,\hdots, a_n)$.
            \end{definition}
            \begin{theorem}
                If $I\subset k[x_1,\hdots ,x_n]$ is an ideal,
                then the following are equivalent:
                \begin{enumerate}
                    \item $I$ can be generated by
                          homogeneous polynomials.
                    \item For every $f\in I$, the degree
                          $d$ part of $f$ in contained in $I$
                \end{enumerate}
            \end{theorem}
            \begin{definition}
                If $I\subset k[x_1,\hdots ,x_n]$ is a
                homogeneous ideal, then
                $\mathbf{V}(I)%
                 =\{(a_1:\hdots:a_{n})\in\mathbb{P}^{n}:%
                 f(a_{1},\hdots,a_{n})=0,f\in I\}$.
            \end{definition}
            \begin{definition}
                An algebraic subset of $\mathbb{P}^{n}$ is a
                set of the form $\mathbf{V}(I)$.
                These are called projective algebraic sets.
            \end{definition}
            \begin{theorem}
                Every projective algebraic set can be
                written as the zero set of finitely many
                homogeneous polynomials of the same degree.
            \end{theorem}
            \begin{definition}
                The projective close of and algebraic set
                $X\subset\mathbb{A}^n$ is the Zariski closure
                in $\mathbb{P}^{n}$ under the mapping
                $\mathbb{A}^{n}\rightarrow\mathbb{P}^n$
                by $(x_{1},\hdots,x_{n})\mapsto(1:x_1,\hdots, x_n)$.
            \end{definition}
            \begin{theorem}
                If $f$ is the sum of forms $f=\sum_{d}f^{(d)}$,
                if $P\in \mathbb{P}^n$ and $f(x_1,\hdots, x_n)=0$
                for every choice of homogeneous coordinates,
                then for each $d$, $f^{(d)}(x_1,\hdots, x_n)=0$.
            \end{theorem}
            \begin{definition}
                If $F\in \mathbb{A}[x_1,\hdots, x_n]$ is homogeneous
                of degree $d$, then its de-homogenization is the
                polynomial $f(x_1,\hdots, x_n)=F(1,x_1,\hdots, x_n)$.
            \end{definition}
            \begin{theorem}
                Let $X\subset \mathbb{A}^n$ be an affine
                algebraic set, $\overline{X}$ the projective closure. Then
                $\mathbb{I}(\overline{X})\subset\mathbb{A}[x_1,\hdots,x_n]$
                is generated by the homogenization of all
                elements of $\mathbb{I}(X)$.
            \end{theorem}
            \begin{theorem}
                An algebraic set $X$ is irreducible
                if and only if the ideal $\mathbb{I}(X)$ is prime.
            \end{theorem}
            \begin{definition}
                An affine algebraic set $X\subset \mathbb{A}^{n+1}$
                is called a cone if it is not empty, and if for all
                $\lambda\in{k}$,
                $(x_1,\hdots, x_n)%
                 \in{X}\Rightarrow(\lambda{x_{1}},\hdots,\lambda{x_{n}})%
                 \in{X}$.
            \end{definition}
            \begin{theorem}[The Projective Nullstellensatz]
                \
                \begin{enumerate}
                    \item If $X_1\subset X_2$ are algebraic
                          set in $\mathbb{P}^{n}$,
                          then $I(X_{2})\subset{I}(X_{1})$.
                    \item For any algebraic set
                          $X\subset\mathbb{P}^{n}$, we have
                          $\mathbf{V}(I(X))=X$.
                    \item For any homogeneous ideal
                          $I\subset{k}[x_{1},\hdots,x_{n}]$ such
                          that $\mathbf{V}(I)\ne\emptyset$,
                          we have
                          $\mathbb{I}(\mathbf{V}(I))=\sqrt{I}$.
                \end{enumerate}
            \end{theorem}
\end{document}