\section{Legendrian and Transverse Knots and Links}
    A knot is a smooth embedding of the circle $\mathbb{S}^{1}$ into
    $\mathbb{R}^{3}$. A link is a smooth embedding of $N\in\mathbb{N}$
    disjoint circles in $\mathbb{R}^{3}$. We may impose
    extra structure by considering the standard \textit{contact structure}
    of $\mathbb{R}^{3}$. This is an assignment
    of a plane to every point in $\mathbb{R}^{3}$ such that there is no
    surface $M\subset\mathbb{R}^{3}$ (even infinitesimally) where for every
    $p\in{M}$ the tangent
    plane $T_{p}M$ is given by the plane of the contact structure. In
    $\mathbb{R}^{3}$ this is described by the one-form
    $\textrm{d}z-y\,\textrm{d}x$, the plane at $(x,y,z)$ being spanned by
    the vectors $\partial_{x}+y\partial_{z}$ and $\partial_{y}$. The
    hyperplane distribution is shown in Fig.~\ref{fig:darboux_form_001}.
    While there are no everywhere tangent surfaces, it is possible for a
    curve to be everywhere tangent to this distribution of planes.
    A \textit{Legendrian link} is a link that is everywhere tangent to
    the contact structure. A gentle introduction can be found
    in \cite{JoshuaMSabloffWhatIsLegendrianKnot}.
    \par\hfill\par
    Two Legendrian links are considered to be Legendrian equivalent if
    there is an isotopy $H:L\times[0,1]\rightarrow\mathbb{R}^{3}$ between
    them, $L=\sqcup_{k=0}^{N-1}\mathbb{S}^{1}$, such that for all
    $t\in[0,1]$ the link $H_{t}$ is Legendrian. It is possible for two links
    to be topologically equivalent but not Legendrian equivalent. In the other
    direction, any link can be made Legendrian by an appropriate isotopy
    (See the introduction of \cite{VeraVertessiTransNonSimpleKnots}). The
    two classical invariants of Legendrian links are the Thurston-Bennequin
    and rotation numbers \cite{Ding2006LEGENDRIANHA}.
    A link type is said to be \textit{Legendrian simple} if
    any two Legendrian embeddings of it with the same Thurston-Bennequin
    and rotation numbers are Legendrian equivalent. That is, the classical
    invariants uniquely classify all Legendrian representations of the knot.
    Certain knot types are known to be Legendrian simple such as the unknot
    \cite{EliashbergFraserClassificationTopTrivialLegKnots}, torus knots,
    and the figure eight knot \cite{EtnyreHondaContactTopologyI}.
    Not every knot is Legendrian simple, the $m_{3}$ twist knot (also
    known as the $5_{2}$ knot) being an example discovered by Chekanov
    \cite{ChekanovDifAlgOfLegLinks}. More examples can be found in the
    Legendrian knot atlas \cite{LegendrianKnotAtlas}.
    \par\hfill\par
    Transverse links are links that are everywhere transverse to the
    contact structure. That is, at every point $p$ on the link the velocity
    vector and the contact hyperplane at $p$ span $\mathbb{R}^{3}$. Any Legendrian
    link can be made transverse by a small perturbation in the direction
    normal to the given plane in the contact structure.
    Two transverse links are transversely equivalent if there is an
    isotopy $H:L\times[0,1]\rightarrow\mathbb{R}^{3}$ such that $H_{t}$ is a
    transverse link for all $t\in[0,1]$. The Bennequin number of a
    transverse knot is defined by the \textit{algebraic crossing number}
    $e(K)$ and the \textit{braid index} $n(K)$. It is:
    \begin{equation}
        \beta(K)=e(K)-n(K)
    \end{equation}
    It is not an invariant of topological knots, but is an invariant under
    transverse equivalence. This is essentially the self-linking number of
    the corresponding topological knot with respect to the natural framing
    coming from the trivialization of the contact structure.
    Similar to Legendrian simple, we define a knot
    (or link) type to be transversely simple if all of it's transverse
    representations are uniquely determined by their Bennequin number
    (See \cite{BirmanWrinkleTransversallySimpleKnots}) and by whether its
    velocity vectors point into the half space where the contact structure
    is positive or not. A paper by Etynre, Ng, and Vertesi
    \cite{EtnyreEtAlLegendrianAndTransverseTwistKnots}
    classifies when twist knots are transversely simple. In
    particular, infinitely many such knots are transversely simple giving
    us a family of knots to test conjectures with. It is also true that
    infinite families of non-Legendrian simple and non-transversally simple
    knots exist. See, for example, the works of Etnyre and Honda
    \cite{EtnyreHondaCabling} and Birman and Menasco
    \cite{BirmanMenasco2006}. More examples can be found in
    \cite{vfoldvari2019legnonsimple}.
    \par\hfill\par
    There are several common ways of representing topological knots, the
    three used in our computations are extended Gauss code, planar diagram
    code (PD code), and Dowker-Thistlewaite code (DT code). Given a knot
    diagram with $N$ crossings, the (unsigned) Gauss code is a string with $2N$
    characters (extended Gauss code is $3N$),
    PD code is a string that is $4N$ long, and DT code is $N$
    characters long. Each has its benefits. Extended Gauss code
    can distinguish mirrors, DT code cannot
    (See \cite{DOWKER198319}). PD code is the easiest to
    reconstruct the knot diagram, and DT code is the shortest. Because of
    this we will present our examples in DT code. To obtain the DT code of
    a knot diagram, place your finger on the knot and \textit{walk} along
    the diagram, labelling the crossings. When you get back to your starting
    point each crossing will have two numbers associated with it. It is
    not difficult to see that each crossing will have exactly one odd number
    and one even number. For each even number, if that number was associated
    with an \textit{over} crossing (that is, your finger ran over the
    crossing as you were labelling it), place a minus sign in front. Write
    out the pairs of integers as $(1,a_{1})$, $(3,a_{2})$, $\dots$,
    $(2n-1,a_{n})$. The DT code is the list $a_{1},a_{2},\dots,a_{n}$.
    See \cite{KatlasDTCode} for several examples.
    \par\hfill\par
    It is possible to go from DT code to unsigned
    Gauss code (i.e. the usual Gauss code, and not the extended Gauss code)
    and back \cite{KhoHoDTCodes}. For certain computations,
    like the Alexander polynomial which
    is mirror insensitive, DT code is easiest since it is the shortest.
    For things like the Jones polynomial and Khovanov homology, invariants
    that distinguish mirrors, extended Gauss code is a must.
    \par\hfill\par
    A note on notation. The tables on the following pages identify knots using their DT
    codes. The \texttt{regina} library \cite{regina} uses a clever trick to efficiently
    express a knots DT code for all knots of up to 26 crossings, and we'll
    adopt this notation for the remainder of the paper. The DT code of an
    $n$ crossing knot is a string of length $n$ of signed even integers up
    to $2n$. Since all entries are even, we can divide by two and obtain
    a string of length $n$ of signed integers up to $n$. So long as $n$ is
    not larger than 26 we can replace integers with letters. We then use
    lower case letters for positive integers, and upper case for negative.
    For example, the trefoil $T(2,\,3)$ becomes:
    \begin{equation}
        4,\,6,\,2
        \Rightarrow
        2,\,3,\,1
        \Rightarrow
        \texttt{bca}
    \end{equation}
    The knot $10_{132}$, which is the 10 crossing knot in
    Tab.~\ref{table:matching_twist_knots} with the same Jones polynomial
    as $T(2,\,5)$, becomes:
    \begin{align}
        8,\,6,\,18,\,2,\,-12,\,-16,\,20,\,-10,\,4,\,14
        &\Rightarrow
        4,\,3,\,9,\,1,\,-6,\,-8,\,10,\,-5,\,2,\,7\\
        &\Rightarrow
        \texttt{dciaFHjEbg}
    \end{align}
\section{Khovanov Homology}
    The Khovanov homology of a link is a powerful, if computationally
    expensive%
    \footnote{%
        The na\"{i}ve algorithm is exponential in the number of
        crossings. Improvements by Bar-Natan \cite{BarNatanFastKhoHo}
        have sped up computations but no polynomial-time algorithm is
        known at the time of this writing.
    },
    invariant first introduced by Mikhail Khovanov
    \cite{Khovanov1999CatJonesPoly} (See also \cite{barnatan2002khovanov}
    for an excellent introduction). It is closely related to the Jones
    polynomial, but able to distinguish many more knots and links. The
    homology groups $KH^{r}(L)$ of a link (or knot) $L$ are the direct sum
    of homogeneous components $KH_{\ell}^{r}(L)$ and the
    \textit{Khovanov Polynomial} (See \cite{KatlasKhoHo}) is given by:
    \begin{equation}
        Kh(L)(q,t)=
        \sum_{r,\ell}t^{r}q^{\ell}\textrm{dim}\big(KH_{\ell}^{r}(L)\big)
    \end{equation}
    The Jones polynomial of $L$ is recovered via:
    \begin{equation}
        J(L)(q)=Kh(L)(q,-1)
    \end{equation}
    Khovanov homology is not a perfect invariant
    \cite{Watson2007KnotsWI}. That is, there are
    distinct knots with the same Khovanov homology, but it is a powerful
    invariant and is capable of detecting certain knot types.
    \begin{theorem}[Kronheimer and Mrowka, 2001]
        If a knot $K$ has the same Khovanov homology as the unknot, then $K$
        is equivalent to the unknot.
    \end{theorem}
    The unknotting problem asks one to determine if a given knot diagram is
    equivalent to the unknot. Khovanov homology is a powerful enough tool
    to accomplish this task. The Khovanov polynomial is a generalization of
    the Jones polynomial and it has been conjectured that if a
    knot has the same Jones polynomial as the unknot, then that knot is
    equivalent to the unknot. At the time of this writing it has not been
    proven, but there is evidence for and against the claim.
    Thistlewaite found links with the same Jones polynomial as the unlink
    \cite{Thistlethwaite2001LINKSWT}, and there is a 3-crossing virtual
    knot that has the same Jones polynomial as the unknot. For the claim,
    all knots of up to 24 crossings are either the unknot, or have a
    Jones polynomial different from the unknot
    \cite{VerificationUnknotJonesConjUpTo24}.
    \begin{theorem}[Baldwin and Sivek, 2022]
        If a knot $K$ has the same Khovanov homology as either of the
        trefoils, then $K$ is equivalent to one of them.
    \end{theorem}
    \begin{theorem}[Baldwin, Dowlin, Levine, Lidman, and Sazdanovic, 2021]
        If a knot $K$ has the same Khovanov homology as the figure-eight
        knot, then $K$ is equivalent to it.
    \end{theorem}
    See \cite{BaldwinSivekKhovanovTrefoils} and
    \cite{BaldwinDowlinKhovanovFigureEight}, respectively.
\section{Conjectures on Khovanov Homology}
    Khovanov homology is capable of detecting the
    unknot, trefoils, and figure-eight knot. The Khovanov homology with
    coefficients in $\mathbb{Z}/2\mathbb{Z}$ is also capable of detecting
    the cinquefoil knot \cite{BaldwinYingSivekCinquefoilKhovanov},
    which is the $T(5,2)$ torus knot. The Jones
    polynomial, on the other hand, is not capable of detecting the
    $T(5,2)$ torus knot since the $10_{132}$ knot yields the same
    polynomial (See Tab.~\ref{table:matching_torus_knots}).
    These are the easiest of the Legendrian simple knots
    leading us to the following.
    \begin{conjecture}
        If a link type $L$ is Legendrian simple, then the Khovanov homology
        of $L$ distinguishes it. That is, if $\tilde{L}$
        is another link with the same Khovanov homology, then $\tilde{L}$ is
        equivalent to $L$.
    \end{conjecture}
    Numerical evidence has been tallied for torus knots
    against all prime knots up to 19 crossings. There are many
    torus knots that have the same Jones polynomial as a non-torus knot
    ($T(2,5)$ matches 10 and 17 crossing knots, $T(2,7)$
    matches a 12 crossing knot, and $T(2,11)$ matches a 14 crossing knot)
    so we cannot generalize the Jones unknot conjecture. Nevertheless, in
    all cases the Khovanov homologies were different
    (see Numerical Results section).
    \par\hfill\par
    The computations were done as follows. There are libraries in Python,
    Sage, and C++ for working with knot polynomials. In particular, we used
    Regina \cite{regina}, SnapPy \cite{SnapPy}, the Sage knot library
    \cite{sage}, and our own ever-growing C library.
    \par\hfill\par
    We first gather the torus knots that could potentially have the same
    Jones polynomial as some other knot based on the bounds of the degree.
    The Jones polynomials of torus knots were computed using the formula
    \cite{jonesfordummyvjones}:
    \begin{equation}
        \label{eqn:jones_poly_torus}%
        J(T(m,n))(q)=q^{(m-1)(n-1)/2}
            \frac{1-q^{m+1}-q^{n+1}+q^{m+n}}{1-q^{2}}
    \end{equation}
    The Kauffman bracket, of which the Jones polynomial is a simple
    normalization \cite{barnatan2002khovanov},
    of a knot $K$ with $N$ crossings has the following formula:
    \begin{equation}
        \langle{K}\rangle=\sum_{n=0}^{2^{N}-1}(-q)^{w(n)}(q+q^{-1})^{c(n)}
    \end{equation}
    where $w(n)$ is the Hamming weight of $n$, the number of 1's in the
    binary representation, and $c(n)$ is the number of disjoint cycles
    that result in the complete smoothing of $K$ corresponding to
    $0\leq{n}\leq{2}^{N}-1$. With this the degree of the bracket polynomial
    is bounded by $3n$ ($w(n)$ is bounded by $n$, and $c(n)$ is bounded
    by $2n$). The degree of the normalization is bounded by $2n$
    \cite{barnatan2002khovanov}, so the
    Jones polynomial of a knot with $n$ crossings has degree at most $5n$.
    \par\hfill\par
    Since we are looking at knots up to $19$ crossings, we collect the
    co-prime pairs $(m,\,n)$ with $1<m<n$ such that the degree
    is less than $5\cdot{19}=95$. Since the Jones polynomial of a mirror
    can be computed by substituting $q\mapsto{q}^{-1}$
    \cite{jonespolyjones}, we need not look at
    negative values. The Khovanov polynomial makes a similar change,
    $(q,\,t)\mapsto(q^{-1},\,t^{-1})$
    \cite{WATSON2017915}.
    \par\hfill\par
    Using any of the aforementioned libraries, the Jones polynomial of all
    prime knots up to 19 crossings were computed and compared against this
    table of torus knot Jones polynomials (Eqn.~\ref{eqn:jones_poly_torus}).
    If a match was found the regina library was used to determine if the
    knots were actually identical. That is, if the knot whose Jones
    polynomial was being compared against the torus knots was indeed a
    torus knot itself. If the knots were distinct, this knot was saved in a
    text file for later examination. At the end of the computation 4
    non-torus knots had the same Jones polynomial as a torus knot
    (See Tab.~\ref{table:matching_torus_knots}).
    Since the Khovanov polynomial contains the Jones polynomial in it
    (recall $J(L)(q)=Kh(L)(q,-1)$) the only possible non-torus knots with
    the same Khovanov homology as a torus knot were these 4.
    \par\hfill\par
    Using the Java library JavaKh\footnote{%
        Thanks must be paid to Nikolay Pultsin who made edits to
        JavaKh-v2 so that it may run on a GNU/Linux machine using
        OpenJDK 17.
    }
    we found that these four knots with the same Jones polynomials as some
    torus knot all had different Khovanov homologies. Thus, we have the
    following claim:
    \begin{theorem}
        If a prime knot $K$ has less than or equal to 19 crossings and has
        the Khovanov homology of a torus knot $T$,
        then $K$ is equivalent to $T$.
    \end{theorem}
    A similar search through the twist knots yielded more results.
    The Jones polynomials of the twist knots are known, with the formula:
    \begin{equation}
        J(m_{n})(q)=
        \begin{cases}
            (1+q^{-2}+q^{-n}+q^{-n-3})/(1+q),&n\textrm{ odd}\\
            (1+q-q^{3-n}+q^{-n})/(1+q),&n\textrm{ even}
        \end{cases}
    \end{equation}
    A search through all prime knots up to 19 crossings against twist knots
    provided many matches for the Jones polynomial
    (See Tab.~\ref{table:matching_twist_knots}), but
    none for Khovanov homology. Infinitely many of the twists knots are
    transversally simple, making them a good candidate to test the following
    conjecture on.
    \begin{conjecture}
        If a link type $L$ is transversally simple, then the Khovanov
        homology of $L$ distinguish it. That is, if $\tilde{L}$
        is another link with the same Khovanov homology, then $\tilde{L}$ is
        equivalent to $L$.
    \end{conjecture}
    A similar search for Knot Floer Homology (KFH), a homology theory
    first introduced by Peter Ozsv\'{a}th and Zolt\'{a}n Szab\'{o}
    \cite{ozsvathszabo2004}, using the Alexander polynomial
    was performed, but a bug was found that caused knots with identical
    Alexander polynomials to give false negatives. This has been corrected,
    and when performing a new search there are several distinct knots
    with the same Knot Floer Homology as a Legendrian simple knot. Steven
    Sivek pointed
    out that the pretzel knots $P(-3,3,2n+1)$ all have the same KFH, meaning
    the $6_{1}$ twist knot matches the KFH of the $9_{46}$ knot in the
    Rolfsen table. This is what first hinted at a bug in our KFH code.
    Matthew Hedden also informed us that the $T(4,3)$ knot and the
    $(2,3)$ cable of the trefoil also have matching KFH.
\section{Torus Knots}
    \begin{table}
        \centering
        \resizebox{\textwidth}{!}{%
            \begin{tabular}{| l | l | l |}
                \hline
                    Torus Knot&
                    Non-Torus Knot&
                    Jones Polynomial\\
                \hline
                    $T(2,\,5)$&
                    \texttt{dciaFHjEbg}&
                    $-q^{14}+q^{12}-q^{10}+q^{8}+q^{4}$\\
                \hline
                    $T(2,\,7)$&
                    \texttt{fJGkHlICEABd}&
                    $-q^{20}+q^{18}-q^{16}+q^{14}-q^{12}+q^{10}+q^{6}$\\
                \hline
                    $T(2,\,11)$&
                    \texttt{gHlImJnKBDFAce}&
                    $-q^{32}+q^{30}-q^{28}+q^{26}-q^{24}+q^{22}-q^{20}+q^{18}-q^{16}+q^{14}+q^{10}$\\
                \hline
                    $T(2,\,5)$&
                    \texttt{iNHlPJqCoKFmdABgE}&
                    $-q^{14}+q^{12}-q^{10}+q^{8}+q^{4}$\\
                \hline
            \end{tabular}%
        }
        \caption{Knots whose Jones polynomial matches that of a Torus Knot}
        \label{table:matching_torus_knots}
    \end{table}
    In Tab.~\ref{table:matching_torus_knots}
    we have found four non-torus knots with the same
    Jones polynomial as some torus knot. In all four cases the Khovanov
    polynomials differ. The tables for these polynomials are given below.
    The coefficient of $q^{\ell}t^{r}$ is given by the corresponding entry.
    Empty equates to zero.
    \par\hfill\par
    The cinquefoil $T(2,\,5)$ has the same Jones polynomial as two
    non-torus knots. As shown below in
    Tabs.~\ref{table:t_2_5_kho}-\ref{table:iNHlPJqCoKFmdABgE_kho}, the
    Khovanov polynomials differ
    (This had already been known, see \cite{KatlasKhoHo}).
    \begin{table}
        \centering
        \begin{tabular}{| c | c | c | c | c | c | c | c |}
            \hline
            $q\symbol{92}t$&$-5$&$-4$&$-3$&$-2$&$-1$&$0$&$\chi$\\
            \hline
            $-15$&1&&&&&&$-1$\\
            \hline
            $-13$&&&&&&&\\
            \hline
            $-11$&&1&1&&&&\\
            \hline
            $-9$&&&&&&&\\
            \hline
            $-7$&&&&1&&&1\\
            \hline
            $-5$&&&&&&1&1\\
            \hline
            $-3$&&&&&&1&1\\
            \hline
        \end{tabular}
        \caption{Khovanov Polynomial for $T(5,2)$}
        \label{table:t_2_5_kho}
    \end{table}
    \begin{table}
        \centering
        \begin{tabular}{| c | c | c | c | c | c | c | c | c | c |}
            \hline
            $q\symbol{92}t$&$-7$&$-6$&$-5$&$-4$&$-3$&$-2$&$-1$&$0$&$\chi$\\
            \hline
            $-15$&1&&&&&&&&$-1$\\
            \hline
            $-13$&&&&&&&&&\\
            \hline
            $-11$&&1&1&&&&&&\\
            \hline
            $-9$&&&&1&1&&&&\\
            \hline
            $-7$&&&&1&&&&&1\\
            \hline
            $-5$&&&&&1&2&&&1\\
            \hline
            $-3$&&&&&&&&1&1\\
            \hline
            $-1$&&&&&&&1&1&\\
            \hline
        \end{tabular}
        \caption{Khovanov Polynomial for \texttt{dciaFHjEbg}}
        \label{table:dciaFHjEbg_kho}
    \end{table}
    \begin{table}
        \centering
        \begin{tabular}{| c | c | c | c | c | c | c | c | c | c | c | c |}
            \hline
            $q\symbol{92}t$&$-9$&$-8$&$-7$&$-6$&$-5$&$-4$&$-3$&$-2$&$-1$&$0$&$\chi$\\
            \hline
            $-15$&1&&&&&&&&&&$-1$\\
            \hline
            $-13$&&&&&&&&&&&\\
            \hline
            $-11$&&1&1&&&&&&&&\\
            \hline
            $-9$&&&&1&1&&&&&&\\
            \hline
            $-7$&&&&1&&&&&&&1\\
            \hline
            $-5$&&&&&1&2&&&&&1\\
            \hline
            $-3$&&&&&&&&1&&&1\\
            \hline
            $-1$&&&&&&&1&&&1&\\
            \hline
            $1$&&&&&&&&&1&1&\\
            \hline
        \end{tabular}
        \caption{Khovanov Polynomial for \texttt{iNHlPJqCoKFmdABgE}}
        \label{table:iNHlPJqCoKFmdABgE_kho}
    \end{table}
    Note the columns for the Euler characteristic $\chi$ are identical,
    indicating matching Jones polynomials.
    \par\hfill\par
    The $T(7,2)$ knot, also the $7_{1}$ knot, and occasionally called the
    septafoil, has the same Jones polynomial as \texttt{fJGkHlICEABd}. The
    Khovanov polynomials are distinct
    (Tabs.~\ref{table:t_7_2_kho}-\ref{table:fJGkHlICEABd_kho}).
    \begin{table}
        \centering
        \begin{tabular}{| c | c | c | c | c | c | c | c | c | c |}
            \hline
            $q\symbol{92}t$&$-7$&$-6$&$-5$&$-4$&$-3$&$-2$&$-1$&$0$&$\chi$\\
            \hline
            $-21$&1&&&&&&&&$-1$\\
            \hline
            $-19$&&&&&&&&&\\
            \hline
            $-17$&&1&1&&&&&&\\
            \hline
            $-15$&&&&&&&&&\\
            \hline
            $-13$&&&&1&1&&&&\\
            \hline
            $-11$&&&&&&&&&\\
            \hline
            $-9$&&&&&&1&&&1\\
            \hline
            $-7$&&&&&&&&1&1\\
            \hline
            $-5$&&&&&&&&1&1\\
            \hline
        \end{tabular}
        \caption{Khovanov Polynomial for $T(7,2)$}
        \label{table:t_7_2_kho}
    \end{table}
    \begin{table}
        \centering
        \begin{tabular}{| c | c | c | c | c | c | c | c | c | c | c | c |}
            \hline
            $q\symbol{92}t$&$-9$&$-8$&$-7$&$-6$&$-5$&$-4$&$-3$&$-2$&$-1$&$0$&$\chi$\\
            \hline
            $-21$&1&&&&&&&&&&$-1$\\
            \hline
            $-19$&&&&&&&&&&&\\
            \hline
            $-17$&&1&1&&&&&&&&\\
            \hline
            $-15$&&&&1&1&&&&&&\\
            \hline
            $-13$&&&&1&1&&&&&&\\
            \hline
            $-11$&&&&&1&2&1&&&&\\
            \hline
            $-9$&&&&&&1&&&&&1\\
            \hline
            $-7$&&&&&&&1&2&&&1\\
            \hline
            $-5$&&&&&&&&&&1&1\\
            \hline
            $-3$&&&&&&&&&1&1&\\
            \hline
        \end{tabular}
        \caption{Khovanov Polynomial for \texttt{fJGkHlICEABd}}
        \label{table:fJGkHlICEABd_kho}
    \end{table}
    Lastly, the $T(11,2)$ torus knot has the same Jones polynomial as the
    14 crossing knot \texttt{gHlImJnKBDFAce}. Once again the Khovanov
    polynomials differ.
    \begin{table}
        \centering
        \begin{tabular}{| c | c | c | c | c | c | c | c | c | c | c | c | c | c |}
            \hline
            $q\symbol{92}t$&$0$&$1$&$2$&$3$&$4$&$5$&$6$&$7$&$8$&$9$&$10$&$11$&$\chi$\\
            \hline
            $9$&1&&&&&&&&&&&&1\\
            \hline
            $11$&1&&&&&&&&&&&&1\\
            \hline
            $13$&&&1&&&&&&&&&&1\\
            \hline
            $15$&&&&&&&&&&&&&\\
            \hline
            $17$&&&&1&1&&&&&&&&\\
            \hline
            $19$&&&&&&&&&&&&&\\
            \hline
            $21$&&&&&&1&1&&&&&&\\
            \hline
            $23$&&&&&&&&&&&&&\\
            \hline
            $25$&&&&&&&&1&1&&&&\\
            \hline
            $27$&&&&&&&&&&&&&\\
            \hline
            $29$&&&&&&&&&&1&1&&\\
            \hline
            $31$&&&&&&&&&&&&&\\
            \hline
            $33$&&&&&&&&&&&&1&1\\
            \hline
        \end{tabular}
        \caption{Khovanov Polynomial for $T(11,\,2)$}
        \label{table:t_2_11_kho}
    \end{table}
    \begin{table}
        \centering
        \begin{tabular}{| c | c | c | c | c | c | c | c | c | c | c | c | c | c | c | c |}
            \hline
            $q\symbol{92}t$&$0$&$1$&$2$&$3$&$4$&$5$&$6$&$7$&$8$&$9$&$10$&$11$&$12$&$13$&$\chi$\\
            \hline
            $9$&1&&&&&&&&&&&&&&1\\
            \hline
            $11$&1&&&&&&&&&&&&&&1\\
            \hline
            $13$&&&1&&&&&&&&&&&&1\\
            \hline
            $15$&&&&&1&1&&&&&&&&&\\
            \hline
            $17$&&&&1&1&&&&&&&&&&\\
            \hline
            $19$&&&&&&1&2&1&&&&&&&\\
            \hline
            $21$&&&&&&1&&&1&&&&&&\\
            \hline
            $23$&&&&&&&&1&2&1&&&&&\\
            \hline
            $25$&&&&&&&&&&1&1&&&&\\
            \hline
            $27$&&&&&&&&&&1&1&&&&\\
            \hline
            $29$&&&&&&&&&&&&1&1&&\\
            \hline
            $31$&&&&&&&&&&&&&&&\\
            \hline
            $33$&&&&&&&&&&&&&&1&1\\
            \hline
        \end{tabular}
        \caption{Khovanov Polynomial for \texttt{gHlImJnKBDFAce}}
        \label{table:t_gHlImJnKBDFAce_kho}
    \end{table}
