\section{Twist Knots}
    \begin{table}
        \centering
        \resizebox{\textwidth}{!}{%
            \begin{tabular}{| l | l | l |}
                \hline
                    Twist Knot&
                    Non-Twist Knot&
                    Jones Polynomial\\
                \hline
                    $m_{2}$&
                    \texttt{eikGbHJCaFd}&
                    $q^{4}-q^{2}+1-q^{-2}+q^{-4}$\\
                \hline
                    $m_{3}$&
                    \texttt{dgikFHaEjbc}&
                    $-q^{12}+q^{10}-q^{8}+2q^{6}-q^{4}+q^{2}$\\
                \hline
                    $m_{3}$&
                    \texttt{gfJKHlaIEBCD}&
                    $-q^{12}+q^{10}-q^{8}+2q^{6}-q^{4}+q^{2}$\\
                \hline
                    $m_{3}$&
                    \texttt{hGJaMlCdEKBfI}&
                    $-q^{12}+q^{10}-q^{8}+2q^{6}-q^{4}+q^{2}$\\
                \hline
                    $m_{5}$&
                    \texttt{bhDGijCkaef}&
                    $-q^{16}+q^{14}-q^{12}+2q^{10}-2q^{8}+2q^{6}-q^{4}+q^{2}$\\
                \hline
                    $m_{6}$&
                    \texttt{cefIgbajkDh}&
                    $q^{12}-q^{10}+q^{8}-2q^{6}+2q^{4}-2q^{2}+2-q^{-2}+q^{-4}$\\
                \hline
                    $m_{6}$&
                    \texttt{femIbaJKLCGHd}&
                    $q^{12}-q^{10}+q^{8}-2q^{6}+2q^{4}-2q^{2}+2-q^{-2}+q^{-4}$\\
                \hline
                    $m_{6}$&
                    \texttt{jpIFNMrClqOhkEDabg}&
                    $q^{12}-q^{10}+q^{8}-2q^{6}+2q^{4}-2q^{2}+2-q^{-2}+q^{-4}$\\
                \hline
                    $m_{7}$&
                    \texttt{cgjFHIaDEkb}&
                    $-q^{20}+q^{18}-q^{16}+2q^{14}-2q^{12}+2q^{10}-2q^{8}+2q^{6}-q^{4}+q^{2}$\\
                \hline
                    $m_{8}$&
                    \texttt{knIHoBjCDQrMPaeLgF}&
                    $q^{16}-q^{14}+q^{12}-2q^{10}+2q^{8}-2q^{6}+2q^{4}-2q^{2}+2-q^{-2}+q^{-4}$\\
                \hline
                    $m_{9}$&
                    jopIFMrDlqNhkEabcg&
                    $-q^{24}+q^{22}-q^{20}+2q^{18}-2q^{16}+2q^{14}-2q^{12}+2q^{10}-2q^{8}+2q^{6}-q^{4}+q^{2}$\\
                \hline
            \end{tabular}%
        }
        \caption{Knots whose Jones polynomial matches that of a Twist Knot}
        \label{table:matching_twist_knots}
    \end{table}
    The twist knots have a few more matching non-twists knots for the
    Jones polynomial (Tab.~\ref{table:matching_twist_knots}), the tables of
    which are found in Appendix B. The first match is the
    figure-eight knot, $m_{2}$, which has the same Jones polynomial as
    K11n19 from the Hoste-Thistlewaite table.
    Again, this had already been known
    (See \cite{KatlasFigureEight} and \cite{KatlasK11n19}).
    The Khovanov polynomials are
    given in Tabs.~\ref{table:m_2_kho}-\ref{table:eikGbHJCaFd_kho}.
    \par\hfill\par
    The $m_{3}$ twist knot, which is $5_{2}$ on the Rolfsen table,
    has the same Jones polynomial as (at least) three other knots. In each
    case the Khovanov polynomial distinguishes it
    (Tabs.~\ref{table:m_3_kho}-\ref{table:hGJaMlCdEKBfI_kho}).
    The $m_{5}$ twist knot, which is $7_{2}$ on the Rolfsen table, has the
    same Jones polynomial as \texttt{bhDGijCkaef}. The Khovanov polynomials
    are given in Tabs.~\ref{table:m_5_kho} and \ref{table:bhDGijCkaef_kho}.
    \par\hfill\par
    Early efforts stopped at 17 crossings. By
    expanding our experiment from 17 crossings to 19 we added a few new
    results, the first of which comes with
    $m_{6}$. An 18 crossing knot was found
    that has the same Jones polynomial, but the Khovanov polynomials
    differ. This is shown in
    Tabs.~\ref{table:m_6_kho} and \ref{table:jpIFNMrClqOhkEDabg_kho}.
    $m_{6}$ also shares its Jones polynomial with an 11 and a 13 crossing
    knot. The Khovanov polynomials are given in
    Tabs.~\ref{table:cefIgbajkDh_kho} and
    \ref{table:femIbaJKLCGHd_kho}.
    One can note here that the Khovanov polynomials of \texttt{cefIgbajkDh} and
    \texttt{femIbaJKLCGHd} are identical, showing this is not a perfect
    invariant.
    \par\hfill\par
    The knots $m_{7}$, $m_{8}$, and $m_{9}$ have the same Jones polynomial
    of at least one other knot, but again differing Khovanov polynomials.
    We may now make the following claim.
    \begin{theorem}
        If a prime knot $K$ has less than or equal to 19 crossings and has
        the Khovanov homology of a twist knot $T$,
        then $K$ is equivalent to $T$.
    \end{theorem}
    An interesting thing to note is that not all twist knots are
    transversally, or Legendrian, simple, yet there are no knots up to
    19 crossings with the same Khovanov polynomial as a twist knot. This
    motivates the following conjecture.
    \begin{question}
        Does Khovanov homology distinguish twist knots?
    \end{question}
