%------------------------------------------------------------------------------%
\documentclass{article}                                                        %
%------------------------------Preamble----------------------------------------%
\makeatletter                                                                  %
    \def\input@path{{../../}}                                                  %
\makeatother                                                                   %
\input{preamble.tex}                                                           %
\makeindex[intoc]                                                              %
%----------------------------Main Document-------------------------------------%
\begin{document}
    \pagenumbering{gobble}
    \title{MATH 114 Algebraic Topology - Assignment 7}
    \author{Ryan Maguire}
    \date{\vspace{-5ex}}
    \maketitle
    \pagenumbering{roman}
    \pagenumbering{arabic}
    \setcounter{section}{7}
    \begin{problem}
        Hatcher 1.3.14.
    \end{problem}
    \begin{solution}
        By van Kampen's theorem the fundamental group of
        $\mathbb{RP}^{2}\lor\mathbb{RP}^{2}$ is the free product of the
        fundamental group of $\mathbb{RP}^{2}$ with itself, which we know to be
        $\mathbb{Z}_{2}$ simply because the universal cover is $\nsphere[2]$
        which has a 2-to-1 covering map, hence the fibers have two elements,
        meaning the only possible group of deck transformations is
        $\mathbb{Z}_{2}$. So
        $\pi_{1}(\mathbb{RP}^{2}\lor\mathbb{RP}^{2})=\mathbb{Z}_{2}*\mathbb{Z}_{2}$.
        Since our space is the wedge of path connected spaces it is still path
        connected, and hence this group invariant up to isomorphism of the
        choice of base point. Up to isomorphism there are four subgroups of this
        group, the trivial subgroup, the group generated by $1_{a}$, the group
        generated by $1_{a}1_{b}$, and the entire group itself. The group
        generated by $1_{a}$ can be seen to be $\mathbb{Z}_{2}$ since
        $1_{a}^{2}=0$. The group generated by $1_{a}1_{b}$ is isomorphic to
        $\mathbb{Z}$ since it is infinite and cyclic. For the trivial subgroup
        this corresponds to the fundamental group of our space, which is
        (countably) infinitely many spheres connected in a chain. Pick one
        sphere and map this to one of the $\mathbb{RP}^{2}$'s, then take the two
        adjacent ones and map the common point of intersection of the spheres to
        the common point in the wedge, and then the rest of the spheres to the
        second $\mathbb{RP}^{2}$ in the usual way which makes this a covering
        map. This infinite chain is simply connected since it is homotopy
        equivalent to the infinite wedge of spheres which has trivial fundamental
        group by van Kampen. For $\mathbb{Z}_{2}*\mathbb{Z}_{2}$ this just
        corresponds to our space since any space covers itself trivially. For
        $\mathbb{Z}_{2}$ we take $\nsphere[2]\lor\mathbb{RP}^{2}$ and map the
        point of common intersection to the point of common intersection in
        $\mathbb{RP}^{2}\lor\mathbb{RP}^{2}$, map the copy of $\mathbb{RP}^{2}$
        to itself via identity, and $\nsphere[2]$ to $\mathbb{RP}^{2}$ via its
        universal covering map. The fundamental group is the trivial group
        free product $\mathbb{Z}_{2}$, which is just $\mathbb{Z}_{2}$.
    \end{solution}
    \begin{problem}
        Hatcher 2.1.4.
    \end{problem}
    \begin{solution}
        We have the following sequence of groups:
        \begin{equation*}
            0\overset{\partial_{3}}{\longrightarrow}\mathbb{Z}
            \overset{\partial_{2}}{\longrightarrow}\mathbb{Z}^{3}
            \overset{\partial_{1}}{\longrightarrow}\mathbb{Z}
            \overset{\partial_{0}}{\longrightarrow}{0}
        \end{equation*}
        Computing we have $\partial_{1}[v,v]=(v-v)=0$, so the image is $0$.
        Since the kernel of $\partial_{0}$ is the entirety of $C_{1}=\mathbb{Z}$
        we have $H_{0}^{\Delta}(X)=\mathbb{Z}/0=\mathbb{Z}$. We have
        $\partial_{2}[v,v,v]=[v,v]-[v,v]+[v,v]=[v,v]$, hence the image is
        $\mathbb{Z}$. From this
        $H_{1}^{\Delta}(X)=\ker(\partial_{1})/\textrm{Im}(\partial_{2})=\mathbb{Z}^{3}/\mathbb{Z}=\mathbb{Z}^{2}$.
        Lastly, since there are no three dimensional objects, $\partial_{3}$ is the
        zero map with image $0$, so $H_{2}^{\Delta}(X)$ is just $\ker(\partial_{2})$ which is 0.
    \end{solution}
    \begin{problem}
        Hatcher 2.1.9.
    \end{problem}
    \begin{solution}
        Since there's only one element for each $k=0,1,\dots,n$, we have:
        \begin{equation}
            0\overset{\partial_{n+1}}{\longrightarrow}\mathbb{Z}
            \overset{\partial_{n}}{\longrightarrow}\mathbb{Z}
            \overset{\partial_{n-1}}{\longrightarrow}
            \cdots
            \overset{\partial_{2}}{\longrightarrow}\mathbb{Z}
            \overset{\partial_{1}}{\longrightarrow}\mathbb{Z}
            \overset{\partial_{0}}{\longrightarrow}0
        \end{equation}
        The image of $\partial_{1}[v,v]=v-v=0$, for $\partial_{2}[v,v,v]$ we get
        $[v,v]-[v,v]+[v,v]=[v,v]$, and inductively we obtain $0$ for $k$ odd and
        $[v,v,\dots,v]$ for $k$ even. That is, the image of $\partial_{k}$
        oscillates between $0$ and $\mathbb{Z}$. Since $\textrm{Im}(\partial_{1})=0$
        and $\ker(\partial_{0})=\mathbb{Z}$, we know that
        $H_{0}^{\Delta}(X)=\mathbb{Z}/0=\mathbb{Z}$. Since
        $\textrm{Im}(\partial_{2})=\mathbb{Z}$ and $\ker(\partial_{1})=\mathbb{Z}$,
        $H_{1}^{\Delta}(X)=\mathbb{Z}/\mathbb{Z}=0$. Now for the higher ones we
        know $\partial_{k}$ has image $\mathbb{Z}$ for $k$ even and $0$ for $k$
        odd. Hence $\partial_{k}$ has kernel $0$ for $k$ even and $\mathbb{Z}$
        for $k$ odd. But then $\ker(\partial_{k})/\textrm{Im}(\partial_{k+1})$
        is $\mathbb{Z}/\mathbb{Z}$ for $k$ even, and $0/0$ for $k$ odd. In
        either case we have $H_{k}^{\Delta}(X)$ is trivial. Lastly, for $k=n$
        we have two possibilities.  $\textrm{Im}(\partial_{n+1})=0$, and hence
        $H_{n}^{\Delta}(X)=\ker(\partial_{n})$. This is $0$ if $n$ is even and
        $\mathbb{Z}$ if $n$ is odd. Summarizing, we have:
        \begin{equation}
            H_{k}^{\Delta}(X)\simeq
            \begin{cases}
                \mathbb{Z},&k=0\\
                0,&1\leq{k}<n\text{ or }k>n\\
                \mathbb{Z},&k=n\text{ and }n\text{ is odd}\\
                0,&k=n\text{ and }n\text{ is even}\\
            \end{cases}
        \end{equation}
    \end{solution}
\end{document}