%------------------------------------------------------------------------------%
\documentclass[oneside]{book}                                                  %
%------------------------------Preamble----------------------------------------%
\makeatletter                                                                  %
    \def\input@path{{../../}}                                                  %
\makeatother                                                                   %
\input{preamble.tex}                                                           %
%----------------------------Main Document-------------------------------------%
\begin{document}
    \title{MATH 102 Geometry Notes}
    \author{%
        Professor: Carolyn Gordon\\
        Notes by: Ryan Maguire%
    }
    \date{\vspace{-5ex}}
    \maketitle
    \tableofcontents
    \chapter{Lie Groups and Lie Algebras}
        \section{Lecture 0: Review}
            \subsection{Coordinate Charts in a Manifold}
            \subsection{Tangent Spaces}
            \subsection{Differentiation in Euclidean Space}
            \subsection{Submanifolds}
                An immersed submanifold is given by an inective immersion
                $f:N\rightarrow{M}$. We write that $(N,f)$ is a submanifold of
                $M$ and usually identify $N$ with $f[N]$. If $f$ is an
                embedding, then we say $(N,f)$ is an embedded submanifold or a
                regular submanifold.
        \section{Lecture 1}
    \chapter{Lie Group Structure Theory}
        \begin{fdefinition}{Topological Group}{Topological_Group}
            A topological group is a topological space $\topspace{G}$ with a
            binary operation $*$ such that $\monoid{G}$ is a group and and
            the functions $h:G\times{G}\rightarrow{G}$ and $\nu:G\rightarrow{G}$
            defined by $h(x,y)=x*y$ and $\nu(g)=g^{\minus{1}}$ are continuous.
        \end{fdefinition}
        A topological subgroup of a topological group is a subgroup with the
        subspace topology.
        \begin{example}
            Given any group $\monoid{G}$, if we endow $G$ with the trivial
            topology $\tau=\{\emptyset,G\}$ then $\topgroup{G}$ is a topological
            group.
        \end{example}
        \begin{example}
            As another trivial example, if we endow a group $\monoid{G}$ with
            the discrete topology $\tau=\powset{G}$, then $\topgroup{G}$ is a
            topologyical group. 
        \end{example}
        \begin{fdefinition}{Lie Group}{Lie_Group}
            A Lie group is a smooth manifold $\manifold{G}$ with a binary
            operation $*$ such that $\monoid{G}$ is a group, and the functions
            $h:G\times{G}\rightarrow{G}$ and $\nu:G\rightarrow{G}$ defined by
            $h(x,y)=x*y$ and $\nu(g)=g^{\minus{1}}$ are smooth.
        \end{fdefinition}
        \begin{example}
            Taking the additive structure from the well known vector spaces
            $\nspace$ and $\mathbb{C}^{n}$ give rise to Lie groups. The topology
            on $\mathbb{C}^{n}$ is the same as the topology on $\nspace[2n]$.
        \end{example}
        \begin{example}
            The unit circle $\nsphere[1]$ with the \textit{rotation} operation:
            \begin{equation}
                \exp(i\theta_{1})*\exp(\theta_{2})
                    =\exp(i(\theta_{1}+\theta_{2}))
            \end{equation}
            Using this we can also see that the $n$ torus $\ntorus$ is also a
            Lie group since it is the product of circles.
        \end{example}
        \begin{example}
            Letting $H$ denote the quaternions, the topological structure is
            homeomorphic to $\nspace[4]$. Thus we may embed the 3-sphere
            $\nsphere[3]$ into $H$ by considering quaternions with norm 1. This
            shows that $\nsphere[3]$ has a Lie group structure.
        \end{example}
        \begin{example}
            The matrix groups $GL_{n}(\nspace[])$.
        \end{example}
        The following question was posed by Hilbert in his famous list of
        problems released at the turn of the $20^{th}$ century. This is known as
        Hilbert's Fifth Problem.
        \begin{equation}
            \begin{split}
                &\text{If }\topgroup{X}\text{ is a topological group such that }
                \topspace{X}\text{ is a topological}\\
                &\text{manifold, then is this a Lie group?}
            \end{split}
        \end{equation}
        The answer is yes, the proof came in the 1950s.
        \begin{fdefinition}{Lie Group Homomorphism}{Lie_Group_Homomorphism}
            A Lie group homomorphism from a Lie group
            $\topgroup[1]{G}$ to a Lie group $\topgroup[2]{G}$ is a smooth
            function $\phi:G_{1}\rightarrow{G}_{2}$ such that $\phi$ is a
            group homomorphism with respect to $\monoid[1]{G}$ and
            $\monoid[2]{G}$.
        \end{fdefinition}
        \begin{theorem}
            If $\topgroup[1]{G}$ and $\topgroup[2]{G}$ are Lie groups and if
            $\phi:G_{1}\rightarrow{G}_{2}$ is a Lie group homomorphism, then
            $\phi$ is a map of constant rank.
        \end{theorem}
        \begin{proof}
            For $a\in{G}_{1}$, let $L_{a}$ be defined by $x\mapsto{a}*x$. This
            is a diffeomorphism.
        \end{proof}
        \begin{theorem}
            If $\phi:G_{1}\rightarrow{G}_{2}$ is a bijective Lie group
            homomorphism, then it is an isomorphism.
        \end{theorem}
        \begin{proof}
            By the inverse function theorem, together with the fact that the map
            has constant rank.
        \end{proof}
        \begin{fdefinition}{Lie Subgroup}{Lie Subgroup}
            A Lie subgroup of a Lie group $\topgroup[*][G]{G}$ is a Lie group
            $\topgroup[*][H]{H}$ and an injective Lie homomorphism
            $f:H\rightarrow{G}$, denoted $(H,f)$.
        \end{fdefinition}
        Note, given a Lie subgroup $(H,f)$ of a Lie group $G$ we often say that
        $f[H]$, the image of $H$ in $G$, is a Lie subgroup of $G$. This
        definition is well founded since a Lie subgroup is an immersed
        submanifold of $G$. This is because a Lie group homomorphism has
        constant rank, and if $f$ is injective then it must be an immersion by
        the theorem on rank. Note that a Lie subgroup of some Lie group $G$ need
        \textit{not} be a topological subgroup. A topological subgroup is a
        subgroup endowed with the subspace topology. Hence a Lie subgroup
        $(H,f)$ yields a topological subgroup if and only if $f$ is an embedding
        of $H$ into $G$.
        \begin{example}
            A line of irrational slope on a torus is an example of a Lie
            subgroup that is not a topological subgroup. It is an immersed
            submanifold, but not an embedded submanifold. If we take a line of
            \textit{rational} slope then we again obtain a Lie subgroup that is
            also a topological subgroup. This is homeomorphic to $\nsphere[1]$.
        \end{example}
        We'll need the following results:
        \begin{theorem}
            If $\iota:N\rightarrow{M}$ is an immersion, if $P$ is a manifold,
            and if $f:P\rightarrow{N}$ is a continuous function such that
            $\iota\circ{f}$ is smooth, then $f$ is smooth.
        \end{theorem}
        \begin{theorem}
            If $\iota:N\rightarrow{M}$ is an embedding, and if $\iota\circ{f}$
            is smooth, then $f$ is smooth.
        \end{theorem}
        With this we may prove the following:
        \begin{theorem}
            If $\topgroup{G}$ is a Lie group, and if $(H,f)$ is a Lie subgroup
            such that $f:H\rightarrow{G}$ is an embedding, then
            $\topgroup[*][H]{H}$ is a Lie group.
        \end{theorem}
\end{document}