%------------------------------------------------------------------------------%
\documentclass{article}                                                        %
%------------------------------Preamble----------------------------------------%
\makeatletter                                                                  %
    \def\input@path{{../../}}                                                  %
\makeatother                                                                   %
\input{preamble.tex}                                                           %
\makeindex[intoc]                                                              %
%----------------------------Main Document-------------------------------------%
\begin{document}
    \pagenumbering{gobble}
    \title{MATH 114 Algebraic Topology - Assignment 8}
    \author{Ryan Maguire}
    \date{\vspace{-5ex}}
    \maketitle
    \pagenumbering{roman}
    \pagenumbering{arabic}
    \setcounter{section}{7}
    \begin{problem}
        Hatcher 2.1.6.
    \end{problem}
    \begin{solution}
        There are no three dimensional object, so $C_{3}=0$, and since the two
        dimensional portions are left untouched in the gluing we have
        $C_{2}=\mathbb{Z}^{n+1}$. There are $3(n+1)$ edges before the gluing,
        all three in $\Delta_{0}^{2}$ are identified, two of which are
        identified in $\Delta_{k}^{2}$ for all other $k$, and the last of which
        being identified to the single edge of $\Delta_{0}^{2}$. So each
        $\Delta_{k}^{2}$ contributes a single edge, so $C_{1}=\mathbb{Z}^{n+1}$.
        $\Delta_{0}^{2}$ has one vertex, all the others have two, but one of
        which is identified with the vertex of $\Delta_{0}^{2}$, so there are
        $n+1$ vertices and hence $C_{0}=\mathbb{Z}^{n+1}$. Since locally this
        structure is a quotient of $\Delta^{2}$, and since all of the pieces
        have a vertex in common, we may conclude the space is path connected and
        hence $H_{0}^{\Delta}(X)=\mathbb{Z}$. The image of $\partial_{1}$ has a
        basis $v_{k}-v_{0}$ for $k=1,1,\dots,n+1$, and this has dimension $n$
        so $\textrm{Im}(\partial_{1})=\mathbb{Z}^{n}$. The kernel of
        $\partial_{0}$ is the entirety of $\mathbb{Z}^{n+1}$, so
        $H_{0}^{\Delta}(X)=\mathbb{Z}^{n+1}/\mathbb{Z}$ which is isomorphic to
        $\mathbb{Z}$, in agreement with the theorem. For $\partial_{1}$, the
        image is $\partial_{2}(v_{0},v_{0},v_{k})=v_{k}$ since two of the
        vertices are identified, and hence only the final one is free, meaning
        the image has dimension $n$, so
        $\textrm{Im}(\partial_{2})=\mathbb{Z}^{n}$. The kernel of
        $\partial_{1}$ is the space of $v_{0}$, which is zero dimensional, so we
        have $H_{1}^{\Delta}(X)=\ker(\partial_{1})/\textrm{Im}(\partial_{2})$
        and this is $\mathbb{Z}/\mathbb{Z}^{n}$ which is zero for $n>0$. The
        kernel of $\partial_{2}$ is also one dimensional, and hence
        $H_{2}^{\Delta})(X)=\mathbb{Z}/0=\mathbb{Z}$.
    \end{solution}
    \begin{problem}
        Hatcher 2.1.11.
    \end{problem}
    \begin{solution}
        Let $r:X\rightarrow{A}$ be such a retract. Then
        $r\circ\iota=\identity{A}$ and hence
        $(r\circ\iota)_{*}=r_{*}\circ\iota_{*}={\identity{A}}_{*}$. Hence if
        $\iota_{*}(a)=\iota_{*}(b)$, then
        $r_{*}(\iota_{*}(a))=r_{*}(\iota_{*}(b))$ which then implies that
        ${\identity{A}}_{*}(a)={\identity{A}}_{*}(b)$, so $a=b$. Hence
        $\iota_{*}$ is injective.
    \end{solution}
    \begin{problem}
        Hatcher 2.1.12.
    \end{problem}
    \begin{solution}
        Suppose $P$ and a chain homotopy between $f_{\sharp}$ and $g_{\sharp}$
        and $Q$ is a chain homotopy between $g_{\sharp}$ and $h_{\sharp}$.
        Then:
        \begin{equation}
            \partial(P+H)+(P+H)\partial
            =\partial{P}+P\partial+\partial{H}+H\partial
            =f_{\sharp}-g_{\sharp}+g_{\sharp}-h_{\sharp}
            =f_{\sharp}-h_{\sharp}
        \end{equation}
        and hence $P+H$ is a chain homotopy between $f_{\sharp}$ and
        $h_{\sharp}$ so we have transitivity. For symmetry, given a chain
        homotopy $P$ between $f_{\sharp}$ and $g_{\sharp}$, choose
        $\minus{P}:C_{n}(X)\rightarrow{C}_{n+1}(Y)$. Then:
        \begin{equation}
            \partial(\minus{P})+(\minus{P})\partial
            =\minus(f_{\sharp}-g_{\sharp})=g_{\sharp}-f_{\sharp}
        \end{equation}
        Lastly, for reflexivity, since the identity homotopy is a homotopy from
        $f$ to $f$, we have that the induced $P$ satisfies
        $P\partial+\partial{P}=f_{\sharp}-f_{\sharp}$, so $P$ is a chain
        homotopy between $f_{\sharp}$ and itself.
    \end{solution}
    \begin{problem}
        Hatcher 2.1.15.
    \end{problem}
    \begin{solution}
        Suppose the sequence is exact and $A\rightarrow{B}$ is surjective and
        $D\rightarrow{E}$ is injective. Since the sequence is exact, the kernel
        of $B\rightarrow{C}$ is equal to the image of $A\rightarrow{B}$, and
        since this is surjective, then kernel of $B\rightarrow{C}$ is the
        entirety of $B$. But then the kernel of $C\rightarrow{D}$ is the image
        of $B\rightarrow{C}$, but all of $B$ maps to zero so the kernel of
        $C\rightarrow{D}$ is zero. But then $C\rightarrow{D}$ is injective. But
        $D\rightarrow{E}$ is injective, so
        the kernel of zero. But the image of $C\rightarrow{D}$ is equal to the
        kernel of $D\rightarrow{E}$, so the image of $C\rightarrow{D}$ is zero.
        Hence $C\rightarrow{D}$ is an injective map of $C$ to zero, so $C$ is
        zero as well. In the other direction, if $C$ is zero then the kernel of
        $B\rightarrow{C}$ is $B$. But the image of $A\rightarrow{B}$ is the
        kernel of $B\rightarrow{C}$, and hence $A\rightarrow{B}$ is surjective.
        Also since $C$ is zero, the image of $C\rightarrow{D}$ is zero. But the
        image of $C\rightarrow{D}$ is the kernel of $D\rightarrow{E}$, so the
        kernel of $D\rightarrow{E}$ is zero and hence $D\rightarrow{E}$ is
        injective.
    \end{solution}
\end{document}