%------------------------------------------------------------------------------%
\documentclass{article}                                                        %
%------------------------------Preamble----------------------------------------%
\makeatletter                                                                  %
    \def\input@path{{../../}}                                                  %
\makeatother                                                                   %
\input{preamble.tex}                                                           %
\geometry{b5paper, margin=1in}
%----------------------------Main Document-------------------------------------%
\begin{document}
    \title{A CW Complex That is Not First Countable}
    \author{Ryan Maguire}
    \date{\vspace{-5ex}}
    \maketitle
    Let $X^{0}=\vector{0}$ consist of a single point and
    $X^{1}=\coprod_{n\in\mathbb{N}}I$. That is, the disjoint union of countably
    many intervals. An element is denoted $(n,x)$ with $n\in\mathbb{N}$ and
    $x\in{I}$. The attaching maps send $(n,0)$ and $(n,1)$ to $\vector{0}$
    for all $n\in\mathbb{N}$, so we obtain countably many circles which are
    connected at a single point. The CW Complex topology is then just the
    normal quotient topology since this is 1 dimensional. The resulting space is
    not first countable since $[\vector{0}]$ does not have a countable
    neighborhood basis. For suppose it does and let $\mathcal{B}$ be such a
    basis. Since $\mathcal{B}$ is hypothesized to be countable, there is a
    surjection $\mathcal{U}:\mathbb{N}\rightarrow\mathcal{B}$. Since
    $\mathcal{U}_{n}\in\mathcal{B}$ for all $n\in\mathbb{N}$, $\mathcal{U}_{n}$
    is open. But a set is open if and only if $\pi^{\minus{1}}[\mathcal{U}_{n}]$
    is open where $\pi$ is the canonical projection map. Since
    $[\vector{0}]\in\mathcal{U}_{n}$, $[(n,0)],[(n,1)]\in\mathcal{U}_{n}$ since
    $[\vector{0}]=[(n,0)]=[(n,1)]$ for all $n\in\mathbb{N}$. But then $(n,0)$
    and $(n,1)$ are elements of $\pi^{\minus{1}}[\mathcal{U}_{n}]$. Since
    $\pi^{\minus{1}}[\mathcal{U}_{n}]$ is open there exists $a_{n}>0$ and
    $b_{n}>0$ such that
    $\{n\}\times[0,a_{n})\subseteq\pi^{\minus{1}}[\mathcal{U}_{n}]$ and
    $\{n\}\times(b_{n},1]\subseteq\pi^{\minus{1}}[\mathcal{U}_{n}]$. Let
    $r_{n}=\min\{a_{n},b_{n},\frac{1}{2}\}/2$ and define:
    \begin{equation}
        \mathcal{O}=\{\vector{0}\}\cup\bigcup_{n\in\mathbb{N}}\Big(
            \big(\{n\}\times[0,r_{n})\big)\cup\big(\{n\}\times(r_{n},1]\big)
        \Big)
    \end{equation}
    Then $\mathcal{O}$ is open in the disjoint topology and is saturated since
    $\pi^{\minus{1}}\big[\pi[\mathcal{O}]\big]=\mathcal{O}$. Therefore
    $[\mathcal{O}]=\pi[\mathcal{O}]$ is open and contains $[\vector{0}]$. But if
    $[\mathcal{O}]$ contains $[\vector{0}]$, then since $\mathcal{B}$ is a
    neighborhood basis of $[\vector{0}]$ there is a $\mathcal{V}\in\mathcal{B}$
    such that $\mathcal{V}\subseteq[\mathcal{O}]$. But $\mathcal{U}$ is
    surjective so there is an $N\in\mathbb{N}$ such that
    $\mathcal{U}_{N}=\mathcal{V}$. But
    $\pi[\{N\}\times(r_{N},a_{N})]\subseteq\mathcal{U}_{N}$ and
    $\pi[\{N\}\times(r_{N},a_{N})]\nsubseteq[\mathcal{O}]$, a contradiction
    since $\mathcal{U}\subseteq[\mathcal{O}]$. Hence, $\mathcal{B}$ is not a
    neighborhood basis.
    \par\hfill\par
    Some comments. We've used countable choice for the $r_{n}$. A sequential
    space is a topological space where sequences suffices to define openness.
    $\mathcal{U}\subseteq{X}$ is open if and only if for every sequence
    converging to a point in $\mathcal{U}$, the sequence is \textit{eventually}
    contained in $\mathcal{U}$. That is, open and sequentially open are
    identical. Open always implies sequentially open, the
    converse may fail (cocountable topology on $\mathbb{R}$). In a sequential
    space continuity and sequential continuity are identical. A very mild
    condition that a space be sequential
    is first countability. It is not necessary, just sufficient. A necessary and
    sufficient condition is the following:
    \begin{theorem}
        A topological space $\topspace{X}$ is sequential if and only if it is
        the quotient of a metric space.
    \end{theorem}
    Since the disjoint union of metric spaces is still a metric space (assuming
    axiom of choice), and since CW complex are obtained from quotients of
    these, CW complexes are indeed sequential. Hence, sequences suffice to prove
    continuity.
    \begin{definition}
        A sequential topological space is a topological space $\topspace{X}$
        such that $\mathcal{U}\subseteq{X}$ is open if and only if $\mathcal{U}$
        is sequentially open. That is, for every sequence
        $a:\mathbb{N}\rightarrow{X}$ with a limit $x\in\mathcal{U}$ there exists
        $N\in\mathbb{N}$ such that for all $n>N$ it is true that
        $a_{n}\in\mathcal{U}$.
    \end{definition}
    We say \textit{a} limit since no separation axioms are assumed, hence limits
    need not be unique. Since CW complexes are Hausdorff this does not cause
    concern.
    \begin{theorem}
        Open implies sequentially open.
    \end{theorem}
    \begin{proof}
        By the definition of convergence. If $a_{n}\rightarrow{x}$, then for
        every open $\mathcal{V}$ containing $x$ there is an $N\in\mathbb{N}$
        such that for all $n>N$ it is true that $a_{n}\in\mathcal{V}$. Setting
        $\mathcal{V}=\mathcal{U}$ gives the result.
    \end{proof}
    \begin{theorem}
        Continuous implies sequentially continuous.
    \end{theorem}
    \begin{proof}
        Standard topological result.
    \end{proof}
    \begin{theorem}
        First countable implies sequential.
    \end{theorem}
    \begin{proof}
        Another standard theorem.
    \end{proof}
    \begin{theorem}
        Metrizable spaces are sequential.
    \end{theorem}
    \begin{proof}
        For metrizable implies first countable, which implies sequential.
    \end{proof}
    \begin{theorem}
        If $\topspace[\alpha]{X_{\alpha}}$ are a collection of sequential
        spaces, if $Y=\coprod_{\alpha}X_{\alpha}$, and if $\tau$ is the
        disjoint union topology, then $\topspace{Y}$ is sequential.
    \end{theorem}
    \begin{proof}
        For suppose $\mathcal{V}\subseteq{Y}$ is sequentially open but not open.
        But $\mathcal{V}$ is open if and only if for all $\alpha$, the pre-image
        under the canonical inclusion mapping
        $\iota_{\alpha}:X_{\alpha}\rightarrow{Y}$ is open. That is,
        $\iota_{\alpha}^{\minus{1}}[\mathcal{V}]$ is open. Hence if
        $\mathcal{V}$ is \textit{not} open, then there exists an $\alpha$ such
        such that $\iota_{\alpha}^{\minus{1}}[\mathcal{V}]\subseteq{X}_{\alpha}$
        is not open. Let $\mathcal{U}=\iota_{\alpha}^{\minus{1}}[\mathcal{V}]$.
        But $X_{\alpha}$ is sequential and hence if $\mathcal{U}$ is not open,
        then it is not sequentially open. But then there is a sequence
        $a:\mathbb{N}\rightarrow{X}_{\alpha}$ with a limit $x\in\mathcal{U}$
        such that for all $N\in\mathbb{N}$ there is an $n>N$ with
        $a_{n}\notin\mathcal{U}$. But $\iota_{\alpha}$ is continuous and hence
        $\iota_{\alpha}(a_{n})\rightarrow\iota_{\alpha}(x)$. But
        $\iota_{\alpha}(x)\in\mathcal{V}$ and $\mathcal{V}$ is sequentially
        continuous. Therefore there is an $N\in\mathbb{N}$ such that for all
        $n>N$ it is true that $\iota_{\alpha}(a_{n})\in\mathcal{V}$. But then
        for all $n>N$, $a_{n}\in\mathcal{U}$, a contradiction. Hence,
        $\mathcal{U}$ is open and $\mathcal{V}$ is also open. That is, $Y$ is
        sequential.
    \end{proof}
    \begin{theorem}[Exercise 2.4G of Engelking's Topology]
        If $\topspace[X]{X}$ and $\topspace[Y]{Y}$ are topological spaces, if
        $X$ is sequential, and if $q:X\rightarrow{Y}$ is a quotient map, then
        $Y$ is sequential.
    \end{theorem}
    \begin{proof}
        For let $\mathcal{V}\subseteq{Y}$ be sequentially open. It suffices to
        prove $\mathcal{V}$ is open. Let
        $\mathcal{U}=q^{\minus{1}}[\mathcal{V}]$ and suppose this is not open.
        But $X$ is sequential and hence $\mathcal{U}$ is not sequentially open.
        But then there is a sequence $a:\mathbb{N}\rightarrow{X}$ with a limit
        $x\in\mathcal{U}$ such that for all $N\in\mathbb{N}$ there is an
        $n\in\mathbb{N}$ such that $n>N$ and $a_{n}\notin\mathcal{U}$. But $q$
        is continuous, and hence sequentially continuous, and therefore
        $q(a_{n})\rightarrow{q}(x)$. But $q(x)\in\mathcal{V}$ and $\mathcal{V}$
        is sequentially open, hence there is an $N\in\mathbb{N}$ such that
        for all $n>N$ it is true that $q(a_{n})\in\mathcal{V}$. But then for
        all $n>N$ we have $a_{n}\in\mathcal{U}$, a contradiction. Hence,
        $\mathcal{U}$ is open. But $\mathcal{V}$ is open if and only if
        $q^{\minus{1}}[\mathcal{V}]$ is open, and therefore $\mathcal{V}$ is
        open. That is, $Y$ is sequential.
    \end{proof}
    \begin{theorem}
        If $\topspace{X}$ is a finite dimensional CW complex, then it is
        sequential.
    \end{theorem}
    \begin{proof}
        We prove by induction on the dimension. The base case $n=0$ is trivially
        true since the disjoint union of points is a discrete space which is
        metrizable, and therefore sequential. Suppose it is true for
        $n\in\mathbb{N}$. If $X$ is an $n+1$ dimensional CW complex then it is
        of the form $X^{n}\coprod{X}^{n+1}/\sim$ where $X^{n}$ is an $n$
        dimensional CW complex, $X^{n+1}$ is the disjoint union of $n+1$
        dimensional closed balls, and $\sim$ is the equivalence relation induced
        by the attaching maps of the $n+1$ skeleton into $X^{n}$. But $X^{n}$ is
        sequential by hypothesis, and $X^{n+1}$ is
        the disjoint union of $n+1$ balls, which is metrizable, and hence
        sequential. But the disjoint union of sequential spaces is sequential,
        and hence $X^{n}\coprod{X}^{n+1}$ is sequential. But then
        $X^{n}\coprod{X}^{n+1}/\sim$ is the quotient of a sequential space, and
        is therefore sequential. Therefore, finite dimensional CW complexes are
        sequential.
    \end{proof}
    \begin{theorem}
        If $X$ is a CW complex, then it is sequential.
    \end{theorem}
    \begin{proof}
        If $X$ is a finite dimensional CW complex, then we are done. So suppose
        not and let $\mathcal{U}\subseteq{X}$ be sequentially open. To show that
        it is open suffices to check that $\mathcal{U}\cap{X}^{n}$ is an open
        subset of $X^{n}$ for all $n\in\mathbb{N}$. But $X^{n}$ is sequential,
        and hence if $\mathcal{U}\cap{X}^{n}$ is not open, then it is not
        sequentially open. But then there is a sequence
        $a:\mathbb{N}\rightarrow{X}^{n}$ with limit $x\in\mathcal{U}\cap{X}^{n}$
        such that for all $K\in\mathbb{N}$ there is an $k>K$ such that
        $a_{k}\notin\mathcal{U}\cap{X}^{n}$. But $\mathcal{U}$ is sequential,
        hence if $a_{k}\rightarrow{x}$ and $x\in\mathcal{U}$, then there is a
        $K\in\mathbb{N}$ such that for all $k>K$ it is true that
        $a_{k}\in\mathcal{U}$. But for all $k\in\mathbb{N}$ we have
        $a_{k}\in{X}^{k}$ by definition since $a$ is a sequence in $X^{n}$, and
        hence for all $k>K$ we have $a_{k}\in\mathcal{U}\cap{X}^{n}$, a
        contradiction. Therefore $\mathcal{U}\cap{X}^{n}$ is sequentially open,
        and thus open in $X^{n}$. But this is true of all $n\in\mathbb{N}$, and
        hence $\mathcal{U}$ is open.
    \end{proof}
\end{document}