%------------------------------------------------------------------------------%
\documentclass{article}                                                        %
%------------------------------Preamble----------------------------------------%
\makeatletter                                                                  %
    \def\input@path{{../../}}                                                  %
\makeatother                                                                   %
\input{preamble.tex}                                                           %
%----------------------------Main Document-------------------------------------%
\begin{document}
    \title{Differential Topology}
    \author{Ryan Maguire}
    \date{\vspace{-5ex}}
    \maketitle
    \tableofcontents
    \section{Homework I}
        \subsection{Sequential Spaces}
            \begin{fdefinition}{Sequentially Continuous}
                               {Sequentially_Continuous}
                A sequentially continuous function from a topological space
                $(X,\tau_{X})$ to a topological space $(Y,\tau_{Y})$ is a
                function $f:X\rightarrow{Y}$ such that for every convergent
                sequence $a:\mathbb{N}\rightarrow{X}$ and for every $x\in{X}$
                such that $a_{n}\rightarrow{x}$, it is true that
                $f(a_{n})\rightarrow{f}(x)$.
            \end{fdefinition}
            We say \textit{for every x} since limits need not be unique in
            spaces that aren't at least $T_{1}$ (an \textit{accessible} space).
            \begin{theorem}
                \label{thm:cont_implies_seq_cont}%
                If $\topspace[X]{X}$ and $\topspace[Y]{Y}$ are topological spaces,
                and if $f:X\rightarrow{Y}$ is a continuous function, then it is
                sequentially continuous.
            \end{theorem}
            \begin{proof}
                For suppose not. Then there is a sequence
                $a:\mathbb{N}\rightarrow{X}$ and a point $x\in{X}$ such that
                $a_{n}\rightarrow{x}$, but $f(a_{n})\not\rightarrow{f}(x)$
                (Def.~\ref{def:Sequentially_Continuous}). But then there exists
                an open subset $\mathcal{V}\in\tau_{Y}$ such that
                $f(x)\in\mathcal{V}$, and for all $N\in\mathbb{N}$ there exists
                an $n\in\mathbb{N}$ such that $n>N$ and
                $f(a_{n})\notin\mathcal{V}$. But $f$ is continuous, and
                therefore $f^{\minus{1}}[\mathcal{V}]$ is an open subset of $X$.
                And since $f(x)\in\mathcal{V}$ it is true that
                $x\in{f}^{\minus{1}}[\mathcal{V}]$. But $a_{n}\rightarrow{x}$,
                and thus there is an $N\in\mathbb{N}$ such that for all
                $n\in\mathbb{N}$ with $n>N$ it is true that
                $a_{n}\in{f}^{\minus{1}}[\mathcal{V}]$. But then for all $n>N$
                it is true that $f(a_{n})\in\mathcal{V}$, a contradiction.
                Therefore, $f$ is sequentially continuous.
            \end{proof}
            This theorem does not reverse.
            \begin{example}
                Let $X$ be the order topology on the ordinal $\omega_{1}+1$, where
                $\omega_{1}$ is the first uncountable ordinal. Define
                $f:X\rightarrow\nspace[]$ by:
                \begin{equation}
                    f(x)=
                    \begin{cases}
                        0,&x\ne\omega_{1}\\
                        1,&x=\omega_{1}
                    \end{cases}
                \end{equation}
                then $f$ is sequentially continuous, but not continuous. If
                $a:\mathbb{N}\rightarrow{X}$ is any sequence, either it coverges to
                $\omega_{1}$ or it is not. In the latter case the limit of
                $f(a_{n})$ will be zero, and in the former case there is an
                $N\in\mathbb{N}$ such that for all $n>N$ it is true that
                $a_{n}=\omega_{1}$, and hence $f(a_{n})\rightarrow{1}$. In both
                scenarios, $f$ is sequentially continuous. It is not continuous
                since $\{\omega_{1}\}$ is not an isolated point of $X$, yet
                $f^{\minus{1}}[(0,\infty)]=\{\omega_{1}\}$.
            \end{example}
            The problem with this space is that it is not first countable. First
            countability implies that sequentially continuous and continuous are
            identical concepts. There's a weaker such notion, called sequential
            spaces.
            \begin{fdefinition}{Sequentially Open}{Sequentially_Open}
                A sequentially open subset of a topological space $\topspace{X}$
                is a subset $\mathcal{U}\subseteq{X}$ such that for every sequence
                $a:\mathbb{N}\rightarrow{X}$ such that $a$ converges to an element
                $x\in\mathcal{U}$ there exists an $N\in\mathbb{N}$ such that for all
                $n\in\mathbb{N}$ with $n>N$, it is true that $a_{n}\in\mathcal{U}$.
            \end{fdefinition}
            \begin{theorem}
                \label{thm:Open_is_Seq_Open}%
                If $\topspace{X}$ is a topological space, if $\mathcal{U}\in\tau$ is
                an open subset of $X$, then $\mathcal{U}$ is sequentially open.
            \end{theorem}
            \begin{proof}
                For suppose not. Then there is a sequence
                $a:\mathbb{N}\rightarrow{X}$ such that $a$ converges to a point
                $x\in\mathcal{U}$, but for all $N\in\mathbb{N}$ there is an
                $n\in\mathbb{N}$ such that $n>N$ and $a_{n}\notin\mathcal{U}$
                (Def.~\ref{def:Sequentially_Open}). But if $\mathcal{U}$ is an open
                subset containing $x$, and if $a_{n}\rightarrow{x}$, then there is
                an $N\in\mathbb{N}$ such that for all $n>N$ it is true that
                $a_{n}\in\mathcal{U}$, a contradiction.
            \end{proof}
            \begin{fdefinition}{Sequential Space}{Sequential_Space}
                A sequential topological space is a topological space
                $\topspace{X}$ such that for every sequentially open subset
                $\mathcal{U}\subseteq{X}$ it is true that $\mathcal{U}\in\tau$.
            \end{fdefinition}
            As the name suggests, the usefulness of sequential spaces stems from the
            fact that continuity and sequential continuity are equivalent. One
            direction is true of any topological space
            (Thm.~\ref{thm:cont_implies_seq_cont}). We now prove the other direction
            in the setting of a sequential space.
            \begin{theorem}
                \label{thm:seq_space_seq_cont_eqiv_cont}%
                If $\topspace[X]{X}$ is a sequential topological space, if
                $\topspace[Y]{Y}$ is a topological space, and if $f:X\rightarrow{Y}$
                is a sequentially continuous function, then $f$ is continuous.
            \end{theorem}
            \begin{proof}
                For suppose not. Then there is a open subset
                $\mathcal{V}\in\tau_{Y}$ such that $f^{\minus{1}}[\mathcal{V}]$ is
                not open. But $\topspace[X]{X}$ is sequential, and thus if
                $f^{\minus{1}}[\mathcal{V}]$ is not open, then it is not
                sequentially open (Def.~\ref{def:Sequential_Space}). But then there
                is a sequence $a:\mathbb{N}\rightarrow{X}$ and a point
                $x\in{f}^{\minus{1}}[\mathcal{V}]$ such that $a_{n}\rightarrow{x}$
                but for all $N\in\mathbb{N}$ there is an $n\in\mathbb{N}$ with
                $n>N$ such that $a_{n}\notin{f}^{\minus{1}}[\mathcal{V}]$
                (Def.~\ref{def:Sequentially_Open}). But $f$ is sequentially
                continuous, and thus if $a_{n}\rightarrow{x}$, then
                $f(a_{n})\rightarrow{f}(x)$
                (Def.~\ref{def:Sequentially_Continuous}). But $\mathcal{V}$ is open
                and $f(x)\in\mathcal{V}$. Therefore if $f(a_{n})\rightarrow{f}(x)$,
                then there is an $N\in\mathbb{N}$ such that for all $n\in\mathbb{N}$
                with $n>N$, it is true that $f(a_{n})\in\mathcal{V}$. But then for
                all $n>N$ it is true that $a_{n}\in{f}^{\minus{1}}[\mathcal{V}]$, a
                contradiction. Therefore, $f$ is continuous.
            \end{proof}
            Two amazing equivalent definitions of sequential spaces that we will not
            prove since these will not be used.
            \begin{itemize}
                \item $\topspace{X}$ is sequential if and only if it is the quotient
                    of a first countable space.
                \item $\topspace{X}$ is sequential if and only if it is the quotient
                    of a metrizable space.
            \end{itemize}
            In just about every setting we will be working with first countable
            spaces. It would be nice to know that first countable spaces are
            sequential, and indeed they are.
            \begin{theorem}
                \label{thm:First_Countable_Implies_Sequential}%
                If $\topspace{X}$ is a first countable topological space, then it
                is a sequential topological space.
            \end{theorem}
            \begin{proof}
                For suppose not. Then there is a sequentially open subset
                $\mathcal{U}\subseteq{X}$ such that $\mathcal{U}$ is not open
                (Def.~\ref{def:Sequential_Space}). But since $\topspace{X}$ is first
                countable, for all $x\in\mathcal{U}$ there is a countable
                neighborhood basis. By the axiom of choice there is a
                function $\mathcal{B}:\mathcal{U}\rightarrow\powset{\tau}$ such that
                for all $x\in\mathcal{U}$, $\mathcal{B}_{x}$ is a countable
                neighborhood basis of $x$. But if for all $x\in\mathcal{U}$ it is
                true that $\mathcal{B}_{x}$ is countable, then there is surjective
                function $\mathcal{V}_{x}:\mathbb{N}\rightarrow\mathcal{B}_{x}$.
                Then there exists an $N\in\mathbb{N}$ such that
                $\mathcal{V}_{x,N}\subseteq\mathcal{U}$. For suppose not and let
                $B:\mathbb{N}\rightarrow{X}$ be defined by:
                \begin{equation}
                    B_{n}=\bigcap_{k\in\mathbb{Z}_{n}}\mathcal{V}_{x,k}
                \end{equation}
                Since $B_{n}$ is the intersection of finitely many open sets, it is
                open. Moreover it is non-empty since $x\in{B}_{n}$ for all $n$.
                But then $B_{n}$ is an open neighborhood about $x$, and since
                $\mathcal{B}_{x}$ is a neighborhood basis there is an element
                $V\in\mathcal{B}_{x}$ such that $V\subseteq{B}_{n}$. But
                $\mathcal{V}:\mathbb{N}\rightarrow\mathcal{B}_{x}$ is a surjection,
                and hence there is an $N\in\mathbb{N}$ such that
                $\mathcal{V}_{x,N}=V$. But by hypothesis,
                $\mathcal{V}_{x,N}\nsubseteq\mathcal{U}$ and hence there is an
                element $y\in\mathcal{V}_{x,N}$ such that $y\notin\mathcal{U}$.
                Therefore we have shown that the sequence $A_{n}$ defined by:
                \begin{equation}
                    A_{n}=\{\,y\in{B}_{n}\;|\;y\not\in\mathcal{U}\,\}
                \end{equation}
                is non-empty for all $n\in\mathbb{N}$, and hence by the axiom of
                (countable) choice there is a sequence $y:\mathbb{N}\rightarrow{X}$
                such that $y_{n}\in{A}_{n}$ for all $n\in\mathbb{N}$. That is,
                for all $n\in\mathbb{N}$, $y_{n}\in{B}_{n}$ and
                $y_{n}\notin\mathcal{U}$. But if $y_{n}\in{B}_{n}$ for all
                $n\in\mathbb{N}$, then $y_{n}\rightarrow{x}$. For if not, then there
                is an open set $U\in\tau$ such that $x\in{U}$ and for all
                $N\in\mathbb{N}$ there exists an $n>N$ such that $y_{n}\notin{U}$.
                But $\mathcal{B}_{x}$ is a neighborhood basis of $x$, and hence
                there is a $V\in\mathcal{B}_{x}$ such that $V\subseteq{U}$. But
                $\mathcal{V}_{x}:\mathbb{N}\rightarrow\mathcal{B}_{x}$ is a
                surjection, and hence there is an $N\in\mathbb{N}$ such that
                $\mathcal{V}_{x,N}=V$. But then for all $n>N$,
                $B_{n}\subseteq\mathcal{V}_{x,N}$ and thus $B_{n}\subseteq{U}$.
                But then for all $n>N$, $y_{n}\in{U}$, a contradiction. Hence,
                $y_{n}\rightarrow{x}$. But for all $n\in\mathbb{N}$,
                $y_{n}\notin\mathcal{U}$. Thus $y_{n}$ is a sequence such that
                $y_{n}\rightarrow{x}$, but for all $N\in\mathbb{N}$ there is an
                $n\in\mathbb{N}$ with $n>N$ such that $y_{n}\notin\mathcal{U}$, a
                contradiction since $x\in\mathcal{U}$ and $\mathcal{U}$ is
                sequentially open (Def.~\ref{def:Sequentially_Open}). Thus, for all
                $x\in\mathcal{U}$ there is an open subset $\mathcal{V}_{x,N}$ such
                that $x\in\mathcal{V}_{x,N}$ and
                $\mathcal{V}_{x,N}\subseteq\mathcal{U}$. But then $\mathcal{U}$ is
                simply the union over all of these open sets, and is thus open,
                a contradiction. Hence, $\topspace{X}$ is sequential.
            \end{proof}
            And now, our useful corollary.
            \begin{theorem}
                \label{thm:First_Countable_Implies_Seq_Cont_is_Cont}%
                If $\topspace[X]{X}$ is a first countable topological space, if
                $\topspace[Y]{Y}$ is a topological space, and if $f:X\rightarrow{Y}$
                is sequential continuous, then $f$ is continuous.
            \end{theorem}
            \begin{proof}
                For since $\topspace[X]{X}$ is first countable, it is sequential
                (Thm.~\ref{thm:First_Countable_Implies_Sequential}). But if
                $\topspace[X]{X}$ is a sequential topological space and if $f$ is
                sequentially continuous, then $f$ is continuous
                (Thm.~\ref{thm:seq_space_seq_cont_eqiv_cont}). Therefore, $f$ is
                continuous.
            \end{proof}
            It's laborious to show a certain space is first countable, especially in
            the case of manifold theory, and so we rely on the following theorems.
            \begin{theorem}
                \label{thm:Locally_Metrizable_is_First_Countable}%
                If $\topspace{X}$ is a locally metrizable topological space, then it
                is first countable.
            \end{theorem}
            \begin{proof}
                For suppose not. Then there is a point $x\in{X}$ with no countable
                neighborhood basis. But if $\topspace{X}$ is locally metrizable,
                then there is an open subset $\mathcal{U}$ such that
                $x\in\mathcal{U}$ and $\topspace[\mathcal{U}]{\mathcal{U}}$ is
                metrizable, where $\tau_{\mathcal{U}}$ is the subspace topology. But
                then there is a metric
                $d:\mathcal{U}\times\mathcal{U}\rightarrow\nspace[]$ such that
                $d$ induces $\tau_{\mathcal{U}}$. Let $\mathcal{B}\subseteq\tau$ be
                defined by:
                \begin{equation}
                    \mathcal{B}=\{\,\rball{n^{\minus{1}}}{\metspace{\mathcal{U}}}{x}
                        \;|\;n\in\mathbb{N}^{+}\}
                \end{equation}
                That is, the set of all open balls about $x$ of radius $1/n$.
                Suppose $\mathcal{V}\in\tau$ is such that $x\in\mathcal{V}$. But
                then $x\in\mathcal{V}\cap\mathcal{U}$. But
                $\mathcal{V}\cap\mathcal{U}$ is an open subset of $\mathcal{U}$, and
                thus there is an $r>0$ such that:
                \begin{equation}
                    \rball{r}{\metspace{\mathcal{U}}}{x}\subseteq\mathcal{V}
                \end{equation}
                but by Archimede's Theorem, there is an $N\in\mathbb{N}$ such that
                $N>r$. But it is true that
                $\rball{N^{\minus{1}}}{\metspace{\mathcal{U}}}{x}\in\mathcal{B}$,
                and hence $\mathcal{B}$ is a countable neighborhood basis of $x$,
                a contradiction. Thus, $\topspace{X}$ is first countable.
            \end{proof}
        \subsection{Various Types of Compactness}
            \begin{fdefinition}{$\sigma$ Compact}{Sigma_Compact}
                A $\sigma$ compact topological space is a topological space
                $\topspace{X}$ such that there exists a sequence
                $K:\mathbb{N}\rightarrow\powset{X}$ of compact subsets of $X$ such
                that:
                \begin{equation*}
                    X=\bigcup_{n\in\mathbb{N}}K_{n}
                \end{equation*}
            \end{fdefinition}
            This definition gives the following triviality.
            \begin{theorem}
                \label{thm:Compact_Implies_Sigma_Compact}%
                If $\topspace{X}$ is a compact topological space, then it is
                $\sigma$ compact.
            \end{theorem}
            \begin{proof}
                For let $K:\mathbb{N}\rightarrow\powset{X}$ be defined by
                $K_{n}=X$. Then $K_{n}$ is compact for all $n$ and
                $\bigcup{K}_{n}=X$. Thus, $\topspace{X}$ is $\sigma$ compact
                (Def.~\ref{def:Sigma_Compact}).
            \end{proof}
            \begin{fdefinition}{Lindel\"{o}f Topological Space}{Lindelof_Space}
                A Lindel\"{o}f topological space is a topological space $(X,\tau)$
                such that for every open cover $\mathcal{O}$ of $X$ there exists a
                countable subcover.
            \end{fdefinition}
            \begin{theorem}
                \label{thm:Second_Countable_Implies_Lindelof}%
                If $\topspace{X}$ is a second countable topological space, then it
                is Lindel\"{o}f.
            \end{theorem}
            \begin{proof}
                For suppose not. Then there exists an open cover $\mathcal{O}$
                with no countable subcover (Def.~\ref{def:Lindelof_Space}). But
                if $\topspace{X}$ is second countable, then there is a countable
                basis $\mathcal{B}$ of $\tau$. But if $\mathcal{B}$ is a basis,
                and since $\mathcal{O}$ is an open cover, for all
                $\mathcal{V}\in\mathcal{O}$ it is true that $\mathcal{V}$ is
                open and thus there is an element $\mathcal{U}\in\mathcal{B}$
                such that $\mathcal{U}\subseteq\mathcal{V}$. That is, the
                function $F:\mathcal{O}\rightarrow\powset{\mathcal{B}}$ defined
                by:
                \begin{equation}
                    F(\mathcal{V})=\{\,\mathcal{U}\in\mathcal{B}\;|\;
                        \mathcal{U}\subseteq\mathcal{V}\,\}
                \end{equation}
                is such that $F(\mathcal{V})\ne\emptyset$ for all
                $\mathcal{V}\in\mathcal{O}$. But then
                $F[\mathcal{O}]\subseteq\powset{\mathcal{B}}$ is a non-empty subset
                of $\powset{B}$ such that $\emptyset\notin{F}[\mathcal{O}]$. Hence
                by the axiom of choice there is a function
                $G:F[\mathcal{O}]\rightarrow\mathcal{B}$ such that for all
                $\Delta\in{F}[\mathcal{O}]$, $G(\Delta)\in\Delta$. Let
                $B=G\big[F[\mathcal{O}]\big]$. But $\mathcal{B}$ is countable and
                $B\subseteq\mathcal{B}$, and thus $B$ is countable. Moreover,
                $F\circ{G}:\mathcal{O}\rightarrow{B}$ is surjective by the
                definition of $B$ and hence there exists a right inverse
                $H:B\rightarrow\mathcal{O}$. And since $B$ is countable,
                $H[B]$ is a countable subset of $\mathcal{O}$. But $\mathcal{O}$ has
                no countable subcover, and hence there is an $x\in{X}$ such that
                $x\notin\bigcup{H}[B]$. But $\mathcal{O}$ is a cover of $X$, and
                thus there is a $\mathcal{V}\in\mathcal{O}$ such that
                $x\in\mathcal{V}$. And since $\mathcal{B}$ is a basis, there is an
                element $\mathcal{U}_{1}\in\mathcal{B}$ such that
                $x\in\mathcal{U}_{1}$. But then $x\in\mathcal{U}_{1}\cap\mathcal{V}$
                and since $\mathcal{B}$ is a basis, there is an element
                $\mathcal{U}_{2}\in\mathcal{B}$ such that $x\in\mathcal{U}_{2}$ and
                $\mathcal{U}_{2}\subseteq\mathcal{U}_{1}\cap\mathcal{V}$. But then
                $H(\mathcal{U}_{2})$ is an element of $H[B]$ such that
                $\mathcal{U}_{2}\subseteq{H}(\mathcal{U}_{2})$, and hence
                $x\in{H}[\mathcal{U}_{2}]$. A contradiction, since
                $x\notin\bigcup{H}[B]$. Therefore, $\topspace{X}$ is Lindel\"{o}f.
            \end{proof}
            \begin{theorem}
                \label{thm:Sigma_Compact_Implies_Lindelof}%
                If $\topspace{X}$ is a $\sigma$ compact topological space, then it
                is Lindel\"{o}f.
            \end{theorem}
            \begin{proof}
                For suppose not. Then there exists an open cover $\mathcal{O}$ of
                $X$ with no countable subcover. But $X$ is $\sigma$ compact, and
                hence there is a sequence $K:\mathbb{N}\rightarrow\powset{X}$ of
                compact sets such that $X=\bigcup{K}_{n}$
                (Def.~\ref{def:Sigma_Compact}). But then for all $n\in\mathbb{N}$,
                $K_{n}$ is a subset of $X$, and hence $\mathcal{O}$ is an open cover
                of $K_{n}$. But by hypothesis, $K_{n}$ is compact and hence there is
                a finite subcover $\mathscr{D}\subseteq\mathcal{O}$ of $K_{n}$. That
                is, if we define the sequence
                $A_{n}:\mathbb{N}\rightarrow\powset{\mathcal{O}}$ by:
                \begin{equation}
                    A_{n}=\{\mathscr{D}\in\powset{\mathcal{O}}\;|\;
                        \mathscr{D}\textrm{ is finite and }
                        K_{n}\subseteq\bigcup\mathscr{D}\,\}
                \end{equation}
                then for all $n\in\mathbb{N}$, $A_{n}$ is non-empty. Hence by the
                axiom of (countable) choice, there is a choice function
                $\Delta:\mathbb{N}\rightarrow\powset{\mathcal{O}}$ such that for all
                $n\in\mathbb{N}$, $\Delta_{n}$ is a finite open subcover of $K_{n}$.
                But then the union of all $\Delta_{n}$ is the countable union of
                finite collections, and is hence countable. But then this collection
                covers $K_{n}$ for all $n\in\mathbb{N}$, and hence covers
                $\bigcup{K}_{n}$. But $\bigcup{K}_{n}=X$, a contradiction since
                $\mathcal{O}$ has no countable subcover. Thus, $\topspace{X}$ is
                Lindel\"{o}f.
            \end{proof}
            This theorem reverses if we add locally compact. The requirement of
            local compactness can be seen by examining the irrational numbers with
            the subspace topology. This is Lindel\"{o}f (since it is second
            countable), but it is not $\sigma$ compact. For any compact subset of
            the irrationals must have empty interior, and by the Baire category
            theorem the irrationals cannot be written as the countable union of
            nowhere dense subsets. Hence they cannot possibly $\sigma$ compact.
            \begin{fdefinition}{Locally Compact Topological Space}{Locally_Compact}
                A locally compact topological space is a topological space
                $\topspace{X}$ such that for all $x\in{X}$ there exists a compact
                subset $K\subseteq{X}$ and an open set $\mathcal{U}\in\tau$ such
                that $x\in\mathcal{U}$ and $\mathcal{U}\subseteq{K}$.
            \end{fdefinition}
            \begin{theorem}
                \label{thm:Loc_Comp_and_Lindelof_Implies_Sigma_Comp}%
                If $\topspace{X}$ is a locally compact Lindel\"{o}f space, then it
                is $\sigma$ compact.
            \end{theorem}
            \begin{proof}
                For if $\topspace{X}$ is locally compact, then for all $x\in{X}$
                there is a compact set $K\subseteq{X}$ and an open set
                $\mathcal{U}\in\tau$ such that $x\in\mathcal{U}$ and
                $\mathcal{U}\subseteq{K}$ (Def.~\ref{def:Locally_Compact}).
                Invoking the axiom of choice, there is a function
                $A:X\rightarrow\tau\times\powset{X}$ such that for all $x\in{X}$
                $A_{x}=(\mathcal{U},K)$ where $x\in\mathcal{U}$ and
                $\mathcal{U}\subseteq{K}$, where $K$ is compact. But then the
                collection of all such $\mathcal{U}$ is an open cover of $X$. But
                $X$ is Lindel\"{o}f and hence there is a countable subcover. But
                then the subcollection of all $K$ form a countable collection of
                compact sets that cover $X$. Hence, $\topspace{X}$ is $\sigma$
                compact (Def.~\ref{def:Sigma_Compact}).
            \end{proof}
            \begin{fdefinition}{Sequentially Compact}{Sequentially_Compact}
                A sequentially compact topological space is a topological space
                $\topspace{X}$ such that for every sequence
                $a:\mathbb{N}\rightarrow{X}$ there exists a strictly increasing
                sequence $k:\mathbb{N}\rightarrow\mathbb{N}$ such that
                $a\circ{k}:\mathbb{N}\rightarrow{X}$ converges.
            \end{fdefinition}
            Since sequences are easier to work with then large open covergs, we
            seek a simple constraint that forces compact spaces to be
            sequentially compact. As it turns out, first countability suffices.
            \begin{theorem}
                \label{thm:First_Countable_Compact_is_Seq_Compact}%
                If $\topspace{X}$ is first countable and compact, then it is
                sequentially compact.
            \end{theorem}
            \begin{proof}
                For suppose not. Then there is a sequence
                $a:\mathbb{N}\rightarrow{X}$ with no convergent subsequence.
                But since $X$ is compact, there must be a limit point. For if
                not, then for all $x\in{X}$ there is an open set
                $\mathcal{U}_{x}$ such that only finitely many $n\in\mathbb{N}$
                are such that $a_{n}\in\mathcal{U}_{x}$. But these
                $\mathcal{U}_{x}$ cover $X$, and since $X$ is compact there is
                a finite subcover. But then finitely many such sets contain
                every $a_{n}$, a contradiction since $\mathbb{N}$ is not finite.
                Hence, there is a limit point. But $\topspace{X}$ is first
                countable and hence there is a neighborhood basis
                $\mathcal{B}$ of $x$. Let $B:\mathbb{N}\rightarrow\mathcal{B}$
                be a surjection and let $U_{n}=\bigcap{B}_{k}$ be the
                intersection of the first $n$ elements. Then $U_{n}$ is an open
                subset that contains $x$, and hence there is a $j\in\mathbb{N}$
                such that $a_{j}\in{U}_{n}$, giving us a convergent subsequence.
                A contradiction. Hence, $\topspace{X}$ is sequentially compact.
            \end{proof}
            Lastly, before moving away from compactness issues, the separation
            axioms that manifolds satisfy are often useful and so we prove them.
            \begin{theorem}
                \label{thm:Compact_Hausdorff_is_Regular}%
                If $\topspace{X}$ is a compact Hausdorff topological space, then
                it is regular.
            \end{theorem}
            \begin{proof}
                For suppose $C\subseteq{X}$ is closed, and $x\in{X}\setminus{C}$.
                But closed subsets of compact spaces are compact, and thus $C$ is
                compact. And since $X$ is Hausdorff, for all $y\in{C}$ there are
                open subsets $\mathcal{U}_{y},\mathcal{V}_{y}$ such that
                $x\in\mathcal{U}_{y}$, $y\in\mathcal{V}_{y}$, and
                $\mathcal{U}_{y}\cap\mathcal{V}_{y}=\emptyset$. But the
                $\mathcal{V}_{y}$ cover $C$, and hence there is a finite subcover
                $\mathcal{V}_{n}$. Let $\mathcal{U}=\bigcap\mathcal{U}_{n}$ and
                $\mathcal{V}=\bigcup\mathcal{V}_{n}$. Then since
                $\mathcal{U}$ is the finite intersection of open subsets, it is
                open. And since $\mathcal{V}$ is the union of open subsets, it is
                open. But $x\in\mathcal{U}$, $C\subseteq\mathcal{V}$, and
                $\mathcal{U}\cap\mathcal{V}=\emptyset$. Hence, $\topspace{X}$ is
                regular.
            \end{proof}
            \begin{theorem}
                \label{thm:Compact_Hausdorff_is_Normal}%
                If $\topspace{X}$ is a compact Hausdorff space, then it is
                normal.
            \end{theorem}
            \begin{proof}
                For suppose not. Then there are two disjoint closed sets $C_{1}$
                and $C_{2}$ that cannot be separated by disjoint open subsets.
                But if $\topspace{X}$ is compact and Hausdorff, then it is
                regular (Thm.~\ref{thm:Compact_Hausdorff_is_Regular}). Thus for
                all $x\in{C}_{1}$ there is an open set $\mathcal{U}_{x}$ and an
                open set $\mathcal{V}_{x}$ such that $x\in\mathcal{U}_{x}$,
                $C_{2}\subseteq\mathcal{V}_{x}$, and
                $\mathcal{U}_{x}\cap\mathcal{V}_{x}=\emptyset$. But the
                $\mathcal{V}_{x}$ cover $C_{1}$, and since $C_{1}$ is compact,
                finitely many cover it. Let $U_{k}$ and $V_{k}$ be the
                corresponding finite collections. But
                $C_{2}\subseteq\bigcap{V}_{k}$, and $\bigcap{V}_{k}$ is the
                finite intersection of open subsets, which is therefore open.
                Moreover, $(\bigcap{V}_{k})\cap(\bigcup{U}_{k})=\emptyset$
                since $V_{k}\cap{U}_{k}=\emptyset$ for all $k$. But then
                $\bigcap{V}_{k}$ and $\bigcup{U}_{k}$ are open subsets that
                are disjoint and contain $C_{1}$ and $C_{2}$, which is a
                contradiction. Therefore, $\topspace{X}$ is normal.
            \end{proof}
            \begin{theorem}
                \label{thm:Loc_Comp_and_Hausdorff_is_Regular}%
                If $\topspace{X}$ is locally compact and Hausdorff, then it is
                regular.
            \end{theorem}
            \begin{proof}
                For let $C\subseteq{X}$ be closed and $x\in{X}\setminus{C}$. Since
                $X$ is locally compact there is an open subset
                $\mathcal{U}\in\tau$ and a compact subset $K\subseteq{X}$ such that
                $x\in\mathcal{U}$ and $\mathcal{U}\subseteq{K}$
                (Def.~\ref{def:Locally_Compact}). But since $K$ is compact and $X$
                is Hausdorff, $K$ is closed. But $C$ is closed, and therefore
                $C\cap{K}$ is closed. If $C\cap{K}=\emptyset$, let
                $\mathcal{V}=X\setminus{K}$. Since $K$ is closed,  $\mathcal{V}$ is
                therefore open. But $C\subseteq\mathcal{V}$ and
                $\mathcal{U}\cap\mathcal{V}=\emptyset$, thus separating $x$ and $C$.
                If $C\cap{K}\ne\emptyset$, then since $X$ is Hausdorff, $\{x\}$ is
                closed. But then $(C\cap{K})\cup\{x\}$ is a closed subset of a
                compact set, and is hence compact. But compact Hausdorff spaces are
                regular (Thm.~\ref{thm:Compact_Hausdorff_is_Regular}). Thus there is
                are open subsets $\mathcal{U}_{0},\mathcal{V}_{0}$ such that
                $x\in\mathcal{U}_{0}$, $C\cap{K}\subseteq\mathcal{V}_{0}$ and
                $\mathcal{U}_{0}\cap\mathcal{V}_{0}=\emptyset$.
                Let $\mathcal{V}=\mathcal{V}_{0}\cup(X\setminus{K})$. Then
                $C\subseteq\mathcal{V}$, and
                $\mathcal{V}\cap\mathcal{U}_{0}=\emptyset$, hence separating
                $x$ and $C$.
            \end{proof}
            \begin{theorem}
                \label{thm:Regular_Lindelof_is_Normal}%
                If $\topspace{X}$ is a regular Lindel\"{o}f topological space,
                then it is normal.
            \end{theorem}
            \begin{proof}
                For let $C_{1},C_{2}$ be disjoint closed sets. Since
                $X$ is regular, for all $x\in{C}_{1}$ there are open subsets
                $\mathcal{U}_{x},\mathcal{V}_{x}$ that have disjoint closures
                and such that $x\in\mathcal{U}_{x}$ and
                $C_{2}\subseteq\mathcal{V}_{x}$. But then the collection of all
                $\mathcal{U}_{x}$ together with $X\setminus{C}_{1}$ form an open
                cover of $X$. But $X$ is Lindel\"{o}f and hence there is a
                countable subcover (Def.~\ref{def:Lindelof_Space}). Let
                $\mathcal{U}_{k}$ and $\mathcal{V}_{k}$ be the corresponding
                sets, and define:
                \begin{align}
                    U_{n}&=\mathcal{U}_{n}\setminus\Big(
                        \bigcup_{k\in\mathbb{Z}_{n}}\closure{V_{k}}
                    \Big)\\
                    V_{n}&=\mathcal{V}_{n}\setminus\Big(
                        \bigcup_{k\in\mathbb{Z}_{n}}\closure{U_{k}}
                    \Big)
                \end{align}
                Let $U=\bigcup{U}_{n}$ and $V=\bigcup{V}_{n}$. Then by
                construction, $U\cap{V}=\emptyset$ and $U$ and $V$ contain
                $C_{1}$ and $C_{2}$, respectively. Hence, $\topspace{X}$ is
                normal.
            \end{proof}
            \begin{theorem}
                \label{thm:Sigma_Compact_Loc_Compact_Hausdorff_is_Normal}%
                If $\topspace{X}$ is a locally compact Hausdorff topological
                space that is $\sigma$ compact, then it is normal.
            \end{theorem}
            \begin{proof}
                For if $\topspace{X}$ is locally compact and Hausdorff, then it
                is regular (Thm.~\ref{thm:Loc_Comp_and_Hausdorff_is_Regular}).
                But if $\topspace{X}$ is $\sigma$ compact, then it is
                Lindel\"{o}f (Thm.~\ref{thm:Sigma_Compact_Implies_Lindelof}).
                But regular Lindel\"{o}f spaces are normal
                (Thm.~\ref{thm:Regular_Lindelof_is_Normal}), completing the
                proof.
            \end{proof}
            \begin{fdefinition}{Paracompact}{Paracompact}
                A paracompact topological space is a topological space
                $\topspace{X}$ such that for every open cover $\mathcal{O}$ of $X$,
                there exists a locally finite refinement $\Delta$ of $\mathcal{O}$.
            \end{fdefinition}
            \begin{ftheorem}{Michael's Theorem}
                            {Michaels_Theorem}
                If $\topspace{X}$ is regular and such that every cover
                $\mathcal{O}$ has a refinement $\Delta=\bigcup\mathcal{O}_{k}$
                where each $\mathcal{O}_{k}$ is locally finite, then $X$ is
                paracompact.
            \end{ftheorem}
            \begin{theorem}
                \label{thm:Regular_Lindelof_is_Paracompact}%
                If $\topspace{X}$ is regular and Lindel\"{o}f, then it is
                paracompact.
            \end{theorem}
            \begin{proof}
                For suppose not. But if $X$ is regular and not paracompact, then
                by Michael's theorem there is a cover $\mathcal{O}$ such that
                there is no countably locally finite refinement
                (Thm.~\ref{thm:Michaels_Theorem}). But $X$ is Lindel\"{o}f and
                hence there is a countable subcover $\Delta$. But then
                $\Delta=\bigcup\{B_{n}\}$, where $B_{n}\in\Delta$. And
                $\{B_{n}\}$ is finite, and hence locally finite, which is a
                contradiction. Therefore, $X$ is paracompact.
            \end{proof}
            \begin{theorem}
                \label{thm:Count_Open_Cover_of_Sec_Count_Implies_Sec_Count}%
                If $\topspace{X}$ is a topological space, if
                $\mathcal{O}\subseteq\tau$ is a countable subset of open sets such
                that for all $\mathcal{U}\in\mathcal{O}$,
                $\topspace[\mathcal{U}]{\mathcal{U}}$ is second countable, where
                $\tau_{\mathcal{U}}$ is the subspace topology, then $\topspace{X}$
                is second countable.
            \end{theorem}
            \begin{proof}
                For let $\mathcal{B}$ be the collection of all of the bases for all
                of the $\mathcal{U}\in\mathcal{O}$. Since it is the countable union
                of countable sets, it is countable. But since $\mathcal{U}$ is open
                for all $\mathcal{U}\in\mathcal{O}$, this is a countable open cover
                of $X$. It suffices to show that it is a basis. Let
                $\mathcal{V}\in\tau$ be an open subset. But then:
                \begin{align}
                    \mathcal{V}&=\mathcal{V}\cap{X}\\
                    &=\mathcal{V}\cap\Big(
                        \bigcup_{\mathcal{U}\in\mathcal{O}}\mathcal{U}
                    \Big)\\
                    &=\bigcup_{\mathcal{U}\in\mathcal{O}}
                        \big(\mathcal{V}\cap\mathcal{U}\big)
                \end{align}
                But $\mathcal{V}\cap\mathcal{U}$ is an open subset of the subspace
                $\topspace[\mathcal{U}]{\mathcal{U}}$, and hence there is a subset
                of $\Delta_{\mathcal{V}}\subseteq\mathcal{B}_{\mathcal{U}}$ such
                that $\mathcal{V}\cap\mathcal{U}=\bigcup\Delta_{\mathcal{V}}$. But
                then the entire of $\mathcal{V}$ is the union of all such
                collections, each of which is contained in $\mathcal{B}$, and hence
                $\mathcal{V}$ can be written as the union of elements of
                $\mathcal{B}$. Thus, $\mathcal{B}$ is a basis.
            \end{proof}
            The requirement that the covering collection be open subspaces is
            crucial. The quotient space $\mathbb{R}/R$, where $R$ is the equivalence
            relation generated by $nRm$ for all $n,m\in\mathbb{Z}$, can be thought
            of as a countable collection of rings all glued together at the origin.
            Hence, it can be covered by countably many closed subspaces, each of
            which is homeomorphic to $\nsphere[1]$ in the subspace topology, and
            hence each of which is second countable. However, this space
            $\mathbb{R}/R$ is not even first countable, let alone second countable.
            The point $[0]\in\mathbb{R}/R$ has no countable neighborhood basis.
        \subsection{Connectedness}
            \begin{theorem}
                \label{thm:loc_path_con_imply_path_comps_open}%
                If $\topspace{X}$ is locally path connected, if $x\in{X}$, and if
                $\mathcal{U}\subseteq{X}$ is a path connected component of $X$,
                then $\mathcal{U}$ is open.
            \end{theorem}
            \begin{proof}
                For if $\topspace{X}$ is locally path connected, there is a basis
                $\mathcal{B}$ of open and path connected subsets of $X$. But if
                $\mathcal{U}\subseteq{X}$ is a path connected component, then for
                all $x,y\in\mathcal{U}$ there is a path
                $\gamma:[0,1]\rightarrow\mathcal{U}$ connecting $x$ and $y$, and for
                all $z\in{X}$ such that $z\notin\mathcal{U}$, there is no path
                between $x$ and $z$. But $\mathcal{B}$ is a basis, and hence for
                all $x\in\mathcal{U}$ there is a $B\in\mathcal{B}$ such that
                $x\in{B}$. By choice, we get a function
                $B:\mathcal{U}\rightarrow\mathcal{B}$. Moreover, since
                $B\in\mathcal{B}$, it is path connected. But then for all
                $x\in\mathcal{U}$, $x\in{B}_{x}$, and since $B_{x}$ is path
                connected it is true that $B_{x}\subseteq\mathcal{U}$ since
                $\mathcal{U}$ is a path connected component. But then
                $\mathcal{U}=\bigcup{B}_{x}$, which is the union of open sets, and
                hence $\mathcal{U}$ is open.
            \end{proof}
            \begin{theorem}
                \label{thm:Loc_Path_and_Con_Imply_Path_Con}
                If $\topspace{X}$ is locally path connected and connected, then it
                is path connected.
            \end{theorem}
            \begin{proof}
                For if not then there are two points $x,y\in{X}$ with no path
                between them. But the since $\topspace{X}$ is locally path
                connected, the path connected components of $x$ and $y$ are open
                (Thm.~\ref{thm:loc_path_con_imply_path_comps_open}). But let
                $\mathcal{U}$ be the path connected component containing $x$, and
                let $\mathcal{V}$ be the union of all other path connected
                components. Then $\mathcal{V}$ is non-empty since $y\in\mathcal{V}$,
                and hence $\mathcal{U}$ and $\mathcal{V}$ are non-empty disjoint
                open subsets that cover $X$, a contradiction since $X$ is connected.
            \end{proof}
        \subsection{Topological Manifolds}
            \begin{fdefinition}{Locally Euclidean}{Locally_Euclidean}
                A locally Euclidean topological space is a topological space
                $\topspace{X}$ such that for all $x\in{X}$ there exists an open
                subset $\mathcal{U}\in\tau$ and an $n\in\mathbb{N}$ such that
                $x\in\mathcal{U}$ and $\mathcal{U}$ is homeomorphic to an open
                subset of $\nspace$.
            \end{fdefinition}
            \begin{theorem}
                \label{thm:Equiv_Def_Loc_Euclidean}%
                If $\topspace{X}$ is locally Euclidean, then for all $x\in{X}$ there
                is an open subset $\mathcal{U}\in\tau$ and an $n\in\mathbb{N}$ such
                that $\mathcal{U}$ is homeomorphic to $\nspace$.
            \end{theorem}
            \begin{proof}
                For if $\topspace{X}$ is locally Euclidean, then for all $x\in{X}$
                there is an open subset $\mathcal{V}\in\tau$ and an $n\in\mathbb{N}$
                such that $x\in\mathcal{V}$ and $\mathcal{V}$ is homeomorphic to an
                open subset of $\nspace$. But then there is an injective continuous
                open mapping $\varphi:\mathcal{V}\rightarrow\nspace$. Let
                $\vector{y}=\varphi(x)$. But since $\varphi$ is an open mapping,
                and since $\mathcal{V}$ is open, $\varphi[\mathcal{V}]$ is an open
                subset of $\nspace$. But $\vector{y}=\varphi(x)$, and hence
                $\vector{y}\in\varphi[\mathcal{V}]$. But if $\varphi[\mathcal{V}]$
                is open and $\vector{y}\in\varphi[\mathcal{V}]$, then there is an
                $r>0$ such that the open ball $B$ defined by:
                \begin{equation}
                    B=\rball{r}{\metspace[\norm{\cdot}_{2}]{\nspace}}{\vector{y}}
                \end{equation}
                is contained in $\varphi[\mathcal{V}]$. But $\varphi$ is continuous,
                and open balls are open, and hence
                $\varphi^{\minus{1}}[B]$ is an open subset of $\mathcal{V}$.
                Moreover, since $\vector{y}\in{B}$,
                $x\in\varphi^{\minus{1}}[B]$.
                But $\varphi$ is an injective continuous open mapping, and thus the
                restriction of $\varphi$ to an open subset is an injective
                continuous open mapping. Hence, $\varphi|_{\varphi^{\minus{1}}[B]}$
                is a homeomorphism onto it's image, which is $B$. And since open
                balls in $\nspace$ are homeomorphic to $\nspace$,
                $\varphi^{\minus{1}}[B]$ is homeomorphic to $\nspace$. Thus, there
                is an open subset $\varphi^{\minus{1}}[B]$ containing $x$ and an
                $n\in\mathbb{N}$ such that $\varphi^{\minus{1}}[B]$ is homeomorphic
                to $\nspace$.
            \end{proof}
            \begin{theorem}
                \label{thm:Loc_Euc_Existence_of_Basis_of_nspace_Sets}%
                If $\topspace{X}$ is a locally Euclidean topological space, then
                there exists a basis $\mathcal{B}$ such that for all
                $\mathcal{U}\in\mathcal{B}$ there is an $n\in\mathbb{N}$ such that
                $\mathcal{U}$ is homeomorphic to $\nspace$.
            \end{theorem}
            \begin{proof}
                For if $\topspace{X}$ is locally Euclidean, then for all $x\in{X}$
                there is an open subset $\mathcal{U}_{x}\in\tau$ and an
                $n\in\mathbb{N}$ such that $\mathcal{U}_{x}$ is homeomorphic to
                $\nspace$ (Thm.~\ref{thm:Equiv_Def_Loc_Euclidean}). Let
                $\varphi_{x}:\mathcal{U}_{x}\rightarrow\nspace$ be such a
                homeomorphism, and let $\mathcal{B}_{x}$ be the set:
                \begin{equation}
                    \mathcal{B}_{x}=\{\,
                        \varphi_{x}^{\minus{1}}\big[
                            \rball{r}{\metspace[\norm{\cdot}_{2}]{\nspace}}
                            {\vector{y}}\big]
                        \;|\;r>0,\,\vector{y}\in\nspace\,\}
                \end{equation}
                Then by construction, every element of $\mathcal{B}_{x}$ is
                homeomorphic to $\nspace$. Let $\mathcal{B}$ be the collection of
                all such sets for all $x\in{X}$. If $\mathcal{U}$, $\mathcal{V}$ are
                elements of $\mathcal{B}$, then there is an $x\in{X}$ such that
                $\mathcal{U}\in\mathcal{B}_{x}$. Let
                $y\in\mathcal{U}\cap\mathcal{V}$ and let $\vector{y}$ be the image
                of $y$ under $\varphi_{x}$. But $\mathcal{U}\cap\mathcal{V}$ is
                open, and hence there is an $r>0$ such that the ball about
                $\vector{y}$ is contained in the image of
                $\varphi_{x}[\mathcal{U}\cap\mathcal{V}]$. But this $r$ ball is
                contained in $\mathcal{B}$. Hence, $\mathcal{B}$ is a basis.
            \end{proof}
            \begin{theorem}
                \label{thm:Loc_Euc_Existence_of_Basis_of_Precompact_Balls}%
                If $\topspace{X}$ is a locally Euclidean topological space, then
                there is a basis $\mathcal{B}$ such that for all
                $\mathcal{U}\in\mathcal{B}$ it is true that $\mathcal{U}$ is
                precompact in $\tau$ and such that there exists an $n\in\mathbb{N}$
                such that $\mathcal{U}$ is homeomorphic to $\nspace$.
            \end{theorem}
            \begin{proof}
                For by Thm.~\ref{thm:Loc_Euc_Existence_of_Basis_of_nspace_Sets},
                there is a basis $\mathcal{B}$ of $\tau$ such that for all
                $\mathcal{U}\in\mathcal{B}$ there is an $n\in\mathbb{N}$ such that
                $\mathcal{U}$ is homeomorphic to $\nspace$. Let
                $\varphi_{\mathcal{U}}:\mathcal{U}\rightarrow\nspace$ be such a
                homeomorphism. Define $\mathcal{B}_{x}$ by:
                \begin{equation}
                    \mathcal{B}_{x}=\{\,
                        \varphi_{\mathcal{U}}^{\minus{1}}\big[
                            \rball{r}{\metspace[\norm{\cdot}_{2}]{\nspace}}
                            {\vector{y}}\big]\;|\;r>0,\,\vector{y}\in\nspace\,\}
                \end{equation}
                But by the Heine-Borel theorem, for all
                $\mathcal{V}\in\mathcal{B}_{x}$,
                $\closure[\nspace]{\varphi_{\mathcal{U}}[\mathcal{V}]}$ is compact
                in $\nspace$, and since $\varphi_{\mathcal{U}}$ is a homeomorphism,
                $\closure{\mathcal{V}}$ is compact in $\mathcal{U}$. But then
                $\closure{\mathcal{V}}$ is compact in $X$. The collection of all
                such $\mathcal{B}_{x}$ is thus a basis of precompact subsets that
                are homeomorphic to open balls in $\nspace$, which are homeomorphic
                to $\nspace$.
            \end{proof}
            \begin{theorem}
                \label{thm:Loc_Euc_is_Loc_Compact}%
                If $\topspace{X}$ is locally Euclidean, then it is locally compact.
            \end{theorem}
            \begin{proof}
                For if $\topspace{X}$ is locally Euclidean, then there exists a
                basis $\mathcal{B}$ of precompact coordinate balls
                (Thm.~\ref{thm:Loc_Euc_Existence_of_Basis_of_Precompact_Balls}). But
                then for all $x\in{X}$ there is a $\mathcal{U}\in\mathcal{B}$ such
                that $x\in\mathcal{U}$ and $\closure{\mathcal{U}}$ is compact. Thus,
                $\topspace{X}$ is locally compact (Def.~\ref{def:Locally_Compact}).
            \end{proof}
            \begin{theorem}
                \label{thm:Loc_Euc_Implies_Loc_Met}%
                If $\topspace{X}$ is locally Euclidean, then it is locally
                metrizable.
            \end{theorem}
            \begin{proof}
                For if $\topspace{X}$ is locally Euclidean, then for all $x\in{X}$
                there is an $n\in\mathbb{N}$ and a $\mathcal{U}\in\tau$ such that
                $x\in\mathcal{U}$ and $\mathcal{U}$ is homeomorphic to
                $\nspace$ (Thm.~\ref{thm:Equiv_Def_Loc_Euclidean}). But
                $\nspace$ is metrizable, and thus $\mathcal{U}$ is metrizable.
                Hence, $X$ is locally metrizable.
            \end{proof}
            \begin{theorem}
                \label{thm:Loc_Euc_is_First_Countable}%
                If $\topspace{X}$ is locally Euclidean, then it is first
                countable.
            \end{theorem}
            \begin{proof}
                For if $X$ is locally Euclidean, then it is locally metrizable
                (Thm.~\ref{thm:Loc_Euc_Implies_Loc_Met}). But locally
                metrizable spaces are first countable
                (Thm.~\ref{thm:Locally_Metrizable_is_First_Countable}).
            \end{proof}
            \begin{theorem}
                \label{thm:Loc_Euc_Haus_is_Regular}%
                If $\topspace{X}$ is locally Euclidean and Hausdorff, then it is
                regular.
            \end{theorem}
            \begin{proof}
                For if $\topspace{X}$ is locally Euclidean, then it is locally
                compact (Thm.~\ref{thm:Loc_Euc_is_Loc_Compact}). But locally
                compact Hausdorff spaces are regular
                (Thm.~\ref{thm:Loc_Comp_and_Hausdorff_is_Regular}). Thus,
                $X$ is regular.
            \end{proof}
            \begin{theorem}
                \label{thm:Comp_Sub_of_Loc_Euc_is_Seq_Comp}%
                If $\topspace{X}$ is locally Euclidean, and if $C\subseteq{X}$
                is compact, then it is sequentially compact.
            \end{theorem}
            \begin{proof}
                For locally Euclidean spaces are first countable
                (Thm.~\ref{thm:Loc_Euc_is_First_Countable}) and every subspace
                of a first countable space is first countable. But then $C$ is
                a compact first countable space, and is therefore sequentially
                compact (Thm.~\ref{thm:First_Countable_Compact_is_Seq_Compact}).
            \end{proof}
            \begin{fdefinition}{Topological Manifold}{Topological_Manifold}
                A topological manifold is a locally Euclidean, Hausdorff, second
                countable topological space of constant dimension.
            \end{fdefinition}
            \begin{theorem}
                \label{thm:Manifolds_are_Lindelof}%
                If $\topspace{X}$ is a topological manifold, then it is
                Lindel\"{o}f.
            \end{theorem}
            \begin{proof}
                For if $X$ is a topological manifold, then it is second countable
                (Def.~\ref{def:Topological_Manifold}). But second countable
                topological spaces are Lindel\"{o}f
                (Thm.~\ref{thm:Second_Countable_Implies_Lindelof}). Thus,
                $\topspace{X}$ is Lindel\"{o}f.
            \end{proof}
            \begin{theorem}
                \label{thm:Manifolds_are_Sigma_Compact}%
                If $\topspace{X}$ is a topological manifold, then it is $\sigma$
                compact.
            \end{theorem}
            \begin{proof}
                For if $X$ is a topological manifold, then it is Lindel\"{o}f
                (Thm.~\ref{thm:Manifolds_are_Lindelof}). But topological manifolds
                are locally Euclidean (Def.~\ref{def:Locally_Euclidean}) and locally
                Euclidean spaces are locally compact
                (Thm.~\ref{thm:Loc_Euc_is_Loc_Compact}). But if $\topspace{X}$ is
                locally compact and Lindel\"{o}f, then it is $\sigma$ compact
                (Thm.~\ref{thm:Loc_Comp_and_Lindelof_Implies_Sigma_Comp}).
            \end{proof}
            \begin{theorem}
                \label{thm:Loc_Euc_Haus_Sigma_Comp_is_Manifold}%
                If $\topspace{X}$ is a locally Euclidean Hausdorff topological
                space that is $\sigma$ compact, then it is a topological manifold.
            \end{theorem}
            \begin{proof}
                For if $\topspace{X}$ is locally Euclidean, then there is a basis
                $\mathcal{B}$ of precompact coordinate balls
                (Thm.~\ref{thm:Loc_Euc_Existence_of_Basis_of_Precompact_Balls}).
                But if $X$ is $\sigma$ compact, then it is Lindel\"{o}f
                (Thm.~\ref{thm:Sigma_Compact_Implies_Lindelof}). But $\mathcal{B}$
                is an open cover of $X$, and hence there is a countable subcover
                $\Delta$. But then $\Delta$ is a countable collection of open
                subspaces of $X$, each of which is homeomorphic to
                $\nspace$ and hence second countable. Hence $X$ is second countable
                (Thm.~\ref{thm:Count_Open_Cover_of_Sec_Count_Implies_Sec_Count}).
                But if $X$ is locally Euclidean, Hausdorff, and second countable,
                then it is a topological manifold
                (Def.~\ref{def:Topological_Manifold}).
            \end{proof}
            \begin{theorem}
                \label{thm:Loc_Euc_Hausdorff_Lindelof_is_Manifold}%
                If $\topspace{X}$ is a locally Euclidean Hausdorff topological space
                that is Lindel\"{o}f, then $X$ is a topological manifold.
            \end{theorem}
            \begin{proof}
                For if $\topspace{X}$ is locally Euclidean, then it is locally
                compact (Thm.~\ref{thm:Loc_Euc_is_Loc_Compact}). But locally compact
                Lindel\"{o}f spaces are $\sigma$ compact
                (Thm.~\ref{thm:Loc_Comp_and_Lindelof_Implies_Sigma_Comp}). But
                locally Euclidean Hausdorff topological spaces that are $\sigma$
                compact are topological manifolds
                (Thm.~\ref{thm:Loc_Euc_Haus_Sigma_Comp_is_Manifold}). Therefore,
                $\topspace{X}$ is a topological manifold.
            \end{proof}
            \begin{theorem}
                \label{thm:Top_Man_is_Paracompact}%
                If $\topspace{X}$ is a topological manifold, then it is paracompact.
            \end{theorem}
            \begin{proof}
                For if $\topspace{X}$ is a topological manifold, then it is
                locally Euclidean and Hausdorff
                (Def.~\ref{def:Topological_Manifold}). But locally Euclidean
                Hausdorff spaces are regular
                (Thm.~\ref{thm:Loc_Euc_Haus_is_Regular}). But manifolds are
                second countable (Def.~\ref{def:Topological_Manifold}) and
                second countable spaces are Lindel\"{o}f
                (Thm.~\ref{thm:Second_Countable_Implies_Lindelof}). But
                regular Lindel\"{o}f spaces are paracompact
                (Thm.~\ref{thm:Regular_Lindelof_is_Paracompact}). Hence,
                $X$ is paracompact.
            \end{proof}
            \begin{fdefinition}{Topological Group}{Topological_Group}
                A topological group, denoted $\topgroup{G}$, is a topological space
                $\topspace{G}$ and a binary operation $*$ such that $\monoid{G}$ is
                a group, and such that $g:G\times{G}\rightarrow{G}$ defined by
                $g(a,b)=a*b$ is continuous with respect to the product topology on
                $G$, and such that $\nu:G\rightarrow{G}$ defined by
                $\nu(a)=a^{\minus{1}}$, where $a^{\minus{1}}$ is the inverse element
                of $a$ under $*$, is continuous.
            \end{fdefinition}
            \begin{fdefinition}{Continuous Group Action}{Continuous_Group_Action}
                A continuous group action of a topological group $\topgroup{G}$
                on a topological space $\topspace[X]{X}$ is a function
                $\Theta:G\times{X}\rightarrow{X}$ such that for all $x\in{X}$ and
                for all $a,b\in{G}$, the following are true:
                \begin{align*}
                    \Theta(e,x)&=x\\
                    \Theta\big(a,\Theta(b,x)\big)&=\Theta(a*b,x)
                \end{align*}
                where $e$ is the unital element of $G$, and such that $\Theta$ is
                continuous with respect to the product topology.
            \end{fdefinition}
            \begin{theorem}
                \label{thm:Quotient_by_Compact_T2_Group_Preserves_T2}%
                If $\topspace[X]{X}$ is a Hausdorff topological space, if
                $\topgroup{G}$ is a compact Hausdorff topological group, if
                $\Theta$ is a continuous group action of $G$ on $X$, and if
                $\topspace[q]{X/G}$ is the quotient topology formed by the orbits
                of $\Theta$, then $X/G$ is Hausdorff.
            \end{theorem}
            \begin{proof}
                Need to fill in.
            \end{proof}
            \begin{theorem}
                \label{thm:Quotient_by_Compact_T2_Group_Preserves_Sec_Count}%
                If $\topspace[X]{X}$ is a second countable topological space, if
                $\topgroup{G}$ is a compact Hausdorff topological group, if
                $\Theta$ is a continuous group action of $G$ on $X$, and if
                $\topspace[q]{X/G}$ is the quotient topology formed by the orbits
                of $\Theta$, then $X/G$ is second countable.
            \end{theorem}
            \begin{proof}
                Also need to fill in.
            \end{proof}
        \subsection{Problems: Part A}
            \begin{problem}
                (Lee Exercise 1.6) Show that $\mathbb{RP}^{n}$ is Hausdorff and
                second countable.
            \end{problem}
            \begin{solution}
                For $\mathbb{RP}^{n}$ is homeomorphic to the quotient space of
                $\nsphere$ by the multiplicative group $G=\{\minus{1},1\}$ with the
                group action $\Theta:G\times\nsphere\rightarrow\nsphere$ defined by
                $\Theta(n,\vector{s})=n\cdot\vector{s}$ (this is well defined since
                $n=\pm{1}$, and hence $\norm{n\cdot\vector{s}}=1$ and thus
                $n\cdot\vector{s}$ still lies in $\nsphere$). Equipping $G$ with the
                discrete topology makes $\topgroup{G}$ a topological group, and
                $\Theta$ a continuous group action on $\nsphere$. But $G$ is finite,
                and hence compact, and moreover it is Hausdorff since the discrete
                topology is always Hausdorff (it is metrizable, in fact). Thus
                $\nsphere/G$ is the quotient of a second countable Hausdorff space
                by a compact Hausdorff group, and is therefore Hausdorff
                (Thm.~\ref{thm:Quotient_by_Compact_T2_Group_Preserves_T2}) and
                second countable
                (Thm.~\ref{thm:Quotient_by_Compact_T2_Group_Preserves_Sec_Count}).
                Thus, $\mathbb{RP}^{n}$ is Hausdorff and second countable.
            \end{solution}
            \begin{problem}
                (Lee Problem 1.5) Show that if $\topspace{X}$ is a locally Euclidean
                connected Hausdorff space, then it is a manifold if and only if it
                is paracompact.
            \end{problem}
            \begin{solution}
                For topological manifolds are paracompact
                (Thm.~\ref{thm:Top_Man_is_Paracompact}). Going the other way, if $X$
                is locally Euclidean, then there is a basis of precompact open
                subsets $\mathcal{B}$, each of which is homeomorphic to $\nspace$
                (Thm.~\ref{thm:Loc_Euc_Existence_of_Basis_of_Precompact_Balls}). But
                $X$ is paracompact, and hence there is a locally finite refinement
                $\Delta$ of $\mathcal{B}$ (Def.~\ref{def:Paracompact}). Let
                $\mathcal{U}_{0}$ be an element of $\Delta$. Since $\Delta$ is a
                refinement of $\mathcal{B}$, there is an element
                $\mathcal{V}\in\mathcal{B}$ such that
                $\mathcal{U}_{0}\subseteq\mathcal{V}$. But then
                $\closure{\mathcal{U}_{0}}\subseteq\closure{\mathcal{V}}$, and
                $\mathcal{V}$ is precompact, and thus $\closure{\mathcal{V}}$
                is compact. But then $\closure{\mathcal{U}_{0}}$ is a closed subset
                of a compact set, and is hence compact. For all $n\in\mathbb{N}$,
                define $\mathcal{U}_{n}$ by:
                \begin{equation}
                    \mathcal{U}_{n}=\Big\{\,x\in{X}\;|\;
                        \exists_{A:\mathbb{Z}_{n}\rightarrow\Delta}\big(
                            \mathcal{U}_{0}=A_{0},\,x\in{A}_{n-1}\textrm{ and }
                            \forall_{i<n-1}(A_{i}\cap{A}_{i+1}\ne\emptyset)
                        \big)\,\Big\}
                \end{equation}
                That is, the set of all points that are separated from
                $\mathcal{U}_{0}$ by at most $n$ consecutive elements of $\Delta$.
                Then $\mathcal{U}_{n}$ is precompact. We prove by induction. The
                base case of $\mathcal{U}_{0}$ is true from the previous paragraph.
                Suppose it is true for $n\in\mathbb{N}$. Since $X$ is locally
                Euclidean, if $\mathcal{C}\subseteq{X}$ is compact, then it is
                sequentially compact
                (Thm.~\ref{thm:Comp_Sub_of_Loc_Euc_is_Seq_Comp}). But
                $\mathcal{U}_{n+1}$ is the union of $\closure{\mathcal{U}_{n}}$
                and elements of $\mathcal{V}\in\Delta$ such that
                $\mathcal{V}\cap\mathcal{U}_{n}\ne\emptyset$. But every element of
                $\Delta$ is precompact, and since $\closure{\mathcal{U}_{n+1}}$ is
                not compact, there must be infinitely many such $\mathcal{V}$. But
                $\mathcal{V}\cap\mathcal{U}_{n}$ is non
                empty for all such $\mathcal{V}$, and hence by the axiom of choice
                there is a sequence $a:\mathbb{N}\rightarrow\mathcal{U}_{n}$ such
                that $a_{j}$ lies in a distinct $\mathcal{V}$ for all
                $j\in\mathbb{N}$. But $\closure{\mathcal{U}_{n}}$ is compact, and
                hence sequentially compact, and thus there is a convergent
                subsequence $a_{k}:\mathbb{N}\rightarrow\closure{\mathcal{U}_{n}}$
                with a limit $x$. But $x\in\closure{\mathcal{U}_{n}}$ and hence
                there is an open set $V\in\tau$ that has non-empty intersection with
                only finitely many elements of $\Delta$, since $\Delta$ is a locally
                finite refinement. But since $a_{k}$ converges to an element of $V$,
                there is an $N\in\mathbb{N}$ such that for all $j>N$,
                $a_{k_{j}}\in{V}$. But each $a_{k_{j}}$ lies in a different
                $\mathcal{V}\in\Delta$, and hence infinitely many elements of
                $\Delta$ have non-empty intersection with $V$, a contradiction.
                Hence, $\mathcal{U}_{n+1}$ is covered by finitely many elements of
                $\Delta$ and is therefore precompact. Moreover,
                $\bigcup\closure{\mathcal{U}_{n}}=X$. For if $y\in{X}$, let
                $x\in\mathcal{U}_{0}$ be any point. Then since $X$ is locally path
                connected and connected, it is path connected
                (Thm.~\ref{thm:Loc_Path_and_Con_Imply_Path_Con}).
                Let $\gamma:[0,1]\rightarrow{X}$ be a path from $x$ to $y$. But
                $[0,1]$ is compact and hence $\gamma\big[[0,1]\big]$ is a compact
                subset of $X$. But then it is covered by only finitely many elements
                of $\Delta$, and hence $y$ is contained in one of the
                $\mathcal{U}_{n}$. Thus $X$ is $\sigma$ compact
                (Def.~\ref{def:Sigma_Compact}). But locally Euclidean $\sigma$
                compact Hausdorff spaces are topological manifolds
                (Thm.~\ref{thm:Loc_Euc_Haus_Sigma_Comp_is_Manifold}).
            \end{solution}
            \begin{problem}
                Lee Problem 1-7.
            \end{problem}
            \begin{solution}
                Let $\vector{x}\in\nsphere\setminus{N}$, where $N$ is the north
                pole. Let $\Gamma$ be the line through $N$ and $\vector{x}$. We can
                parameterize this as follows:
                \begin{equation}
                    \Gamma(t)=tN+(1-t)\vector{x}
                \end{equation}
                To find when this lies on the $\nspace$ hyperplane of $\nspace[n+1]$
                defined by $(x_{1},\dots,x_{n},0)$ we simply need to find
                $t$ such that $\Gamma(t)=(x_{1},\dots,x_{n},0)$. Solving for the
                last coordinate, we get (Since $N=(0,\dots,0,1)$):
                \begin{equation}
                    t+(1-t)x_{n+1}=0
                    \Longrightarrow
                    t(1-x_{n+1})=\minus{x}_{n+1}
                    \Longrightarrow
                    t=\frac{x_{n+1}}{x_{n+1}-1}
                \end{equation}
                evaluating $\Gamma$ at this particular time obtains:
                \begin{equation}
                    \Gamma\Big(\frac{x_{n+1}}{x_{n+1}-1}\Big)
                        =\frac{1}{1-x_{n+1}}(x_{1},\dots,x_{n},0)
                \end{equation}
                in agreement with $\sigma$. For the south pole we repeat the
                argument, obtaining the curve $\Lambda$ defined by:
                \begin{equation}
                    \Lambda(t)=tS+(1-t)\vector{x}
                \end{equation}
                Solving for $\Lambda(t)=(x_{1},\dots,x_{n},0)$, we look at the last
                component and set this equal to zero:
                \begin{equation}
                    \minus{t}+(1-t)x_{n+1}=0
                    \Longrightarrow
                    \minus{t}(1+x_{n+1})=\minus{x}_{n+1}
                    \Longrightarrow
                    t=\frac{x_{n+1}}{1+x_{n+1}}
                \end{equation}
                Evaluating this $t$ into $\Lambda$ gives:
                \begin{align*}
                    \Lambda\Big(\frac{x_{n+1}}{1+x_{n+1}}\Big)
                    &=\Big(0,\dots,0,\frac{\minus{x}_{n+1}}{1+x_{n+1}}\Big)
                        +\Big(1-\frac{x_{n+1}}{1+x_{n+1}}\Big)
                        (x_{1},\dots,x_{n},x_{n+1})\\
                    &=\Big(0,\dots,0,\frac{\minus{x}_{n+1}}{1+x_{n+1}}\Big)+
                        \Big(\frac{1}{1+x_{n+1}}\Big)(x_{1},\dots,x_{n},x_{n+1})\\
                    &=\frac{(x_{1},\dots,x_{n},0)}{1+x_{n+1}}
                \end{align*}
                To show that $\sigma$ is bijective, it suffices to show that
                $\sigma\circ\sigma^{\minus{1}}$ and $\sigma^{\minus{1}}\circ\sigma$
                are the identity mappings, where:
                \begin{equation}
                    \sigma^{\minus{1}}(X_{1},\dots,X_{n})=
                        \frac{(2X_{1},\dots,2X_{n},\norm{\vector{X}}^{2}-1)}
                            {\norm{\vector{X}}^{2}+1}
                \end{equation}
                But:
                \begin{align*}
                    (\sigma\circ\sigma^{\minus{1}})(\vector{X})&=
                    \sigma\Big(
                        \frac{(2X_{1},\dots,2X_{n},\norm{\vector{X}}^{2}-1)}
                            {\norm{\vector{X}}^{2}+1}
                    \Big)\\
                    &=\frac{1}
                        {1-\frac{\norm{\vector{X}}^{2}-1}{\norm{\vector{X}}^{2}+1}}
                        \Big(\frac{2X_{1}}{\norm{\vector{X}}^{2}+1)},\dots,
                        \frac{2X_{n}}{\norm{\vector{X}}^{2}+1)}\Big)\\
                    &=\frac{1}{\norm{\vector{X}^{2}}+1}\cdot
                        \frac{1}
                        {1-\frac{\norm{\vector{X}}^{2}-1}{\norm{\vector{X}}^{2}+1}}
                        (2X_{1},\dots,2X_{n})\\
                    &=\frac{1}{\norm{\vector{X}}^{2}+1-\norm{\vector{X}}^{2}+1}
                        (2X_{1},\dots,2X_{n})\\
                    &=\frac{1}{2}(2X_{1},\dots,2X_{n})\\
                    &=(X_{1},\dots,X_{n})\\
                    &=\vector{X}
                \end{align*}
                and therefore $\sigma\circ\sigma^{\minus{1}}$ is the identity. Going
                the other way, for $\vector{x}\in\nsphere\setminus\{N\}$ we have:
                \begin{align*}
                    (\sigma^{\minus{1}}\circ\sigma)(\vector{x})
                    &=\sigma^{\minus{1}}\Big(
                        \frac{(x_{1},\dots,x_{n})}{1-x_{n+1}}
                    \Big)\\
                    &=\frac{1}{\norm{\frac{(x_{1},\dots,x_{n})}{1-x_{n+1}}}^{2}+1}
                        \Big(
                            \frac{2x_{1}}{1-x_{n+1}},\dots,\frac{2x_{n}}{1-x_{n+1}},
                            \frac{\norm{(x_{1},\dots,x_{n})}^{2}}{(1-x_{n+1})^{2}}-1
                        \Big)
                \end{align*}
                But since $\vector{x}\in\nsphere{S}\setminus\{N\}$,
                $\norm{\vector{x}}=1$. And:
                \begin{align*}
                    \frac{1}{\norm{\frac{(x_{1},\dots,x_{n})}{1-x_{n+1}}}^{2}+1}
                    &=\frac{(1-x_{n+1})^{2}}
                        {\norm{(x_{1},\dots,x_{n})}^{2}+(1-x_{n+1})^{2}}\\
                    &=\frac{(1-x_{n+1})^{2}}{\norm{\vector{x}}^{2}+1-2x_{n+1}}\\
                    &=\frac{(1-x_{n+1})^{2}}{1+1-2x_{n+1}}\\
                    &=\frac{(1-x_{n+1})^{2}}{2(1-x_{n+1})}\\
                    &=\frac{1-x_{n+1}}{2}
                \end{align*}
                returning to the problem, we then get:
                \begin{align*}
                    (\sigma^{\minus{1}}\circ\sigma)(\vector{x})
                    &=\frac{1-x_{n+1}}{2}\Big(
                        \frac{2x_{1}}{1-x_{n+1}},\dots,\frac{2x_{n}}{1-x_{n+1}},
                        \frac{\norm{(x_{1},\dots,x_{n})}^{2}}{(1-x_{n+1})^{2}}-1
                    \Big)\\
                    &=\frac{1-x_{n+1}}{2}\Big(
                        \frac{2x_{1}}{1-x_{n+1}},\dots,\frac{2x_{n}}{1-x_{n+1}},
                        \frac{1-x_{n+1}^{2}}{(1-x_{n+1})^{2}}-1
                    \Big)\\
                    &=\frac{1-x_{n+1}}{2}\Big(
                        \frac{2x_{1}}{1-x_{n+1}},\dots,\frac{2x_{n}}{1-x_{n+1}},
                        \frac{1+x_{n+1}}{1-x_{n+1}}-1
                    \Big)\\
                    &=\frac{1-x_{n+1}}{2}\Big(
                        \frac{2x_{1}}{1-x_{n+1}},\dots,\frac{2x_{n}}{1-x_{n+1}},
                        \frac{2x_{n+1}}{1-x_{n+1}}
                    \Big)\\
                    &=(x_{1},\dots,x_{n},x_{n+1})
                \end{align*}
                and therefore, $\sigma^{\minus{1}}\sigma$ is the identity. Thus,
                $\sigma$ and $\sigma^{\minus{1}}$ are bijections and inverses of
                each other. The transition map
                $\tilde{\sigma}\circ\sigma^{\minus{1}}$, where $\tilde{\sigma}$ is
                the stereographic graphic projection from the south pole, can be
                computed as follows:
                \begin{align*}
                    (\tilde{\sigma}\circ\sigma^{\minus{1}})(\vector{X})
                    &=\tilde{\sigma}\Big(
                        \frac{2X_{1},\dots,2X_{n},\norm{\vector{X}}^{2}-1}
                            {\norm{\vector{X}}^{2}+1}
                        \Big)\\
                    &=\frac{1}{1+\frac{\norm{\vector{X}}^{2}-1}
                                    {\norm{\vector{X}}^{2}+1}}
                        \Big(\frac{2X_{1}}{\norm{\vector{X}}^{2}+1},\dots,
                            \frac{2X_{n}}{\norm{\vector{X}}^{2}+1}\Big)\\
                    &=\frac{1}{\norm{\vector{X}}^{2}}(X_{1},\dots,X_{n})\\
                    &=\frac{\vector{X}}{\norm{\vector{X}}^{2}}
                \end{align*}
                Since $N$ and $S$ are not included, $\vector{0}$ is not in the
                domain of $\tilde{\sigma}\circ\sigma^{\minus{1}}$, and hence this
                is well defined everywhere and smooth. By symmetry,
                $\sigma\circ\tilde{\sigma}^{\minus{1}}$ is smooth. Hence, these two
                charts constitute a smooth atlas on $\nsphere$ since they cover
                the set and overlap smoothly. Lastly, show that the standard smooth
                structure on $\nsphere$ and the stereographic one are compatible.
                For $i\in\mathbb{Z}_{n}$, let $\varphi_{i}$ be the projection
                mapping of $\mathcal{U}_{i}^{+}$ down to $\nsphere$. We have:
                \begin{align*}
                    (\varphi_{i}\circ\sigma^{\minus{1}})(\vector{X})
                    &=\varphi_{i}\Big(
                        \frac{(2X_{1},\dots,2X_{n},\norm{\vector{X}}^{2}-1)}
                            {\norm{\vector{X}}^{2}+1}
                    \Big)\\
                    &=\frac{(2X_{1},\dots,2X_{i-1},2X_{i+1},\dots,
                            \norm{\vector{X}}^{2}-1)}{\norm{\vector{X}}^{2}+1}
                \end{align*}
                which is smooth. Similarly:
                \begin{align*}
                    (\sigma\circ\varphi_{i}^{\minus{1}})(\vector{X})
                    &=\sigma\Big(
                        \big(x_{1},\dots,x_{i-1},\sqrt{1-\norm{\vector{X}}^{2}},
                        x_{i},\dots,x_{n}\big)\Big)\\
                    &=\frac{(x_{1},\dots,x_{i-1},\sqrt{1-\norm{\vector{X}}^{2}},
                            x_{i+1},\dots,x_{n-1})}{1-x_{n}}
                \end{align*}
                which, since the domain of $\sigma$ does not include $x_{n}=1$, this
                is well defined and smooth. Hence, the standard smooth structure on
                $\nsphere$ is compatible with the stereographic one.
            \end{solution}
            \begin{problem}
                (Lee Problem 1-9) Show that $\mathbb{CP}^{n}$ is a smooth $2n$
                dimensional manifold.
            \end{problem}
            \begin{solution}
                Given a $\vector{z}$, let
                $\uvector{z}=\vector{z}/\norm{\vector{z}}$. Then $[\vector{z}]$ is
                the same as the orbit of $\uvector{z}$ by the rotation group
                $U(1)$ acting on $\nsphere[2n+1]$, and similary the quotient
                topologies are the same. But $U(1)$ is a compact topological group.
                It is compact since it is a closed and bounded subset of Euclidean
                space, since all of the elements of $U(1)$ have norm 1. But then
                $\nsphere[2n+1]/U(1)$ is Hausdorff
                (Thm.~\ref{thm:Quotient_by_Compact_T2_Group_Preserves_T2}) and
                second countable
                (Thm.~\ref{thm:Quotient_by_Compact_T2_Group_Preserves_Sec_Count}).
                Moreover, since it is the quotient of a compact topological space
                ($\nsphere[2n+1]$ is compact), $\mathbb{CP}^{n}$ is compact as well.
                Lastly, we must show that $\mathbb{CP}^{n}$ can be given a smooth
                structure compatible with this quotient topology. For all
                $i\in\mathbb{Z}_{n+1}$, let $\mathcal{U}_{i}$ be the set of all
                $\vector{z}\in\mathbb{C}^{n+1}$ such that the $i^{th}$ component
                $z_{i}$ is non-zero. Let $\mathcal{V}_{i}=q[\mathcal{U}_{i}]$, where
                $q$ is the canonical projection of $\mathbb{C}^{n+1}$ down to
                $\mathbb{CP}^{n}$ sending $\vector{z}\mapsto[\vector{z}]$. Since
                $\mathcal{U}_{i}$ is a saturated set, $\mathcal{V}_{i}$ is therefore
                open and the restriction of $q$ to $\mathcal{U}_{i}$ is a quotient
                map. Let $\varphi_{i}:\mathcal{V}_{i}\rightarrow\mathbb{C}^{n}$
                be defined by:
                \begin{equation}
                    \varphi_{i}[\vector{z}]=\Big(
                        \frac{z_{1}}{z_{i}},\dots,\frac{z_{i-1}}{z_{i}},
                        \frac{z_{i+1}}{z_{i}},\dots,\frac{z_{n+1}}{z_{i}}
                    )
                \end{equation}
                this is well defined, for if $\vector{w}\in[\vector{z}]$,
                then there is a $c\in\mathbb{C}$ such that
                $\vector{w}=c\vector{z}$. But then:
                \begin{align*}
                    \varphi_{i}[\vector{w}]&=\Big(
                        \frac{w_{1}}{w_{i}},\dots,\frac{w_{i-1}}{w_{i}},
                        \frac{w_{i+1}}{w_{i}},\dots,\frac{w_{n+1}}{w_{i}}
                    \Big)\\
                    &=\Big(
                        \frac{cz_{1}}{cz_{i}},\dots,\frac{cz_{i-1}}{cz_{i}},
                        \frac{cz_{i+1}}{cz_{i}},\dots,\frac{cz_{n+1}}{cz_{i}}
                    \Big)\\
                    &=\Big(
                        \frac{z_{1}}{z_{i}},\dots,\frac{z_{i-1}}{z_{i}},
                        \frac{z_{i+1}}{z_{i}},\dots,\frac{z_{n+1}}{z_{i}}
                    \Big)\\
                    &=\varphi_{i}[\vector{z}]
                \end{align*}
                Thus, $\varphi_{i}$ is continuous. Moreover, it is a
                homeomorphism onto it's image, with inverse:
                \begin{equation}
                    \varphi_{i}^{\minus{1}}(z_{1},\dots,z_{n})
                    =[z_{1},\dots,z_{i-1},1,z_{i+1},\dots,z_{n}]
                \end{equation}
                which is continuous. Thus, $\mathcal{V}_{i}$ is homeomorphic to an
                open subset of $\mathbb{C}^{n}$. But $\mathbb{C}^{n}$ is
                homeomorphic to $\nspace[2n]$ (Indeed, set theoretically it simply
                \textit{is} $\nspace[2n]$). This shows that $\mathbb{CP}^{n}$ is
                locally Euclidean, and since it is also Hausdorff and second
                countable, it is therefore a topological manifold
                (Def.~\ref{def:Topological_Manifold}). Lastly, we must show that
                the $\varphi_{i}$ overlap smoothly. But:
                \begin{align*}
                    \varphi_{i}\circ\varphi_{j}^{\minus{1}}(z_{1},\dots,z_{n})
                    &=\varphi_{i}\big(
                        [z_{1},\dots,z_{j-1},1,z_{j+1},\dots,z_{n}]
                    \big)\\
                    &=\Big(
                        \frac{z_{1}}{z_{i}},\dots,\frac{z_{j-1}}{z_{i}},
                        \frac{1}{z_{i}},\frac{z_{j+1}}{z_{i}},\dots,
                        \frac{z_{i-1}}{z_{i}},\frac{z_{i+1}}{z_{i}},\dots,
                        \frac{z_{n}}{z_{i}}
                    \Big)
                \end{align*}
                which is smooth.
            \end{solution}
            \begin{problem}
                (Lee Problem 1-12) Prove that the product of smooth manifolds
                together with a manifold with boundary is a smooth manifold with
                boundary.
            \end{problem}
            \begin{solution}
                We prove by induction on the number of manifolds without boundary.
                In the base case, let $\manifold[M]{M}$ be a smooth manifold without
                boundary and $\manifold[N]{N}$ a smooth manifold with boundary.
                Let $(M\times{N},\tau_{M}\times\tau_{N})$ be the product topological
                space. Since $M$ and $N$ are second countable and Hausdorff,
                $M\times{N}$ is. We must now show that it is locally Euclidean with
                boundary. For all $q\in\textrm{Int}(N)$ there is an open subset
                $\mathcal{V}\in\tau_{N}$ such that $q\in\mathcal{V}$ and
                $\mathcal{V}$ is homeomorphic to $\nspace$. For all $p\in{M}$ there
                is an open subset $\mathcal{U}\in\tau_{M}$ such that
                $p\in\mathcal{U}$ and $\mathcal{U}$ is homeomorphic to $\nspace[m]$.
                But then $(p,q)\in\mathcal{U}\times\mathcal{V}$, and by the
                definition of the product topology,
                $\mathcal{U}\times\mathcal{V}\in\tau_{M}\times\tau_{N}$. Moreover,
                since $\mathcal{U}$ is homeomorphic to $\nspace[m]$ and
                $\mathcal{V}$ is homeomorphic to $\nspace$,
                $\mathcal{U}\times\mathcal{V}$ is homeomorphic to
                $\nspace[m]\times\nspace$, which is homeomorphic to $\nspace[m+n]$.
                Thus for all $(p,q)\in{M}\times\textrm{Int}(N)$ there is an open
                subset containing $(p,q)$ that is homeomorphic to Euclidean space.
                If $q\in\partial{N}$, then there is an open subset
                $\mathcal{V}$ such that $q\in\mathcal{V}$ and $\mathcal{V}$ is
                homeomorphic to $\mathbb{H}^{n}$. But then
                $\mathcal{U}\times\mathcal{V}$ is homeomorphic to
                $\nspace[m]\times\mathbb{H}^{n}$, which is homeomorphic to
                $\mathbb{H}^{n+m}$. Thus, every point $(p,q)\in{M}\times{N}$ is
                locally either $\nspace[m+n]$ or $\mathbb{H}^{m+n}$. That is,
                $(M\times{N},\tau_{M}\times\tau_{N})$ is a topological manifold
                with boundary. Moreover, this shows that $(p,q)$ lies on the
                boundary of $M\times{N}$ if and only if $q\in\partial{N}$. Hence,
                $\partial(M\times{N})=M\times\partial{N}$. We now how to show that
                this is a smooth manifold. Give $p\in{M}$ and $q\in\textrm{Int}(N)$,
                there are smooth charts $(\mathcal{U},\varphi)$ and
                $(\mathcal{V},\psi)$ such that $p\in\mathcal{U}$, $q\in\mathcal{V}$,
                $\varphi:\mathcal{U}\rightarrow\nspace[m]$ is a diffeomorphism, and
                $\psi:\mathcal{V}\rightarrow\nspace$ is a diffeomorphism. But then
                the product function $\varphi\times\psi$ is a diffeomorphism from
                $\mathcal{U}\times\mathcal{V}$ to $\nspace[m]\times\nspace$. If
                $(U,\phi)$ and $(V,\xi)$ are different charts, then
                $\phi\times\xi$ overlaps smoothly since:
                \begin{equation}
                    (\varphi\times\psi)\circ(\phi\times\xi)^{\minus{1}}
                    =(\varphi\circ\phi^{\minus{1}})\times(\psi\circ\xi^{\minus{1}})
                \end{equation}
                and since $M$ and $N$ are smooth manifolds, $\varphi$ and $\phi$
                overlap smoothly, and similarly for $\phi$ and $\xi$. But then this
                is the product of smooth functions, and hence smooth. Now if
                $q\in\partial{N}$, then there is a smooth boundary chart
                $(\mathcal{V},\psi)$ such that
                $\psi:\mathcal{V}\rightarrow\mathbb{H}^{n}$ is a diffeomorphism.
                But the $\varphi\times\psi$ is a diffeomorphism from
                $\mathcal{U}\times\mathcal{V}$ to
                $\nspace[m]\times\mathbb{H}^{n}$, which is diffeomorphic to
                $\mathbb{H}^{m+n}$. Therefore, $M\times{N}$ is a smooth manifold
                with boundary. For the general case, if $M_{1},\dots,M_{n}$ are
                manifolds with boundary, and if $N$ is a manifold with boundary,
                let $M=\prod{M}_{i}$. Then the product of the $M_{k}$ with $N$ is
                homeomorphic to $M\times{N}$, which reduces us to the previous
                problem. Thus, $M_{1}\times\dots\times{M}_{n}\times{N}$ is a smooth
                manifold and $\partial(M\times{N})=M\times\partial{N}$.
            \end{solution}
        \subsection{Problems: Part B}
            \begin{problem}
                Show that the group action
                $\Theta:\autgroup[]{V}\times{V}\rightarrow{V}$ given by
                $\Theta(T,v)=Tv$ is continuous, where $V$ is an $n$ dimensional
                vector space over $\nspace[]$, and $\autgroup[]{V}$ carries the
                subspace topology of $\nspace[n^{2}]$.
            \end{problem}
            \begin{solution}
                Both spaces are second countable, and hence first countable, and
                thus to check continuity it suffices to show that $\Theta$ is
                sequentially continuous
                (Thm.~\ref{thm:First_Countable_Implies_Seq_Cont_is_Cont}).
                Let $(T_{n},v_{n})$ be a sequence such that
                $T_{n}\rightarrow{T}$ and $v_{n}\rightarrow{v}$. But then:
                \begin{subequations}
                    \begin{align}
                        \norm{T_{n}v_{n}-Tv}&=\norm{T_{n}v_{n}-T_{n}v+T_{n}v-Tv}\\
                        &\leq\norm{T_{n}v_{n}-T_{n}v}+\norm{T_{n}v-Tv}\\
                        &\leq\norm{T_{n}}\norm{v_{n}-v}+\norm{T_{n}-T}\norm{v}
                    \end{align}
                \end{subequations}
                and since $T_{n}\rightarrow{T}$ and $v_{n}\rightarrow{v}$, this
                converges to zero. Hence, $T_{n}v_{n}\rightarrow{T}v$, and thus
                $\Theta$ is sequentially continuous, and therefore continuous.
                Moreover, it is a group action:
                \begin{equation}
                    \Theta(\identity{V},v)=\identity{V}(v)=v
                \end{equation}
                and for $T,S\in\autgroup{V}$ we have:
                \begin{equation}
                    \Theta\big(T,\theta(S,v)\big)=\Theta(T,Sv)
                    =T(Sv)=(TS)v=\Theta(TS,v)
                \end{equation}
                and thus $\Theta$ is a continuous group action
                (Def.~\ref{def:Continuous_Group_Action}).
            \end{solution}
            \begin{problem}
                Let $G$ be a topological Lie group and $V$ a finite dimensional real
                vector space with the usual topology. A real representation of $G$
                on $V$ is a continuous group homeomorphism
                $\rho:G\rightarrow\autgroup{V}$. Any real representation $(V,\rho)$
                or $G$ on $V$ defines a group action
                $\Theta:G\times{V}\rightarrow{V}$ given by
                $\Theta(g,v)=\rho(g)v$. Show that $\rho$ is a representation if and
                only if $\Theta$ is a continuous group action such that
                $\Theta_{g}=\Theta(g,\cdot)\in\autgroup{V}$ for all $g\in{G}$.
            \end{problem}
            \begin{proof}
                Suppose $\rho$ is a real representation of $G$ on $V$. Since $G$ and
                $V$ are manifolds, so is $G\times{V}$. And manifolds are locally
                metrizable, and hence first countable
                (Thm.~\ref{thm:Locally_Metrizable_is_First_Countable}), and
                therefore sequential
                (Thm.~\ref{thm:First_Countable_Implies_Sequential}). Thus, it
                suffices to show that $\Theta$ is a group action and that it is
                sequentially continuous
                (Thm.~\ref{thm:seq_space_seq_cont_eqiv_cont}). It is indeed a group
                action, for:
                \begin{equation}
                    \Theta(e,v)=\rho(e)v=\identity{v}=v
                \end{equation}
                since $\rho$ is a group homeomorphism, and thus takes the identity
                of $G$ to the identity of $\autgroup{V}$. Moreover, if
                $g_{1},g_{2}\in{G}$, $v\in{V}$, then since $\rho$ is a group
                homeomorphism we obtain::
                \begin{subequations}
                    \begin{align}
                        \Theta\big(g_{1},\Theta(g_{2},v)\big)
                            &=\Theta\big(g_{1},\rho(g_{2})v\big)\\
                            &=\rho(g_{1})\big(\rho(g_{2})v\big)\\
                            &=\big(\rho(g_{1})\rho(g_{2})\big)v\\
                            &=\rho(g_{1}*g_{2})v
                    \end{align}
                \end{subequations}
                and thus $\Theta$ is a group action. It is continuous, for let
                $(g_{n},v_{n})\rightarrow(g,v)$. Then:
                \begin{equation}
                    \Theta(g_{n},v_{n})=\rho(g_{n})v_{n}
                \end{equation}
                But $\rho$ is continuous, and is therefore sequentially continuous
                (Thm.~\ref{thm:cont_implies_seq_cont}). Thus if
                $g_{n}\rightarrow{g}$, then $\rho(g_{n})\rightarrow\rho(g)$
                (Def.~\ref{def:Sequentially_Continuous}). But then:
                \begin{subequations}
                    \begin{align}
                        \norm{\Theta(g_{n},v_{n})-\Theta(g,v)}
                        &=\norm{\rho(g_{n})v_{n}-\rho(g)v}\\
                        &=\norm{\rho(g_{n})v_{n}-\rho(g)v_{n}
                            +\rho(g)v_{n}-\rho(g)v}\\
                        &\leq\norm{\rho(g_{n})v_{n}-\rho(g)v_{n}}+
                            \norm{\rho(g)v_{n}-\rho(g)v}\\
                        &\leq\norm{\rho(g_{n})-\rho(g)}\norm{v_{n}}
                            +\norm{\rho(g)}\norm{v_{n}-v}
                    \end{align}
                \end{subequations}
                But $v_{n}$ is a convergent sequence, and is therefore bounded, and
                hence $\norm{v_{n}}$ is bounded. Since $v_{n}\rightarrow{v}$ and
                $\rho(g_{n})\rightarrow\rho(g)$, this whole things tends to zero.
                Therefore, $\Theta$ is sequentially continuous and therefore
                continuous. Moreover, if $g\in{G}$, then
                $\Theta(g,\cdot)\in\autgroup{V}$. For
                $\Theta(g,\cdot)=\rho(g)(\cdot)$, and $\rho(g)\in\autgroup{V}$ by
                hypothesis. In the other direction, suppose $\Theta$ is a continuous
                group action such that $\Theta(g,\cdot)\in\autgroup{V}$. Again,
                since $G$ is a manifold, it suffices to show that $\rho$ is
                sequentially continuous. If $g_{n}\rightarrow{g}$, then for all
                $v\in{V}$, $\Theta(g_{n},v)=\rho(g_{n})v\rightarrow\rho(g)v$ since
                $\Theta$ is continuous and therefore
                $\Theta(g_{n},v)\rightarrow\Theta(g,v)$. But then:
                \begin{equation}
                    \norm{\rho(g_{n})v-\rho(g)v}
                    \leq\norm{\rho(g_{n})-\rho(g)}\norm{v}
                \end{equation}
                and this tends to zero, showing that
                $\rho(g_{n})\rightarrow\rho(g)$. Hence, $\rho$ is continuous.
                Moreover, it is a group homeomorphism. For if $e\in{G}$ is the
                identity, then for all $v\in{V}$ it is true that:
                \begin{equation}
                    \rho(e)v=\Theta(e,v)=v
                \end{equation}
                since $\Theta$ is a group action. Hence, $\rho(e)$ is the identity
                mapping. If $g_{1},g_{2}\in{G}$, then:
                \begin{equation}
                    \rho(g_{1}*g_{2})(\cdot)=\Theta(g_{1}*g_{2},\cdot)
                        =\Theta\big(g_{1},\Theta(g_{2},\cdot)\big)
                        =\big(\rho(g_{1})\rho(g_{2})\big)(\cdot)
                \end{equation}
                and thus $\rho(g_{1}*g_{2})=\rho(g_{1})\rho(g_{2})$. Therefore,
                $\rho$ is a group homeomorphism.
            \end{proof}
    \section{Homework II}
        \begin{problem}
            (Lee Problem 2-2) Prove that if $M_{1},\dots,M_{k}$ are smooth
            manifolds with or without boundary such that at most one of them has
            non-empty boundary, if $\mathcal{M}$ is the product manifold, if
            $\pi_{i}$ is the $i^{th}$ projection mapping, then
            $F:N\rightarrow\mathcal{M}$ is smooth if and only if
            $\pi_{i}\circ{F}$ is smooth for all $i\in\mathbb{Z}_{k}$.
        \end{problem}
        \begin{solution}
            First we show that $\pi_{i}$ is smooth. Let
            $\mathcal{M}=M_{1}\times{M}_{2}$ and let $\pi_{1}$ be the projection
            map $(p,q)\mapsto{p}$. Let $(p,q)\in\mathcal{M}$. Since
            $M_{1}$ and $M_{2}$ are manifolds, there are charts
            $(\mathcal{U}_{1},\varphi_{1})$ and $(\mathcal{U}_{2},\varphi_{2})$
            such that $p\in\mathcal{U}_{1}$ and $q\in\mathcal{U}_{2}$ but by the
            definition of the product manifold,
            $\mathcal{U}_{1}\times\mathcal{U}_{2}$ is open in $\mathcal{M}$ and
            $(p,q)\in\mathcal{U}_{1}\times\mathcal{U}_{2}$. Moreover, the
            product function $\varphi_{1}\times\varphi_{2}$ is smooth. But then
            for all $(x,y)\in\mathcal{U}_{1}\times\mathcal{U}_{2}$ we have:
            \begin{align}
                \varphi_{1}\circ\pi_{1}\circ
                    (\varphi_{1}\times\varphi_{2})^{\minus{1}}(x,y)
                &=\varphi_{1}\circ\big(
                    \pi_{1}\circ(\varphi_{1}\times\varphi_{2})^{\minus{1}}(x,y)
                \big)\\
                &=\varphi_{1}\circ\Big(
                    \pi_{1}\big(\varphi_{1}^{\minus{1}}(x),
                                \varphi_{2}^{\minus{1}}(y)\big)\Big)\\
                &=\varphi_{1}\circ\big(\varphi_{1}^{\minus{1}}(x)\big)\\
                &=x
            \end{align}
            And thus we have the projection map from $\mathbb{R}^{d_{1}+d_{1}}$
            to $\mathbb{R}^{d_{1}}$, which is smooth. Hence for all
            $(p,q)\in\mathcal{M}$ there is a chart $(\mathcal{U},\varphi)$
            containing $(p,q)$ and a chart $(\mathcal{V},\psi)$ containg
            $\pi_{1}(p,q)$ such that $\psi\circ\pi_{1}\circ\varphi^{\minus{1}}$
            is smooth, and thus $\pi_{1}$ is smooth. Similarly, $\pi_{2}$ is
            smooth. For the general case we proceed by induction and write:
            \begin{equation}
                \mathcal{M}=\prod_{k=1}^{n+1}M_{k}=
                    \Big(\prod_{k=1}^{n}M_{k}\Big)\times{M}_{n+1}
                \equiv\widehat{\mathcal{M}}\times{M}_{n+1}
            \end{equation}
            which is the product of two manifolds, one of dimension
            $d_{1}+d_{2}+\dots+d_{n}$ and the other of dimension $d_{n+1}$, and
            thus by the previous argument the projection maps are smooth. Hence,
            $\pi_{n+1}$ is smooth. But by the induction hypothesis, all of the
            $\pi_{i}$ are smooth for $i=1,\dots,n$, and thus all $\pi_{i}$ are
            smooth for $i=1,\dots,n,n+1$. Now, suppose
            $f:N\rightarrow\mathcal{M}$ is smooth. Then $F_{i}=\pi_{i}\circ{F}$
            is the composition of smooth function and hence by theorem 2.10 (d)
            in Lee's text, $F_{i}$ is smooth. In the other direction, we again
            start with the case that $\mathcal{M}=M_{1}\times{M}_{2}$. Suppose
            $F:N\rightarrow\mathcal{M}$ is such that $\pi_{1}\circ{F}$ and
            $\pi_{2}\circ{F}$ are smooth. Let $v\in{N}$ and let
            $(\mathcal{V},\psi)$ be a chart containing $v$ and let
            $(\widehat{\mathcal{U}},\widehat{\varphi})$ be a chart containing
            $F(v)$. Let $\mathcal{U}_{i}=\pi_{i}[\widehat{\mathcal{U}}]$ and
            let $\varphi_{i}=\pi_{i}\circ\widehat{\varphi}$. Then the
            $\varphi_{i}$ are the composition of smooth functions, and hence are
            smooth, and the $\mathcal{U}_{i}$ are the projections of open sets
            and are hence open. Moreover,
            $(\mathcal{U}_{1}\times\mathcal{U}_{2},%
             \varphi_{1}\times\varphi_{2})$ is a chart containing $F(v)$. But
            \begin{equation}
                \varphi_{1}\times\varphi_{2}\circ(F\circ\psi^{\minus{1}})(x)
                =\big(\varphi_{1}\circ\pi_{1}\circ{F}\circ\psi^{\minus{1}}),
                      \varphi_{2}\circ\pi_{2}(F)\circ\psi^{\minus{1}})\big)
            \end{equation}
            and by hypothesis, $F\circ\pi_{i}$ is smooth. But then this is the
            composition of smooth functions in each component, and is therefore
            smooth in the each component. But a function
            $f:\nspace\rightarrow\nspace[m]$ is smooth if and only if it is
            smooth in each component, and thus this transition map is smooth.
            Thus, $F$ is smooth.
        \end{solution}
        \begin{problem}
            (Lee 2-3) Show that $z^{n}:\nsphere[1]\rightarrow\nsphere[1]$ is
            smooth, the antipodal map $\vector{x}\mapsto\minus\vector{x}$, and
            the function $f:\nsphere[3]\rightarrow\nsphere[2]$ defined by:
            \begin{equation}
                f(w,z)=(z\overline{w}+w\overline{z},
                        iw\overline{z}-iz\overline{w},
                        z\overline{z}-w\overline{w})
            \end{equation}
        \end{problem}
        \begin{solution}
            Since $\nsphere[1]$ can be covered by two charts, we simply need to
            check that this function is smooth on these charts. Let
            $\mathcal{U}^{-}=\nsphere[1]\setminus\{(0,1)\}$ and similarly for
            $\mathcal{U}^{+}$. The stereographic projection onto $\nspace[]$
            is just:
            \twocolumneq{\varphi_{\minus}(x,y)=\frac{x}{1-y}}
                        {\varphi_{+}(x,y)=\frac{x}{1+y}}
            The inverse functions are:
            \begin{equation}
                \varphi_{\minus}^{\minus{1}}(X)
                    =\Big(\frac{X}{1+X^{2}},\frac{X^{2}-1}{X^{2}+1}\Big)
            \end{equation}
            and similarly for $\varphi_{+}$. To show that $p_{n}$ is smooth it
            suffices to show that
            $\varphi_{\minus}\circ{p}_{n}\circ\varphi_{\minus}^{\minus{1}}$ is
            smooth. We have:
            \begin{align}
                \big(\varphi_{\minus}\circ{p}_{n}\circ
                    \varphi_{\minus}^{\minus{1}}\big)(X)
                    &=\big(\varphi_{\minus}\circ{p}_{n}\big)
                    \Big(\frac{2X+i(X^{2}-1)}{1+X^{2}}\Big)\\
                    &=\varphi_{\minus}\Big(
                        \frac{\big(2X+i(X^{2}-1)^{2})^{n}}{(1+X^{2}\big)^{n}}
                    \Big)
            \end{align}
            Thus, the $x$ and $y$ components will both be rational functions
            in $X$, and therefore $\varphi+_{\minus{1}}(x,y)$ will be a rational
            function in $X$, which is smooth. In a similarly manner,
            $\varphi_{+}\circ{p}_{n}\circ\varphi_{+}^{\minus{1}}$ is smooth.
            Thus for every point $\vector{x}\in\nsphere[1]$ there is a chart
            $(\mathcal{U},\varphi)$ such that $\vector{x}\in\mathcal{U}$ and
            $\varphi\circ{p}_{n}\circ\varphi^{\minus{1}}$ is smooth. Therefore,
            $p_{n}$ is smooth. For the antipodal map on $\nsphere$ we can use
            the orthographic projections. That is,
            $(\mathcal{U}_{j}^{+},\varphi_{+})$ is the chart where
            $\mathcal{U}_{j}^{+}$ is the $j^{th}$ upper hemisphere and
            $\varphi$ is the mapping that projects
            $\nsphere\subseteq\nspace[n+1]$ down to the $\nspace$ hyper plane
            obtained by fixed all but the $j^{th}$ coordinate, and similarly
            let $(\mathcal{U}^{\minus},\varphi_{\minus})$ be the opposite
            hemisphere. Given $\vector{s}\in\nsphere$, $\vector{s}$ is contained
            in one of these, and $\minus\vector{s}$ will be contained in the
            opposite. We thus need to show that, if $f$ is the antipodal map,
            then $\varphi_{\minus}\circ{f}\circ\varphi_{+}^{\minus{1}}$ is
            smooth. We have:
            \begin{align}
                \varphi_{\minus}\circ{f}\circ\varphi_{+}^{\minus{1}}(\vector{x})
                &=\varphi_{\minus}\circ{f}(x_{0},\dots,x_{j-1},
                    \sqrt{1-\norm{\vector{x}}^{2}},x_{j+1},\dots,x_{n})\\
                &=\varphi_{\minus}(\minus{x}_{0},\dots,\minus{x}_{j-1},
                    \minus\sqrt{1-\norm{\vector{x}}^{2}},\minus{x}_{j+1},
                    \dots,\minus{x}_{n}\big)\\
                &=(\minus{x}_{0},\dots,\minus{x}_{j-1},\minus{x}_{j+1},\dots,
                    \minus{x}_{n})\\
                &=\minus\vector{x}
            \end{align}
            Hence, this is a smooth mapping since multiplying by a constant is
            a smooth mapping from $\nspace$ to itself. Lastly, we show that the
            \textit{Hopf Fibration} is smooth. Again, sticking to orthographic
            projections, let $(\mathcal{U},\varphi)$ and $(\mathcal{V},\psi)$
            be orthographic charts in $\nsphere[3]$ and $\nsphere[2]$,
            respectively (Suppose both in the $x$ axis). Let
            $f:\nsphere[3]\rightarrow\nsphere[2]$ be the Hopf fibration. Then
            for $\vector{x}\in\nball[3]$, we have:
            \begin{equation}
                \psi\circ{f}\circ\varphi^{\minus{1}}(\vector{x})
                =\psi\circ{f}\circ(\sqrt{1-\norm{\vector{x}}^{2}},\vector{x})
                =\psi\circ{f}\Big(
                    \big(\sqrt{1-\norm{\vector{x}}^{2}}+ix_{1}\big),
                    \big(x_{2}+ix_{3}\big)
                \Big)
            \end{equation}
            Using the definition of $f$ and $\psi$ (which simply projection
            down to the $yz$ plane), we have:
            \begin{equation}
                \psi\circ{f}\circ\varphi^{\minus{1}}(\vector{x})=\big(
                    2\sqrt{1-\norm{\vector{x}}^{2}}x_{1}+2x_{2}x_{3},1-x_{1}^{2}
                \big)
            \end{equation}
            which is smooth in both components, and hence is a smooth function
            from an open subset of $\nspace[3]$ to an open subset of
            $\nsphere[2]$ and is therefore smooth. Similarly for the other
            hemispheres.
        \end{solution}
        \begin{problem}
            (Lee 2-6) Show that if
            $f:\nspace[n+1]\setminus\{0\}\rightarrow\nspace[k+1]\setminus\{0\}$
            is a smooth homogeneou function s of degree $d\in\mathbb{Z}$, then
            the induced maps $\tilde{f}:\nrealproj\rightarrow\nrealproj[k]$ are
            well defined and smooth.
        \end{problem}
        \begin{solution}
            It is indeed well defined, for if $\vector{x},\vector{y}$ have the
            the same equivalence class: $[\vector{x}]=[\vector{y}]$, then there
            is a $\lambda\in\nspace[]\setminus\{0\}$ such that
            $\vector{y}=\lambda\vector{x}$. But then:
            \begin{equation}
                \tilde{f}([\vector{y}])=[f(\vector{y})]
                    =[f(\lambda\vector{x})]
                    =[\lambda^{d}f(\vector{x})]
                    =[f(\vector{x})]
                    =\tilde{f}([\vector{x}])
            \end{equation}
            and therefore elements of the same equivalence class map to the same
            points.
        \end{solution}
        \begin{problem}
            Lee 2-10.
        \end{problem}
        \begin{solution}
            Let $\manifold[M]{M}$ and $\manifold[N]{N}$ be manifolds,
            $F:M\rightarrow{N}$ continuous. $F^{*}$ is linear. For if
            $a,b\in\mathbb{R}$, $f,g\in\Ckspace{}{M}$, then:
            \begin{subequations}
                \begin{align}
                    F^{*}(af+bg)&=(af+bg)\circ{F}\\
                    &=\big((af)\circ{F}\big)+\big((bg)\circ{F}\big)\\
                    &=a(f\circ{F})+b(g\circ{F})\\
                    &=aF^{*}(f)+bF^{*}(g)
                \end{align}
            \end{subequations}
            If $F:M\rightarrow{N}$ is smooth, then for all
            $f\in\Ckspace{\infty}{N}$ we have $F^{*}(f)=f\circ{F}$, which is the
            composition of smooth function and is hence smooth. Therefore, we
            obtain $F^{*}[\Ckspace{\infty}{N}]\subseteq\Ckspace{\infty}{M}$.
            Conversely, suppose
            $F^{*}[\Ckspace{\infty}{N}]\subseteq\Ckspace{\infty}{M}$ and suppose
            that $F$ is not smooth. Then there is a point $p\in{M}$ such that
            for every chart $(\mathcal{U},\varphi)\in\mathcal{A}_{M}$ that
            contains $p$ and for every chart
            $(\mathcal{V},\psi)\in\mathcal{A}_{N}$ that contains $F(p)$, the
            function $\psi\circ{F}\circ\varphi^{\minus{1}}$ is not smooth. But
            since $N$ is a manifold, there is a precompact chart
            $(\mathcal{V},\psi)$ that contains $F(p)$. But $F$ is continuous,
            and hence $F^{\minus{1}}[\mathcal{V}]$ is an open subset of $M$ that
            contains $p$. Let $(\tilde{\mathcal{U}},\tilde{\varphi})$ be a
            precompact chart containing $p$, and let
            $\mathcal{U}=\tilde{\mathcal{U}}\cap{F}^{\minus{1}}[\mathcal{V}]$
            and $\varphi=\tilde{\varphi}|_{\mathcal{U}}$. Then, since
            $\mathcal{U}$ is the non-empty intersection of two open subsets,
            it will open and non-empty, and hence $(\mathcal{U},\varphi)$
            is a chart in $M$. Since $\mathcal{A}_{M}$ is maximal,
            $(\mathcal{U},\varphi)\in\mathcal{A}_{M}$. By hypothesis,
            $\psi\circ{F}\circ\varphi^{\minus{1}}$ is not smooth, and hence
            there a component $k$ such that composing with the projection map
            $\pi_{k}:\nspace[m]\rightarrow\nspace[]$ is not smooth. But we may
            use the bump function to extend $\pi_{k}\circ\psi$ to all of $N$,
            obtaining a smooth function in $\Ckspace{\infty}{N}$. But then by
            hypothesis, $\pi_{k}\circ\psi\circ{F}$ is smooth. And
            $\varphi^{\minus{1}}$ is smooth, so
            $\pi_{k}\circ\psi\circ{F}\circ\varphi^{\minus{1}}$ is smooth,
            a contradiction. Hence, $F$ is smooth. Lastly, show that if $F$ is a
            homeomorphism, then it is a diffeomorphism if and only if $F^{*}$ is
            an isomorphism. Since $F$ and $F^{\minus{1}}$ are continuous, they
            are both smooth if and only if
            $F^{*}[\Ckspace{\infty}{N}]\subseteq\Ckspace{\infty}{M}$ and
            ${F^{\minus{1}}}^{*}[\Ckspace{\infty}{M}]%
             \subseteq\Ckspace{\infty}{N}$. That is, they are smooth if and only
            if $F^{*}|_{\Ckspace{\infty}{N}}\rightarrow\Ckspace{\infty}{M}$ is a
            bijective function. Since $F^{*}$ is linear, $F$ and $F^{\minus{1}}$
            are smooth if and only if $F^{*}$ is an isomorphism.
        \end{solution}
        \begin{problem}
            (Lee 2-13) Show that paracompactness and subordinate partitions of
            unity are equivalent.
        \end{problem}
        \begin{solution}
            That paracompactness implies subordinate partitions of unity was
            proved both in class and in Lee. Going the other way, let
            $\topspace{X}$ be a topological space and suppose every
            open cover has a subordinate partition of unity. Let $\mathcal{O}$
            be an open cover and let $\mathcal{F}$ be a subordinate partition of
            unity. Let $\Delta$ be defined by:
            \begin{equation}
                \Delta=\{\mathcal{U}\;|\;\exists_{f\in\mathcal{F}}
                (\mathcal{U}=f^{\minus{1}}[\nspace[]\setminus\{0\}])\}
            \end{equation}
            Then, since all $f$ are continuous, all of the $\mathcal{U}$ are the
            pre-images of open sets and are therefore open. Since $\mathcal{F}$
            is a partiion of unity, for every point $x\in{X}$ there is an
            $f\in\mathcal{F}$ such that $f(x)\ne{0}$, hence $\Delta$ is an open
            subcover of $X$. Moreover, every $\mathcal{U}$ is contained in the
            support of some function, and since $\mathcal{F}$ is partition of
            unity, these form a locally finite cover. Therefore $\Delta$ is a
            locally finite refinement of $\mathcal{O}$. Thus, $\topspace{X}$
            is paracompact.
        \end{solution}
        \begin{problem}
            (Lee 2-14) Show that disjoint closed subsets can be separated by
            smooth functions.
        \end{problem}
        \begin{solution}
            For manifolds are Hausdorff and second countable
            (Def.~\ref{def:Topological_Manifold}), and are regular
            (Thm.~\ref{thm:Loc_Euc_Haus_is_Regular}) and Lindel\"{o}f
            (Thm.~\ref{thm:Manifolds_are_Lindelof}). But regular Lindel\"{o}f
            spaces are normal (Thm.~\ref{thm:Regular_Lindelof_is_Normal}), and
            thus if $C_{1}$ and $C_{2}$ are disjoint closed sets then there are
            disjoint open sets $\mathcal{U}_{1}$, $\mathcal{U}_{2}$ containing
            $C_{1}$ and $C_{2}$. Furthermore, we can shrink $\mathcal{U}_{1}$
            and $\mathcal{U}_{2}$ so that they have disjoint closures. From
            theorem 2.29 we can find functions $f,g:M\rightarrow\mathbb{R}$ such
            that $f^{\minus{1}}[\{0\}]=C_{1}$ and $g^{\minus{1}}[\{1\}]=C_{2}$.
            But since $\closure{\mathcal{U}_{1}}$ is closed, we can find a bump
            function for $\closure{\mathcal{U}_{1}}$ supported on $\mathcal{U}$
            that evaluates to $1$ on $C_{1}$, and similarly for $C_{2}$.
            Denote these bump functions $h_{1},h_{2}$. Let
            $F:M\rightarrow\mathbb{R}$ be defined by:
            \begin{equation}
                F(p)=g_{1}(p)f(p)+g_{2}(p)g(p)
            \end{equation}
        \end{solution}
    \section{Homework III}
        \subsection{Weierstrass Approximation Theorem}
            \begin{ftheorem}{Weierstrass Approximation Theorem}
                            {Weierstrass Approximation Theorem}
                If $f:[0,1]\rightarrow\nspace[]$ is a continuous function and if
                $\varepsilon>0$, then there is a polynomial
                $P:[0,1]\rightarrow\nspace[]$ such that
                $\norm{P-f}_{\infty}<\infty$. That is:
                \begin{equation*}
                    \sup\big\{\,|f(x)-P(x)|\;\big|\;x\in[0,1]\,\big\}<\varepsilon
                \end{equation*}
            \end{ftheorem}
            \begin{theorem}
                \label{thm:Weierstrass_Approx_Endpoints_Eq_Zero}%
                If $f:[0,1]\rightarrow\nspace[]$ is a continuous function, if
                $f(0)=0$, $f(1)=0$, and if $\varepsilon>0$, then there is a
                polynomial $P:[0,1]\rightarrow\nspace[]$ such that $P(0)=f(0)$,
                $P(1)=f(1)$, and $\norm{P-f}_{\infty}<\varepsilon$.
            \end{theorem}
            \begin{proof}
                For by the Weierstrass approximation theorem there exists a
                polynomial $Q:[0,1]\rightarrow\nspace[]$ such that
                $\norm{f-Q}<\varepsilon/4$
                (Thm.~\ref{thm:Weierstrass Approximation Theorem}. Define $P$ by:
                \begin{equation}
                    P(x)=Q(x)-Q(0)-\big(Q(1)-Q(0)\big)x
                \end{equation}
                Then:
                \begin{equation}
                    \norm{P-f}_{\infty}\leq
                    \norm{Q-f}_{\infty}+2|Q(0)|+|Q(1)|
                    <\frac{\varepsilon}{4}+\frac{\varepsilon}{2}
                        +\frac{\varepsilon}{4}=\varepsilon
                \end{equation}
                and moreover, $P(0)=0$ and $P(1)=0$.
            \end{proof}
            \begin{theorem}
                \label{thm:Weierstrass_Fixed_Endpoints}%
                If $f:[0,1]\rightarrow\nspace[]$ is a continuous function, and if
                $\varepsilon>0$, then there is a polynomial
                $P:[0,1]\rightarrow\nspace[]$ such that $P(0)=f(0)$, $P(1)=f(1)$,
                and $\norm{P-f}_{\infty}<\varepsilon$.
            \end{theorem}
            \begin{proof}
                For let $g(x)=f(x)-f(b)x-(1-x)f(a)$. Then $g$ is continuous,
                $g(0)=0$, $g(1)=0$, and thus there is a polynomial
                $Q:[0,1]\rightarrow\nspace[]$ such that $Q(0)=g(0)$, $Q(1)=f(1)$,
                and $\norm{Q-g}_{\infty}<\varepsilon$
                (Thm.~\ref{thm:Weierstrass_Approx_Endpoints_Eq_Zero}). Let
                $P=Q+f(b)x+(1-x)f(a)$. Then $P(0)=f(0)$, $P(1)=f(1)$, and
                $\norm{P-f}_{\infty}<\varepsilon$.
            \end{proof}
            \begin{theorem}
                \label{thm:Existence_of_Smooth_Path_in_Rn_Fixed_Endpoints}%
                If $f:[0,1]\rightarrow\nspace$ is a smooth function, and if
                $\varepsilon>0$, then there is a smooth function
                $\Gamma:[0,1]\rightarrow\nspace$ such that $\Gamma(0)=f(0)$,
                $\Gamma(1)=f(1)$, and  $\norm{\Gamma-f}_{\infty}<\varepsilon$.
            \end{theorem}
            \begin{proof}
                For let $g_{k}=f\circ\pi_{k}$, where
                $\pi_{k}:\nspace\rightarrow\nspace[]$ is the projection mapping. But
                the projection of a continuous function is continuous, and thus
                $g_{k}:[0,1]\rightarrow\nspace$ is continuous. By the Weierstrass
                approximation theorem, there is a polynomial
                $P_{k}:[0,1]\rightarrow\nspace[]$ such that
                $\norm{g_{k}-P_{k}}_{\infty}<\varepsilon/n$, and such that
                $P_{k}(0)=g_{k}(0)$ and $P_{k}(1)=g_{k}(1)$
                (Thm.~\ref{thm:Existence_of_Smooth_Path_in_Rn_Fixed_Endpoints}). Let
                $\Gamma:[0,1]\rightarrow\nspace$ be the function such that
                $\Gamma\circ\pi_{k}=P_{k}$. Since polynomials are smooth, and since
                $\Gamma$ is smooth in every projection, it is smooth. But then:
                \begin{equation}
                    \norm{f-\Gamma}_{\infty}
                    \leq\sum_{k\in\mathbb{Z}_{n}}\norm{g_{k}-P_{k}}_{\infty}
                    <\sum_{k\in\mathbb{Z}_{n}}\frac{\varepsilon}{n}
                    =\varepsilon
                \end{equation}
                completing the proof.
            \end{proof}
            \begin{theorem}
                \label{thm:Existence_of_Smooth_Path_in_Manifold}%
                If $\manifold{M}$ is a smooth connected manifold, and if
                $x,y\in{M}$, then there is a smooth function
                $\Gamma:[0,1]\rightarrow{M}$ such that $\Gamma(0)=x$ and
                $\Gamma(1)=y$.
            \end{theorem}
            \begin{proof}
                For suppose not. Then there are points $x,y\in{M}$ with no smooth
                path between them. But manifolds are locally path connected, and
                locally path connected topological spaces that are connected are
                also path connected
                (Thm.~\ref{thm:Loc_Path_and_Con_Imply_Path_Con}). Hence, there is a
                path $\gamma:[0,1]\rightarrow{M}$ such that $\gamma(0)=x$ and
                $\gamma(1)=y$. Let $A\subseteq[0,1]$ be the set of elements $t$ such
                that there is a smooth curve from $\gamma(0)$ to $\gamma(t)$. Then
                $A$ is non-empty since $0\in{A}$. That is, the constant function
                is a smooth function from $\gamma(0)$ to $\gamma(0)$. Moreover $A$
                is bounded by 1, and hence there is a least upper bound $r$.
                Suppose $r<1$. Since $M$ is a manifold, there is a chart
                $(\mathcal{U},\varphi)$ such that $\gamma(r)\in\mathcal{U}$ and
                $\mathcal{U}$ is homeomorphic to $\nspace$. Since $\mathcal{U}$ is
                open, $\gamma^{\minus{1}}[\mathcal{U}]$ is open. Hence there exists
                $t_{0}<r<t_{1}$ such that
                $\gamma\big[[t_{0},t_{1}]\big]\subseteq\mathcal{U}$. But then
                $\gamma|_{[t_{0},t_{1}]}\circ\varphi$ is the composition of
                continuous function, and is thus a continuous function from
                $[t_{0},t_{1}]$ to $\nspace$. And since $[t_{0},t_{1}]$ is compact,
                it's image is compact. Hence there is an $\varepsilon>0$ such that
                the image sits inside that $\varepsilon$ ball about the origin.
                But then there is a smooth function $P$ such that
                $P(t_{0})=\varphi(\gamma(t_{0}))$, $P(t)=\varphi(\gamma(t_{1}))$,
                and $\norm{P_{1}-\varphi}\circ\gamma|_{[t_{0},t_{1}]}<\varepsilon/2$
                and hence the image of $P$ sits inside the $\varepsilon$ ball.
                But then the pull back of $P$ by $\varphi$ is a smooth curve
                connecting $\gamma(t_{0})$ and $\gamma(t_{1})$. But $t_{0}<r$ and
                hence there is a smooth curve $\Gamma_{0}:[0,1]\rightarrow{M}$
                connecting $\gamma(0)$ and $\gamma(t_{0})$ Let
                $\Gamma_{1}$ be the concatenation of $\Gamma_{0}$ and the pull back
                of $P$ by $\varphi$, smoothed out at $\gamma(t_{0})$ by any
                smoothing function ($\exp(\minus{1}/t^{2})$ will do). But then
                $\Gamma$ is a smooth curve connecting $\gamma(0)$ and
                $\gamma(t_{1})$, a contradiction since $r<t_{1}$ and $r$ is the
                least upper bound of such $t$.
            \end{proof}
        \subsection{Homework III}
            \begin{problem}
                Lee 3-1.
            \end{problem}
            \begin{solution}
                It suffices to look at a single connected component of $M$.
                Suppose $F$ is not constant. Then there are $x,y\in{M}$ such
                that $F(x)\ne{F}(y)$. But since $\manifold{M}$ is a smooth
                connected manifold, there exists a smooth path
                $\Gamma:[0,1]\rightarrow{M}$ such that $\Gamma(0)=x$ and
                $\Gamma(1)=y$
                (Thm.~\ref{thm:Existence_of_Smooth_Path_in_Manifold}). But for
                all $p\in{M}$ it is true that $\diff_{p}F$ is the zero map, and
                thus for all $t\in[0,1]$, $\diff_{\Gamma(t)}F=0$. Let
                $\gamma:[0,1]\rightarrow{N}$ be defined by
                $\gamma=F\circ\Gamma$. Then since $\gamma$ is the composition of
                smooth functions, it is smooth, and moreover $\gamma(0)=F(x)$
                and $\gamma(1)=F(y)$. But for all $t\in[0,1]$,
                $\dot{\gamma}(t)=0$. Thus, for all $f\in\Ckspace{\infty}{N}$ it
                is true that $\dot{\gamma}(t)(f)=0$. But $f\circ\gamma$ is a
                function from $[0,1]$ to $\nspace$, and if
                $\dot{\gamma}(t)(f)=0$ then $f\circ\gamma$ is constant. Then in
                particular, for any chart $(\mathcal{V},\psi)$ in $N$ that
                overlaps with $\gamma\big[[0,1]\big]$, the projection maps
                $\pi_{k}:\mathcal{V}\rightarrow\nspace[]$ are such that $\gamma$
                is constant on $\mathcal{V}$. But then $\gamma$ is a locally
                constant function and since $\gamma\big[[0,1]\big]$ is
                connected, $\gamma$ is thus constant. But then
                $\gamma(0)=\gamma(1)$ and hence $F(x)=F(y)$, a contradiction. In
                the other direction, if $F$ is constant, let $p\in{M}$ and
                $v\in\tanspace{p}{M}$. Then for all
                $f\in\Ckspace{\infty}{N}$ we have:
                \begin{equation}
                    \diff_{p}F(v)(f)=v(f\circ{F})
                \end{equation}
                But $f\circ{F}$ is a constant function, and a derivation of a
                constant is zero since:
                \begin{equation}
                    v(1)=v(1\cdot{1})=v(1)\cdot{1}+1\cdot{v}(1)=v(1)+v(1)
                \end{equation}
                and hence $v(1)=0$. Then for any $c$ such that $v(c)=cv(1)=0$.
                But then $\diff_{p}F(v)(f)=0$ for all $f\in\Ckspace{\infty}{N}$
                and thus $\diff_{p}F$ is the zero mapping for all $p\in{M}$.
            \end{solution}
            \begin{problem}
                If $M_{1},\dots,M_{n}$ are smooth manifolds, if
                $\mathcal{M}=\prod{M}_{k}$, and if
                $\alpha:T_{p}\mathcal{M}\rightarrow\oplus{T}_{p_{k}}M_{k}$
                is defined by;
                \begin{equation}
                    \alpha(v)=(\diff{\pi_{1}}_{p}(v),\dots,
                                \diff{\pi_{n}}_{p}(v))
                \end{equation}
                then $\alpha$ is an isomorphism. The same is true if one of the
                $M_{k}$ has boundary.
            \end{problem}
            \begin{solution}
                We must show that $\alpha$ is linear and bijective. It is linear
                since:
                \begin{align}
                    \alpha(av+bw)&=
                        \big(\diff{\pi_{1}}_{p}(av+bw),\dots,
                            \diff{\pi_{n}}_{p}(av+bw)\big)\\
                        &=\big(a\diff{\pi_{1}}_{p}(v)+b\diff{\pi_{1}}_{p}(w)
                            \dots,a\diff{\pi_{n}}_{p}(v)+b\diff{\pi_{n}}_{p}(w)
                        \big)\\
                        &=(a\diff{\pi_{1}}_{p}(v),\dots,a\diff{\pi_{n}}_{p}(v))
                        +(b\diff{\pi_{1}}_{p}(w),\dots,b\diff{\pi_{n}}_{p}(w))\\
                        &=a(\diff{\pi_{1}}_{p}(v),\dots,\diff{\pi_{n}}_{p}(v))+
                        b(\diff{\pi_{1}}_{p}(w),\dots,\diff{\pi_{n}}_{p}(w))\\
                        &=a\alpha(v)+b\alpha(w)
                \end{align}
                and thus, $\alpha$ is linear. It is injective, for if
                $v,w\in\tanspace{p}{\mathcal{M}}$ and if $\alpha(v)=\alpha(u)$,
                then the projections of $u$ and $v$ agree in every component,
                and hence $u=v$. Lastly, it is surjective. For if
                $v_{k}\in\tanspace{p_{k}}{M_{k}}$, let
                $v=v_{1}\times\dots\times{v}_{n}$. Then the $k^{th}$ component
                of $\alpha(v)$ is:
                \begin{equation}
                    \diff{\pi_{k}}_{p}(v)(f)=v(f\circ\pi_{k})=v_{k}(f)
                \end{equation}
                and thus $\diff{\pi_{k}}_{p}(v)=v_{k}$ so $\alpha$ is
                surjective.
            \end{solution}
            \begin{problem}
                Show that $T\nsphere[1]$ is diffeomorphic to
                $\nsphere[1]\times\nspace[]$.
            \end{problem}
            \begin{solution}
                For every $\vector{s}\in\nsphere[1]$ and for every
                $v\in\tanspace{\vector{s}}{\nsphere[1]}$, by the basis theorem
                there is a $c\in\nspace[]$ such that $v=c\diff/\diff\theta$.
                Let $f:T\nsphere[1]\rightarrow\nsphere[1]\times\nspace[]$ be
                defined by $f(\vector{s},v)=(\vector{s},r)$. We must show that
                this is a diffeomorphism. It is injective, for if
                $f(s_{1},v_{1})=f(s_{2},v_{2})$, then $s_{1}=s_{2}$, and hence
                $v_{1},v_{2}\in\tanspace{s_{1}}{\nsphere[1]}$. But
                $v_{1}=c\diff/\diff\theta$ and $v_{2}=c\diff/\diff\theta$, and
                hence $v_{1}=v_{2}$. Thus, $f$ is injective. It is surjective
                by the basis theorem. That is, every element of
                $T\nsphere[1]$ is of the form $(\vector{s},c\diff/\diff\theta)$
                for some $c\in\nspace[]$. But this is smooth in both components,
                and hence it is a smooth function. The inverse function
                $f^{\minus{1}}(s,c)=(s,c\diff/\diff\theta)$ is also smooth in
                both components, and hence $f$ is a diffeomorphism.
            \end{solution}
            \begin{problem}
                Let $M$ be a smooth manifold with or without boundary and
                $p\in{M}$. Let $C_{p}^{\infty}(M)$ denote ths algebra of germs
                of smooth real-valued functions at $p$< and
                $\mathcal{D}_{p}^{\infty}(M)$ the vector space of derivations of
                $C_{p}^{\infty}(M)$. Show that
                $\Phi:\mathcal{D}_{p}(M)\rightarrow\tanspace{p}{M}$ defined by:
                \begin{equation}
                    \Phi(v)(f)=v([f]_{p})
                \end{equation}
                is an isomorphism.
            \end{problem}
            \begin{solution}
                We have to show that $\Phi$ is linear and bijective. It is
                linear since:
                \begin{equation}
                    \Phi(av+bw)(f)=(av+bw)([f]_{p})
                        =av([f]_{p})+bw([f]_{p})
                        =a\Phi(v)+b\Phi(w)
                \end{equation}
                it is injective since if $\Phi(u)=\Phi(v)$, then for all
                $f$ we have that $v([f]_{p})=w([f]_{p})$ and thus $v$ and $w$
                are the same derivation, and hence $v=w$. It is surjective, for
                if $\tilde{v}$ is a tangent vector, let
                $v\in\mathcal{D}_{p}^{\infty}$ simply be the element such that
                $v([f])=\tilde{v}(f)$. This is well defined since if
                $g\in[f]$, then $g$ agrees with $f$ on some neighborhood of
                $p$ and thus $\tilde{v}(f)=\tilde{v}(g)$. But then
                $\Phi(v)=\tilde{v}$, and therefore $\Phi$ is surjective. Thus,
                $\Phi$ is an isomorphism.
            \end{solution}
\end{document}