%------------------------------------------------------------------------------%
\documentclass{article}                                                        %
%------------------------------Preamble----------------------------------------%
\makeatletter                                                                  %
    \def\input@path{{../../}}                                                  %
\makeatother                                                                   %
\input{preamble.tex}                                                           %
%----------------------------Main Document-------------------------------------%
\begin{document}
    \title{Misc Notes from Semi-Remiannian Geometry}
    \author{Ryan Maguire}
    \date{\vspace{-5ex}}
    \maketitle
    \tableofcontents
    \section{More on Topological Manifolds}
        \begin{definition}
            A precompact subset of a topological space $(X,\tau)$ is a subset
            $\mathcal{U}\subseteq{X}$ such that $\textrm{Cl}(\mathcal{U})$
            is compact.
        \end{definition}
        \begin{theorem}
            Every topological $n$ manifold has a countable basis of precompact
            coordinate balls.
        \end{theorem}
        \begin{proof}
            Let $(X,\tau)$ be a topological manifold and
            $\{(\mathcal{U}_{\alpha},\varphi_{\alpha})\}$ a cover by coordinate
            charts. Since second countable spaces are Lindelof, there is a
            countable subcover. Since each $\varphi_{k}$ is an open mapping,
            $\varphi_{k}(\mathcal{U}_{k})$ is an open subset of
            $\mathbb{R}^{n}$.
        \end{proof}
        \begin{definition}
            A locally path connected topological space is a topological space
            $(X,\tau)$ such that there exists a basis of path connected open
            sets.
        \end{definition}
        \begin{definition}
            A locally compact topological space is such that for all $x\in{X}$
            there is an open $\mathcal{U}\subseteq{X}$ and a compact
            $K\subseteq{X}$ such that $x\in\mathcal{U}$ and
            $\mathcal{U}\subseteq{K}$.
        \end{definition}
        \begin{definition}
            A connected component of $X$ is a maximal connected subset of $X$.
        \end{definition}
        Connected components partition the space. If two connected sets have
        a point in common, their union is connected.
        \begin{definition}
            A path connected component s a maximal path component.
        \end{definition}
        \begin{theorem}
            If $(X,\tau)$ is a topological manifold, then $M$ is locally path
            connected, locally compact, and the path components and connected
            components are identical. Moreover, $M$ has countably many connected
            components, each of which is open.
        \end{theorem}
        \begin{proof}
            Locally path connected and connected implies path connected, hence
            connected components and path connected components are the same.
            Locally compact since compact coordinate balls about each point
            suffice. Countably many connected components since second countable.
        \end{proof}
        \begin{definition}
            A locally finite subset $\mathcal{O}\subseteq\mathcal{P}(X)$ is a
            collection such that for all $x\in{X}$ there is a neighborhood
            $\mathcal{U}\in\tau$ such that $\mathcal{U}$ intersects at most
            finitely many elements of $\mathcal{O}$.
        \end{definition}
        \begin{definition}
            A refinitement of a collection $\mathcal{O}\subseteq\mathcal{P}(X)$
            is a collection $\mathcal{D}\subseteq\mathcal{P}(X)$ such that for
            all $\mathcal{V}\in\mathcal{D}$ there is a
            $\mathcal{U}\in\mathcal{O}$ such that
            $\mathcal{V}\subseteq\mathcal{U}$.
        \end{definition}
        \begin{definition}
            A paracompact space is a space such that every open cover has a
            locally finite refinement.
        \end{definition}
        \begin{theorem}
            If $\mathcal{O}$ is a locally finite collection of subsets of $X$,
            then the collection of the closures is locally finite and the union
            of the closures is the closure of the unions.
        \end{theorem}
        \begin{theorem}
            If $(X,\tau)$ is a topological manifold, then it is paracompact.
        \end{theorem}
    \section{Smooth Manifolds}
        \begin{definition}
            A diffeomprhism from an open subset
            $\mathcal{U}\subseteq\mathbb{R}^{n}$ to an open subset
            $\mathcal{V}\subseteq\mathbb{R}^{n}$ is a homeomorphism
            $f:\mathcal{U}\rightarrow\mathcal{V}$ such that $f$ and
            $f^{\minus{1}}$ are smooth functions.
        \end{definition}
        \begin{definition}
            Let $M$ an $n$ dimensional topological manifold. Two coordinate
            charts $(\mathcal{U},\varphi)$ and $(\mathcal{V},\psi)$ are said to
            be $C^{\infty}$ compatible if $\psi\circ\phi^{\minus{1}}$,
            defined as a function from $\varphi(\mathcal{U}\cap\mathcal{V})$ to
            $\psi(\mathcal{U}\cap\mathcal{V})$, is a diffeomprhism.
        \end{definition}
        \begin{definition}
            Let $M$ be an $n$ dimensional topological manifold. A smooth atlas
            on $M$ is a collection $\mathcal{A}$ of charts
            $(\mathcal{U},\varphi)$ that cover $M$ and such that all charts
            are smoothly compatible. A smooth atlas $\mathcal{A}$ on $M$ is
            called maximal if it is not contained in any strictly larger
            smooth atlas. A smooth structure on $M$ is a maximal smooth atlas.
        \end{definition}
        \begin{definition}
            A smooth manifold is a topological manifold $(X,\tau)$ with a
            smooth structure $\mathcal{A}$.
        \end{definition}
        \begin{theorem}
            If $M$ is an $n$ dimensional topological manifold, and if
            $\mathcal{A}$ is a smooth atlas on $M$, then there is a unique
            maximal atlas $\mathcal{A}'$ such that
            $\mathcal{A}\subseteq\mathcal{A}'$.
        \end{theorem}
\end{document}