%------------------------------------------------------------------------------%
\documentclass[crop=false,class=article]{standalone}                           %
%------------------------------Preamble----------------------------------------%
\makeatletter                                                                  %
    \def\input@path{{../../../../}}                                            %
\makeatother                                                                   %
\input{preamble.tex}                                                           %
%----------------------------Main Document-------------------------------------%
\begin{document}
    \pagenumbering{roman}
    \title{Measure Theory and Complex Analysis}
    \author{Ryan Maguire}
    \date{\vspace{-5ex}}
    \maketitle
    \vspace{10ex}
    \pagenumbering{arabic}
    \setcounter{section}{1}
    \section*{Final}
    \begin{problem}
        \label{Final_Problem_1}%
        Let $z_{0}\in\mathbb{C}$, $r>0$, and let $A_{r}(z_{0})$ be defined by:
        \begin{equation}
            A_{r}(z_{0})=\{\,z\in\mathbb{C}\;|\;r<|z-z_{0}|\,\}
        \end{equation}
        In other words,
        $A_{r}(z_{0})=\mathbb{C}\setminus\textrm{Cl}(B_{r}(z_{0}))$, where
        $B_{r}(z_{0})$ is the open ball of radius $r$ centered about $z_{0}$.
        Suppose $b:\mathbb{N}\rightarrow\mathbb{C}$ is a sequence such that,
        for all $z\in{A}_{r}(z_{0})$, the following sum converges:
        \begin{equation}
            g(z)=\sum_{n=1}^{\infty}\frac{b_{n}}{(z-z_{0})^{n}}
        \end{equation}
        Show that $g$ and $g'$ are holomorphic on $A_{r}(z_{0})$ and that:
        \begin{equation}
            \dot{g}(z)=\sum_{n=1}^{\infty}\frac{\minus{n}b_{n}}{(z-z_{0})^{n+1}}
        \end{equation}
    \end{problem}
    \begin{figure}[H]
        \centering
        \captionsetup{type=figure}
        \begin{tikzpicture}[>=Latex]
            \coordinate (z0) at (2.000, 2.000);
            \coordinate (C)  at (3.300, 3.300);
            \coordinate (r)  at (2.707, 2.707);
            \fill[fill=cyan,opacity=0.5] (-2.2, -2.2) rectangle (4.2, 4.2);
            \draw[densely dashed,fill=white] (z0) circle (1);

            \draw[<->] (-2.2,  0.0) to (4.2, 0.0) node[below left]  {$\Re(z)$};
            \draw[<->] ( 0.0, -2.2) to (0.0, 4.2) node[below right] {$\Im(z)$};
            \draw[densely dashed] (2.0, 0.0) to (z0);
            \draw[densely dashed] (0.0, 2.0) to (z0);
            \draw[fill=black] (z0) circle (0.5mm);
            \draw (z0) to node[below] {$r$} (r);
            \node at (z0) [below left] {$z_{0}$};
            \node at (C) {\Large{$\mathbb{C}$}};
        \end{tikzpicture}
        \caption{Drawing for Problem~\ref{Final_Problem_1}}
        \label{fig:Problem_1}
    \end{figure}
    \begin{solution}
        For the convergence can be proven to be almost uniform. Indeed, if
        $R>r$ and $|z-z_{0}|=R$, then:
        \begin{equation}
            \Big|\sum_{n=1}^{\infty}\frac{b_{n}}{(z-z_{0})^{n}}\Big|
            \leq\sum_{n=1}^{\infty}\Big|\frac{b_{n}}{(z-z_{0})^{n}}\Big|
            \leq\sum_{n=1}^{\infty}\frac{|b_{n}|}{R^{n}}
        \end{equation}
        But the sum converges, and thus by Cauchy's convergence criterion, for
        all $z\in{A}_{r}(z_{0})$, the following is true:
        \begin{equation}
            \underset{n\rightarrow\infty}{\lim}\frac{b_{n}}{(z-z_{0})^{n}}=0
        \end{equation}
        We can thus take the modulus of this, showing:
        \begin{equation}
            \underset{n\rightarrow\infty}{\lim}
            \Big|\frac{b_{n}}{(z-z_{0})^{n}}\Big|=
            \underset{n\rightarrow\infty}{\lim}
            \frac{|b_{n}|}{|z-z_{0}|^{n}}=
            \underset{n\rightarrow\infty}{\lim}
            \frac{|b_{n}|}{R^{n}}=0
        \end{equation}
        But this is true for all $R>r$, and thus it is true of $(R+r)/2$.
        But then:
        \begin{equation}
            \Big|\sum_{n=1}^{\infty}\frac{b_{n}}{(z-z_{0})^{n}}\Big|
            \leq\sum_{n=1}^{\infty}\frac{(R+r)^{n}}{2^{n}R^{n}}
        \end{equation}
        And by the ratio test, this converges. Thus, by the Weierstrass M test,
        for all $R>r$ the sum converges uniformly on $A_{R}(z_{0})$, and since
        $\mu(A_{R}(z_{0})\setminus{A}_{r}(z_{0}))=\pi(R^{2}-r^{2})$ can be made
        arbitrarily small, the convergence is almost uniform. More precisely,
        for all $R>r$ the convergence is uniform on $A_{R}(z_{0})$ and the
        uniform limit of holomorphic functions is holomorphic, and thus
        $g(z)$ is holomorphic on $A_{R}(z_{0})$. But $R>r$ is arbitrary, and
        thus $g(z)$ is holomorphic on $A_{r}(z_{0})$. Similarly, let:
        \begin{equation}
            F(z)=\sum_{n=1}^{\infty}\frac{\minus{n}b_{n}}{(z-z_{0})^{n+1}}
        \end{equation}
        By a similar argument, this sum converges uniformly and thus $F(z)$
        is holomorphic. But uniform limits of functions may be integrated
        term by term. Applying the fundamental theorem of line integrals thus
        shows that $F(z)=\dot{g}(z)$.
        \par\hfill\par
        We can also apply Theorem 23, since we've shown that the convergence is
        uniform, it will thus be uniform on every compact subset of $\Omega$.
        Thus $g$ is holomorphic, and we may obtain $g'$ be differentiating
        term by term.
    \end{solution}
    \clearpage
    \begin{problem}
        Let $u:\Omega\rightarrow\mathbb{R}$ be a non-constant harmonic function
        on a convex open subset $\Omega\subseteq\mathbb{R}^{2}$. Show that $u$
        cannot have a local maximum.
    \end{problem}
    \begin{solution}
        For if $u$ is harmonic, then $u_{xx}+u_{yy}=0$.
        Let $F(z)=u_{x}(x,y)-iu_{y}(x,y)$. Then $F$ is holomorphic since it
        satisfies the Cauchy-Riemann equations:
        \begin{equation}
            \frac{\partial{u}_{x}}{\partial{x}}-
            \frac{\partial(\minus{u}_{y})}{\partial{y}}
            =\frac{\partial^{2}u}{\partial{x}^{2}}
            +\frac{\partial^{2}u}{\partial{y}^{2}}
            =0
        \end{equation}
        And thus the first Cauchy-Riemann equation is satisfied, and similarly
        for the second. But $\Omega$ is convex, and thus if $F$ is holomorphic
        on $\Omega$ then there is an antiderivative $f$ of $F$. That is, a
        function $f:\Omega\rightarrow\mathbb{C}$ such that $f'=F$. But then
        $\Re(f)=u_{x}+C$ for some constant $C$. We can take this to be zero.
        Let $g(z)=\exp(f(z))$. Then $g$ is holomorphic, and thus by the
        maximum modulus principle, $|g|$ has no local maximum. But
        $|g|=|\exp(f)|=\exp(\Re(f))=\exp(u)$, and thus $\exp(u)$ has no local
        maximum. But then $u$ has no local maximum.
    \end{solution}
    \clearpage
    \begin{problem}
        Suppose $f\in{H}(\Omega\setminus\{a\})$ has a pole of order $m$ at $a$.
        Prove that:
        \begin{itemize}
            \item[(a)]  $\underset{z\rightarrow{a}}{\lim}|(z-a)^{k}f(z)|=\infty$
                        for $0\leq{k}<m$.
            \item[(b)]  $\underset{z\rightarrow{a}}{\lim}|(z-a)^{m}f(z)|=L\ne0$ 
        \end{itemize} 
    \end{problem}
    \begin{solution}
        By the definition of a pole of order $m$, the function:
        \begin{equation}
            g(z)=f(z)-\sum_{k=1}^{m}\frac{b_{k}}{(z-a)^{k}}
        \end{equation}
        has a removable singularity at $a$ and $b_{m}\ne{0}$. That is,
        $\lim_{z\rightarrow{a}}g(z)$ exists. But then:
        \begin{equation}
            |(z-a)^{k}f(z)|=
            \Big|g(z)(z-a)^{k}+\sum_{k=1}^{m}\frac{b_{k}}{(z-a)^{m-k}}\Big|
        \end{equation}
        Thus, if $0\leq{k}<m$ the right side tends to infinity, and thus so
        does the left. If $k=m$ the limit is $|b_{m}|$, which is non-zero.
    \end{solution}
    \clearpage
    \begin{problem}
        Let $\Omega$ be a region and $a\in\Omega$. Suppose that
        $g\in{H}(\Omega\setminus\{a\})$ and that $g$ has a pole of order $m$ at
        $a$. Show that there is an $h\in{H}(\Omega)$ such that $h(a)\ne{0}$ and:
        \begin{equation}
            g(z)=\frac{h(z)}{(z-a)^{m}}
            \quad\quad
            z\in\Omega\setminus\{a\}
        \end{equation}
        Show that $f\in{H}(\Omega)$ has a zero of order $m$ at $a$ if and only
        if $1/f$ has a pole of order $m$ at $a$.
    \end{problem}
    \begin{solution}
        For if $g$ has a pole of order $m$ at $a$, then the function:
        \begin{equation}
            f(z)=g(z)-\sum_{k=1}^{m}\frac{b_{k}}{(z-a)^{k}}
        \end{equation}
        has a removable singularity at $a$, and $b_{m}\ne0$.
        But then for $z\ne{a}$:
        \begin{equation}
            g(z)=\frac{1}{(z-a)^{m}}
                \Big(f(z)(z-a)^{m}+\sum_{k=1}^{m}b_{k}(z-a)^{m-k}\Big)
        \end{equation}
        Let $h(z)$ be the numerator. Then $h(a)=b_{m}\ne{0}$, and moreover
        $h\in{H}(\Omega)$. This is because $f\in{H}(\Omega\setminus\{a\})$, and
        $f$ is continuous at $a$. But if $f$ is continuous at $a$, then
        $f(z)(z-a)^{m}$ is differentiable at $a$, and hence
        $f(z)(z-a)^{m}$ is differentiable for all $z\in\Omega$. Thus $h$ is the
        sum of a holomorphic function and a polynomial, and is therefore
        holomorphic.
        \par\hfill\par
        If $f\in{H}(\Omega)$ has a zero of order $m$ at $a$, then:
        \begin{equation}
            f(z)=\sum_{k=m}^{\infty}a_{k}(z-a)^{k}
            =(z-a)^{m}\sum_{k=0}^{\infty}a_{k+m}(z-a)^{k}
            \equiv(z-a)^{m}g(z)
        \end{equation}
        where $a_{m}\ne{0}$. But $g(a)\ne{0}$, and thus $1/g$ is well defined.
        And the reciprocal of a differentiable function is differentiable, and
        thus $1/g$ is differentiable in a neighborhood of $a$ and is therefore
        holomorphic. But then:
        \begin{equation}
            \frac{1}{f(z)}=\frac{\frac{1}{g(z)}}{(z-a)^{m}}
        \end{equation}
        which is the reciprocal of a holomorphic function and a power of
        $z-a$, and thus by the previous part of the problem, $1/f$ has a pole of
        order $m$ at $z=a$. Going the other way is a simple flip of this
        argument. If $f$ has a pole of order $m$, there is a holomorphic
        function $h$ such that:
        \begin{equation}
            f(z)=\frac{h(z)}{(z-a)^{m}}
        \end{equation}
        such that $h(a)\ne{0}$. But then
        $1/f(z)=(z-a)^{m}/h(z)$, and since $h(a)\ne{0}$, there is a neighborhood
        about $a$ such that $h(z)\ne{0}$ for all $z$ in that neighborhood. Thus,
        $1/f$ has a zero of order $m$ at $z=a$.
    \end{solution}
    \clearpage
    \begin{problem}
        Such that if $f\in{L}^{1}(\mathbb{R})$, and if $y\in\mathbb{R}$, then:
        \begin{equation}
            \int_{\mathbb{R}}f(x)\diff\mu(x)
            =\int_{\mathbb{R}}f(x-y)\diff\mu(y)
        \end{equation}
        Then show that $\phi_{y}(f)(x)=f(x-y)$ is a continuous function from
        $\mathbb{R}$ to $L^{1}(\mathbb{R})$.
    \end{problem}
    \begin{solution}
        For if $f\in{L}^{1}(\mathbb{R})$, then given $\varepsilon>0$,
        there is an $N\in\mathbb{N}$ such that for all $n,m>N$:
        \begin{equation}
            \Big|\int_{\mathbb{R}}f\diff\mu-\int_{[\minus{m},n]}f\diff\mu\Big|
            <\varepsilon
        \end{equation}
        But:
        \begin{equation}
            \Big|\int_{\mathbb{R}}f\diff\mu
                -\int_{[\minus{n},n]}f(x-y)\diff\mu(x)\Big|
            =\Big|\int_{\mathbb{R}}f\diff\mu
            -\int_{[\minus{n-y},n-y]}f\diff\mu\Big|
        \end{equation}
        And by the Archimedean property there is an $M\in\mathbb{N}$ such that
        $M>|y|$. Then for all $n>\max\{N,M\}$, we have:
        \begin{equation}
            \Big|\int_{\mathbb{R}}f\diff\mu
            -\int_{[\minus{n-y},n-y]}f\diff\mu\Big|<\varepsilon
        \end{equation}
        Thus proving the first claim. Suppose $y_{n}\rightarrow{y}$. Then:
        \begin{equation}
            \norm{\phi_{y_{n}}(f)-\phi_{y}(f)}_{1}
            =\int\big|f(x-y)-f(x-y_{n})\big|\diff\mu
        \end{equation}
        If $\norm{f}_{1}=0$, then $f=0$ $\mu$ almost everywhere and the problem
        is trivial. Thus, suppose not. Then since $y_{n}\rightarrow{y}$ there is
        an $N\in\mathbb{N}$ such that for all $n>N$ it is true that
        $|y-y_{n}|<\varepsilon/\norm{f}_{1}$.
    \end{solution}
\end{document}