\section{Stationary Phase Approximation}
    Suppose $g$ is an analytical function about
    the origin (i.e. it has a convergent MacLaurin series),
    and consider the integral:
    \begin{equation}
        I(k) = \int_{a}^{b}e^{ikg(x)}dx
    \end{equation}
    Suppose that there is a $c\in(a,b)$ such
    that $g'(c)=0$ and $g''(c)\ne 0$. Then:
    \begin{align}
        \nonumber I(k)&=e^{ikg(c)}\int_{a}^{b}e^{ik[g(x)-g(c)]}dx\\
        &=e^{ikg(c)}\int_{a}^{b}e^{ik[\frac{g''(c)}{2}(x-c)^{2}+\hdots]}dx
    \end{align}
    Higher terms are extremely oscillatory, and so we neglect them.
    Note that higher terms can indeed cancel each
    other out, meaning these neglected terms may
    not be negligible. For example, if
    $g(x)=-sin(\pi x)$, then $\exp(ig(x))$ is never
    too oscillatory. However, so long as the interval
    $[a,b]$ is small enough, the approximation is still
    valid. The previously mentioned $g(x)$ is how
    one approximates the $J_{0}(x)$ Bessel function.
    Out integral then becomes:
    \begin{align}
        I(k)&\approx e^{ikg(c)}
                \int_{a}^{b}e^{ik\frac{g''(c)}{2}(x-c)^{2}}dx\\
            &\approx e^{ikg(c)}
                \int_{\infty}^{\infty}
                \exp(ik\frac{g''(c)}{2}(x-c)^{2})\diff{x}\\
            &=e^{ikg(c)}\sqrt{\frac{2\pi i}{kg''(c)}}
    \end{align}
    We can use this for our double integral,
    and make it a single integral. The first and
    second integrals of $\psi$ are nasty, however.
    \begin{equation}
        \begin{split}
            \frac{\partial\psi}{\partial\phi}
            &=kD\Big[\frac{2D\rho\cos(B)
                \sin(\phi)+2\rho\rho_{0}
            \sin(\phi-\phi_{0})}{2D^2\sqrt{1+2\cos(B)
            \frac{\rho_{0}\cos(\phi_{0})-\rho\cos(\phi)}{D}+
            \frac{\rho^{2}+\rho_{0}^{2}-
            2\rho\rho_{0}\cos(\phi-\phi_{0})}{D^2}}}\\
            &\quad\quad\quad\quad\quad
            -\frac{\rho\cos(B)\sin(\phi)}{D}\Big]
        \end{split}
    \end{equation}
    The second derivative is equally bad.
    Solving for $\frac{\partial\psi}{\partial\phi}=0$
    must be done iteratively by successive approximations.
    A further approximation can be made as $\psi$
    is analytic in $\phi$. Let $\phi_{s}$ be
    the solution to $\frac{\partial\psi}{\partial\phi}$
    and let $\phi_{s_{n}}$ be a sequence such that
    $\phi_{s_{n}}\rightarrow\phi_{s}$.
