%------------------------------------------------------------------------------%
\chapter{Logic}
    This chapter serves as providing preliminary material for the rest of
    the text and discussing how the English language will be used to formulate
    mathematics.
    \par\hfill\par
    Talk about or, and, the symbols $\land$ and $\lor$, if then statements,
    logical negation, truth tables, quantifies ($\exists$ and $\forall$).
    Talk about theorems and proofs, hypotheses and conclusions.
    Vacuous truths. Provide examples. Converse and contrapositive.
\chapter{Zermelo-Fraenkel Set Theory}
    We'll start from the basics and develop mathematics from an axiomatic
    standpoint, adopting as truths the few postulates of Zermelo and
    Fraenkel. We'll then add the axiom of choice to our toolbelt and
    proceed from there to define and prove many of the basic and familiar
    results and concepts of mathematics. It is important not to take anything
    for granted even if something seems obvious. The existence of many sets
    will be proved, rather than accepting these things as trivial truths.
    \ifcsname\PATH\endcsname
        \newcommand{\PATH}{books/Foundations/Zermelo_Fraenkel_Set_Theory}
    \else
        \renewcommand{\PATH}{books/Foundations/Zermelo_Fraenkel_Set_Theory}
    \fi

    %   Similarly {a}\inP(X) but {a}\nsubseteq{P}(X)

    %   Add a comment about unions and intersections over empty collections.

    %   Add a comment about ordered pair notation vs. interval notation.

    \input{\PATH/Elementary_Set_Theory/Zermelo_Fraenkel.tex}
    % \input{\PATH/Elementary_Set_Theory/Relations.tex}
\chapter{Function Theory}
    \input{\PATH/Function_Theory/Boolean_Algebra.tex}