\documentclass[crop=false,class=article,oneside]{standalone}
%----------------------------Preamble-------------------------------%
\input{../../../../preamble.tex}
\graphicspath{{../../../../images/}}    % Path to Image Folder.
%--------------------------Main Document----------------------------%
\begin{document}
    \ifx\ifmathcourseschaostheory\undefined
        \section*{Chaos Theory}
        \setcounter{section}{1}
        \renewcommand\thefigure{\arabic{section}.\arabic{figure}}
        \renewcommand\thesubfigure{%
            \arabic{section}.\arabic{figure}.\arabic{subfigure}}
    \else
        \section{Lecture Notes from Fall 2016 (UML)}
    \fi
    \subsection{First Order Equations}
        The first differential equation that is often studied
        is $\dot{x}(t)=ax(t)$, where $\dot{x}$ denotes the
        derivative of $x$ with respect to $t$. In this equation
        $a$ is some fixed constant parameter, and each real
        value $a$ defines a different differential equation.
        We can solve this by integrating and invoking the
        fundamental theorem of calculus. In general, a
        differential equation is an equation that relates
        a differentiable functions to its derivatives.
        The general solution to a differential equation is
        the set of all functions that satisfy the
        differential equation.
        \begin{frametheorem}{}{thm:CHAOS:SIMPLE_DIFF_EQ}
            If $x(t)$ is a differentiable function such
            that $x(0)=x_{0}$ and there is a $k\in\mathbb{R}$
            such that for all $t\in\mathbb{R}$, $\dot{x}(t)=kx(t)$,
            then $x(t)=x_{0}\exp(kt)$.
        \end{frametheorem}
        \begin{proof}
            Let $y(t)=\exp(kt)$. Then $\dot{y}(t)=ky(t)$,
            and $y(t)\ne{0}$ for all $t\in\mathbb{R}$.
            Let $F(t)=x(t)/y(t)$. Then:
            \begin{equation*}
                \dot{F}(t)=
                \frac{y(t)\dot{x}(t)-\dot{y}(t)x(t)}{y^{2}(t)}
                =\frac{y(t)\big(\dot{x}(t)-kx(t)\big)}{y^{2}(t)}
                =\frac{1}{y(t)}\big(\dot{x}(t)-kx(t)\big)
            \end{equation*}
            But $\dot{x}(t)-kx(t)=0$, and thus $\dot{F}(t)=0$ for
            all $t\in\mathbb{R}$. But then $F(t)$ is a constant
            function. Thus there is a $C\in\mathbb{R}$ such
            that $x(t)=Cy(t)$. But $x(0)=x_{0}$, and therefore
            $C=x_{0}$. Thus, $x(t)=x_{0}\exp(kt)$.
        \end{proof}
        The proof shows that the solution to $\dot{x}(t)=kx(t)$
        is uniquely determined if $x(0)$ is known. This can
        be replaced by knowledge of $x(t_{0})$ for any point
        $t_{0}\in\mathbb{R}$.
        Such restraints are called initial conditions to a
        differential equation. Initial conditions are
        requirements that a solution to the differential
        equation must satisfy. Such requirements can be
        the value of $x(t_{0})$ at a certain point
        $t_{0}$, or a requirement on $\dot{x}(t)$.
        \begin{frameexample}{}{}
            Consider the following initial value problem:
            \begin{align*}
                \dot{x}(t)&=ax(t)
                &
                x(t_{0})&=x_{0}
            \end{align*}
            Using the previous theorem, we can translate the
            problem by $\exp(-kt_{0})$ to create the initial
            value problem $\dot{y}(t)=ky(t)$, $y(0)=x_{0}$.
            We know the solution to this is
            $y(t)=x_{0}\exp(kt)$. Thus, the solution to the
            original initial value problem is:
            \begin{equation*}
                x(t)=x_{0}\exp(k(t-t_{0}))
            \end{equation*}
        \end{frameexample}
        An important class of solutions to differential
        equations are \textit{equilibrium solutions}.
        \begin{framedefinition}{Equilibrium Solution}{}
            An equilibrium solution to a differential
            equation is a solution $x(t)$ such that
            $\dot{x}(t)=0$ for all $t\in\mathbb{R}$.
            That is, a constant solution $x(t)=c$.
        \end{framedefinition}
        Studying our first problem $\dot{x}(t)=kx(t)$,
        we see that the only equilibrium solution
        occurs when $x_{0}=0$. Another important concept
        is the limiting behavior of the solution to a
        differential equation. The limiting behavior
        is often dependent on the various parameters that
        may be present in a given differential equation.
        We can see this by further studying $\dot{x}(t)=kx(t)$.
        If $k=0$ we see that $x(t)$ is a constant function. That
        is, $x(t)=x_{0}$ for all $t\in\mathbb{R}$. For $k>0$,
        solutions diverges monotonically to $\infty$
        ($x_{0}>0$) or $-\infty$ ($x_{0}<0$).
        Finally, if $k<0$ then $x(t)$ converges to $0$
        for all values of $x_{0}$.
        \subsubsection{Notes on the Jordan Normal Form}
            Every square matrix $A$ is similar to an upper
            triangular matrix $J$ in
            \textit{Jordan normal form} whose diagonal entries
            are the eigenvalues of $A$. That is, there exists
            an invertible matrix $P$ such that $P^{-1}AP=J$.
            The trace of $A$ is equal to the trace of $J$:
            \begin{equation*}
                \Tr(J)
                =\Tr(P^{-1}AP)
                =\Tr(P^{-1}PA)
                =\Tr(IA)=\Tr(A)
            \end{equation*}
        \subsubsection{Notes on Conjugacy}
            \begin{minipage}[t]{0.49\textwidth}
                We have:
                \begin{align*}
                    X'(t)&=AX(t),\quad
                    X(0)=X_{0}\\
                    \Rightarrow
                    X(t)&=e^{tA}X_{0}\\
                    \Rightarrow
                    \phi^{A}(t,X_{0})
                    &=e^{tA}X_{0}
                \end{align*}
            \end{minipage}
            \vline
            \hfill
            \begin{minipage}[t]{0.49\textwidth}
                If $B=T^{-1}AT$, for some matrix $T$, then:
                \begin{align*}
                    Y'(t)&=BY(t),\quad
                    Y(0)=Y_{0}\\
                    &=T^{-1}ATY(t)\\
                    \Rightarrow
                    Y(t)
                    &=e^{tT^{-1}AT}Y_{0}\\
                    &=T^{-1}e^{tA}TY_{0}\\
                    \Rightarrow
                    \phi^{B}(t,Y_{0})
                    &=T^{-1}e^{tA}TY_{0}
                \end{align*}
            \end{minipage}
            Thus, the homeomorphism is $h(X)=T^{-1}X$,
            and we have:
            \begin{equation*}
                \phi^{B}(t,h(X_{0}))
                =\phi^{B}(t,T^{-1}X_{0})
                =T^{-1}e^{tA}T(T^{-1}X_{0})
                =T^{-1}e^{tA}X_{0}
                =h(\phi^{A}(t,X_{0}))
            \end{equation*}
\end{document}