%------------------------------------------------------------------------------%
\begingroup
    \ifcsname\PATH\endcsname
        \newcommand{\PATH}{books/Foundations/ZFC}
        \newcommand{\OLDPATH}{\PATH}
    \else
        \newcommand{\OLDPATH}{\PATH}
        \renewcommand{\PATH}{books/Foundations/ZFC}
    \fi
    \chapter{Logic}
        \label{chapt:Logic}%
        This chapter provides preliminary material for the rest of the text and
        discusses how the English language is be used to formulate mathematics.
        \input{\PATH/Logic/Connectives.tex}
        \input{\PATH/Logic/Quantifiers.tex}
    \chapter{Zermelo-Fraenkel Set Theory}
        \label{chapt:Zermelo_Fraenkel_Set_Theory}%
        We'll develop mathematics from an axiomatic view built on set theory,
        adopting as truths the few postulates of Zermelo and Fraenkel. We'll
        then add the axiom of choice and proceed from there to define many
        familiar concepts and prove some basic results that are often taken for
        granted. The existence of many types of sets will be proven, rather than
        accepting these things as trivial truths.
        \input{\PATH/Elementary_Set_Theory/Zermelo_Fraenkel.tex}
        \input{\PATH/Elementary_Set_Theory/The_Structure_of_Sets.tex}
        \input{\PATH/Elementary_Set_Theory/Relations.tex}
    \chapter{Function Theory}
        \label{chapt:Function_Theory}%
        Functions serve as a basic tool for studying mathematics, so much so
        that it is often taken as fundamental and no definition is given. We've
        adopted the definition that a function\index{Function} from a set $A$ to
        a set $B$, $f:A\rightarrow{B}$, is a subset of the Cartesian product
        $A\times{B}$ with a few properties. We now take the time to examine the
        implications of this definition.
        \input{\PATH/Function_Theory/Definitions.tex}
        \input{\PATH/Function_Theory/Binary_Operations.tex}
        \input{\PATH/Function_Theory/Boolean_Algebras.tex}
        \input{\PATH/Function_Theory/Sequences_and_Matrices.tex}
    \chapter{The Real Numbers}
        Now that the notion of function has been developed, and most of ZFC laid
        out, we take the time to discuss the next axiom on the list:
        \textit{the axiom of infinity}\index{Axiom!of Infinity}. This axiom,
        while controversial, posits the existence of an infinite set and allows
        us to construct the natural numbers and the real numbers in the
        framework of set theory.
    \chapter{Cardinality}
        \input{\PATH/Cardinality/Cardinality.tex}
    \renewcommand{\PATH}{\OLDPATH}
\endgroup