\section{Definitions}
    The notion described in the preceding paragraph is that of a \gls{ring}. We
    can weaken this slightly and describe what is called a \textit{rng}.
    \subsection{Rngs}
        \begin{fdefinition}{Rng}{Rng}
            A \gls{rng} is an \gls{Abelian group} $(R,+)$ and a \gls{semigroup}
            $(R,\cdot\,)$ such that $\cdot$ is a \gls{distributive operation}
            over $+$. A rng is denoted $(R,+,\cdot\,)$.
        \end{fdefinition}
        The unital element of the Abelian group $(R,+)$ is often denoted 0 and
        is called the zero element. Zero has the property that multiplication by
        zero returns zero for any element.
        \begin{theorem}
            \label{thm:Mult_By_Zero_in_Rng}%
            If $(R,+,\cdot\,)$ is a rng, if 0 is the unital element of $(R,+)$,
            and if $r\in{R}$, then $r\cdot{0}=0$.
        \end{theorem}
        \begin{proof}
            For since $(R,+)$ is an Abelian group, if $r\cdot{0}\in{R}$ then
            there is an inverse element $\minus{r}\cdot{0}$
            (Def.~\ref{def:Group}). But then:
            \begin{align}
                0&=r\cdot{0}-r\cdot{0}
                \tag{Inverse Property of Groups}\\
                &=r\cdot(0-0)
                \tag{Distributive Property}\\
                &=r\cdot{0}
                \tag{Identity Property}
            \end{align}
            And therefore $r\cdot{0}=0$.
        \end{proof}
        The converse of this theorem fails in a general rng, but is true in a
        ring (see Thm.~\ref{thm:Mult_by_Zero_Always_Zero_Implies_Zero_in_Ring}).
        To see this we will show that we can construct a rng from any Abelian
        group in a trivial manner such that the converse fails.
        \begin{theorem}
            \label{thm:rng_induced_by_Abelian_group}%
            If $(R,+)$ is an Abelian group, then there is an associative
            binary operation $\cdot$ on $R$ such that $(R,+,\cdot\,)$ is a rng.
        \end{theorem}
        \begin{proof}
            For let $\cdot:R\times{R}\rightarrow{R}$ be defined by $r\cdot{s}=0$
            for all $r,s\in{R}$. Then $\cdot$ is a binary operation since for
            all $(r,s)\in{R}\times{R}$ there is a unique $x\in{R}$ such that
            $r\cdot{s}=x$, and thus $\cdot$ is a function
            (Def.~\ref{def:Function}). Moreover, it is associative. For if not
            then there are $r,s,t\in{R}$ such that
            $r\cdot(s\cdot{t})\ne(r\cdot{s})\cdot{t}$. But by definition
            $s\cdot{t}=0$, and thus $r\cdot{0}=0$. Similarly, $r\cdot{s}=0$
            and $0\cdot{t}=0$, a contradiction. Thus $\cdot$ is associative.
            Thus, $(R,\cdot)$ is a semigroup (Def.~\ref{def:Semigroup}).
            Finally, $\cdot$ is associative over $+$. For let $a,b,c\in{R}$.
            Then:
            \begin{equation}
                a\cdot(b+c)=0=0+0=(a\cdot{b})+(a\cdot{c})
            \end{equation}
            and thus by the transitivity of equality
            (Thm.~\ref{thm:Transitivity_of_Equality}),
            $a\cdot(b+c)=(a\cdot{b})+(a\cdot{c})$. Thus, $(R,+,\cdot\,)$ is a
            rng (Def.~\ref{def:Rng}).
        \end{proof}
        A rng with the property that $a\cdot{b}=0$ for all $a,b\in{R}$ is a
        occasionally called a rng of square zero. If we take an Abelian group
        with at least two elements, the rng of square zero generated from this
        will have the property that there exists a $b\in{R}$ such that $b\ne{0}$
        and for all $a\in{R}$, $a\cdot{b}=b\cdot{a}=0$.
    \subsection{Rings}
        \begin{fdefinition}{Ring}{Ring}
            A \gls{ring} is a \gls{rng} $(R,+,\cdot\,)$ such that $(R,\cdot\,)$
            is a \gls{monoid}. That is, an \gls{Abelian group} $(R,+)$ and a
            monoid $(R,\cdot\,)$ such that $\cdot$ is a
            \gls{distributive operation} over $+$.
        \end{fdefinition}
        Once $(R,\cdot)$ has a unital element we can prove that zero is the
        only element such that $0\cdot{r}=0$ for all $r\in{R}$. That is, the
        converse of Thm.~\ref{thm:Mult_By_Zero_in_Rng} is true in a ring.
        \begin{theorem}
            \label{thm:Mult_by_Zero_Always_Zero_Implies_Zero_in_Ring}%
            If $(R,+,\cdot\,)$ is a ring, if $0$ is the unital element of
            $(R,+)$, and if $r$ is such that for all $s\in{R}$ it is true that
            $r\cdot{s}=0$, then $r=0$.
        \end{theorem}
        \begin{proof}
            For if $(R,+,\cdot\,)$ is a ring, then $(R,\cdot\,)$ is a monoid
            (Def.~\ref{def:Ring}) and thus there is a unital element, 1, of
            $(R,\cdot\,)$ (Def.~\ref{def:Monoid}). But then for all $s\in{R}$
            we have:
            \begin{align}
                r+s&=(r+s)\cdot{1}
                \tag{Identity Property of 1}\\
                &=(r\cdot{1})+(s\cdot{1})
                \tag{Distributive Property}\\
                &=0+s\cdot{1}
                \tag{Hypothesis}\\
                &=s\cdot{1}
                \tag{Identity Property of 0}\\
                &=s
                \tag{Identity Property of 1}
            \end{align}
            And thus, for all $s\in{R}$, $r+s=s$. But $(R,+)$ is an Abelian
            group, and thus if $r+s=s$, then $s+r=s$
            (Def.~\ref{def:Abelian_Group}) and therefore $r$ is a unital element
            of $(R,+)$ (Def.~\ref{def:Unital_Element}). But the unital element
            of a group is unique, and therefore $r=0$.
        \end{proof}
        Given any Abelian group $(R,+)$, there is an associative binary
        operation $\cdot$ such that $(R,+,\cdot\,)$ is a rng
        (Thm.~\ref{thm:rng_induced_by_Abelian_group}). Rings do not have this
        property, as we will now demonstrate.
        \begin{theorem}
            \label{thm:Abelian_group_that_is_not_a_ring}%
            If $(R,+)$ is an Abelian group such that for all $a\in{R}$ there is
            an $n\in\mathbb{N}^{+}$ such that $na=0$, if $E$ is the set:
            \begin{equation}
                E=\{\,n\in\mathbb{N}^{+}\;|
                    \;\exists_{a\in{R}}:na=0\land
                    \forall_{k\in\mathbb{Z}_{n}\setminus\{0\}}(ka\ne{0})\,\}
            \end{equation}
            and if $E$ is infinite, then there is no binary operation $\cdot$ on
            $R$ such that $(R,+,\cdot\,)$ is a ring.
        \end{theorem}
        \begin{proof}
            For suppose not and let $\cdot$ be such a binary operation. But if
            $(R,+,\cdot\,)$ is a ring, then $(R,\cdot)$ is a monoid
            (Def.~\ref{def:Ring}) and thus there is a unital element $1$ of
            $(R,\cdot\,)$ (Def.~\ref{def:Monoid}). But by hypothesis there is an
            $n\in\mathbb{N}$ such that $n1=0$. But then for all $a\in{R}$, by
            associativity and Thm.~\ref{thm:Mult_By_Zero_in_Rng} we have:
            \begin{equation}
                ka=k(1\cdot{a})=(k1)\cdot{a}=0\cdot{a}=0
            \end{equation}
            Thus the set $E$ is bounded by $k$. But then
            $E\subseteq\mathbb{Z}_{k}$, and is therefore finite. A contradiction
            as $E$ is infinite. Thus, $(R,+,\cdot)$ is not a ring.
        \end{proof}
        \begin{example}
            Let $(\mathbb{Q},+)$ and $(\mathbb{Z},+)$ be the usual additive
            groups and consider the quotient group on $\mathbb{Q}/\mathbb{Z}$.
            This is Abelian since $\mathbb{Z}$ is a normal subgroup of
            $(\mathbb{Q},+)$, but for every element $a\in\mathbb{Q}/\mathbb{Z}$
            there is an $n\in\mathbb{N}^{+}$ such that $na=0$. That is, given an
            equivalence class $a\in\mathbb{Q}/\mathbb{Z}$, let $p/q\in[0,1)$ be
            a representative. Then $qa=[p]=[0]$, where $[p]$ is the equivalence
            class of $[p]$ in the quotient group. Thus every element is a
            torsion element. Morevoer, for all $n\in\mathbb{N}^{+}$ there is a
            $a\in\mathbb{Q}/\mathbb{Z}$ such $na=0$ and for all
            $k\in\mathbb{Z}_{n}^{+}$, $ka\ne{0}$. To see this, let
            $a=[1/n]$. So by Thm.~\ref{thm:Abelian_group_that_is_not_a_ring}
            there is no ring structure on $\mathbb{Q}/\mathbb{Z}$.
        \end{example}