%------------------------------------------------------------------------------%
\begingroup
    \ifcsname\PATH\endcsname
        \newcommand{\PATH}{books/Foundations/Logic_and_Sets}
        \newcommand{\OLDPATH}{\PATH}
    \else
        \newcommand{\OLDPATH}{\PATH}
        \renewcommand{\PATH}{books/Foundations/Logic_and_Sets}
    \fi
    \chapter{Propositional Logic}
        \label{chapt:Propositional_Logic}%
        We'll begin our discussion of logic with the most primitive kind:
        propositional logic\index{Logic!Propositional}. This form, also called
        \textit{sentential logic}\index{Logic!Sentential}, deals with the
        structure of sentences. We'll learn how the English language is used to
        formulate arguments and deduce new facts. It is for this reason that one
        should start with the foundations of logic, for at the heart of
        mathematics is the concept of \textit{definition}, \textit{theorem}, and
        \textit{proof}. The word definition, it is hoped, is understood as a
        primitive word in the English language (much like the word \textit{the})
        but theorem and proof need an explaination if we are to use them
        consistently. We'll discuss propositions, predicates, and the concepts
        of implication and negation. Later we will study mathematical logic when
        developing Boolean algebras\index{Boolean Algebra} in
        Book~\ref{book:Foundations} and Stone spaces in
        Book~\ref{book:Topology}, culminating in Stone's representation
        theorem\index{Theorem!Stone's Representation}, connecting logic, set
        theory, topology, and measure theory in a remarkable way.
        \input{\PATH/Propositional_Logic/What_is_Logic.tex}
        \input{\PATH/Propositional_Logic/Hilbert_Systems.tex}
    \chapter{Predicate Calculus}
        \label{chapt:Predicate_Calculus}%
        \input{\PATH/Predicate_Calculus/Quantifiers.tex}
    \chapter{Zermelo-Fraenkel Set Theory}
        \label{chapt:Zermelo_Fraenkel_Set_Theory}%
        We'll develop mathematics from an axiomatic view built on set theory,
        adopting as truths the few postulates of Zermelo and Fraenkel. We'll
        then add the axiom of choice and proceed from there to define many
        familiar concepts and prove some basic results that are often taken for
        granted. The existence of many types of sets will be proven, rather than
        accepting these things as trivial truths.
        \input{\PATH/Elementary_Set_Theory/Zermelo_Fraenkel.tex}
        \input{\PATH/Elementary_Set_Theory/The_Structure_of_Sets.tex}
        \input{\PATH/Elementary_Set_Theory/Relations.tex}
        \chapter{The Real Numbers}
        Now that most of ZFC has been laid out, we take the time to discuss the
        next axiom on the list:
        \textit{the axiom of infinity}\index{Axiom!of Infinity}. This axiom,
        while controversial, posits the existence of an infinite set and allows
        us to construct the natural numbers and the real numbers in the
        framework of set theory.
    \chapter{Function Theory}
        \label{chapt:Function_Theory}%
        Functions serve as a basic tool for studying mathematics, so much so
        that it is often taken as fundamental and no definition is given. We've
        adopted the definition that a function\index{Function} from a set $A$ to
        a set $B$, $f:A\rightarrow{B}$, is a subset of the Cartesian product
        $A\times{B}$ with a few properties (see Def.~\ref{def:Function}). We now
        take the time to examine the implications of this definition.
        \input{\PATH/Function_Theory/Definitions.tex}
        \input{\PATH/Function_Theory/Binary_Operations.tex}
        \input{\PATH/Function_Theory/Boolean_Algebras.tex}
        \input{\PATH/Function_Theory/Sequences_and_Matrices.tex}
    \chapter{Arithmetic}
        \input{\PATH/Arithmetic/Elementary_Number_Theory.tex}
        \input{\PATH/Arithmetic/Modulo_Arithmetic.tex}
    \chapter{Cardinality}
        \input{\PATH/Cardinality/Cardinality.tex}
    \renewcommand{\PATH}{\OLDPATH}
\endgroup