%------------------------------------------------------------------------------%
\documentclass{article}                                                        %
%------------------------------Preamble----------------------------------------%
\makeatletter                                                                  %
    \def\input@path{{../../}}                                                  %
\makeatother                                                                   %
\input{preamble.tex}                                                           %
%----------------------------Main Document-------------------------------------%
\begin{document}
    \title{Galois Theory}
    \author{Ryan Maguire}
    \date{\vspace{-5ex}}
    \maketitle
    \tableofcontents
    Riemann existence theorem, branched covers, etc.
    \section{Rings}
        Definition of ring, commutative ring, subring, and ideal are assumed.
        \begin{fdefinition}{Prime Ideal}{Prime_Ideal}
            A prime ideal of a commutative ring $\ring{R}$ is an ideal
            $I\subsetneq{R}$ such that for all $a,b\in{R}$ such that
            $a\cdot{b}\in{I}$, it is true that either $a\in{I}$ or $b\in{I}$.
        \end{fdefinition}
        This is a generalization of a theorem due to Euclid which states that if
        $a,b\in\mathbb{Z}$ are integers, and if $p\in\mathbb{N}$ is a prime such
        that $p$ divides $a\cdot{b}$, then either $p$ divides $a$ or $p$ divides
        $b$. We can use this to prove the following theorem.
        \begin{theorem}
            \label{thm:Prime_Ideals_of_Z}%
            If $\ring{\mathbb{Z}}$ is the usual ring structure on $\mathbb{Z}$,
            and if $p\in\mathbb{Z}$, then $p\mathbb{Z}$ is a prime ideal of
            $\mathbb{Z}$ if and only if $p$ is prime.
        \end{theorem}
        \begin{proof}
            For if $p\in\mathbb{N}$ is prime, and if $a,b\in\mathbb{Z}$ are such
            that $a\cdot{b}\in{p}\mathbb{Z}$, then there is an $m\in\mathbb{Z}$
            such that $a\cdot{b}=m\cdot{p}$. But then $p$ divides $a\cdot{b}$,
            and thus either $p$ divides $a$ or $p$ divides $b$. But if $p$
            divides $a$, then $a\in{p}\mathbb{Z}$, and similarly if $p$ divides
            $b$. Hence, $p\mathbb{Z}$ is a prime ideal. In the other direction,
            if $p\mathbb{Z}$ is a prime ideal, suppose $p$ is not prime. Then
            there are integers $a,b\in\mathbb{Z}$, neither of which are units,
            such that $p=a\cdot{b}$. But by hypothesis $p\mathbb{Z}$ is a prime
            ideal, and hence if $a\cdot{b}\in{p}\mathbb{Z}$, then either
            $a\in{p}\mathbb{Z}$ or $b\in{p}\mathbb{Z}$. But if
            $a\in{p}\mathbb{Z}$, then there is an $m\in\mathbb{Z}$ such that
            $a=m\cdot{p}$. But $a\cdot{b}=p$, and hence $m\cdot{p}\cdot{b}=p$.
            But then $m\cdot{b}=1$, and thus $b$ is a unit, which is a
            contradition. Hence, $p$ is prime.
        \end{proof}
        We can use this to generate examples of prime ideals.
        \begin{example}
            The even integers $\mathbb{Z}_{e}$ form a prime ideal of
            $\mathbb{Z}$. This can be seen immediately once one notes that
            $\mathbb{Z}_{e}=2\mathbb{Z}$, and since $2$ is a prime number,
            by Thm.~\ref{thm:Prime_Ideals_of_Z} we see that $2\mathbb{Z}$ is a
            prime ideal.
        \end{example}
        A useful equivalent definition of prime ideals goes as follows:
        \begin{theorem}
            If $\ring{R}$ is a ring, and if $I\subsetneq{R}$ is an ideal, then
            it is a prime ideal if and only if for all $a,b\in{R}\setminus\{I\}$
            it is true that $a\cdot{b}\in{R}\setminus\{I\}$.
        \end{theorem}
        \begin{proof}
            For if $I$ is a prime ideal, then for all $a,b\in{R}$ such that
            $a\cdot{b}\in{I}$, it is true that either $a\in{I}$ or $b\in{I}$.
            Suppose there exists $a,b\in{R}\setminus\{I\}$ such that
            $a\cdot{b}\notin{R}\setminus\{I\}$. But since $\cdot$ is a binary
            operation it is true that $a\cdot{b}\in{R}$, and hence if
            $a\cdot{b}\notin{R}\setminus{I}$, then $a\cdot{b}\in{I}$. But $I$ is
            a prime ideal, and thus if $a\cdot{b}\in{I}$ then either $a\in{I}$
            or $b\in{I}$, a contradiction since by hypothesis $a,b\notin{I}$.
            Therefore, $a\cdot{b}\in{R}\setminus\{I\}$. In the other direction,
            if $R\setminus\{I\}$ is multiplicatively closed, suppose $a,b\in{R}$
            are such that $a\cdot{b}\in{I}$. But $R\setminus\{I\}$ is
            multiplicatively closed, and thus if $a,b\in{R}\setminus\{I\}$, then
            $a\cdot{b}\in{R}\setminus\{I\}$, a contradiction, and thus either
            $a\in{I}$ or $b\in{I}$. Thus, $I$ is a prime ideal.
        \end{proof}
        \begin{theorem}
            \label{thm:homo_pre_image_of_ideal_is_ideal}%
            If $\ring[R]{R}$ and $\ring[S]{S}$ are rings, if
            $\phi:R\rightarrow{S}$ is a ring homomoprhism, and if
            $I\subseteq{S}$ is an ideal in $S$, then $\phi^{\minus{1}}[I]$ is an
            ideal in $R$.
        \end{theorem}
        \begin{proof}
            Since $I$ is an ideal, $0_{S}\in{I}$, and since $\phi$ is a ring
            homomoprhism it is true that $\phi(0_{R})=0_{S}$. Hence,
            $\phi^{\minus{1}}[I]$ is non-empty. But if
            $a,b\in\phi^{\minus{1}}[I]$, then $\phi(a),\phi(b)\in{I}$. But
            $\phi$ is a ring homomoprhism and hence
            $\phi(a+_{R}b)=\phi(a)+_{S}\phi(b)$, and since $I$ is an ideal it is
            true that $\phi(a)+_{S}\phi(b)\in{I}$. Therefore
            $\phi(a+_{R}b)\in{I}$, and thus $a+_{R}b\in\phi^{\minus{1}}[I]$.
            Hence $\phi^{\minus{1}}[I]$ is closed to addition. But if $r\in{R}$
            and $a\in\phi^{\minus{1}}[I]$, then since $\phi$ is a ring
            homomoprhism it is true that
            $\phi(r\cdot_{R}a)=\phi(r)\cdot_{S}\phi(a)$. But since
            $a\in\phi^{\minus{1}}[I]$ it is true that $\phi(a)\in{I}$, and since
            $I$ is an ideal in $S$ it is therefore true that
            $\phi(r)\cdot_{S}\phi(a)\in{I}$. Thus, $\phi(r\cdot_{R}a)\in{I}$,
            and hence $r\cdot_{R}a\in\phi^{\minus{1}}[I]$. Therefore,
            $\phi^{\minus{1}}[I]$ is an ideal in $R$.
        \end{proof}
        \begin{theorem}
            If $\ring[R]{R}$ and $\ring[S]{S}$ are commutative rings, if
            $I\subsetneq{S}$ is a prime ideal, and if $\phi:R\rightarrow{S}$ is
            a ring homomoprhism, then $\phi^{\minus{1}}[I]$ is a prime ideal in
            $R$.
        \end{theorem}
        \begin{proof}
            For if $I$ is an ideal in $S$ and $\phi:R\rightarrow{S}$ is a ring
            homomorphism, then $\phi^{\minus{1}}[I]$ is an ideal in $R$
            (Thm.~\ref{thm:homo_pre_image_of_ideal_is_ideal}). Suppose
            $a,b\in{R}$ are such that $a\cdot_{R}b\in\phi^{\minus{1}}[I]$.
            But then $\phi(a\cdot_{R}b)\in{I}$, and since $\phi$ is a ring
            homomoprhism it is therefore true that
            $\phi(a\cdot_{R}b)=\phi(a)\cdot_{S}\phi(b)$. But $I$ is a prime
            ideal, and if $\phi(a)\cdot_{S}\phi(b)\in{I}$, then either
            $\phi(a)\in{I}$ or $\phi(b)\in{I}$. But then either
            $a\in\phi^{\minus{1}}[I]$ or $b\in\phi^{\minus{1}}[I]$, and hence
            $\phi^{\minus{1}}[I]$ is a prime ideal.
        \end{proof}
        Given a ring $\ring{R}$, the existence of prime ideals follows directly
        from the existence of \textit{maximal} ideals. We first must define such
        things, and then prove that every maximal ideal is prime.
        \begin{fdefinition}{Maximal Ideal}{Maximal_Ideal}
            A maximal ideal in a ring $\ring{R}$ is an ideal $I\subsetneq{R}$
            such that for every ideal $J\subsetneq{R}$ such that
            $I\subseteq{J}$, it is true that $I=J$.
        \end{fdefinition}
        \begin{theorem}
            \label{thm:Proper_Ideal_Does_Not_Contain_1}%
            If $\ring{R}$ is an ideal, if $I\subseteq{R}$ is a proper ideal, and
            if $1\in{R}$ is the multiplicative idenity, then $1\notin{R}$.
        \end{theorem}
        \begin{proof}
            For suppose not. But if $1\in{R}$, then since $I$ is an ideal for
            all $r\in{R}$ it is true that $r\cdot{1}\in{R}$. But $1$ is the
            multiplicative identity, and hence $r\cdot{1}\in{I}$. But then for
            all $r\in{R}$ it is true that $r\in{I}$, and hence $r=I$, a
            contradiction since $I$ is a proper ideal. Thus, $1\notin{I}$.
        \end{proof}
        \begin{ftheorem}{Krull's Theorem}{Krulls_Theorem}
            If $\ring{R}$ is a non-zero commutative ring, then there is a
            maximal ideal $I\subseteq{R}$.
        \end{ftheorem}
        \begin{bproof}
            For let $J\subseteq\powset{R}$ be defined as follows:
            \begin{equation}
                J=\{\,I\in\powset{R}\;|\;I\textit{ is a proper ideal of }R\,\}
            \end{equation}
            But $R$ is non-zero, and hence $\{0\}$ is a proper ideal of $R$,
            and therefore $J$ is non-empty. Then if $\subseteq$ is the inclusion
            relation, then $(J,\subseteq)$ is a partially ordered set. Suppose
            $\Lambda\subseteq{J}$ is a chain. But then $\bigcup\Lambda\in{J}$.
            For if $x,y\in\bigcup\Lambda$, then there is a $I_{x}\in\Lambda$ and
            an $I_{y}\in\Lambda$ such that $x\in{I}_{x}$ and $y\in{I}_{y}$. But
            since $\Lambda$ is a chain, either $I_{x}\subseteq{I}_{y}$ or
            $I_{y}\subseteq{I}_{x}$. Suppose $I_{x}\subseteq{I}_{y}$. But then
            $x,y\in{I}_{y}$, and since $I_{y}\in{J}$ it is an ideal. But then
            $x+y\in{I}_{y}$, and similarly if $I_{y}\subseteq{I}_{x}$. Hence,
            $x+y\in\bigcup\Lambda$. Moreover, if $r\in{R}$ and
            $x\in\bigcup\Lambda$, then there is an $I\in\Lambda$ such that
            $x\in{I}$. But $I$ is an ideal, and therefore $r\cdot{x}\in{I}$.
            But then $r\cdot{x}\in\bigcup\Lambda$. Therefore, $\bigcup\Lambda$
            is an ideal. Moreover, since for all $I\in\Lambda$ it is true that
            $I\in{J}$, $I$ is thus a proper ideal. But if $I$ is a proper ideal,
            then $1\not\in{I}$ (Thm.~\ref{thm:Proper_Ideal_Does_Not_Contain_1}).
            But this is true of all $I\in\Lambda$, and hence
            $1\notin\bigcup\Lambda$, and therefore $\bigcup\Lambda$ is a proper
            ideal. Therefore, every chain of $(J,\subseteq)$ is bounded, and
            therefore there exists a maximal element $I\in{J}$. But then $I$
            is a proper ideal of $R$ that is not contained in any other proper
            ideals, and is therefore a maximal ideal
            (Def.~\ref{def:Maximal_Ideal}).
        \end{bproof}
        Zorn's lemma is indeed required for this proof. Krull's original proof
        invoked transfinite induction, a consequence of the well-ordering
        theorem, and indeed Krull's theorem implies the axiom of choice. Since
        the axiom of choice and Zorn's lemma are equivalent, any axiomatic
        system capable of proving Krull's theorem must contain, or be able to
        prove, the axiom of choice. Nevertheless, we can now prove that every
        non-zero ring contains a prime ideal.
        \begin{ltheorem}{Maximal Ideals are Prime}{Maximal_Ideals_are_Prime}
            If $\ring{R}$ is a ring, if $I\subseteq{R}$ is a maximal ideal, then
            $I$ is a prime ideal.
        \end{ltheorem}
        \begin{proof}
            For suppose not. Then there exists $a,b\in{R}$ such that
            $a,b\notin{I}$, but $a\cdot{b}\in{I}$ (Def.~\ref{def:Prime_Ideal}).
            But then neither $a$ nor $b$ are units, for otherwise since $I$ is
            an ideal, since $a\cdot{b}\in{I}$, it is then true that
            $a^{\minus{1}}\cdot{a}\cdot{b}\in{I}$, and thus $b\in{I}$, a
            contradiction. But then the ideal generated by $I\cup\{a\}$ is a
            proper ideal since it does not contain 1. But then
            $I\subsetneq(I\cup\{a\})$ since $a\notin{I}$, a contradiction since
            $I$ is maximal. Thus, $I$ is prime.
        \end{proof}
        \begin{theorem}
            \label{thm:Existence_of_Prime_Ideals}%
            If $\ring{R}$ is a non-zero ring, then there exists a prime ideal
            $I\subseteq{R}$.
        \end{theorem}
        \begin{proof}
            For by Krull's theorem, there exists a maximal ideal
            $I\subseteq{R}$ (Thm.~\ref{thm:Krulls_Theorem}). But maximal ideals
            are prime ideals (Thm.~\ref{thm:Maximal_Ideals_are_Prime}). Hence,
            $I$ is a prime ideal.
        \end{proof}
        Given a ring homomoprhism $\varphi:R\rightarrow{S}$, there is a map
        $\varphi^{\#}:\textrm{Spec}(S)\rightarrow\textrm{Spec}(R)$, where
        $\textrm{Spec}(X)$ is the set of all prime ideals on $X$.
        Zariski topology. Define, for all $r\in{R}$:
        \begin{equation}
            X_{r}=\{p\in\textrm{Spec{R}}\;|\;r\in{p}\}
        \end{equation}
        The topology is $\tau=\{X_{r}\;|\;r\in{R}\}$.
        \begin{example}
            Take the polynomial ring $\mathbb{C}[x]$. The prime ideals on this
            space are $(z-a)$ for some $a\in\mathbb{C}$. The topology is then
            $\{(x-a)\;|\;a\in\mathbb{C}\}\cup\{(0)\}$. The weirdness about this
            is that $(0)$ is dense in this space.
        \end{example}
        \begin{theorem}
            If $\ring[F]{F}$ is a field, if $\ring[K]{K}$ is a field extension,
            and if $\alpha\in{K}$, then $F[\alpha]$ is a field if and only if
            $\alpha$ is algebraic. 
        \end{theorem}
        \begin{fdefinition}{Integral Domain}{Integral Domain}
            An integral domain is a commutative ring $\ring{R}$ such that for
            every $a,b\in{R}\setminus\{0\}$ it is true that $a\cdot{b}\ne{0}$.
        \end{fdefinition}
        That is, an integral domain is a commutative ring that contains no zero
        divisors.
        \begin{definition}
            A unique factorization domain (UFD) $R$ is an integral domain
            (no zero divisors) such that for every element $r\in{R}$ with
            $r\ne{0}$ and $r$ not a unit, we have that $r=\prod_{i}r_{i}$ where
            $r_{i}$ are irreducible elements, and if $r=\prod_{j}s_{j}$ with
            $s_{j}$ irreducible, then the size of the products are the same, and
            $r_{i}=s_{i}\cdot{u}_{i}$ for some unit $u_{i}$.
        \end{definition}
        \begin{example}
            The fundamental theorem of arithmetic states the $\mathbb{Z}$ is a
            UFD.
        \end{example}
        \begin{theorem}
            If $F$ is a field, then $F[x]$ is a UFD.
        \end{theorem}
        \begin{proof}
            Any principal ideal domain is a unique factorization domain.
        \end{proof}
        \begin{example}
            There are non-unique factorization domains. For example,
            $\mathbb{Z}[\sqrt{\minus{5}}]$ since
            $6=2\cdot{3}=(1+\sqrt{\minus{5}})(1-\sqrt{\minus{5}})$.
        \end{example}
        The converse of the previous example is not true.
        \begin{theorem}
            $\mathbb{Z}[x]$ is a UFD.
        \end{theorem}
        However, $\mathbb{Z}[x]$ is not a PID since $(2,x)$ is not principal.
    \section{Roots and Irreducibility}
        \begin{definition}
            An element $\alpha\in{F}$ is a root of a polynomial $f(x)$ if
            $f(x)=0$.
        \end{definition}
        \begin{theorem}
            $\alpha\in{F}$ is a root of $f\in{F}[x]$ if and only if
            $(x-\alpha)$ divides $f$.
        \end{theorem}
        \begin{proof}
            One was is clear, if $(x-\alpha)|f$, then $f(x)=(x-\alpha)r(x)$ for
            some $r\in{F}[x]$. But then $f(\alpha)=0\cdot{r}(\alpha)=0$, and
            thus $\alpha$ is a root. In the other direction, use the division
            algorithm. Write $f(x)=(x-\alpha)q(x)+r(x)$. But $r(x)$ must have
            degree less than $x-\alpha$, and is therefor a constant. But then
            $f(\alpha)=r=0$, so $r=0$. Hence, $f(x)=(x-\alpha)q(x)$, so
            $x-\alpha$ divides $f$.
        \end{proof}
        \begin{theorem}
            If $f\in{F}[x]$ is a polynomial of degree $n$, then there are at
            most $n$ roots.
        \end{theorem}
        \begin{proof}
            By induction. If there are no roots, we are done. If not, write
            $f(x)=(x-\alpha)q(x)$. Then $q$ is a polynomial of degree $n-1$, and
            by the induction hypothesis has at most $n-1$ roots. Thus, there are
            at most $n$ roots.
        \end{proof}
        \begin{example}
            $x^{2}-1\in\mathbb{Z}_{8}[x]$ has 4 roots. That is, 1, 3, 5, 7
            are all roots. This does not contradict the previous theorem since
            $\mathbb{Z}_{8}$ is not a field.
        \end{example}
        \begin{theorem}
            The fundamental theorem of algebra states that every non-constant
            polynomial $f\in\mathbb{C}[z]$ has a root.
        \end{theorem}
        \begin{theorem}
            Any linear polynomial $ax+b\in{F}[x]$ is irreducible.
        \end{theorem}
        \begin{theorem}
            If $f\in{F}[x]$ is irreducible and $\textrm{deg}(g)\geq{2}$, then
            $f$ has no roots. Moreover, the converse holds if
            $\textrm{deg}(f)=2$ or 3.
        \end{theorem}
        \begin{example}
            The previous theorem is very special for degree 2 and 3. Let
            $f(x)=x^{2}+x+1$ where $f\in\mathbb{F}_{p}[x]$, $p$ a prime.
            For the case of $p=2$ have seen that this is a irreducible. For
            $p=3$ we have that 1 is a root: $1^{2}+1+1=3\cong{0}$ in
            $\mathbb{F}_{3}$. For $p=5$, this is once again irreducible,
            but not in $\mathbb{F}_{7}$.
        \end{example}
        \begin{example}
            Consider $x^{4}+x^{2}+1\in\mathbb{F}_{2}[x]$. This has no roots,
            since 0 and 1 both map to 1, but it is reducible since
            $x^{4}+x^{2}+1=(x^{2}+x+1)^{2}$ in $\mathbb{F}_{2}[x]$. That is,
            the so called \textit{freshman's dream} is true in this case, and
            we can distribute the power. Thus we have a reducible polynomial
            with no roots. Note, however, that the degree is not 2 or 3.
        \end{example}
        Next, we present Gauss's Lemma. Note that being irreducible over
        $\mathbb{Z}$ is stronger than being irreducible over $\mathbb{Z}$.
        Consider $f(x)=2x$. While this is linear in $\mathbb{Q}$, and since
        $\mathbb{Q}$ is a field, $f$ is irreducible in $\mathbb{Q}[x]$. However
        when viewed in $\mathbb{Z}[x]$, we have $2x=2\cdot{x}$, neither of
        which are units, and hence $f$ is reducible in $\mathbb{Z}[x]$.
        \begin{theorem}
            If $f\in\mathbb{Z}[x]$ is irreducible, then it is irreducible in
            $\mathbb{Q}[x]$.
        \end{theorem}
        \subsection{Reduction Modulo a Prime}
            Consider the projection map
            $\pi:\mathbb{Z}[x]\rightarrow\mathbf{F}_{p}[x]$, reduction mod $p$
            of the coefficients:
            \begin{equation}
                f(x)=\sum{a}_{k}x^{k}\longrightarrow
                    \overline{f}(x)\sum\overline{a}_{k}x^{k}
            \end{equation}
            The mapping $\pi$ is a ring homomoprhism.
            \begin{example}
                $x^{3}+21x+31\mapsto{x}^{3}+x+1$ in $\mathbb{F}_{2}[x]$.
            \end{example}
            \begin{theorem}
                If $f\in\mathbb{Z}[x]$, if $p$ is prime, and if $p\not|a_{n}$,
                and if $\pi(f)\in\mathbb{F}_{p}[x]$ is irreducible, then
                $f\in\mathbb{Z}[x]$ is irreducible.
            \end{theorem}
            \begin{proof}
                We prove by the contrapositive. If $f(x)=g(x)h(x)$, then
                $\overline{f}(x)=\overline{g}(x)\overline{h}(x)$ since $\pi$ is
                a homomoprhism. But $\overline{g}$ and $\overline{h}$ are not
                units since $p$ does not $a_{n}$, and thus the degree of the
                reduction is equal to the degree of the original polynomial.
                That is, $\textrm{deg}(f)=\textrm{deg}(\overline{f})$. But also
                $\textrm{deg}(g)=\textrm{deg}(\overline{g})$ and similarly for
                $h$ since:
                \begin{equation}
                    \textrm{deg}(\overline{g})+\textrm{deg}(\overline{h})
                    =\textrm{deg}(g)+\textrm{deg}(h)=\textrm{deg}(f)
                \end{equation}
                Since $p$ does not divide the leading coefficients of either
                $g$ or $h$, the degrees of $\overline{g}$ and $\overline{h}$
                remain the same, and hence are not units. Thus, $\overline{f}$
                is reducible.
            \end{proof}
            \begin{example}
                Consider $x^{3}+21x+31\in\mathbb{Z}[x]$. In $\mathbb{F}_{3}[x]$
                we have $x^{3}+x+1$, which is indeed irreducible, and hence
                the original polynomial $x^{3}+21x+31$ is irreducible.
            \end{example}
            \begin{example}
                The converse is not true. There are polynomials that are
                reducible for all $p$, yet in $\mathbb{Z}[x]$ it is irreducible.
                Consider $(2x+1)(x+1)=2x^{2}+3x+1$. This is reducible, since
                we have the factorization, however in $\mathbb{F}_{2}[x]$ this
                is simply $x+1$, which is irreducible. However, 2 divides 2 so
                the theorem does not apply.
            \end{example}
            \begin{example}
                In $\mathbb{Z}[x]$, consider $x^{2}+x+1$ which we know is
                irreducible since it is irreducible in $\mathbb{R}[x]$
                (the roots are complex). In $\mathbb{F}_{2}[x]$ we can check and
                see that there are no roots, and thus $x^{2}+x+1$ is irreducible
                by Gauss' lemma. However, in $\mathbb{F}_{3}[x]$ it is reducible
                since $x^{2}+x+1=(x-1)^{2}$. That is, 1 is a root of $x^{2}+x+1$
                in $\mathbb{F}_{2}[x]$ with multiplicity 2.
            \end{example}
            \begin{ftheorem}{Eisenstein's Criterion}{Eisensteins_Criterion}
                If $p$ is prime, if $f\in\mathbb{Z}[x]$, if $p$ does not divide
                $a-{n}$, if $p$ divides $a_{k}$ for all $k<n$, and if
                $p^{2}$ does not divide $a_{0}$, then $f$ is irreducible.
            \end{ftheorem}
            \begin{bproof}
                We prove by the contradiction. Suppose $f$ is reducible.
                If $p$ divides all of the $a_{i}$, then in the reduction map
                $\pi:\mathbb{Z}[x]\rightarrow\mathbb{F}_{p}[x]$, all of the
                $a_{i}$ map to zero. So we have:
                \begin{equation}
                    \overline{a}_{n}x^{n}=\overline{f}(x)
                    =\overline{g}(x)\overline{h}(x)
                \end{equation}
                But since $\mathbb{Z}[x]$ is a UFD, both $\overline{g}$ and
                $\overline{h}$ are monomials, $\overline{g}(x)=g_{0}x^{i}$ and
                $\overline{h}(x)=h_{0}x^{j}$. If $i,j<n$, then $i,j>0$, and so
                both constant terms must be divisible by $p$. Thus
                $g(x)h(x)$ has a constant term divisible by $p^{2}$, a
                contradiction.
            \end{bproof}
            \begin{example}
                Let $f(x)=x^{4}+22x^{2}+33x+44$. By Eisenstein, with $p=11$, we
                have that this is irreducible.
            \end{example}
        \subsection{Review of Previous Lecture}
            If $\mathbf{F}$ is a field, then $\zeta\in\mathbf{F}$ is called a
            root of unity of there is some $n\geq{1}$ such that $\zeta^{n}=1$.
            \begin{example}
                In the field $\mathbb{R}$, the roots of unity of 1 and
                $\minus{1}$. The number 1 is a first root of unity, whereas
                $\minus{1}$ is a second root of unity.
            \end{example}
            \begin{example}
                In the complex numbers $\mathbb{C}$, there is an $n^{th}$ root
                of unity for all $n\in\mathbb{N}^{+}$. Let
                $\zeta=\exp(2\pi{i}/n)$. The roots of unity are scattered along
                the unit circle.
            \end{example}
            A root of unity is some element $\zeta\in\mathbb{F}$ such that
            $\zeta$ is a root of the polynomial $f(x)=x^{n}-1$.
            \begin{example}
                Let $p$ be a prime integer, and consider the roots of
                $f(x)=x^{p}-1$. There is always a root since 1 satisfies this
                criterion, and hence we can factor this and obtain:
                \begin{equation}
                    f(x)=x^{p}-1=(x-1)(x^{p-1}+x^{p-2}+\dots+x+1)
                \end{equation}
                This latter polynomial $x^{p-1}+x^{p-1}+\dots+x+1$ is
                irreducible over $\mathbb{Q}$.
            \end{example}
            \begin{theorem}
                If $p$ is prime and $f(x)=x^{p-1}+x^{p-2}+\dots+x+1$,
                $f\in\mathbb{R}[x]$, then $f$ is irreducible over $\mathbb{Q}$.
            \end{theorem}
            \begin{proof}
                For:
                \begin{equation}
                    xf(x+1)=(x+1)^{p}-1
                \end{equation}
                by the binomial theorem we have:
                \begin{equation}
                    xf(x+1)=(x+1)^{p}-1=
                    \minus{1}+\sum_{k=0}^{p}\binom{p}{k}x^{k}
                    =\sum_{k=1}^{p}\binom{p}{k}x^{k}
                \end{equation}
                Thus, simplifying, we have:
                \begin{equation}
                    f(x+1)=\sum_{k=1}^{p}\binom{p}{k}x^{k-1}
                \end{equation}
                Thus by the Eisenstein criterion, $f(x+1)$ is irreducible over
                $\mathbb{Q}$. But if $f(x+1)$ is irreducible over $\mathbb{Q}$,
                then $f(x)$ is as well.
            \end{proof}
            The converse of the statement before is not true. If the translation
            of a polynomial is reducible, it need not mean the original
            polynomial was reducible. For let $f(x)\in\mathbb{F}_{2}[x]$ be
            defined by $f(x)=x^{2}+x+1$. Plugging in $x^{2}$ we get
            $f(x)^{2}=x^{4}+x^{2}+1=(x^{2}+x+1)^{2}$, which is reducible.
    \section{Gauss's Lemma}
        \begin{definition}
            A polynomial $f\in\mathbb{Z}[x]$ is called primitive if
            $\textrm{GCD}(a_{0},\dots,a_{n})=1$. Equivalently, for all primes
            $p$ there is an $i$ such that $p\not|a_{i}$. That is, $p$ does not
            divide $a_{i}$.
        \end{definition}
        \begin{example}
            Let $f(x)=10x^{3}+5x^{2}+2x+23$. This is a primitive polynomial.
            If $p$ divides all of the $a_{i}$, it must divide 2, but 2 is the
            only prime that divides 2, and hence $p=2$. But 5 and 23 are odd,
            and hence 2 does not divide them. So, $f$ is primitive.
        \end{example}
        \begin{ltheorem}{Gauss's Lemma}{Gauss_Lemma}
            FOr any $f\in\mathbb{Q}[x]$ there is a unique $c\in\mathbb{Q}$ and
            a unique primitive polynomial $g\in\mathbb{Z}[x]$ such that
            $f(x)=c\cdot{g}(x)$.
        \end{ltheorem}
        \begin{proof}
            Existence is straight forward. Clear out the denominators of $f$,
            let $c$ be the common factor, and we're done. Suppose
            $cg(x)=c'g'(x)$. If $c$ and $c'$ are not integers, multiply by their
            denominators and thus we may assume $c$ and $c'$ are integers. Then
            we have:
            \begin{equation}
                cg(x)=c'(b_{0}+b_{1}x+\dots+b_{n}x^{n})
            \end{equation}
            And hence:
            \begin{equation}
                c=\textrm{GCD}(c'b_{0},\dots,c'b_{n})
                 =c\textrm{GCD}((b_{0},\dots,b_{n}))
            \end{equation}
            But $g'$ is trivial, so the greatest common denominator is 1. Hence,
            $c=c'$. Also, $g=g'$.
        \end{proof}
        \begin{ltheorem}{Gauss' Lemma Version 2}{Gauss_Lemma_2}
            If $g\in\mathbb{Z}[x]$ is primitive and $f\in\mathbb{Z}[x]$, and if
            $g|f$ in $\mathbb{Q}[x]$, then $g|f$ in $\mathbb{Z}[x]$.
        \end{ltheorem}
        \begin{proof}
            For if $g|f$, then $f=gh$ with $h\in\mathbb{Q}[x]$. But by Gauss'
            lemma there is a unique $c\in\mathbb{Q}$ such that
            $h(x)=ch_{0}(x)$, where $h_{0}\in\mathbb{Z}[x]$ is primitive. So
            $f(x)=cg(x)h_{0}(x)$. But then $g(x)h_{0}(x)$ is primitive, and
            hence $c$ is an integer. Thus, $h\in\mathbb{Z}[x]$. That is, since
            the product of primitive is primitive, the numerator of $c$ is equal
            to the denominator of $c$ times the GCD of the coefficients of $f$.
            But this GCD is a positive integer, and hence the numerator divides
            it, and hence $c$ is an integer itself.
        \end{proof}
        \begin{ltheorem}{Gauss' Lemma V3}{Gauss_Lemma_3}
            If $f\in\mathbb{Z}[x]$ and if $g,h\in\mathbb{Q}[x]$ are such that
            $f=gh$, then $f=g_{0}h_{0}$.
        \end{ltheorem}
    \section{Field Extensions}
        \begin{ftheorem}{Tower Law}{Tower_Law}
            If $\mathbb{F}$, $\mathbb{K}$, and $\mathbb{L}$ are fields, if
            $\mathbb{K}$ is a field extension of $\mathbb{F}$, if $\mathbb{L}$
            is a field extension over $\mathbb{K}$, then $\mathbb{L}/\mathbb{F}$
            is a finite dimensional vector space if and only if
            $\mathbb{L}/\mathbb{K}$ and $\mathbb{K}/\mathbb{F}$ is finite.
            Moreover:
            \begin{equation*}
                [\mathbb{L}:\mathbb{F}]=
                [\mathbb{L}:\mathbb{K}][\mathbb{K}:\mathbb{F}]
            \end{equation*}
        \end{ftheorem}
        Suppose $K/F$ is a field extension. That is, $F\subseteq{K}$ and $F$ is
        a subfield of $K$. Let $X\subseteq{K}$ be any non-empty subset. We now
        define the adjoinment of $X$ to $F$.
        \begin{definition}
            The field extension generated by a subfield $F$ of a field $K$ by a
            subset $X\subseteq{K}$ is the subfield:
            \begin{equation}
                F(X)=
                \bigcap_{\overset{F\subseteq{L}\subseteq{K}}{X\subseteq{L}}}L
            \end{equation}
            Where $L$ is a subfield.
        \end{definition}
        $F(X)$ is non-empty since $K$ is in the intersection, and the
        intersection of subfields is again a subfield, so $F(X)$ is a field.
        If $X=\{a_{0},a_{1},\dots\}$, we often write $F(X)=F(a_{0},a_{1},\dots)$
        and if $X$ if finite we call $F(X)/F$ finitely generated. If $X$ is a
        single element, $F(\alpha)$ is called a simple extension. A field
        extension is simple if it can be written as a simple extension.
        \begin{example}
            $\mathbb{R}/\mathbb{Q}$ is not finitely generated. A simple
            cardinality argument works here, for if it were countably generated
            then since $\mathbb{Q}$ is countable, $\mathbb{R}$ would again be
            countable, which is false.
        \end{example}
        \begin{example}
            $\mathbb{Q}(\sqrt{2},\sqrt{3},\sqrt{5},\sqrt{7},\dots)$ is not
            finitely generated. We can show this by building a chain of
            subfields. First consider $\mathbb{Q}(\sqrt{2})/\mathbb{Q}$. This
            is a field extension of degree two. One can see this since
            $\sqrt{2}$ is not rational. The next field extension
            $\mathbb{Q}(\sqrt{2},\sqrt{3})/\mathbb{Q}(\sqrt{2})$ is also an
            extension of degree 2. For suppose not and suppose:
            \begin{equation}
                \sqrt{3}=a+b\sqrt{2}
            \end{equation}
            Squaring, we obtain:
            \begin{equation}
                3=a^{2}+2b^{2}+2ab\sqrt{2}
            \end{equation}
            Now since $\sqrt{2}$ is irrational we must conclude that $ab=0$.
            Thus either $a=0$ or $b=0$. f $b=0$, then $\sqrt{3}$ is an integer,
            which is false. If $a=0$ then $3=2b^{2}$, but $3$ is prime, a
            contradiction. Thus $\sqrt{3}$ is not contained in
            $\mathbb{Q}(\sqrt{3})$.
        \end{example}
        \begin{theorem}
            If $F$ is a field, if $K$ is a field extension, if $\alpha\in{K}$,
            then:
            \begin{equation}
                F(\alpha)=\big\{\frac{f(\alpha)}{g(\alpha)}\;|\;
                    f,g\in{F}[x],g(\alpha)\ne{0}\big\}
            \end{equation}
        \end{theorem}
        \begin{theorem}
            A field extension of a field $F$ is a field extension $K$ of $F$
            is an injective homomoprhism $\iota:F\rightarrow{K}$.
        \end{theorem}
        \begin{definition}
            A morphism of field extensions $K/F$ and $K'/F$ is a homomoprhism
            $\varphi:K\rightarrow{K}'$ such that the injective homomoprhisms
            $\iota$ and $\iota'$ commute with $\varphi$. That is,
            $\iota'=\varphi\circ\iota$.
        \end{definition}
        \begin{example}
            $\mathbb{C}$ and $\mathbb{R}[x]/(x^{2}+1)$ are isomorphic field
            extensions of $\mathbb{R}$.
            $\varphi\mathbb{R}[x]\rightarrow\mathbb{R}$ mapping
            $f\mapsto{f}(i)$ is surjective since $a+ib=a(i)+b(i)^{4}$. Thus this
            is a surjective $\mathbb{R}$ algebra homomoprhism. The kernel is
            the ideal generated by $x^{2}+1$. Then by the first isomorphism
            theorem,
            $\tilde{\varphi}:\mathbb{R}[x]/(x^{2}+1)\rightarrow\mathbb{C}$ is an
            isomorphism. Hence, these are isomorphic.
        \end{example}
    \section{Minimal Polynomial}
        If $F\subseteq{K}$ is a subfield, if $\alpha\in{K}$, then there exists
        an $F$ algebra homomoprhism $\varphi_{\alpha}:F[x]\rightarrow{K}$.
        Then $\textrm{Ker}(\varphi_{\alpha})\subseteq{F}[x]$. If
        $\varphi_{\alpha}$ is injective, then the kernel is 0, and this is
        true if and only if $f(\alpha)\ne{0}$ for all $f\in{F}[x]$. That is,
        $\alpha$ is \textit{transcendental} over $F$. On the other hand, if
        $\varphi_{\alpha}$ is not injective then
        $\textrm{Ker}(\varphi_{\alpha})=(m_{\alpha}/F(x))$ where
        $m_{\alpha}/F(x)$ is a monic polynomial in $F[x]$, and this is called
        the minimal polynomial of $\alpha$ over $F$. In this case we say that
        $\alpha$ is algebraic over $F$.
        \begin{theorem}
            If $K/F$ is a field extension, $\alpha\in{K}$ is algebraic over $F$,
            if $f\in{F}[x]$ with $f(\alpha)=0$, then
            $m_{\alpha/F}(x)|f$, hence $m_{\alpha}/F(x)$ is the unique monic
            polynomial over $F$ of minimal degree with $\alpha$ as a root.
            Moreover, $m_{\alpha}/F(x)$ is irreducible over $F$ and is the
            unique monic irreducible polynomial over $F$ with $\alpha$ as a
            root.
        \end{theorem}
        \begin{example}
            Let $d\in\mathbb{Z}$ be a non-square. Then the minimal polynomial of
            $d$ is $m_{\sqrt{d}}/\mathbb{Q}(x)=x^{2}-d$.
        \end{example}
        \begin{example}
            Let $\alpha=\sqrt{2}+\sqrt{3}$. What is the minimal polynomial of
            $\alpha$ over $\mathbb{Q}$? Well we first try to find a polynomial
            that has $\alpha$ as a root. Squaring, we have:
            \begin{equation}
                \alpha^{2}=2+2\sqrt{6}+3=5+2\sqrt{6}
            \end{equation}
            Bringing the 5 over and squaring:
            \begin{equation}
                (\alpha^{2}-5)^{2}=24=\alpha^{4}-10\alpha^{2}+25
            \end{equation}
            Thus letting $f(x)=x^{4}-10x+1$, we obtain a polynomial with
            $\alpha$ as a root.
        \end{example}
        \begin{theorem}
            If $\alpha\in{K}$ is algebraic over $F$, then
            $F[x]/(m_{\alpha}/F(x))$ is isomorphic to $F[\alpha]$, and
            $F[\alpha]=F(\alpha)$.
        \end{theorem}
        Since $F(\alpha)\subseteq{F}[\alpha]$ because the first part,
        $F[x]$ is a field since $m_{\alpha}/F(x)$ is irreducible, so
        $F[x]/(m_{\alpha}/F(x))$ is a field. Hence
        $F(\alpha)\subseteq{F}[\alpha]$ since $F(\alpha)$ is minimal field
        containing $\alpha$. GIven $\alpha$ algebraic over $F$,
        $\alpha^{\minus{1}}$ is a polynomial in $\alpha$. There exists an
        algorithm demonstrating this using Bezout's identity.
        \begin{definition}
            A field extension $K/F$ is algebraic if for all $\alpha\in{K}$,
            $\alpha$ is algebraic over $F$.
        \end{definition}
        \begin{theorem}
            $K/F$ finite if and only if $K/F$ is algebraic and finitely
            generated.
        \end{theorem}
    \section{Review of Previous Lectures}
        A field extension $K/F$ is algebraic if every element $\alpha\in{K}$ is
        algebraic over $F$.
        \begin{theorem}
            A field extension $K/F$ is finite if and only if $K/F$ is algebraic
            and finitely generated.
        \end{theorem}
        \begin{proof}
            For if $K/F$ is finite, then $K$ is a finite dimensional vector
            space over $F$. Thus, if $\alpha\in{K}$, then the set
            $\{1,\alpha,\alpha,\dots\}$ is linearly dependent. That is, there
            exists $a_{0},\dots,a_{n}\in{F}$ such that
            $a_{0}+\dots+a-{n}\alpha^{n}=0$. Let $\alpha_{1},\dots,\alpha_{m}$
            be an $F$ basis for $K$. Then $K=F(\alpha_{1},\dots,\alpha_{n})$,
            and so $K$ is finitely generated. The converse is trickier. Since
            $K$ is finitely generated, $K=F(\alpha_{1},\dots,\alpha_{n})$. But
            since $K$ is algebraic over $F$, $\alpha_{i}$ is algebraic in $F$.
            Thus we build a tower:
            \begin{equation}
                F\rightarrow{F}(\alpha_{1})\rightarrow{F}(\alpha_{1},\alpha_{2})
                    \rightarrow\dots\rightarrow{F}(\alpha_{1},\dots,\alpha_{n})
                    =K
            \end{equation}
            By the generalized tower law, $K$ is finite over $F$.
        \end{proof}
        $K/F$ is transcendental (that is, not algebraic) implies that $K/F$ is
        of infinite degree. Given $\alpha\in{K}$ transcendental over $F$, then
        $\varphi_{\alpha}:F[x]\rightarrow{F}[\alpha]\subseteq{F}(\alpha)$.
        \begin{theorem}
            If $K/L$ is algebraic and $L/F$ is algebraic, then $K/F$ is
            algebraic.
        \end{theorem}
        \begin{proof}
            For let $\alpha\in{K}$. We want to show that $\alpha$ is algebraic
            over $F$. This is equivalent to the claim that $F(\alpha)$ is finite
            over $F$. But $\alpha$ is algebraic over $L$, and hence there is a
            minimal polynomial
            $m_{\alpha}/L(x)=a_{0}+\dots+a_{n-1}x^{n-1}+x^{n}\in{L}[x]$. Since
            $L/F$ is algebraic, $a_{i}$ is algebraic over $F$.
        \end{proof}
        The converse is true as well.
    \section{Compass and Straight Edge}
        Consider some subset $S\subseteq\mathbb{C}$, equipped with some rules:
        \begin{itemize}
            \item Given two points $P,Q$ there is a line through $P$ and $Q$.
            \item Given $P,Q$, there is a circle $C(P,|Q-P|)$ centering at $P$
                  with radius $|P-Q|$.
        \end{itemize}
        Any point that is the intersection of any of the lines and circles is
        said to be constructible by compass and straightedge.
        \begin{example}
            Bisecting a line is possible. Bisecting an angle is possible. Can
            you trisect an angle? What about double a cube?
        \end{example}
        We'll define inductively some sets $P_{n}$, $L_{n}$, and $C_{n}$.
        $P_{0}=\{0,1\}\subseteq\mathbb{C}$, $L_{0},C_{0}=\emptyset$. If
        $L_{n}$ has been constructed, let $L_{n+1}$ be the set of all lines
        through all points in $P_{n}$. If $C_{n}$ has been constructed, let
        $C_{n+1}$ be the set of all circles about all points in $P_{n}$ with
        radii all of the distances $|z_{1}-z_{2}|$ for points
        $z_{1},z_{2}\in{P}_{n}$. Then $P_{n}$ is finite for all $n\in\mathbb{N}$
        and thus the union over all $P_{n}$ is at most countable. This
        cardinality argument shows that there are inconstructible numbers.
        Moreover, $P=\bigcup{P}_{n}$ is a subfield of $\mathbb{C}$. To see this
        we must show that $P$ is closed to addition, multiplication, and
        inverses.
        \begin{theorem}
            The set of constructible numbers is a subfield of $\mathbb{C}$.
        \end{theorem}
        \begin{proof}
            It suffices to show that $P\cap\mathbb{R}$ is a subfield. For let
            $a,b\in{P}\cap\mathbb{R}$. We need to show that $a+b$, $a\cdot{b}$,
            and $a/b$ are constructible. Given the length $a$ and the length
            $b$, we can translate the length $b$ to start at $a$, given us the
            point $a+b$, which will have length $a+b$. For $ab$ we construct
            two triangles, one with length 1 and the other with length $a$.
            We build a triangle on the first with a length $b$, and a similar
            triangle on the second length which will have length $ab$ by
            similiarity. Lastly, do the same triangle with $b$ on the inside to
            get $a/b$. Draw some pictures later.
        \end{proof}
        \begin{theorem}
            $\mathbb{Q}\subseteq{P}$.
        \end{theorem}
        \begin{proof}
            Since $1\in{P}$, every integer multiple of 1 is also contained in
            $P$ since we can add 1 to itself $n$ times. Thus $n/m$ is contained
            in $P$, so $\mathbb{Q}\subseteq{P}$.
        \end{proof}
        \begin{theorem}
            $P$ is closed to square roots.
        \end{theorem}
        \begin{proof}
            Draw a circle of diameter $a+1$. Do that fancy circle.
        \end{proof}
        Let $Q^{py}$ be the intersection of all subfields $K\subseteq\mathbb{C}$
        such that for all $z\in{K}$ it is true that $\sqrt{z}\in{K}$. This is
        the smallest subfield of $\mathbb{C}$ in which one can always take
        square roots. It's called the Pythagorean closure of $\mathbb{Q}$. From
        the previous theorem, $Q^{py}\subseteq{P}$ is a subfield.
        \begin{theorem}
            $\mathbb{Q}^{py}=P$.
        \end{theorem}
        \begin{proof}
            For let $z\in{P}$. It suffices to show that
            $P_{n}\subseteq\mathbb{Q}^{n}$ for all $n$, since the
            $\bigcup{P}_{n}=P\subseteq\mathbb{Q}^{py}$. We prove this by
            induction. The base case is true since $P_{0}=\{0,1\}$ and this is a
            subset of $\mathbb{Q}^{py}$. Suppose $P_{n}\subseteq\mathbb{Q}^{py}$
            and recall that $P_{n+1}$ is defined as all $z\in\mathbb{C}$ such
            that $z\in{L}\cap{L}'$, or $z\in{L}\cap{C}$, or $z\in{C}\cap{C}'$,
            where $L$, $L'$, $C$, and $C'$ are lines and circles through points
            in $P_{n}$. Case 1, $z\in{L}\cap{L}'$ Then there are four points
            $z_{1},z_{2},z_{3},z_{4}$ such that:
            \begin{equation}
                z=z_{1}\alpha+(1-\alpha)z_{2}=z_{3}\beta+(1-\beta)z_{4}
            \end{equation}
            We can solve this and note that $P_{n}$ is closed under complex
            conjugation. Thus, in case 1 we have that $z$ is contained in
            $\mathbb{Q}^{py}$. Here we have:
            \begin{equation}
                z=z_{1}\alpha+(1-\alpha)z_{2}=z_{3}+r\exp(i\theta)
            \end{equation}
            This be true as well. The final case is two circles:
            \begin{equation}
                z=z_{1}+r_{1}\exp(i\theta_{1})=z_{2}+r_{2}\exp(i\theta_{2})
            \end{equation}
            Which also be like it is.
        \end{proof}
        \begin{theorem}
            $\mathbb{Q}^{py}$ is algebraic over $\mathbb{Q}$.
        \end{theorem}
        We can build the Pythagorean closure from $\mathbb{Q}$ by considering
        $\sqrt{\mathbb{Q}}$, all numbers of the for $a+b\sqrt{c}$ with
        $a,b,c\in\mathbb{Q}$, and then $\sqrt{\sqrt{\mathbb{Q}}}$, and so on.
        \begin{theorem}
            $z\in\mathbb{Q}^{py}$ if and only if there is a tower of extensions
            $K_{0},\dots,K_{n}$ such that $\mathbb{Q}=K_{0}$ and
            $K_{n}=\mathbb{Q}[z]$ where $K_{j+1}$ has degree 2 over $K_{j}$.
        \end{theorem}
        \begin{theorem}
            If $\alpha\in\mathbb{Q}^{py}$, then
            $[\mathbb{Q}[\alpha]:\mathbb{Q}]=2^{n}$ for some $n\in\mathbb{N}$.
        \end{theorem}
        \begin{proof}
            Apply the tower law to the previous theorem.
        \end{proof}
        From this we can do all of the impossibility proofs of various
        constructions.
        \begin{example}
            It is impossible to double the volume of a cube with lengths 1. The
            minimal polynomial of $\sqrt[3]{2}$ is $x^{3}-2$ by Eisenstein. Thus
            the degree of the field extension
            $[\mathbb{Q}[\sqrt[3]{2}]:\mathbb{Q}]=3$ which is not a power of 2.
            It is also impossible to trisect angles. For let $\theta=2\pi/3$.
            Trisecting this is equivalent to constructed $2\pi/9$. The minimal
            polynomial of this is $x^{3}-\frac{3}{4}x+\frac{1}{8}$, and thus
            the degree of the extension is again 3, which is not a power of 2.
        \end{example}
    \section{Review}
        If $f\in{F}[x]$ is irreducible, then $f$ has no roots. The converse is
        false. If $f\in{F}[x]$ has no roots, it may still be reducible. This
        holds for any field if $f$ has degree 2 or 3.
        \begin{example}
            If $f(x)=x^{4}+1$, $f\in\mathbb{R}[x]$, then $f$ is reducible. For
            we have:
            \begin{equation}
                x^{4}+1=(x^{2}-\sqrt{x}x+1)(x^{2}+\sqrt{2}x+1)
            \end{equation}
            We can now complete this since $x^{2}-\sqrt{2}x+1$ and
            $x^{2}+\sqrt{2}x+1$ have no real roots by the quadratic formula,
            and hence these are irreducible. Thus, $x^{4}+1$ is reducible and
            factors as above.
        \end{example}
        \begin{example}
            There is only one irreducible quadratic polynomial over
            $\mathbb{F}_{2}[x]$ and that is $x^{2}+x+1$. Using this, is the
            polynomial $x^{4}+x^{2}+x+1$ irreducible in $\mathbb{F}_{2}[x]$?
            Since this has no roots, we know that it has no linear factors, and
            thus if it is reducible it must be the product of irreducible
            quadratics. But there is only one irreducible quadratic, so we can
            use this to check. We have:
            \begin{equation}
                (x^{2}+x+1)^{2}=
                x^{4}+2x^{3}+x^{2}+2x+1=x^{4}+x^{2}+1
            \end{equation}
            Since in $\mathbb{F}_{2}$ we have that $2=0$. But this is not equal
            to the original polynomial $x^{4}+x^{3}+x^{2}+x+1$, and hence
            this is indeed irreducible.
        \end{example}
    \section{More Stuff}
        If $\alpha\in\mathbb{C}$ is constructible, and if
        $K_{i}$ is a tower of field extensions each of degree 2 over the
        previous one, then $[\mathbb{Q}(\alpha):\mathbb{Q}]=2^{n}$.
        \begin{theorem}
            A regular $n$ gon is constructible if and only if the complex number
            $\exp(2\pi{i}/n)$ is constructible.
        \end{theorem}
        If $p$ is a prime number, then the minimal polynomial of
        $\exp(i2\pi{i}/n)$ is just $x^{p-1}+\dots+1$. Thus
        $[\mathbb{Q}(\zeta_{p}):\mathbb{Q}]=p-1$. Thus we need $p-1$ to be a
        power of 2.
        \begin{theorem}
            If $p-1$ is not a power of 2 then we can not construct a regular
            $p$ gone.
        \end{theorem}
        \begin{theorem}
            If $2^{k}+1$ is a prime, then $k=2^{n}$ for some $n$.
        \end{theorem}
        There are only 5 Fermat primes, $p=3,5,17,257,65537$. An unsolved
        problem (as of 2020) is whether or not there are more such primes, or
        are there infinitely many primes? 
    \section{Splitting Fields}
        If $f\in{F}[x]$, we have given a construction of $K/F$ in which $f$ has
        a root $\alpha\in{K}$. That is, $(x-\alpha)$ divides $f$ in$ K[x]$. For
        if $f$ splits completely (factors into a product of linear polynomials
        over $f$), then there is nothing to prove. If not, let $g(x)$ be an
        irreducible factor of $f$ and define $K=F[x]/(g)$, where $(g)$ is the
        ideal generated by $g$ in $F[x]$. Then $g(x)$ has a root $\overline{x}$,
        $K=F(\alpha)$, so $(x-\alpha)$ divides $g$, which divides $f$, so we're
        done.
        \begin{example}
            Let $f(x)=x^{3}-2$, $f\in\mathbb{Q}[x]$. This has three roots,
            $\sqrt[3]{2}$, $\sqrt[3]{2}\omega$, and
            $\sqrt[3]{2}\overline{\omega}$, where $\omega$ is a complex cubed
            root of unity, and $\overline{\omega}$ is its complex conjugate.
            Thus $\mathbb{Q}[x]/(x^{3}-2)$ is isomorphic to
            $\mathbb{Q}(\sqrt[3]{2})$.
        \end{example}
        \begin{definition}
            An extension $K/F$ is a splitting field of $f\in{F}[x]$ if
            $f$ splits completely in $K[x]$ and does not split in any proper
            subfield.
        \end{definition}
        \begin{theorem}
            Splitting fields exist.
        \end{theorem}
        \begin{proof}
            Proof by induction on the degree of $n$. If it is true for $n$,
            write $f=(x-\alpha)g$ for some $\alpha$ in $F[x]/(h)$. Then
            $g$ is of degree $n$ or less, and hence has a splitting field
            $K$. Adjoing $\alpha$ to $K$. Let $E$ be the intersection of all
            subfields of $E$ containing this $K$ adjoing $\alpha$.
        \end{proof}
        \subsection{Review from Previous Lecture}
            If $F$ is a field, and if $f\in{F}[x]$, then an extension field
            $K$ over $F$ is a splitting field if $f\in{K}[x]$ is a splitting
            polynomial. That is, there are linear factors
            $a_{k}x+b_{k}$, with $a_{k},b_{k}\in{K}$, such that:
            \begin{equation}
                f(x)=\prod_{k\in\mathbb{Z}_{n}}(a_{k}x+b_{k})
            \end{equation}
            Splitting fields exists since given $f$ we can find an irreducible
            factor $g$, and thus $F[x]/(g)$ will be a field extension of $F$.
            Letting $\alpha_{1}=\overline{x}$, the equivalence class of $x$,
            this will be a root of $g$ in $F[x]/(g)$, and hence a root of
            $f$ in $G$. The extension field will have degree less than or equal
            to $n$. Continuing on inductively, obtaining $\alpha_{k}$, we find
            that $f\in{F}[\alpha_{1},\dots,\alpha_{n}]$ splits completely and
            that this field extension has at most degree $n!$. If $f$ was
            irreducible to begin with then $f$ is a minimal polynomial up to
            scalar multiplication, and hence the degree of $F[\alpha_{1}]$ over
            $F$ will be $n$. From the tower law, $n$ will divide the degree of
            $F[\alpha_{1},\dots,\alpha_{n}]$.
            \begin{example}
                Let $f(x)=x^{4}+4$. This factors as:
                \begin{equation}
                    x^{4}+4(x^{2}-2x+2)(x^{2}+2x+2)
                \end{equation}
                We can invoke the quadratic formula to find the roots of these
                two over $\mathbb{C}$:
                \twocolumneq{
                    \alpha_{1}=\frac{2\pm\sqrt{\minus{4}}}{2}
                              =1\pm{i}
                }
                {
                    \alpha_{2}=\frac{\minus{2}\pm\sqrt{\minus{4}}}{2}
                              =\minus{1}\pm{i}
                }
                So the splitting field is $K=\mathbb{Q}(\pm{1}\pm{i})$, and this
                is just $\mathbb{Q}(i)$. Thus, $[K:\mathbb{Q}]=2$.
            \end{example}
            \begin{theorem}
                If $F$, $F'$ are fields, if $\varphi:F\rightarrow{F}'$ is
                a field isomorphism, and if $f\in{F}[x]$, if
                $f'(x)(\varphi\circ{f})(x)\in{F}'[x]$, if $K$ is a splitting
                field for $f$, and if $K'$ is a splitting field for
                $f'$, then there is an isomorphism $\sigma:K\rightarrow{K}'$
                such that for all $c\in{F}$, $\sigma(c)=\varphi(c)$.
            \end{theorem}
            \begin{proof}
                We prove by induction on the degree of $f$. Since $\varphi$ is
                an isomorphism, $f'$ and $f$ have the same degree. Thus if
                $f\in{F}[x]$ and $f'\in{F}'[x]$ are degree one polynomials, then
                they already split and hence if we let $\sigma=\varphi$, then
                we have shown that the splitting fields are isomorphic. Assume
                the claim is true for $n\in\mathbb{N}$. We can assume that $f$
                has an irreducible factor $g$ of degree greater than 1. Then
                $g$ has a root in $K$, label it $\alpha$, and let
                $g'=\varphi\circ{g}$. Then $g'|f'$ and $g'$ is irreducible
                over $F'$. So let $\alpha$ be a root of $g'$ in $K'$. Then
                $F[x]/(g)\simeq{F}[\alpha]\simeq{F}'[\alpha']\simeq{F}'[x]/(g')$
                and thus we can extend this isomorphism one step up. So now we
                have:
                \twocolumneq{f(x)=(x-\alpha)f_{1}(x)}
                            {f'(x)=(x-\alpha')f_{1}'(x)}
                $f_{1}$ splits in $K$ and thus we need to show that $K$ is
                minimal. Suppose $K/L/F_{1}$. Then since $f_{1}$ splits in $L$,
                $F$ splits in $L$ as well, contradicting the minimality of $K$
                over $F$, and hence $K$ is minimal over $F_{1}$. Thus, $K$ is
                a splitting field for $f_{1}$ over $F_{1}$. Thus by induction
                there is an isomorphism $\sigma:K\rightarrow{K}'$ with the
                desired property over $F_{1}$ and $F_{1}'$. But $F_{1}$ and
                $F_{1}'$ are extensions over $F$ and $F'$, so we're done.
            \end{proof}
    \section{Separability}
            Let $F$ be a field, $f\in{F}[x]$ be a polynomial of degree $n$, and
            $K$ the splitting field of $f$ over $F$. Then:
            \begin{equation}
                f(x)=a_{n}\prod_{k\in\mathbb{Z}_{r}}(x-\alpha_{k})^{m_{k}}
            \end{equation}
            where the $\alpha_{k}$ are distinct roots, and the $m_{k}$ are all
            positive integers.
            \begin{definition}
                A simply root of a polynomial $f$ over a field $F$ is an element
                $\alpha\in{F}$ such that $\alpha$ is a root of $f$ and
                $(x-\alpha)^{2}$ does not divide $f$. Otherwise $\alpha$ is
                called a multiple root.
            \end{definition}
            \begin{example}
                In $\mathbb{Q}[x]$ we can consider $x^{2}-1$. This splits as
                $(x-1)(x+1)$ and so we see that the roots are $\pm{1}$. However
                neither $(x-1)^{2}$ nor $(x+1)^{2}$ divides $f$, and hence both
                roots are simple. If we consider $x^{2}+2x+1$ then we know this
                factors as $(x+1)^{2}$ and so the only root is $\minus{1}$ and
                it is a multiple root with multiplicity 2.
            \end{example}
            \begin{definition}
                A separable polynomial is one such that every rot is simple.
                Otherwise, $f$ is inseparable.
            \end{definition}
            Over $\mathbb{C}$ we can use calculus to determine separability.
            Let $\alpha\in\mathbb{C}$ be a root of $f(x)\in\mathbb{C}[x]$ and
            suppose:
            \begin{equation}
                f(x)=(x-\alpha)^{m}g(x)
            \end{equation}
            with $m\geq{1}$. If we look at the derivative of $f$, we obtain:
            \begin{equation}
                \dot{f}(x)=m(x-\alpha)^{m-1}g(x)+(x-\alpha)^{m}\dot{g}(x)
            \end{equation}
            where $g(\alpha)\ne{0}$. Then there are two possibilities:
            \begin{equation}
                \dot{f}(\alpha)=
                \begin{cases}
                    0,&m\geq{2}\\
                    g(\alpha),&m=1
                \end{cases}
            \end{equation}
            Since $g(\alpha)$ is non-zero we see that $\alpha$ is a simply root
            if and only if the derivative of $f$ evaluated at $\alpha$ is
            non-zero. The idea is to generalize such notions to general fields
            where we may not have the structure to perform calculus. We thus
            define a derivation on $F[x]$.
            \begin{definition}
                A derivation on an algebra $\mathscr{A}$ over a field $F$ is a
                function $D:\mathscr{A}\rightarrow\mathscr{A}$ such that:
                \begin{align}
                    D(af+bg)&=aD(f)+bD(g)\\
                    D(x^{n})&=nx^{n-1}\\
                    D(f\circ{g})&=Df(g(x))\cdot{D}g(x)\\
                    D(fg)&=D(f)g+fD(g)
                \end{align}
            \end{definition}
            \begin{theorem}
                Linearity, Liebnizean, and $D(x)=1$ imply the other properties.
            \end{theorem}
            \begin{example}
                Let $p\in\mathbb{N}$ be a prime, and consider the field
                $\ring{\mathbb{Z}_{p}}$ with the usual arithmetic modulo $p$.
                Let $t\in\mathbb{Z}_{p}$ be some fixed constant, and consider
                the polynomial $f\in\mathbb{Z}_{p}[x]$ defined by
                $f(x)=x^{p}-t$. Then $f$ is irreducible, regardless of choice of
                $t$ by applying Eisenstein's criterion to the field
                $\mathbb{Z}_{p}[t]\subseteq\mathbb{Z}_{p}$. Let
                $\mathbb{Z}_{p}(\sqrt[p]{t})=\mathbb{Z}_{p}[x]/(x^{p}-t)$. Then:
                \begin{equation}
                    f(x)=x^{p}-t=x^{p}-(\sqrt[p]{t})^{p}-(x-\sqrt[p]{t})^{p}
                \end{equation}
                and thus $f$ has root $\sqrt[p]{t}$ with multiplicity $p$. Note
                that we can distribute the power only because $\mathbb{Z}_{p}$
                has characteristic $p$, and hence $(a+b)^{p}=a^{p}+b^{p}$,
                a consequence of the binomial theorem.
            \end{example}
            \begin{theorem}
                If $\ring{F}$ is a field, $f\in{F}[x]$ is a nonconstant, then
                $f$ is separable if and only if $f$ and $Df$ are relatively
                prime.
            \end{theorem}
            \begin{proof}
                First note that the greatest common denominator is independent
                of the base field for two polynomials $f$ and $g$. Thus, suppose
                $K$ is a splitting field for $f$ and $\alpha$ is a root. Then
                $f$ being separable implies that:
                \begin{align}
                    f(x)&=(x-\alpha)g(x)\\
                    \Rightarrow{Df}(x)&=g(x)+(x-\alpha)Dg(x)\\
                    \Rightarrow(Df)(\alpha)&=g(\alpha)
                \end{align}
                But $g(\alpha)\ne{0}$, and hence $Df(\alpha)\ne{0}$. In the
                other direction, let $\alpha\in{K}$ be a multiple root of $f$ so
                that $f(x)=(x-\alpha)^{2}h(x)$ with $h\in{K}[x]$. But then:
                \begin{align}
                    f(x)&=(x-\alpha)^{2}h(x)\\
                    \Rightarrow{Df}(x)&=2(x-\alpha)h(x)+(x-\alpha)^{2}Dh(x)
                    \Rightarrow{Df}(\alpha)&=0)
                \end{align}
                So $\alpha$ is also a root of $Df$ in $K$.
                If $f\in{F}[x]$ and $K/F$ is an extension field with
                $\alpha\in{K}$ such that $f(\alpha)=0$, then $m_{\alpha/F}(x)$
                divides $f(x)$. So $m_{\alpha/F}(x)$ divides the greatest
                common denominator of $f$ and $Df$, and thus $f$ and $Df$ are
                relatively prime.
            \end{proof}
            \begin{example}
                Let $F$ be a field, and let $f(x)=x^{n}-a$ for some $a\in{F}$.
                Using the previous theorem we can determine when $f$ is
                separable over $F$. Suppose $a\ne{0}$. Then we have
                $Df(x)=nx^{n-1}$, and thus we have two cases: $n=0$ and
                $n\ne{0}$. In the first case we have that the characteristic of
                $F$ then divides $n$, and hence $f$ is not separable. In the
                latter, $n\ne{0}$ and thus the characteristic does not divide
                $n$, and since the GCD of $nx^{n-1}$ and $x^{n}-a$ is 1,
                for otherwise $0$ would be a root of $f$ but it is not, and thus
                $f$ is separable.
            \end{example}
            \begin{theorem}
                If $f\in{F}[x]$ is irreducible, then $f$ is separable if and
                only if $Df$ is non-zero.
            \end{theorem}
            \begin{theorem}
                If $F$ is a field with characteristic zero, then any irreducible
                polynomial is separable. Hence $f\in{F}[x]$ is separable if and
                only if $f$ is the product of distinct irreducibles.
            \end{theorem}
            \begin{theorem}
                If $F$ is a field with characteristic $p>0$ then any irreducible
                $f(x)=g(x^{p^{r}})$ for $g\in{F}[x]$ is irreducible, separable,
                and uniquely determined for some $r\geq{1}$.
            \end{theorem}
            \begin{definition}
                The Frobenius map on a field of characteristic $p\in\mathbb{N}$
                is the function $\phi:F\rightarrow{F}$ defined by
                $\phi(x)=x^{p}$.
            \end{definition}
            \begin{definition}
                A perfect field is a field $F$ such that every irreducible
                polynomial is separable.
            \end{definition}
            \begin{example}
                Every field of characteristic zero is perfect by the previous
                theorems.
            \end{example}
            Do there exists fields of characteristic $p>0$ that are perfect?
            The answer is yes, and this can be categorized by the following
            theorem.
            \begin{theorem}
                If $\ring{F}$ is a field, then $F$ is perfect if and only if
                either $F$ has characteristic zero, or if the Frobenius
                map $\phi:F\rightarrow{F}$ is surjective.
            \end{theorem}
    \section{Subfields and Automorphisms}
        If $K/F$ is a finite field extension, $A=\autgroup[F]{K}$ the
        automorphism group, $H\subseteq{A}$ a subgroup, the fixed field of $H$
        is the set $K^{H}$ defined by all $\alpha\in{K}$ such that for all
        $\sigma\in{H}$ it is true that $\sigma(\alpha)=\alpha$.
        \begin{theorem}
            If $\ring{F}$ is a field, if $\ring{K}$ is a field extension of $F$,
            if $\autgroup[F]{K}$ is the automorphism group of $K$ over $F$,
            and if $H\subseteq\autgroup[F]{K}$ is a subgroup, then the fixed
            field $K^{H}$ is a subfield of $K$.
        \end{theorem}
        \begin{proof}
            For if $\alpha,\beta\in{K}^{H}$, then:
            \begin{equation}
                \sigma(\alpha+\beta)=\sigma(\alpha)+\sigma(\beta)
                    =\alpha+\beta
            \end{equation}
            and thus $\alpha+\beta\in{K}^{H}$. Similarly:
            \begin{equation}
                \sigma(\alpha\cdot\beta)=\sigma(\alpha)\cdot\sigma(\beta)
                    =\alpha\cdot\beta
            \end{equation}
            and therefore $\alpha\cdot\beta\in{K}^{H}$. Lastly:
            \begin{equation}
                \sigma(\alpha^{\minus{1}})=\sigma(\alpha)^{\minus{1}}
                    =\alpha^{\minus{1}}
            \end{equation}
            and hence $\alpha^{\minus{1}}\in{K}^{H}$.
        \end{proof}
        Note that since $\sigma\in\autgroup[F]{K}$, for all $x\in{F}$ it is true
        that $\sigma(x)=x$. Hence, $F\subseteq{K}^{H}$.
        \begin{theorem}
            If $\ring{F}$ is a field, if $\ring{L}$ is a field extension of
            $F$, and if $\ring{K}$ is a field extension of $L$, then
            $\autgroup[L]{K}$ is a subgroup of $\autgroup[F]{K}$.
        \end{theorem}
        \begin{theorem}
            If $\ring[F]{F}$ is a field, if $\ring[K]{K}$ is a field extension
            of $F$, if $H$ is a subgroup of the automorphism group
            $\autgroup[F]{K}$, and if $K^{H}$ is the fixed field of $H$,
            then $H$ is a subgroup of $\autgroup[K^{H}]{K}$.
        \end{theorem}
        \begin{theorem}
            If $\ring[F]{F}$ is a field, if $\ring[L]{L}$ is an extension field
            of $F$, if $\ring[K]{K}$ is an extension field of $L$, if
            $\autgroup[L]{K}$ is the automorphism group, and if
            $K^{\autgroup[L]{K}}$ is the fixed field, then
            $L\subseteq{K}^{\autgroup[L]{K}}$.
        \end{theorem}
        \begin{theorem}
            $K/L_{1}/L_{2}/F$ implies that $\autgroup[L_{2}]{K}$ is a subgroup
            of $\autgroup[L_{1}]{K}$.
        \end{theorem}
        \begin{theorem}
            If $H_{1}\subseteq{H}_{2}\subseteq\autgroup[F]{K}$, then
            $K^{H_{2}}\subseteq{K}^{H_{1}}$.
        \end{theorem}
        \begin{definition}
            A Galois extension of a field $\ring[F]{F}$ is a field $\ring[K]{K}$
            such that $\cardinality{\autgroup[F]{K})}=[K:F]$.
        \end{definition}
    \section{More on Symmetric Polynomials}
        Given the symmetric group $S_{n}$, this acts on $F[x_{1},\dots,x_{n}]$
        by permuting the variables. The symmetric polynomials are those that are
        invariant under permutations of variables. This is a ring.
    \section{Stuff}
        If $K/F$ is a finite extension field, then the number of automorphisms
        is bounded by the degree. That is,
        $\cardinality{\autgroup[F]{K}}\leq[K:F]$. Let $K/F$ and $L/F$ are
        extensions, where $K/F$ is finite (there is no constraint on $L/F$). We
        look at $\homomorphisms[F]{K}{L}$ which is the set of all homomoprhisms
        $\varphi:K\rightarrow{L}$ that fix $F$. Then $\homomorphisms[F]{K}{L}$
        is finite. For if $K/F$ is finite, then it is finitely generated:
        $K=F(\alpha_{1},\dots,\alpha_{n})$, and thus any $\varphi$ is determined
        by where it maps the $\alpha_{i}$, and the $\varphi(\alpha_{i})$ are
        roots of the minimal polynomial $m_{\alpha_{i}/F}$. So there are
        finitely many cuch choices for $\varphi$. If we consider the vector
        space homomoprhisms $\homomorphisms[F(VS)]{K}{L}$ of all linear
        transformations $\varphi:K\rightarrow{L}$ that fix $F$, then there are
        infinitely many elements. If $L/F$ is also finite, then the dimension
        of this space is also finite since it's the space of $m\times{n}$
        matrices where $m=[K:F]$ and $n=[L:F]$.
        \begin{theorem}
            $\homomorphisms[F]{K}{L}\subseteq\homomorphisms[F(VS)]{K}{L}$.
        \end{theorem}
        \begin{proof}
            Asuume $\homomorphisms[F]{K}{L}$ is dependent. So there exists
            elements $a_{j}\in{L}$, not all of which are zero, and function
            $\varphi_{j}\in\homomorphisms[F]{K}{L}$ such that:
            \begin{equation}
                \sum_{i=1}^{m}a_{j}\varphi_{j}=0
            \end{equation}
        \end{proof}
        \begin{theorem}
            Letting $L=K$, we have $\autgroup[F]{K}$ has less than $[K:F]$
            elements.
        \end{theorem}
        Heading back to the before time:
        \begin{theorem}
            If $\ring{K}$ is a field, if $H\subseteq\autgroup{K}$ is a finite
            subgroup of the automorphism group of $K$, and if $K^{H}$ is the
            fixed field of $H$, then $K/K^{H}$ is a finite field extension and
            $[K:K^{H}]=\cardinality{H}$.
        \end{theorem}
        Let $K/F$ be a finite Galois extension, and let $G\in\autgroup[F]{G}$.
        There is a bijection between the subgroups of $H$ and the subextensions
        of $L$ such that $K/L/F$. We map $H\mapsto{K}^{H}$, the fixed field
        of $H$, and we map $L$ to $\autgroup[L]{K}$. Moreover,
        $H=\autgroup[K^{H}]{K}$. Next we need to prove that for any extension
        field $L$ of $F$ such that $K$ is an extension of $L$, we must show
        that $L=K^{\autgroup[L]{K}}$. That is, $L$ is equal to the fixed field
        generated by the automorphism group $\autgroup[L]{K}$.
        \begin{theorem}
            If $\ring[F]{F}$ is a field, if $\ring[L]{L}$ is a field
            extension of $F$, is $\ring[K]{K}$ is a field extension of $L$,
            and if $K$ is a Galois extension of $F$, then $K$ is a Galois
            extension of $L$.
        \end{theorem}
        \begin{proof}
            For let $X=\homomorphisms[F]{L}{K}$. Then for $\iota\in{X}$,
            $\iota:L\rightarrow{K}$ is an inclusion mapping. Note that
            $G$ acts on $\autgroup[F]{K}$ by $g\cdot\varphi=g\circ\varphi$
            for all $g\in\autgroup[F]{K}$ and $\varphi\in{X}$. Then the
            stabilizer $G_{\iota}$ of $\iota$, which is the set of all
            $g\in{G}$ such that $g\cdot\iota=\iota$. But then
            $G_{\iota}=\autgroup[L]{K}$ since $\iota$ fixes $L$. But since $K$
            is a Galois extension of $F$,
            $[K:F]=\cardinality{\autgroup[F]{G}}$. But by the orbit stabilizer
            theorem:
            \begin{equation}
                \cardinality{\autgroup[F]{G}}
                =\cardinality{\autgroup[F]{K}_{\iota}}\cdot
                    \cardinality{\autgroup[F]{K}\cdot\iota}
            \end{equation}
            where $G\cdot\iota=\{g\cdot\iota|g\in\autgroup[F]{K}\}$. But
            $\autgroup[F]{K}_{\iota}=\autgroup[L]{K}$, and hence:
            \begin{equation}
                [K:F]=\cardinality{\autgroup[L]{K}}\cdot
                    \cardinality{\autgroup[F]{K}\cdot\iota}
            \end{equation}
            But $G\cdot\iota\subseteq{X}$, and hence:
            \begin{equation}
                [K:F]=\cardinality{\autgroup[L]{K}}\cdot\cardinality{X}
                \leq[K:L]\cdot[L:F]=[K:F]
            \end{equation}
            and hence these inequalities are actually equalities. Thus,
            $\autgroup[L]{K}=[K:L]$.
        \end{proof}
        \begin{theorem}
            If $\ring[F]{F}$ is a field, and if $\ring[K]{K}$ is a Galois
            extension of $F$, then $F=K^{\autgroup[F]{K}}$, where
            $K^{\autgroup[F]{G}}$ is the fixed field of $\autgroup[F]{K}$.
        \end{theorem}
        \begin{proof}
            For let $E=K^{\autgroup[F]{G}}$. We know that $F\subseteq{E}$.
            But since $K$ is a Galois extension of $F$, it is true that
            $[K:F]=\cardinality{\autgroup[F]{K}}$. But any
            $\varphi:K\rightarrow{K}$ that fixed $F$ also fixed $E$, and hence
            $\autgroup[F]{G}=\autgroup[E]{G}$, and therefore:
            \begin{equation}
                [K:F]=\cardinality{\autgroup[F]{K}}
                    =\cardinality{\autgroup[E]{K}}
                    \leq[K:E]=[K:F]/[E:F]
            \end{equation}
            and thus $[E:F]=1$. But if $E$ has degree 1 over $F$, then
            $E$ is equal to $F$. Thus, $F=K^{\autgroup[F]{K}}$.
        \end{proof}
        Some known properties of the bijection given by the fundamental theorem
        of Galois theory: If $H_{1}\subseteq{H}_{2}$, then
        $K^{H_{2}}\subseteq{K}^{H_{1}}$. That is, the bijection is inclusion
        reversing. If $H$ is a subgroup of $\autgroup[F]{K}$, then
        the index $[G:H]=[K^{H}:F]$. In other words, if $L$ is the
        subextension corresponding to $H$, then the index of $G$ over $H$ is
        equal to the degree of $L$ over $F$.
        \begin{theorem}
            If $K/L/F$ is a subextension, if $K/F$ is a finite Galois extension,
            if $G=\autgroup[F]{K}$, and if $H=\autgroup[L]{K}$, then
            $L/F$ is Galois if and only if $H$ is a normal subgroup of $G$.
        \end{theorem}
        \begin{proof}
            Let $X=\homomorphisms[F]{L}{K}$, $\iota\in{X}$. $G$ acts on $X$ and
            $G_{\iota}=\autgroup[L]{K}=H$. If $L/F$ is Galois, then
            $\cardinality{\autgroup[F]{L}}=[L:F]$ and this is equal to
            $\cardinality{X}$. The mapping $\autgroup[F]{L}\rightarrow{X}$
            defined by $\tau\mapsto\iota\circ\tau$ is injective since $\iota$
            is injective, and hence this is also surjective since
            $\cardinality{\autgroup[F]{L}}=\cardinality{X}$, and these are
            finite sets. So given any $\sigma\in\autgroup[F]{K}$,
            $\sigma|_{L}:L\rightarrow{K}$, so $\sigma_{L}\in{X}$ and hence
            there is a $\tau\in\autgroup[F]{L}$ such that
            $\sigma|_{L}=\iota\circ\tau$. Hence $\sigma(L)=\iota(\tau(L))=L$.
        \end{proof}
    \section{Notes from Milne (Chapter 1)}
        Def of rings, subrings, ring homomorphisms, commutative rings.
        \begin{definition}
            An integral domain is a ring $\ring{R}$ such that for all
            $a,b\in{R}$ such that $a\cdot{b}=0$, it is true that either $a=0$ or
            $b=0$.
        \end{definition}
        \begin{definition}
            An ideal of a ring $\ring{R}$ is a subring $\ring[I]{I}$ such that
            for all $a,b\in{I}$ it is true that $a+b\in{I}$, and for all
            $r\in{R}$ and for all $a\in{I}$ it is true that $r\cdot{a}\in{I}$
            and $a\cdot{r}\in{I}$.
        \end{definition}
        \begin{definition}
            A field is a commutative division ring $\ring{F}$.
        \end{definition}
        \begin{example}
            Since by definition a division ring is a non-zero ring, fields are
            required to have at least two elements. The smallest field is thus
            $\ring{\mathbb{Z}_{2}}$ with modulo arithmetic.
        \end{example}
        \begin{theorem}
            If $\ring{F}$ is a commutative ring, then it is a field if and only
            if there only ideals are the zero ideal and the entire ring.
        \end{theorem}
        \begin{proof}
            For if $\ring{F}$ is a field then for all $a\in{F}$ such that
            $a\ne{0}$ there exists a multiplicative inverse
            $a^{\minus{1}}\in{F}$ such that $a\cdot{a}^{\minus{1}}=1$. But then
            if $\ring[I]{I}$ is a non-zero subring of $R$, there is a non-zero
            element $a\in{I}$, and thus $a\cdot{a}^{\minus{1}}\in{I}$, and
            therefore $1\in{I}$. But then for all $r\in{F}$, $r\cdot{1}\in{I}$,
            but $r\cdot{1}=r$. Hence, $I=R$. In the other direction, if
            the only ideals are the zero ideal and the entire ring, then for
            any non-zero $a\in{F}$ the ideal generated by $a$ must be the entire
            ring. Hence, there is a $b\in{I}$ such that $a\cdot{b}=1$, and so
            $1\in{I}$, and hence $I$ is the entire ideal.
        \end{proof}
        \begin{example}
            Fields: $\mathbb{Q}$, $\mathbb{R}$, $\mathbb{C}$, $\mathbb{Z}_{p}$
            with $p$ a prime.
        \end{example}
        Def field homomoprhism, same as rings.
        \begin{theorem}
            If $\ring[F]{F}$ and $\ring[K]{K}$ are fields, and if
            $\phi:F\rightarrow{K}$ is a field homomoprhism, then it is
            injective.
        \end{theorem}
        \begin{proof}
            For $\phi^{\minus{1}}[\{0_{K}\}]$ is an ideal in $F$, and since it
            doesn't contain 1 by the definition of a field homomoprhism, it
            must be a proper ideal. Hence, it is the zero ideal. But then if
            $\phi(a)=\phi(b)$, then $\phi(a-b)=0_{K}$, and thus $a-b=0_{F}$.
            That is, $a=b$.
        \end{proof}
        \begin{theorem}
            If $\ring[F]{F}$ is a field, if $\ring{\mathbb{Z}}$ is the standard
            ring of integers, if $\ring{\mathbb{Q}}$ is the field of
            rational numbers, and if $f:\mathbb{Z}\rightarrow{F}$ is an
            injective ring homomoprhism, then there exists a field homomoprhism
            $\tilde{f}:\mathbb{Q}\rightarrow{F}$.
        \end{theorem}
        \begin{proof}
            For any $n\in\mathbb{Z}$, we have:
            \begin{equation}
                f(n)=f\Big(\sum_{k\in\mathbb{Z}_{n}}1\Big)
                =\sum_{k\in\mathbb{Z}_{n}}f(1)
            \end{equation}
            But $f$ is injective, and hence $f(1)\ne{0}_{R}$. Thus, since
            $\ring[F]{F}$ is a field, for all $n\in\mathbb{Z}\setminus\{0\}$
            there is an $m\in\mathbb{Z}\setminus\{0\}$ such that
            $f(n)\cdot{f}(m)=f(1)$. Define $\tilde{f}$ as follows:
            \begin{equation}
                \tilde{f}\big((n,m)\big)=
                \begin{cases}
                    0,&n=0\\
                    f(n)\cdot_{F}f(m)^{\minus{1}},&\textrm{otherwise}
                \end{cases}
            \end{equation}
        \end{proof}
        \begin{definition}
            A field of characteristic zero is a field $\ring{F}$ such that there
            exists a field homomoprhism $f:\mathbb{Q}\rightarrow{F}$.
        \end{definition}
        Equivalently one could say that adding $1_{F}$ to itself $n$ times never
        results in zero.
        \begin{example}
            $\mathbb{Q}$, $\mathbb{R}$, and $\mathbb{C}$ are fields of
            characteristic zero.
        \end{example}
        \begin{definition}
            The characteristic of a field $\ring{F}$ is the smallest non-zero
            $n\in\mathbb{N}$ such that:
            \begin{equation}
                \sum_{k\in\mathbb{Z}_{n}}1_{F}=0_{F}
            \end{equation}
        \end{definition}
        \begin{theorem}
            If $n\in\mathbb{N}^{+}$ is a non-negetive integer, and if
            $\ring{F}$ is a field of characteristic $n$, then $n$ is a prime
            number.
        \end{theorem}
        \begin{proof}
            For suppose not. Then there are integers $p,q\in\mathbb{N}^{+}$ such
            that $p,q<n$ and $p\cdot{q}=n$. Let $f:\mathbb{Z}\rightarrow{F}$ be
            defined by:
            \begin{equation}
                f(n)=
                \begin{cases}
                    0_{F},&n=0\\
                    \sum_{k\in\mathbb{Z}_{n}}1_{F},&n>0\\
                    \minus\sum_{k\in\mathbb{Z}_{|n|}}1_{F},&n<0
                \end{cases}
            \end{equation}
            This is a ring homomoprhism, and hence
            $f(p\cdot{q})=f(p)\cdot{f}(q)$. But $f(n)=0$, and since all fields
            are integral domains, either $f(p)=0$ or $f(q)=0$. But then there
            exists a positive integer smaller than $n$ such that $f(p)=0$,
            a contradiction as $n$ is the characteristic of $F$. Hence, $n$ is
            a prime.
        \end{proof}
        \begin{ftheorem}{Binomial Theorem}{Binomial_Theorem}
            If $\ring{R}$ is a commutative ring, if $a,b\in{R}$, and if
            $n\in\mathbb{N}$, then:
            \begin{equation*}
                (a+b)^{n}=\sum_{k\in\mathbb{Z}_{n}}\binom{n}{k}a^{k}b^{n-k}
            \end{equation*}
        \end{ftheorem}
        \begin{theorem}
            If $p\in\mathbb{N}$ is a prime number, if $r\in\mathbb{N}$ is such
            that $1\leq{r}$ and $r\leq{p}^{n}-1$, then $p$ divides
            $\binom{p^{n}}{r}$.
        \end{theorem}
        \begin{theorem}
            If $\ring{F}$ is a field of characteristic $p\in\mathbb{N}^{+}$,
            if $n\in\mathbb{N}$, and if $a,b\in{F}$, then:
            \begin{equation}
                (a+b)^{p^{n}}=a^{p^{n}}+b^{p^{n}}
            \end{equation}
        \end{theorem}
        \begin{proof}
            Apply the binomial in combintation with the previous theorem.
        \end{proof}
        \begin{definition}
            The ring of polynomials over a field $\ring{F}$ is the set of all
            finitely supported sequences $a:\mathbb{N}\rightarrow{F}$ with the
            following addition and multiplication:
            \begin{align}
                (a+b)_{n}&=a_{n}+b_{n}\\
                (ab)_{n}&=\sum_{k=0}^{n}a_{k}b_{n-k}
            \end{align}
        \end{definition}
        This is very much mimicing polynomials. The sum rule says we simply add
        the coefficients of two polynomials, and the product is the Cauchy
        product of two polynomials. That is, we multiply
        $(a_{0}+a_{1}x+\dots+a_{n}x^{n})$ by $(b_{0}+b_{1}x+\dots+b_{n}x^{n})$
        and collect the coefficients of all terms with order $x^{k}$ and group
        them. The resulting coefficient is precisely this sum.
        \begin{theorem}
            If $\ring{F}$ is a field, then $\ring{F[x]}$ is a commutative ring.
        \end{theorem}
        \begin{theorem}
            If $\ring{F}$ is a field, then $\ring{F[x]}$ is a commutative
            algebra over $F$.
        \end{theorem}
        There is a natural embedding of $F$ into $F[x]$ by looking at the
        subspace of all sequence $a:\mathbb{N}\rightarrow{F}$ such that
        $a_{k}=0$ for all $k>0$. That is, the only possible non-zero term is
        $a_{0}$.
        \begin{theorem}
            If $\ring[F]{F}$ is a field, if $\ring[R]{R}$ is a ring, if
            $F\subseteq{R}$ is a subring, and if $r\in{R}$, then there is a
            unique homomoprhism $f:F[x]\rightarrow{R}$ such that for all
            $a\in{F}$, $f(a)=r$.
        \end{theorem}
        \begin{definition}
            The degree of a non-zero polynomial $a\in{F}[x]$ is the largest
            $n\in\mathbb{N}$ such that $a_{n}\ne{0}$. The degree of the zero
            polynomial is zero.
        \end{definition}
        Since $F[x]$ is the space of all finitely supported sequences, for any
        such $a\in{F}[x]$ there will eventually be an $N\in\mathbb{N}$ such that
        for all $n>N$ it is true that $a_{n}=0$. By the well-ordering all of the
        integers, there will be a least such element, and hence the above
        definition is well defined. There's a natural way of looking at
        $F[x]$ as a subset of $\funcspace[F]{F}$, the set of all functions from
        $F$ to itself. Given $a\in{F}[x]$ of degree $n\in\mathbb{N}$ we consider
        the function $f\in\funcspace[F]{F}$ defined by:
        \begin{equation}
            f(x)=\sum_{k\in\mathbb{Z}_{n+1}}a_{k}\cdot_{F}x^{k}
            =a_{0}+_{F}a_{1}\cdot_{k}x+_{F}a_{2}\cdot_{F}x^{2}+_{F}\dots
            +_{F}a_{n}\cdot_{F}x^{n}
        \end{equation}
        In more familiar language (dropping the subscripts and using
        concatenation to denote multiplication), we have:
        \begin{equation}
            f(x)=a_{0}+a_{1}x+\cdots+a_{n}x^{n}
        \end{equation}
        The sequence definition is good for rigor and solving theorems, since
        the Cauchy product allows one to easily manipulate expressions without
        worrying about the non-existent dummy variable $x$, whereas the function
        definition (as a subset of $\funcspace[F]{F}$) is good for intuition.
        \begin{definition}
            A monic polynomial of degree $n$ in a field $\ring{F}$ is a
            polynomial $a\in{F}[x]$ of degree $n\in\mathbb{N}$ such that
            $a_{n}=1$.
        \end{definition} 
        \begin{theorem}
            If $\ring{F}$ is a field, then $F[x]$ is a Euclidean domain.
        \end{theorem}
        \begin{theorem}
            If $\ring{F}$ is a field, if $\ring[I]{I}$ is an ideal in $F[x]$,
            and if $a\in{I}$ is of least degree, then $I=(a)$, where $(a)$ is
            the ideal generated by $a$.
        \end{theorem}
        \begin{proof}
            For given $b\in(a)$, there is an $r\in{F}[x]$ such that
            $b=r\cdot{a}$. But $I$ is an ideal, and $a\in{I}$, and hence
            $b\in{I}$. Thus, $(a)\subseteq{I}$. If $b\in{I}$, then by the
            division algorithm there are polynomials $p,q\in{F}[x]$ such that
            $b=aq+r$ where the degree of $r$ is strictly less than the degree of
            $a$. But then $r=b-aq$. And since $b\in{I}$ and $q\in{F}[x]$, it is
            true that $bq\in{I}$ since $I$ is an ideal. But if $a\in{I}$ and
            $bq\in{I}$, then $b-aq\in{I}$ since $I$ is an ideal. Thus,
            $r\in{I}$. But $r$ is a polynomial of degree strictly less than
            $a$, and $a$ is a non-zero polynomial of least degree in $I$.
            Therefore, $r=0$. But then $b=aq$, and hence $b\in(a)$. Thus,
            $I\subseteq(a)$. From the definition of equality, $I=(a)$.
        \end{proof}
        \begin{theorem}
            There exists a bijection between monic polynomials in $F[x]$ and
            the ideals of $F[x]$.
        \end{theorem}
        \begin{definition}
            A root of a polynomial $a\in{F}[x]$ of degree $n\in\mathbb{N}$ over
            a field $\ring{F}$ is an element $r\in{F}$ such that:
            \begin{equation}
                \sum_{k\in\mathbb{Z}_{n+1}}a_{k}\cdot_{F}x^{k}=0_{F}
            \end{equation}
        \end{definition}
        \begin{theorem}
            If $\ring{\mathbb{Q}}$ is the field of rational numbers, if
            $a\in\mathbb{Q}[x]$ is a polynomial of degree $n\in\mathbb{N}$,
            if $r\in\mathbb{Q}$ is a root of $a$, and if $p,q\in\mathbb{Q}$
            are such that $r=p/q$ and $\GCD(p,q)=1$, then $p$ divides $a_{0}$
            and $q$ divides $a_{n}$.
        \end{theorem}
        \begin{proof}
            For if $r$ is a root, then:
            \begin{equation}
                \sum_{k\in\mathbb{Z}_{n+1}}a_{k}\cdot{r}^{k}=0
            \end{equation}
            But $r=p/q$, and thus:
            \begin{equation}
                \sum_{k\in\mathbb{Z}_{n+1}}a_{k}\cdot\big(\frac{p}{q}\big)^{k}
                =0
            \end{equation}
            Simplifying, and multiplying both sides by $q^{k}$, we have:
            \begin{equation}
                \sum_{k\in\mathbb{Z}_{n+1}}a_{k}\cdot{p}^{k}q^{n-k}=0
            \end{equation}
            From this, $q$ divides $a_{n}p^{n}$. But $\GCD(p,q)=1$, and hence
            $q$ does not divide $p^{n}$. Thus, $q$ divides $a_{n}$. Similarly,
            $p$ divides $a_{0}$.
        \end{proof}
        \begin{example}
            Sticking with $\mathbb{Q}[x]$, the polynomial $f(x)=x^{3}-3x-1$ is
            irreducible over $\mathbb{Q}$. By the previous theorem, the only
            possible roots $p/q$ must be such that $p$ divides $\minus{1}$ and
            $q$ divides $1$. Hence, $p/q=\pm{1}$. But $f(1)=\minus{3}$ and
            $f(\minus{1})=1$, neither of which are zero. Hence, $f$ has no roots
            over $\mathbb{Q}$. Since it is a cubic, it must be irreducible.
        \end{example}
        \begin{ftheorem}{Gauss's Lemma for Polynomials}
                        {Gauss's Lemma for Polynomials}
            If $\ring{\mathbb{Z}}$ is the ring of integers, if
            $\ring{\mathbb{Q}}$ is the field of rational numbers, if
            $a\in{\mathbb{Z}}[x]$ is such that $a$ factors non-trivially in
            $\mathbb{Q}[x]$, then $a$ factors non-trivially in $\mathbb{Z}[x]$.
        \end{ftheorem}
        \begin{bproof}
            For if $b,c\in\mathbb{Q}[x]$ are such that $a=b\cdot{c}$, if
            $M,N\in\mathbb{N}$ are the products of the denominators of $b$
            and $c$, respectively, then $Ma,Nb\in\mathbb{Z}[x]$. But then
            $NMa\in\mathbb{Z}[x]$. By the fundamental theorem of arithmetic,
            there exists a prime $p\in\mathbb{N}$ such that $p$ divides $MN$.
            But then $Ma\cdot{N}b$ is the zero polynomial in $\mathbb{F}_{p}[x]$
            and since $\mathbb{F}_{p}$ is a field, this means that $p$ divides
            the coefficients of every element of either $Ma$ or $Nb$. Continuing
            we remove all of the prime factor of $MNa$ and obtain a
            factorization of $a$ in $\mathbb{Z}[x]$.
        \end{bproof}
        \begin{theorem}
            If $\ring{\mathbb{Z}}$ is the ring of integers, if
            $a\in\mathbb{Z}[x]$ is a monic polynomial of degree
            $n\in\mathbb{N}$, and if $b\in\mathbb{Q}[x]$ is a monic factor of
            $a$, then $b\in\mathbb{Z}[x]$.
        \end{theorem}
        \begin{proof}
            For if $b,c\in\mathbb{Q}[x]$ are such that $a=bc$, with $b$ a monic
            polynomial, then by the Cauchy product, since $a$ is monic, $c$
            must also be monic. Let $m$ and $n$ by the least integers such that
            $mb,nc\in\mathbb{Z}[x]$. If $p\in\mathbb{N}$ is a prime that divides
            $mn$, then it divides all of the coefficients of either $mb$ of $nc$
            and hence either $(m/p)b\in\mathbb{Z}[x]$ or
            $(n/p)c\in\mathbb{Z}[x]$, a contradiction since $m$ and $n$ are the
            least such integers with this property. Hence, $m=1$ and $n=1$.
        \end{proof}
        \begin{definition}
            An algebraic integer in $\mathbb{C}$ is a complex number
            $z\in\mathbb{C}$ such that $z$ is the root of a monic polynomial
            $a\in\mathbb{Z}[x]$.
        \end{definition}
        \begin{ftheorem}{Eisenstein's Criterion}{Eisenstein_Criterion}
            If $\ring{\mathbb{Z}}$ is the ring of integers, if
            $a\in\mathbb{Z}[x]$ is a polynomial in $\mathbb{Z}$ of degree
            $n\in\mathbb{N}$, if $p\in\mathbb{N}$ is a prime number such that
            $p$ does not divide $a_{n}$, $p^{2}$ does not divide $a_{0}$, and
            such that $p$ divides $a_{k}$ for all $k\in\mathbb{Z}_{n}$, then $a$
            is irreducible in $\mathbb{Q}[x]$.
        \end{ftheorem}
        \begin{bproof}
            For suppose $a$ factors in $\mathbb{Q}[x]$. But then it factors in
            $\mathbb{Z}[x]$. Suppose $b,c\in\mathbb{Z}[x]$ are non-trivial
            factors. By the Cauchy product, $a_{0}=b_{0}c_{0}$, and thus
            $p$ divides either $b_{0}$ or $c_{0}$. Suppose it divides $b_{0}$.
            But since $p^{2}$ does not divide $a_{0}$, $p$ does not divide
            $c_{0}$. But again by the Cauchy product,
            $a_{1}=b_{0}c_{1}+b_{1}c_{0}$. But $p$ divides $a_{1}$, and hence
            $p$ divides $b_{1}$. Continuing by induction on the Cauchy product,
            $p$ divides all of the $b_{k}$, contradicting that $p$ does not
            divide $a_{n}$.
        \end{bproof}
        It is important again to note that $\mathbb{Z}_{n}=\{0,1,\dots,n-1\}$,
        hence $\mathbb{Z}_{n}$ does not contain $n$. So we require $p$ to divide
        $a_{0},\dots,a_{n-1}$, but not $a_{n}$, and we require $p^{2}$ not to
        divide $a_{0}$. Eisenstein's criterion holds for any unique
        factorization domain.
        \begin{theorem}
            If $\ring{Z}$ is the ring of integers, if $a\in\mathbb{Z}[x]$ is a
            reducible polynomial in $\mathbb{Z}$ of degree $n\in\mathbb{N}$, if
            $p\in\mathbb{N}$ is a prime, and if $p$ does not divide $a_{n}$,
            then $\overline{a}\in\mathbb{F}_{p}[x]$ is reducible.
        \end{theorem}
        \begin{proof}
            For since $a\in\mathbb{Z}[x]$ is reducible, there exists
            $b,c\in\mathbb{Z}[x]$ such that $a=b\cdot{c}$. But since
            $p$ does not divide $a_{n}$, it does not divide
            $a_{0}b_{n}+a_{n}b_{0}$, and thus
            $\overline{a}=\overline{b}\cdot\overline{c}$ is a non-trivial
            factorization. Hence, $\overline{a}$ is reducible in
            $\mathbb{F}_{p}$.
        \end{proof}
        A more useful result is the contrapositive.
        \begin{theorem}
            If $\ring{\mathbb{Z}}$ is the ring of integers, if
            $p\in\mathbb{N}$ is a prime, if $\ring[p]{\mathbb{F}_{p}}$ is the
            field of integers modulo $p$, if $a\in\mathbb{Z}[x]$ is a polynomial
            of degree $n\in\mathbb{N}$ such that $p$ does not divide $a_{n}$,
            and if $\overline{a}\in\mathbb{F}_{p}[x]$ is irreducible, then
            $a$ is irreducible in $\mathbb{Z}[x]$.
        \end{theorem}
        The converse of this theorem does not hold. Indeed, there exist
        polynomials $a\in\mathbb{Z}[x]$ that are reducible in
        $\mathbb{F}_{p}[x]$ for every prime integer $p\in\mathbb{N}$, yet $a$
        is not reducible in $\mathbb{Z}[x]$.
        \begin{theorem}
            If $\ring{F}$ is a field, if $a\in{F}$, and if $f\in{F}[x]$, then
            there exists a polynomial $q\in{F}[x]$ such that, for all
            $x\in{F}$ it is true that:
            \begin{equation}
                f(x)=q(x)\cdot(x-a)+f(a)
            \end{equation}
        \end{theorem}
        \begin{proof}
            For by the division algorithm, there exists polynomials
            $q,r\in{F}[x]$ such that $f(x)=q(x)\cdot(x-a)+r(x)$ and $r$ has
            degree less than $x-a$. But the degree of $x-a$ is 1, and hence
            $r$ is a constant (has degree zero). Moreover:
            \begin{equation}
                f(a)=q(a)\cdot(a-a)+r(a)=q(a)\cdot{0}+r(a)=0+r(a)=r(a)
            \end{equation}
            Therefore $r(x)=f(a)$. Thus, for all $x\in{F}$,
            $f(x)=q(x)\cdot(x-a)+f(a)$.
        \end{proof}
        \begin{theorem}
            If $\ring{F}$ is a field, if $f\in{F}[x]$ is a polynomial, if
            $a\in{F}$, and if $x-a$ divides $f(x)$, then $f(a)=0$.
        \end{theorem}
        \begin{proof}
            For by the previous theorem, there is a polynomial $q\in{F}[x]$
            such that $f(x)=q(x)\cdot(x-a)+f(a)$. But if $f(a)=0$, then
            $f(x)=q(x)\cdot(x-a)$, and hence $x-a$ divides $f$. In the other
            direction, if $x-a$ divides $f(x)$, then there is a $q\in{F}[x]$
            such that $f(x)=q(x)\cdot(x-a)$. But then $f(a)=q(a)\cdot(a-a)$,
            and thus $f(a)=0$.
        \end{proof}
        \begin{theorem}
            If $\ring{F}$ is a field, if $f\in{F}[x]$ is a non-zero polynomial
            in $F$ of degree $n\in\mathbb{N}$, the there are at most $n$ roots.
        \end{theorem}
        \begin{proof}
            For by induction. If $f\in{F}[x]$ is a polynomial of degree 1, then
            $f(x)=ax+b$ for some $a,b\in{F}$. But if $\alpha$ is a root, then
            $f(x)=q(x)\cdot(x-\alpha)$. But since $f$ is degree 1, and since
            $x-\alpha$ is degree 1, $q$ must be of degree 0, and hence a
            constant. But $f$ is non-zero, and hence $\alpha\ne{0}$. Thus
            $f(x)=0$ if and only if $x=\alpha$. Suppose the proposition is true
            for $n\in\mathbb{N}$, and let $f\in{F}[x]$ be a non-zero polynomial
            of degree $n+1$. Suppose $f$ has more than $n+1$ roots. But if
            $\alpha$ is a root, then $x-\alpha$ divides $f$. Hence
            $f(x)=q(x)\cdot(x-\alpha)$, where $q$ is a polynomial of degree less
            than $f$. But by hypothesis $q$ then has at most $n$ roots. And any
            root of $q$ is a root of $f$, and hence $f$ has at most $n+1$ roots,
            a contradiction. Thus, $f$ has at most $n+1$ roots.
        \end{proof}
        \begin{theorem}
            If $\monoid{G}$ is a finite Abelian group, if $m\in\mathbb{N}$ is
            such that $m$ divides $\cardinality{G}$, then there are at most
            $m$ elements in $G$ whose order divides $m$ if and only if $G$ is
            cyclic.
        \end{theorem}
        \begin{proof}
            For if $G$ is cycle, and if $d$ divides $\cardinality{G}$, let
            $G_{d}=\{x\in{G}\;|\;x^{d}=1\}$. If $G_{d}$ is empty, then
            $\cardinality{G_{d}}<m$. If not then there is a $y\in{G}_{d}$.
            But then $\innerprod{y}\subseteq{G}_{d}$. For if
            $x\in\innerprod{y}$, then $x=y^{k}$ for some $k\in\mathbb{Z}_{n}$.
            But then $x^{d}=(y^{k})^{d}=y^{kd}=1$, and hence $x\in{G}_{d}$.
            Therefore, $\innerprod{y}\subseteq{G}_{d}$. Now let $x\in{G}_{d}$
            Since $\monoid{G}$ is cyclic there exists $z\in{G}$ such that
            $\innerprod{z}=G$. But then there exists
            $k_{1},k_{2}\in\mathbb{Z}_{n}$ such that $z^{k_{1}}=y$ and
            $z^{k_{2}}=x$. But then $y^{k_{2}-k_{1}}=x$, and therefore
            $x\in\innerprod{y}$. Thus, $\innerprod{y}=G_{d}$. But
            $\innerprod{y}$ has $d$ elements, and hence there are at most $d$
            elements of order $d$. Going the other way, suppose that if $d$
            divides $n$ then there are at most $d$ elements of order $d$.
            Since $\monoid{G}$ is finite and Abelian, it is the product of
            finite cyclic groups $\monoid[][+]{\mathbb{Z}_{{p_{k}}^{n_{k}}}}$.
            Suppose two of the primes $p_{k}$ are equal. But then there are at
            least $p_{k}^{2}$ elements of order $p_{k}$, and $p_{k}$ divides the
            order of the group, a contradiction. Thus, all of the primes are
            distinct. By the direct product of coprime cyclic groups is a cyclic
            group. Thus, $\monoid{G}$ is cyclic.
        \end{proof}
        \begin{theorem}
            If $\ring{F}$ is a field, if $\monoid[][\cdot]{F\setminus\{0\}}$ is
            the multiplicative group of $F$, then it is cyclic.
        \end{theorem}
        \begin{proof}
            Since $\ring{F}$ is a field, $\monoid[][\cdot]{F\setminus\{0\}}$ is
            Abelian. Suppose $d\in\mathbb{N}$ divides the cardinality of
            $F\setminus\{0\}$ and let $f\in{F}[x]$ be the polynomial
            $f(x)=x^{d}-1$. Then by the previous theorem there are at most
            $d$ roots. But then there are at most $d$ elements of
            $F\setminus\{0\}$ such that $x^{d}=1$, and thus by the previous
            theorem $\monoid[][\cdot]{F\setminus\{0\}}$ is cyclic.
        \end{proof}
        With this we now return to the claim that there are irreducible
        polynomials in $\mathbb{Q}[x]$ that are reducible if $\mathbb{Z}_{p}[x]$
        for every prime $p\in\mathbb{N}$.
        \begin{theorem}
            If $\monoid{G}$ is a cyclic group, if $a,b\in{G}$ do not have
            square roots, then $a*b$ has a square root.
        \end{theorem}
        \begin{proof}
            For since $\monoid{G}$ is cyclic there is an $x\in{G}$ such that
            $\innerprod{x}=G$. But then if $a,b\in{G}$, there exists
            $n,m\in\mathbb{N}$ such that $x^{n}=a$ and $x^{m}=b$. But $a$ and
            $b$ do not have square roots, and hence $n$ and $m$ are odd. But
            then $a*b=x^{n}*x^{m}=x^{n+m}$, and $n+m$ is even. Hence,
            $x^{n+m}$ has a square root, and thus $a*b$ has a square root.
        \end{proof}
        \begin{example}
            The polynomial $f(x)=x^{4}-10x^{2}+1$ is irreducible in
            $\mathbb{Z}[x]$, yet it is reducible in $\mathbb{F}_{p}[x]$ for
            every prime $p\in\mathbb{N}$. If $p\in\mathbb{N}$ is such that
            2 has a square root in $\mathbb{Z}_{p}$, then we can factor this
            to obtain:
            \begin{equation}
                (x^{2}-2\sqrt{2}x-1)(x^{2}+2\sqrt{2}x-1)
                =x^{4}-10x^{2}-1
            \end{equation}
            And hence $f$ is reducible over all such $\mathbb{Z}_{p}[x]$. If $p$
            is such that 3 has a square root, then:
            \begin{equation}
                (x^{2}-2\sqrt{3}x-1)(x^{2}+2\sqrt{2}x+1)
                =x^{4}-10x^{2}+1
            \end{equation}
            For all other such $p$, neither 2 nor 3 are square roots, and hence
            by the previous theorem their product $2\cdot{3}=6$ does have a
            square root. But then:
            \begin{equation}
                x^{4}-10x^{2}+1=
                    \big(x^{2}-(5+2\sqrt{6})\big)\big(x^{2}-(5-2\sqrt{6})\big)
            \end{equation}
        \end{example}
        There is a stronger result that for every non-prime
        $n\in\mathbb{N}^{+}$ there is a polynomial $f\in\mathbb{Z}[x]$ of degree
        $n$ such that $f$ is irreducible over $\mathbb{Z}[x]$ but reducible
        over $\mathbb{Z}_{p}[x]$ for every prime $p$.
        (See Brandl, R. American Mathematical Monthly, 1986).
        \begin{definition}
            An extension field of a field $\ring[F]{F}$ is a field $\ring[K]{K}$
            such that $\ring[F]{F}$ is a subfield of $\ring[K]{K}$.
        \end{definition}
        Thus, a field extension is to fields as supersets are to sets. Unlike
        set theory where one considers subsets most of the time, most of field
        theory is obsessed with field extensions.
        \begin{theorem}
            If $\ring[F]{F}$ and $\ring[K]{K}$ are fields, and if $K$ is an
            extension field of $F$, then $\ring[K]{K}$ is a vector field
            over $\ring[F]{F}$.
        \end{theorem}
        \begin{definition}
            The degree of a field extension $\ring[K]{K}$ of a given field
            $\ring[F]{F}$ is the dimension of the vector space
            $\ring[K]{K}$ over $\ring[F]{F}$. This is denoted $[K:F]$.
        \end{definition}
        \begin{definition}
            A finite extension of a field $\ring[F]{F}$ is an extension field
            $\ring[K]{K}$ of $F$ such that $[K:F]\in\mathbb{N}$.
        \end{definition}
        \begin{example}
            The field of complex numbers $\mathbb{C}$ is a field extension over
            $\mathbb{R}$. Moreover, it is a finite extension since $\mathbb{C}$
            has the bases $\{1,i\}$. Thus, $[\mathbb{C}:\mathbb{R}]=2$
        \end{example}
        \begin{example}
            The field $\mathbb{R}$ is also a field extension over the rational
            numbers $\mathbb{Q}$. However, unlike $[\mathbb{C}:\mathbb{R}]$,
            which is finite, $[\mathbb{R}:\mathbb{Q}]=\cardinality{\mathbb{R}}$.
            This can be shown since any finite extension of $\mathbb{Q}$ must
            be countable, and any countable extension must have cardinality
            $\cardinality{\mathbb{Q}\times\mathbb{Q}}$, but this is equal to
            $\cardinality{\mathbb{N}}$, and $\mathbb{R}$ is uncountable. Hence,
            at the very least, $[\mathbb{Q}:\mathbb{R}]$ is uncountable, and if
            we assume the continuum hypothesis then the cardinality must then
            be equal to the cardinality of $\mathbb{R}$ (for it is certinaly not
            greater).
        \end{example}
        \begin{example}
            The Gaussian numbers are a subfield of $\mathbb{C}$ defined as
            follows:
            \begin{equation}
                \mathbb{Q}(i)=\{\,a+ib\in\mathbb{C}\;|\;a,b\in\mathbb{Q}\,\}
            \end{equation}
            We can then see that $[\mathbb{Q}:\mathbb{Q}(i)]=2$ since this
            vector field has $\{1,i\}$ as a basis.
        \end{example}
        \begin{example}
            While $[\mathbb{Q}:\mathbb{R}]$ is uncountable, there are countably
            infinite extension fields. Given any field $\ring{F}$, the field of
            rational functions $F(x)$ has the countable basis $x^{n}$ for all
            $n\in\mathbb{N}$. The subspace of polynomials $F[x]$, while not a
            field, is still a vector space over $F$ and has the same basis.
        \end{example}
        \begin{theorem}
            If $\ring[F]{F}$ is a field, if $\ring[K]{K}$ is a finite field
            extension of $F$, and $\ring[L]{L}$ is a finite field extension of
            $K$, then $L$ is a finite field extension of $F$ and:
            \begin{equation}
                [L:F]=[L:K][K:F]
            \end{equation}
        \end{theorem}
        \begin{proof}
            For if $\ring[K]{K}$ is a finite field extension of $\ring[F]{F}$,
            then it is a finite dimensional vector space over $F$ and thus there
            is an $m\in\mathbb{N}$ and a finite sequence
            $a:\mathbb{Z}_{m}\rightarrow{K}$ such that $a[\mathbb{Z}_{m}]$ is a
            basis for $K$ over $F$. And similarly if $\ring[L]{L}$ is a finite
            field extension over $\ring[K]{K}$ then there is an $n\in\mathbb{N}$
            and a finite sequence $b:\mathbb{Z}_{n}\rightarrow{L}$ such that
            $b[\mathbb{Z}_{n}]$ is a basis for $L$ over $K$. Define
            $A:\mathbb{Z}_{m}\times\mathbb{Z}_{n}\rightarrow{L}$ by
            $A(i,j)=a_{i}\cdot{b}_{j}$ for all
            $(i,j)\in\mathbb{Z}_{m}\times\mathbb{Z}_{n}$. Let
            $f:\mathbb{Z}_{m\cdot{n}}\rightarrow%
             \mathbb{Z}_{m}\times\mathbb{Z}_{n}$ be a bijection and define
            $e:\mathbb{Z}_{n\cdot{m}}\rightarrow{L}$ by $e=A\circ{f}$. Suppose
            $e[\mathbb{Z}_{n\cdot{m}}]$ does not span all of $L$ over $F$. Then
            there exists $x\in{L}$ such that for every sequence
            $c:\mathbb{Z}_{n\cdot{m}}\rightarrow{F}$, $\alpha$ is not the
            sum over $c_{i}\cdot{e}_{i}$. But $b[\mathbb{Z}_{n}]$ forms a basis
            of $L$ over $K$, and thus there is a sequence
            $\beta:\mathbb{Z}_{n}\rightarrow{K}$ such that:
            \begin{equation}
                \alpha=\sum_{k\in\mathbb{Z}_{n}}\beta_{k}\cdot_{L}{b}_{k}
            \end{equation}
            But for each $k$ it is true that $\beta_{k}\in{K}$, and since
            $a[\mathbb{Z}_{m}]$ is a basis for $K$ over $F$, there is a sequence
            $\gamma_{k}:\mathbb{Z}_{m}\rightarrow{F}$ such that:
            \begin{equation}
                \beta_{k}=\sum_{i\in\mathbb{Z}_{m}}\gamma_{i}\cdot_{K}a_{i}
            \end{equation}
            Let $c:\mathbb{Z}_{m}\times\mathbb{Z}_{n}\rightarrow{F}$ be defined
            by $c(i,j)=\gamma_{i}$ and let
            $d:\mathbb{Z}_{m\cdot{n}}\rightarrow{F}$ be defined by
            $d=c\circ{f}$. But then:
            \begin{align}
                \alpha&=\sum_{j\in\mathbb{Z}_{n}}\beta_{j}\cdot_{L}b_{j}\\
                &=\sum_{j\in\mathbb{Z}_{n}}\Big(
                    \sum_{i\in\mathbb{Z}_{m}}\gamma_{i}\cdot_{K}a_{i}\Big)
                    \cdot_{L}b_{j}\\
                &=\sum_{j\in\mathbb{Z}_{n}}\sum_{i\in\mathbb{Z}_{m}}
                    \Big(\gamma_{k}\cdot_{k}\big(a_{i}\cdot_{L}b_{j}\big)\Big)\\
                &=\sum_{j\in\mathbb{Z}_{n}}\sum_{i\in\mathbb{Z}_{m}}
                    c(i,j)\cdot_{K}A(i,j)\\
                &=\sum_{k\in\mathbb{Z}_{n\cdot{m}}}
                    \big((c\cdot_{K}A)\circ{f}\big)(k)\\
                &=\sum_{k\in\mathbb{Z}_{n\cdot{m}}}d_{k}\cdot_{K}e_{k}
            \end{align}
            A contradiction. Hence, $e[\mathbb{Z}_{n\cdot{m}}]$ does span
            $L$. Moreover, it is linearly independent. For if
            $d:\mathbb{Z}_{m\cdot{n}}\rightarrow{F}$ is a sequence such that:
            \begin{equation}
                \sum_{k\in\mathbb{Z}_{m\cdot{n}}}d_{k}\cdot_{K}e_{k}=0
            \end{equation}
            The composing with $f^{\minus{1}}$ such that:
            \begin{equation}
                \sum_{j\in\mathbb{Z}_{n}}\sum_{i\in\mathbb{Z}_{n}}
                    d_{ij}a_{i}b_{j}=0
            \end{equation}
            From the linear independence of the $a_{i}$ and the $b_{j}$,
            all of the $d_{ij}$ are zero. Hence, by the basis theorem,
            $[L:K]=n\cdot{m}$.
        \end{proof}
        Given a field $F$ and a monic irreducible polynomial of positive degree
        $f\in{F}[x]$, we can always obtain a field extension for $F$ by
        considering the quotient $F[x]/(f)$, where $(f)$ is the ideal generated
        by $f$.
        \begin{example}
            Consider the field of real numbers $\ring{\mathbb{R}}$ and let
            $f(x)=x^{2}+1$. This is irreducible over $\mathbb{R}$ since it is
            a quadratic with no roots, as one can determine via the quadratic
            formula. If we consider $\mathbb{R}[x]/(x^{2}+1)$, we obtain the
            following arithmetic:
            \begin{equation}
                (a+bx)+(c+dx)=(a+c)+(b+d)x
            \end{equation}
            Multiplication is carried out as follows:
            \begin{equation}
                (a+bx)(c+dx)=ac+(bc+ad)x+bdx^{2}
            \end{equation}
            But in the quotient we have $x^{2}+1=0$, and hence
            $x^{2}=\minus{1}$. Thus, we can simplify this to:
            \begin{equation}
                (a+bx)(c+dx)=(ac-bd)+(ad+bc)x
            \end{equation}
            And this is precisely the multiplicative structure on $\mathbb{C}$.
            Thus the field $\mathbb{R}[x]/(x^{2}+1)$ is isomorphic to the
            complex numbers $\mathbb{C}$ under the mapping
            $\phi(1)=1$ and $\phi(x)=i$.
        \end{example}
        Such fields are called stem fields. That is, stem fields are fields of
        the form $F[x]/(f)$. The intersection of subrings is a subring. The
        subring generated by a subset $S\subseteq{R}$ in a ring $\ring{R}$ is
        the intersection of all subrings containing $S$. Given a ring
        $\ring{R}$ and a subring $\ring{S}$, and given any subset
        $A\subseteq{R}$, the subring generated by $S$ over $A$ is the
        intersection of all subrings of $R$ that contains $A\cup{S}$.
        \begin{example}
            Letting $\mathbb{C}$ and $\mathbb{R}$ have their usual field
            structures, and taking $A\subseteq\mathbb{C}$ to be $A=\{i\}$, the
            subring generated by $\mathbb{R}$ over $A$ is simply the entire
            complex plane $\mathbb{C}$. We can write this as
            $\mathbb{C}=\mathbb{R}[i]$ or
            $\mathbb{C}=\mathbb{R}[\sqrt{\minus{1}}]$
        \end{example}
        The subring generated by a subset is equal to the set of all possible
        linear combintations of elements in the subset. Rigorously, we look at
        all finite sequence $a:\mathbb{Z}_{n}\rightarrow{F}$ and
        $b:\mathbb{Z}_{n}\rightarrow\mathcal{P}(S)$ such that $b_{k}$ is finite
        for all $k\in\mathbb{Z}_{n}$, and we form the sums:
        \begin{equation}
            z=\sum_{k\in\mathbb{Z}_{n}}\Big(
                a_{k}\prod_{\alpha\in{b}_{k}}\alpha
            \Big)
        \end{equation}
        \begin{theorem}
            If $\ring{R}$ is an integral domain, if $\ring[F]{F}$ is a subring
            of $R$ such that $\ring[F]{F}$ is also a field, and if $R$ is a
            finite dimensional vector space over $F$, then $\ring{R}$ is a
            field.
        \end{theorem}
        \begin{proof}
            For if not then there is a non-zero element $a\in{R}$ with no
            inverse element. But the function $f:R\rightarrow{R}$ defined by
            $f(x)=a\cdot{x}$ is injective. For if $f(x)=f(y)$, then:
            \begin{equation}
                a\cdot{x}-a\cdot{y}=a\cdot(x-y)=0
            \end{equation}
            But $\ring{R}$ is an integral domain and thus either $a=0$ or
            $x-y=0$. But by hypothesis $a$ is non-zero, and hence $x-y=0$.
            Thus, $f$ is injective. But it is also linear since:
            \begin{equation}
                f(x+y)=a\cdot(x+y)=a\cdot{x}+a\cdot{y}=f(x)+f(y)
            \end{equation}
            And thus $f$ is a linear map from a finite dimensional vector space
            to itself and is therefore surjective. But then there exists
            $x\in{R}$ such that $f(x)=1$. But then $a\cdot{x}=1$, a
            contradiction. Hence, $\ring{R}$ is a field.
        \end{proof}
        \begin{theorem}
            If $\ring{F}$ is a field, if $\ring{K}$ is a finite extension field,
            and if $\ring{S}$ is a subring of $K$ that contains $F$, then it is
            a field.
        \end{theorem}
        \begin{theorem}
            For such a ring will be an integral domain, and will also be a
            finite dimensional vector space over $F$, and hence will be a field
            by the previous theorem.
        \end{theorem}
        The intersection of subfields is a field. We can similarly define field
        generated by subset. Given the ring generated by $S$, $F[S]$, the field
        generated by $S$ $F(S)$ is also called the field of fractions of $F[S]$.
        This is because it is obtained by considering all fractions of elements
        in $F[S]$. For example, in the polynomial ring $F[x]$, the field that
        this generates is the field of rational functions $F(x)$.
        \begin{example}
            The ring $\mathbb{Q}[\pi]$ is a subset of $\mathbb{R}$ that is all
            linear combinations of powers of $\pi$ with rational coefficients.
            The field generated by this $\mathbb{Q}(\pi)$ is the set of all
            $f(\pi)/g(\pi)$ where $f,g$ are rational polynomials evaluated at
            $\pi$, and $g$ is non-zero.
        \end{example}
        \begin{definition}
            A simple extension of a field $\ring{F}$ is an extension field
            $\ring{K}$ such that there exists $\alpha\in{K}$ such that
            $K=F(\alpha)$.
        \end{definition}
        \begin{definition}
            The composite of two subfields $\ring{F_{1}}$ and $\ring{F_{2}}$
            of a field $\ring{F}$ is the field generated by $F_{1}\cup{F}_{2}$.
        \end{definition}
        \begin{theorem}
            If $\ring{F}$ is a field, if $\ring{F_{1}}$ and $\ring{F_{2}}$ are
            subfields, and if $K$ is the composite of $F_{1}$ and $F_{2}$,
            then $K$ is the field generated by $F_{1}$ over $F_{2}$, and $K$ is
            the field generated by $F_{2}$ over $F_{1}$.
        \end{theorem}
        Given a field $\ring{F}$ and an extension field $\ring{K}$, for any
        element $\alpha\in{E}$ we can define the homomoprhism
        $\phi:F[x]\rightarrow{E}$ be $\phi(f)=f(\alpha)$. If the kernel of this
        is zero, then we say $\alpha$ is transcendental. It then turns out that
        $\phi:F[x]\rightarrow{F}[\alpha]$ is an isomorphism and this extends
        to an isomorphism $\tilde{\phi}:F(x)\rightarrow{F}(\alpha)$. In the
        latter case, where the kernel is non-zero, we call $\alpha$ algebraic.
        \begin{definition}
            An algebraic element of a field extension $\ring{K}$ over a field
            $\ring{F}$ is an element $\alpha\in{K}$ such that there exists a
            polynomial $f\in{F}[x]$ such that $f(\alpha)=0$.
        \end{definition}
        \begin{definition}
            A minimal polynomial of an algebraic element $\alpha$ of a field
            extension $\ring{K}$ over a field $\ring{F}$ is a monic irreducible
            polynomial such that $f(\alpha)=0$.
        \end{definition}
        Minimal polynomials are unique. We can define
        $\phi:F[x]/(f)\rightarrow{F}[\alpha]$ by
        $\phi(\overline{f})=f(\alpha)$. Since $F[x]/(f)$ is a field, $F[\alpha]$
        is as well. Therefore $F[\alpha]=F(\alpha)$, and $F[\alpha]$ is a stem
        field.
        \begin{definition}
            An algebraic extension field of a field $\ring{F}$ is an extension
            field $\ring{K}$ such that for all $\alpha\in{K}$ it is true that
            $\alpha$ is algebraic in $F$.
        \end{definition}
        \begin{example}
            The set of algebraic numbers in $\mathbb{R}$ are an algebraic
            extension over $\mathbb{Q}$. The complex numbers are an algebraic
            extension over $\mathbb{R}$. The real numbers are not an algebraic
            extension over $\mathbb{Q}$ however, since $\pi$ is transcendental.
            Indeed, the set of all algebraic numbers in $\mathbb{R}$ form a
            countable subset, and so most real numbers are transcendental.
        \end{example}
        \begin{theorem}
            If $\ring{F}$ is a field, and if $\ring{K}$ is an extension field,
            then $K$ is a finite extension if and only if it is algebraic and
            finitely generated.
        \end{theorem}
        \begin{ftheorem}{Liouville's Transcendental Theorem}
                        {Liouvilles_Transcendental_Theorem}
            If $a\in\mathbb{N}$, if $a\geq{2}$, and if $s\in\mathbb{R}$ is
            defined by:
            \begin{equation}
                s=\sum_{k\in\mathbb{N}}\frac{1}{a^{n!}}
            \end{equation}
            then $s$ is transcendental.
        \end{ftheorem}
        \begin{bproof}
            For suppose not. Then $s$ is algebraic and thus there is a
            $d\in\mathbb{N}$ and a minimal polyomial $f\in\mathbb{Q}[x]$ of
            degree $d$ such that $f(s)=0$. But then $\mathbb{Q}[s]$ is a
            $d$ dimensional vector space over $\mathbb{Q}$. Let $N\in\mathbb{N}$
            be such that $N\cdot{f}\in\mathbb{Z}[x]$ and let $S_{n}$ be the
            $n^{th}$ partial sums:
            \begin{equation}
                S_{n}=\sum_{k\in\mathbb{Z}_{n}}\frac{1}{a^{k!}}
            \end{equation}
            Thus, $|S_{n}-s|\rightarrow{0}$. If $s$ is rational, then the
            minimal polynomial has degree one and hence $f(x)=x-s$. Otherwise,
            since $f$ is irreducible and of degree greater than one, $f$ has no
            rational roots. Moreover, for all $n\in\mathbb{N}$, $S_{n}\ne{s}$
            and hence $f(S_{n})\ne{0}$. Moreover, by induction
            $S_{n}\in\mathbb{Q}$ for all $n\in\mathbb{N}$, and
            $(a^{n!})^{d}DS_{n}$ is an integer, and therefore:
            \begin{equation}
                |(a^{n!})^{d}DS_{n}|\geq{1}
            \end{equation}
            From the fundamental theorem of algebra, $f$ splits into it's roots
            and so:
            \begin{equation}
                f(x)=\prod_{k\in\mathbb{Z}_{d}}(x-\alpha_{k})
            \end{equation}
            Where the $\alpha_{k}$ are the complex roots of $f$. Let
            $M_{1}=\maximum{|\alpha_{k}|\;:\;k\in\mathbb{Z}_{d}\setminus\{0\}}$.
            That is, $M$ is the largest modulus of all the roots, neglecting the
            zeroth term. Let $M=\maximum{M_{1},1}$. Then:
            \begin{equation}
                |f(S_{n})|=\prod_{k\in\mathbb{Z}_{d}}|S_{n}-\alpha_{k}|
                    \leq|S_{n}-\alpha_{0}|(S_{n}+M)^{d-1}
            \end{equation}
            But we can simplify this further, since:
            \begin{equation}
                |S_{n}-\alpha_{1}|=\sum_{k=n+1}^{\infty}\frac{1}{a^{k!}}
                \leq\frac{1}{a^{(k+1)}!}\sum_{k\in\mathbb{N}}\frac{1}{a^{k}}
                =\frac{a}{a-1}\frac{1}{a^{(n+1)!}}
            \end{equation}
            Piecing this together, we obtain:
            \begin{equation}
                |f(S_{n})|\leq\frac{2}{2^{(n+1)!}}(S_{n}+M)^{d-1}
            \end{equation}
            And this convergences to zero. Therefore:
            \begin{equation}
                |(a^{n!})^{d}DS_{n}|\leq\frac{a}{a-1}
                    \frac{a^{d\cdot{n!}}}{a^{(n+1)!}}(S_{n}+M)^{d-1}
            \end{equation}
            Which thus convergences to zero, contradicting that this is always
            greater than one.
        \end{bproof}
        \begin{definition}
            A splitting polynomial in a field $\ring{F}$ is a polynomial
            $f\in{F}[x]$ of degree $n\in\mathbb{N}$ such that there exists
            finite sequences $a,b:\mathbb{Z}_{n}\rightarrow{F}$ such that:
            \begin{equation}
                f(x)=\prod_{k\in\mathbb{Z}_{n}}(a_{k}x-b_{k})
            \end{equation}
        \end{definition}
        \begin{theorem}
            If $\ring{F}$ is a field, then every non-constant polynomial
            $f\in{F}[x]$ is a splitting polynomial if and only if every
            non-constant polynomial has at least one root in $F$.
        \end{theorem}
        \begin{proof}
            If every non-constant polynomial $f\in{F}[x]$ splits, then given
            such an $f$ of degree $n\in\mathbb{N}$ there are sequences
            $a,b:\mathbb{Z}_{n}\rightarrow{F}$ such that:
            \begin{equation}
                f(x)=\prod_{k\in\mathbb{Z}_{n}}(a_{k}x-b_{k})
            \end{equation}
            But then $b^{k}/a_{k}$ is a root for all $k$, and hence there is at
            least one root. Going the other way, let $f\in{F}[x]$ be a
            non-constant polynomial. Then there is a root $\alpha$ and hence
            $f(x)=(x-\alpha)g(x)$. Then either $g$ is a constant or a
            non-constant polynomial. In the latter case it has a root $\beta$
            and so $f(x)=(x-\alpha)g(x)=(x-\alpha)(x-\beta)h(x)$. Continuing
            inductively we find that $f$ is a splitting polynomial.
        \end{proof}
        \begin{theorem}
            If $\ring{F}$ is a field, then every non-constant polynomial
            $f\in{F}[x]$ has at least one root in $F$ if and only if every
            irreducible polynomial in $F[x]$ has degree 1.
        \end{theorem}
        \begin{proof}
            For if $f\in{F}[x]$ is a non-constant polynomial, then either
            the degree of $f$ is 1 or it is greater than 1. But if the degree
            of $f$ s 1, then $f(x)=ax+b$ and thus $f$ has a root. If the degree
            of $f$ is greater than 1, then it is reducible and hence there
            are polynomials $g,h\in{F}[x]$ of positive degree such that
            $f=gh$. Continuing inductively we eventually factor $f$ down to the
            product of degree 1 polynomials, and thus $f$ has a root. Going the
            other way, if $f\in{F}[x]$ is non-constant and irreducible then it
            has a root, and thus $f(x)=ax+b$. Thus, the only irreducible
            polynomials have degree 1.
        \end{proof}
        \begin{theorem}
            If $\ring{F}$ is a field, then every irreducible polynomial
            $f\in{F}[x]$ has degree 1 if and only if for every finite field
            extension $\ring{K}$ over $F$, $K=F$.
        \end{theorem}
        \begin{proof}
            For if $\ring{K}$ is a finite field extension over $F$, then the
            minimal polynomial $f\in{F}[x]$ for any element $\alpha\in{K}$ has
            degree 1 and hence $f(x)=x-\alpha$. But then $\alpha\in{F}$, and
            thus $F=K$. In the reverse direction, if $f\in{F}[x]$ is an
            irreducible polynomial, then $F[x]/(f)$ is a finite extension field
            of $F$. But by hypothesis, $F[x]/(f)=F$, and since the degree of
            $f$ is equal to $[F[x]/(f):F]=1$, $f$ is a degree 1 polynomial.
        \end{proof}
        \begin{definition}
            An algebraically closed field is a field $\ring{F}$ such that for
            all non-constant polynomials $f\in{F}[x]$, there exists a root
            $\alpha\in{F}$ of $f$.
        \end{definition}
        \begin{definition}
            An algebraic closure of a field $\ring{F}$ is an extension field
            $\ring{K}$ of $F$ such that $K$ is algebraically closed.
        \end{definition}
        \begin{example}
            By the fundamental theorem of algebra, $\mathbb{C}$ is algebraically
            closed. It is therefore an algebraic closure of $\mathbb{R}$. To
            note that $\mathbb{R}$ is not algebraically closed one need only
            consider the polynomial $f(x)=x^{2}+1$.
        \end{example}
        \begin{theorem}
            If $\ring{F}$ is a field, if $\ring{K}$ is an algebraic extension
            field of $F$, and if for every polynomial $f\in{F}[x]$ it is true
            that $f$ is a splitting polynomial in $K[x]$, then $\ring{K}$ is
            algebraically closued.
        \end{theorem}
        \begin{proof}
            For if $f\in{K}[x]$ is a non-constant polynomial then there is a
            finite extension field $\ring{L}$ of $K$ such that $f\in{L}[x]$ has
            a root $\alpha\in{L}$. But then by the tower law, $L$ is a finite
            extension field over $F$. Thus $\alpha$ is algebraic over $F$ and
            so there is a polynomial $g\in{F}[x]$ such that $g(\alpha)=0$. But
            by hypothesis, $g$ splits in $K$ and so the roots of $g$ lie in
            $K$. Thus, $\alpha\in{K}$. Hence, $K$ is algebraically closed.
        \end{proof}
        \begin{theorem}
            If $\ring{K}$ is an extension field of a field $\ring{F}$ and if
            $\mathbb{A}_{F}$ is the set:
            \begin{equation}
                \mathbb{A}_{F}=\{\,\alpha\in\Omega\;|\;
                    \alpha\textrm{ is algebraic over }F\}
            \end{equation}
            Then $\ring{\mathbb{A}_{F}}$ is a field.
        \end{theorem}
        \begin{proof}
            For if $\alpha,\beta\in{K}$ are algebraic over $F$, then
            $F[\alpha,\beta]$ is a field of finite degree over $F$. Thus every
            element of $F[\alpha,\beta]$ is algebraic over $F$, and hence
            $\alpha+\beta$, $\alpha-\beta$, $\alpha\cdot\beta$, and
            $\alpha/\beta$ are all algebraic. Therefore, $\mathbb{A}_{F}$ is a
            field.
        \end{proof}
        \begin{definition}
            The algebraic closure of a field $\ring{F}$ with respect to an
            extension field $\ring{K}$ is the subfield $\ring{\mathbb{A}_{F}}$
            defined by:
            \begin{equation}
                \mathbb{A}_{F}=\{\,\alpha\in\Omega\;|\;
                \alpha\textrm{ is algebraic over }F\}
            \end{equation}
        \end{definition}
        By the previous theorem, the algebraic of a field $\ring{F}$ with
        respect to any field extension $\ring{K}$ is a subfield, and hence this
        is well defined.
        \begin{theorem}
            If $\ring{F}$ is a field, if $\ring{K}$ is an algebraically closed
            field extension of $F$, and if $\mathbb{A}_{F}$ is the algebraic
            closure of $F$ with respect to $K$, then $\mathbb{A}_{F}$ is an
            algebraic closure of $F$.
        \end{theorem}
        \begin{proof}
            Since $\mathbb{A}_{F}$ is algebraic over $F$, and since every
            polynomial $f\in{F}[x]$ splits in $\mathbb{A}_{F}[x]$, we thus have
            that, since $K$ is algebraically closed, the $f$ has a root in
            $\mathbb{A}_{F}$. Hence, $\mathbb{A}_{F}$ is an algebraic closure
            of $F$.
        \end{proof}
        Combining this with the fundamental theorem of algebra we see that
        every subfield of $\mathbb{C}$ has an algebraic closure.
        \begin{example}
            Let $\mathbb{Q}$ denote the standard field of rational numbers, and
            let $\mathbb{Q}[\sqrt{2},\sqrt{3}]$ be the field extension obtained
            by appending $\sqrt{2}$ and $\sqrt{3}$. The degree of
            $[\mathbb{Q}[\sqrt{2},\sqrt{3}]:\mathbb{Q}]$ is four, and to prove
            this we use the tower law. Firstly, note that
            $[\mathbb{Q}[\sqrt{2}]:\mathbb{Q}]=2$ for $\{1,\sqrt{2}\}$ form a
            linear independent basis of $\mathbb{Q}[\sqrt{2}]$ over
            $\mathbb{Q}$. Next,
            $[\mathbb{Q}[\sqrt{2},\sqrt{3}]:\mathbb{Q}[\sqrt{2}]]=2$. For
            $\{1,\sqrt{3}\}$ certainly forms a basis, but moreover it is
            linearly independent. For suppose not and suppose we have:
            \begin{equation}
                a+b\sqrt{3}=0\quad\quad
                a,b\in\mathbb{Q}[\sqrt{2}]
            \end{equation}
            Then we have that $\sqrt{3}=\minus{a}/b$ with
            $a,b\in\mathbb{Q}[\sqrt{2}]$. With this we may write:
            \begin{equation}
                \sqrt{3}=\minus\frac{a_{1}+a_{2}\sqrt{2}}{b_{1}+b_{2}\sqrt{2}}
            \end{equation}
            Squaring both sides yields:
            \begin{equation}
                a_{1}^{2}+2a_{1}a_{2}\sqrt{2}+2a_{2}^{2}=
                3b_{1}^{2}+6b_{1}b_{2}\sqrt{2}+6b_{2}^{2})
            \end{equation}
            If we collect the $\sqrt{2}$ terms, we obtain:
            \begin{equation}
                \sqrt{2}(2a_{1}a_{2}-6b_{1}b_{2})=
                3b_{1}^{2}-a_{1}^{2}+6b_{2}^{2}-2a_{2}^{2}
            \end{equation}
            Now if $2a_{1}a_{2}-6b_{1}b_{2}\ne{0}$, then we may divide through
            by this showing that $\sqrt{2}$ is a rational number, which is a
            contradiction. Thus, $2a_{1}a_{2}-6b_{1}b_{2}=0$ and hence
            $a_{1}a_{2}=3b_{1}b_{2}$. But then:
            \begin{align}
                a_{1}+a_{2}\sqrt{2}+b_{1}\sqrt{3}+b_{2}\sqrt{6}&=0\\
                \Rightarrow
                a_{1}^{2}+3b_{1}b_{2}\sqrt{2}
                    +a_{1}b_{1}\sqrt{3}+a_{1}b_{2}\sqrt{6}&=0\\
                \Rightarrow
            \end{align}
        \end{example}
    \section{Chapter 2 (Milne)}
        \begin{definition}
            An $F$ homomoprhism from an extension field $\ring{E}$ over a field
            $\ring{F}$ to an extension field $\ring{E'}$  over $F$ is a field
            homomoprhism $\phi:E\rightarrow{E}'$ such that
            $\phi|_{F}=\identity{F}$.
        \end{definition}
        \begin{theorem}
            If $\ring{F}$ is a field, if $\ring{E}$ is a simply field extension
            of $F$, if $\ring{K}$ is a field extension of $F$, and if
            $\varphi:E\rightarrow{K}$ is an $F$ homomoprhism, if $\alpha\in{E}$
            is such that $E=F(\alpha)$, if $\alpha$ is transcendental over $F$,
            then $\varphi(\alpha)$ is transcendental over $F$ and the function
            $f:\homomorphisms{E}{K}\rightarrow{E}\setminus\mathbb{A}_{F}$
            defined by $f(\varphi)=\varphi(\alpha)$ is a bijection.
        \end{theorem}
\end{document}