\documentclass[crop=false,class=article,oneside]{standalone}
%----------------------------Preamble-------------------------------%
\input{../../../../preamble.tex}
%--------------------------Main Document----------------------------%
\begin{document}
    \ifx\ifmathcoursessurgery\undefined
        \section*{Surgery Theory}
        \setcounter{section}{1}
        \renewcommand\thesubfigure{%
            \arabic{section}.\arabic{figure}.\arabic{subfigure}%
        }
    \fi
    \subsection{Lecture 5: The Wall L-Groups}
        The Wall L-Groups are defined on all commutative rings.
        In fact, there is a functor $L_{n}$ which takes
        commutative rings to groups. Some facts about this:
        \begin{enumerate}
            \item L-Groups are $4$ periodic.
                  For all commutative rings $R$, we have
                  $L_{n}(R)\simeq L_{n+4}(R)$.
                  This is hard to prove.
            \item Surgery theory requires for
                  $R=\mathbb{Z}G$, where $G$ is the
                  fundamental group of the manifold in
                  question, and $\mathbb{Z}G$ is all
                  finite linear combinations of the elements
                  in $G$.
            \item There is a whole theory of computing
                  $L_{n}(R)$ when $R$ is a field,
                  usually denoted $\mathbb{F}$.
            \item Potentially true statement: L-groups
                  only have 2 or 4 torsion, if they have
                  torsion at all. This is hard to prove,
                  as well.
            \item For $G$ equal to the trivial group,
                  $L_{n}(\mathbb{Z}[e])$ we have
                  $L_{n}(\mathbb{Z}[e])%
                   =\begin{cases}%
                        \mathbb{Z},&n\cong{0}(4)\\%
                        0,&n\cong{1}(4)\\%
                        \mathbb{Z}_{2},&n\cong{2}(4)\\%
                        0,&n\cong{3}(4)%
                    \end{cases}$
        \end{enumerate}
        Suppose $\mathcal{M}^{n}$ is a closed
        manifold and $n\geq 5$, and $\pi_{1}(M)=e$.
        Suppose $n=5$. Then:
        \begin{align*}
            L_{6}(\mathbb{Z}[e])
            &\rightarrow[\mathcal{M},G/Cat]
            \rightarrow{S^{Cat}}(\mathcal{M})
            \rightarrow{L_{5}}(\mathbb{Z}[e]\\
            \mathbb{Z}_{2}&\rightarrow
            [\mathcal{M},G/Cat]
            \overset{f}{\rightarrow}S^{Cat}(\mathcal{M})
            \rightarrow{0}
        \end{align*}
        If $n=6$, we have:
        \begin{align*}
            L_{7}(\mathbb{Z}[e])
            &\rightarrow[M,G/Cat]\rightarrow
            S^{cat}(\mathcal{M})\rightarrow L_{6}(\mathbb{Z}[e])\\
            0&\rightarrow [M,G/Cat]
            \overset{g}{\rightarrow}S^{Cat}(\mathcal{M})
            \overset{?}{\rightarrow}\mathbb{Z}_{2}
        \end{align*}
        In the case of $n=4$, there are these
        things called 'Good' groups in which some
        of these results still hold. The
        dimensions can be broken up like this:
        \begin{itemize}
            \item $2$ Completely solved.
            \item $3$ This is Knot Theory.
            \item $4$ Very hard.
            \item $\geq 5$ Surgery Theory.
        \end{itemize}
        How do you classify manifolds?
        \begin{itemize}
            \item In two dimensions the genus
                  (number of wholes) and the
                  orientation (Euler characteristic)
                  gives you everything.
            \item In three dimensions, Thurnston and
                  Perelman did the classification of this.
            \item Four is a big vacuum of unsolved
                  stuff. 'Good' groups come up here.
            \item For every group $G$ there is a
                  manifold $\mathcal{M}$ of dimensions
                  $5$ or greater such that
                  $\pi_{1}(\mathcal{M})=G$
        \end{itemize}
        Let's study $L_{n}(\mathbb{Z}[e])$.
        This is surprisingly hard enough to study.
        The computation of this was known by Brouder,
        but the use of the surgery exact sequences
        wasn't done until Wall (Hence, Wall groups).
        \subsubsection{The Witt Group}
            $L_{0}(\mathbb{Z}[e])$ is equal to something
            called the Witt group $Witt(\mathbb{Z})$.
            First let's talk about the Witt group of fields.
            The Witt group of a field $\mathbb{F}$ is
            the set of symmetric bilinear forms
            $B:V\times{V}\rightarrow\mathbb{F}$
            of finite dimensional vector spaces
            $V$ over $\mathbb{F}$, modulo some
            equivalence relation. So $B$ can be
            represented by some symmetric matrix
            in $M_{n}(\mathbb{F})$ with respect to
            some basis $\{\beta\}$. So if
            $B:V\times{V}\rightarrow\mathbb{F}$
            has matrix $A_{\beta}$ and if
            $D:V\times{V}\rightarrow\mathbb{F}$
            has matrix $A'_{\delta}$,
            then construct the matrix:
            \begin{equation*}
                \tilde{A}=
                \begin{pmatrix}
                    A&0\\
                    0&A'
                \end{pmatrix}_{\beta,\delta}
            \end{equation*}
            Then one can get a Bilinear form
            $B\perp{D}:V\oplus{V}\rightarrow{V}\oplus{V}$
            using this matrix. This is called the
            orthogonal sum. The equivalence relation
            on these Bilinear forms is a bit complicated.
            Consider the matrix:
            \begin{equation*}
                \begin{bmatrix}
                    x&y
                \end{bmatrix}
                \begin{bmatrix}
                    1&0\\
                    0&-1
                \end{bmatrix}
                \begin{bmatrix}
                    x&y
                \end{bmatrix}
                =x^{2}-y^{2}
            \end{equation*}
            This is called a Hyperbolic form $H_{2}(\mathbb{F})$
            \begin{enumerate}
                \item Two forms 
                      $B_{1}:V\times V\rightarrow \mathbb{F}$
                      and $B_{2}:W\times W\rightarrow \mathbb{F}$,
                      with $\dim(V)=\dim(W)$.
                      If $A^{T}[B_{1}]A=[B_{2}]$,
                      then $B_{1}\sim B_{2}$.
                \item We can also write
                      $B_{1}\sim B_{2}$ is
                      $B_{1}%
                       =B_{2}\underset{k}{\perp}H_{2}(\mathbb{F})$.
                      So $H_{2}(\mathbb{F})$ is the $0$
                      element in $Witt(\mathbb{F})$.
                      Note that, since $H_{2}(\mathbb{F})$
                      has dimension $2$,
                      $\dim(B_{1})=\dim(B_{2})\mod{2}$.
                \item What is the inverse of $B_{1}$?
                      It is a form $B_{2}$ for which
                      $B_{1}\perp B_{2}\simeq H_{2}(\mathbb{F})$
            \end{enumerate}
            There is a map, called the signature map,
            of a matrix
            $W(\mathbb{F})\rightarrow%
             L_{0}(\mathbb{Z}[e])\simeq \mathbb{Z}$.
            It is defined for matrices with real eigenvalues.
            It is the number of positive eigenvalues minus
            the number of negative eignvalues.
\end{document}