\documentclass[crop=false,class=article,oneside]{standalone}
%----------------------------Preamble-------------------------------%
\input{../../../../preamble.tex}
%--------------------------Main Document----------------------------%
\begin{document}
    \ifx\iffunct\undefined
        \section*{Functional Analysis}
        \setcounter{section}{1}
        \setcounter{subsection}{1}
    \fi
\subsection{Lecture 2: September 17, 2018}
    \subsubsection{More on Continuity}
        A function $f$ is continuous at a point $x$ if
        for all $\varepsilon>0$ there exists a $\delta>0$
        such that for all $x_{0}$ such that
        $|x-x_{0}|<\delta$, we have that
        $|f(x)-f(x_{0})|<\varepsilon$. This defines
        continuity at a point. Continuity on a set
        $S$ simply means that $f$ is continuous
        at every point on the set. Uniform continuity,
        however, is a set property. You don't have
        uniform continuity at a point, you have this
        on a set. A function $f$ is uniformly continuous
        if for all $\varepsilon>0$ there is a $\delta>0$
        such that for all $x$ and $x_{0}$ such that
        $|x-x_{0}|<\delta$, it is true that
        $|f(x)-f(x_{0})|<\varepsilon$. Note that in
        the definition of continuity, the point $x$
        is the first thing that is mentioned, whereas in
        uniform continuity we really don't care about it
        until the end of the definition.
        \begin{theorem}
            If $x_{n}$ and $y_{n}$ are sequences such
            in a set $S$ such that $x_{n}-y_{n}\rightarrow{0}$,
            and if $f:{S}\rightarrow\mathbb{R}$, then
            $f$ is uniformly continuous if and only if
            $f(x_{n})-f(y_{n})\rightarrow{0}$
        \end{theorem}
        \begin{theorem}
            If $f:[a,b]\rightarrow\mathbb{R}$ is continuous,
            then $f$ is uniformly continuous.
        \end{theorem}
        \begin{proof}
            Let $x_{n}$, $y_{n}\in[a,b]$ be sequences such
            that $x_{n}-y_{n}\rightarrow{0}$. By the
            Bolzano-Weierstrass theorem there is a
            convergent subsequence $x_{k_{n}}$. Let $x$
            be the limit. But
            $y_{k_{n}}=x_{k_{n}}-(y_{k_{n}}-x_{k_{n}})$,
            and therefore $y_{k_{n}}\rightarrow{x}$.
            Let $X_{n}=x_{k_{n}}$, and $Y_{n}=y_{k_{n}}$.
            Then
            $f(X_{n})-f(Y_{n})%
             =(f(X_{n})-f(x))-(f(Y_{n}-f(x))$.
            But from continuity, $f(x_{n})\rightarrow{f(x)}$
            and $f(y_{n})\rightarrow{f(x)}$. Therefore, $f$
            is uniformly continuous.
        \end{proof}
        A few notes on pointwise convergence, recapping
        from last week. We say that $f_{n}\rightarrow{f}$
        point-wise on a set $S$ if for all $x\in{S}$,
        $f_{n}(x)-f(x)\rightarrow{0}$. We say that
        $f_{n}\rightarrow{f}$ uniformly on $S$ if
        $\underset{x\in{S}}{\sup}%
         |f_{n}(x)-f(x)|\rightarrow{0}$.
        \begin{example}
            Let $f_{n}(x)=nxe^{-nx}$ on $[0,1]$.
            Then for $x\in[0,1]$, $f_{n}(x)\rightarrow{0}$
            and therefore $f_{n}(x)\rightarrow{0}$ poinwise
            on $[0,1]$. Note that
            $f_{n}'(x)=(n-n^{2}x)e^{-nx}$. This has a
            zero at $x=\frac{1}{n}$, so we see that
            $f_{n}(x)$ has a maximum
            which evaluates to $e^{-1}$. But
            $\sup|f_{n}(x)-f(x)|=\sup|f_{n}(x)|=e^{-1}$.
            So $f_{n}(x)$ does not
            \textit{uniformly} converge to $0$. The
            convergence is only \textit{pointwise}.
        \end{example}
        \begin{theorem}[Weierstrass Approximation Theorem]
            If $f:[a,b]\rightarrow\mathbb{R}$ is continuous,
            then there is a sequence of polynomials
            $f_{n}$ such that $f_{n}\rightarrow{f}$
            uniformly on $[a,b]$.
        \end{theorem}
        \begin{proof}
            We'll assume, for now, that $[a,b]=[0,1]$
            and that $f(0)=f(1)=0$. Extend $f$ to be
            zero outside of $[0,1]$. Let
            $Q_{n}(x)=c_{n}(1-x^{2})^{n}$ on $[-1,1]$,
            and choose $c_{n}$ such that
            $\int_{-1}^{1}Q_{n}(x)dx=1$. So we have:
            \begin{align*}
                c_{n}\int_{-1}^{1}(1-x^{2})^{n}dx
                &=2c_{n}\int_{0}^{1}(1-x^{2})^{n}dx
                &
                &\geq{2c_{n}}\int_{0}^{1}(1-x)^{n}dx\\
                &=2c_{n}\int_{0}^{1}(1-x)^{n}(1+x)^{n}dx
                &
                &=\frac{2}{n+1}c_{n}
            \end{align*}
        From this we have that $c_{n}\leq{n+1}$. Let
        $f_{n}(x)=\int_{0}^{1}f(t)Q_{n}(x-t)dx$.
        Then $f_{n}(x)$ is a polynomial. Note that
        $f(t)Q_{n}(x-t)$ is roughly zero when $t$ differs
        from $x$ and $n$ is large enough. So we have:
        \begin{equation*}
            f_{n}(x)=\int_{0}^{1}f(t)Q_{n}(x-t)dt
            \approx{f(x)}\int_{0}^{1}Q_{n}(x-t)dt=f(x)
        \end{equation*}
        The remainder of the proof is to quantify this.
        Since $f$ is zero outside of $[0,1]$, if
        we let $s=t-x$, then:
        \begin{align*}
            f_{n}(x)&=\int_{-x}^{1-x}f(s+x)Q_{n}(s)ds
            =\int_{-1}^{1}f(s+x)Q_{n}(s)ds\\
            \Rightarrow|f_{n}(x)-f(x)|
            &=\bigg|\int_{-1}^{1}f(x+t)Q_{n}(t)dt
            -\int_{-1}^{1}f(x)Q_{n}(t)dt\bigg|\\
            \Rightarrow|f_{n}(x)-f(x)|
            &\leq\int_{-1}^{1}|f(x+t)-f(x)|Q_{n}(t)dt
        \end{align*}
        This comes for the fact that$\int_{-1}^{1}Q_{n}(t)=1$
        and from the integral version of the triangle
        inequaility.
        Suppose $\varepsilon>0$. Since $f$ is continuous
        on $[0,1]$, it is uniformly continuous. But
        if $f$ is uniformly continuous then there exists
        a $\delta>0$ such that
        $|f(x+t)-f(x)|<\frac{\varepsilon}{2}$ for all
        $t<\delta$. So we have:
        \begin{equation*}
            |f_{n}(x)-f(x)|\leq
            \int_{-1}^{-\delta}|f(x+t)-f(x)|Q_{n}(t)dt
            +\int_{-\delta}^{\delta}|f(x+t)-f(x)|Q_{n}(t)dt
            +\int_{\delta}^{1}|f(x+t)-f(x)|Q_{n}(t)dt
        \end{equation*}
        But $f$ is continuous on a closed and bounded
        set and therefore $f$ is bounded. Let $M$ be
        such a bound. Then $|(f(x+t)-f(x)|\leq{2M}$.
        We have:
        \begin{equation*}
            |f_{n}(x)-f(x)|\leq
            2M\int_{-1}^{-\delta}Q_{n}(t)dt
            +\frac{\varepsilon}{2}
            \int_{-\delta}^{\delta}Q_{n}(t)dt
            +2M\int_{\delta}^{1}Q_{n}(t)dt
        \end{equation*}
        But for all $t\in[-1,-\delta]$,
        $Q_{n}(t)\leq{Q_{n}(-\delta)}$. Similarly for
        $t$ in $[\delta,1]$. Since $Q_{n}(t)$
        is an even function:
        \begin{equation*}
            |f_{n}(x)-f(x)|\leq
            4MQ_{n}(\delta)+
            \frac{\varepsilon}{2}\int_{-1}^{1}Q_{n}(t)dt
            =4MQ_{n}(\delta)+\frac{\varepsilon}{2}
        \end{equation*}
        But since $\delta>0$, $Q_{n}(\delta)\rightarrow0$.
        Therefore, there is an $N\in\mathbb{N}$ such that
        for all $n>N$,
        $|Q_{n}(\delta)|<\frac{\varepsilon}{8M}$.
        But then $4MQ_{n}(\delta)<\frac{\varepsilon}{2}$.
        Therefore, etc.
    \end{proof}
        Another way to put this is that if $f$ is continuous
        on $[a,b]$ and if $\varepsilon>0$, then there is
        a polynomial $P$ such that for all $x\in[0,1]$,
        $|f(x)-P(x)|<\varepsilon$. There is a generalization
        of this. The set of functions need not be
        polynomials. The set needs to be closed
        under addition, multiplication, and scalar
        multiplication, it must separate points,
        and must not take every point to zero.
        This is the Stone-Weierstrass theorem.
    \subsubsection{Functional Analysis}
        Functional analysis is concerned with normed spaces.
        This is a vector space $V$ with a function, called
        a norm, from $V$ to $[0,\infty)$. This is usually
        written $\norm{\mathbf{x}}$ for an element
        $\mathbf{x}\in{V}$. This norm must satisfy the
        folllowing for all $\mathbf{x}$, $\mathbf{y}\in{V}$:
        \begin{enumerate}
            \item $\norm{\mathbf{x}}=0$ if and only
                  if $\mathbf{x}=\mathbf{0}$
                  \hfill[Definiteness]
            \item $\norm{c\mathbf{x}}=|c|\norm{\mathbf{x}}$
                  for all $c\in\mathbb{R}$.
                  \hfill[Positiveness]
            \item $\norm{\mathbf{x}+\mathbf{y}}%
                   \leq\norm{\mathbf{x}}+\norm{\mathbf{y}}$
                  \hfill[Triangle Inequality]
        \end{enumerate}
        \begin{example}
            The following are normed spaces:
            \begin{enumerate}
                \begin{multicols}{2}
                    \item $\mathbb{R}$ with $\norm{x}=|x|$
                    \item $\mathbb{R}^{n}$ with
                          $\norm{\mathbf{x}}%
                           =\sqrt{\sum_{k=1}^{n}x_{k}^{2}}$
                    \item $\mathbb{R}^{n}$ with
                          $\norm{\mathbf{x}}%
                           =(\sum_{k=1}^{n}x_{k}^{p})^{1/p}$
                    \item $\ell^{p}$: sequences $x_{n}$
                          such that
                          $\sum_{k=1}^{\infty}|x_{n}|^P%
                           <\infty$.
                    \item $\mathbb{R}^{n}$ with
                          $\norm{\mathbf{x}}%
                           =\max\{x_{1},\hdots,x_{n}\}$
                    \item $\ell^{\infty}$: Bounded sequences
                          with $\norm{v}=\sup\{v_{n}\}$
                \end{multicols}
            \end{enumerate}
        \end{example}
        From the fact that $\ell^{\infty}$ is a normed space
        we have that the set of convergent sequences,
        again with the $\norm{}_{\infty}$ norm, is also
        a normed space. The set of null sequences, which
        is the set of sequences that converge to zero,
        is also a normed space. A stranger normed space
        is the set of all bounded continuous functions
        $f:S\rightarrow\infty$ with norm
        $\norm{f}=\sup\{|f(x)|\}$. Furthermore, the
        set of all integrable functions with
        bounded integrals, with norm
        $(\int_{S}|f|^{p})^{1/p}$. If you allow integral
        to mean Lebesgue Integrable, then this becomes
        a special space denoted $L^{p}(S)$. As a final
        example, the set of functions
        $f:[a,b]\rightarrow\mathbb{R}$ such that
        $(\int_{a}^{b}\sum_{k=0}^{n}|f^{(k)}|^{p})^{(1/p)}$
        exists, denoted $W^{n,p}([a,b])$ is called
        the Sobolev space.
    \subsubsection{Metric Spaces}
        A lot of the things we wish to
        prove don't rely on the fact that all of these
        spaces are vector spaces. Really, we only care about
        the properties that the norm on the space has.
        What matters is that there's a set and a notion
        of distance on the set. This abstraction is the
        fundamental concept of a metric space.
        \begin{definition}
            A metric space is a set $S$ and a function
            $d:{X}\times{X}\rightarrow[0,\infty)$ such that:
            \begin{enumerate}
                \item For all $x$, $y\in{X}$, $d(x,y)=0$
                      if and only if $x=y$.
                      \hfill[Definitenes]
                \item For all $x$, $y\in{X}$,
                      $d(x,y)=d(y,x)$
                      \hfill[Symmetry]
                \item For all $x$, $y\in{X}$,
                      $d(x,z)\leq{d(x,y)+d(y,z)}$
                      \hfill[Triangile Inequality]
            \end{enumerate}
        \end{definition}
        \begin{theorem}
            If $(V,\norm{})$ is a vector space,
            and if $d:{V}\times{V}\rightarrow[0,\infty)$
            is defined by
            $d(\mathbf{x},\mathbf{y})%
             =\norm{\mathbf{x}-\mathbf{y}}$,
            then $(V,d)$ is a metric space.
        \end{theorem}
        \begin{proof}
            In order:
            \begin{enumerate}
                \item If $\norm{\mathbf{x}-\mathbf{y}}=0$,
                      then $\mathbf{x}=\mathbf{y}$.
                      Similarly,
                      $\norm{\mathbf{x}-\mathbf{x}}%
                       =\norm{\mathbf{0}}=0$.
                \item $d(\mathbf{x},\mathbf{y})%
                       =\norm{\mathbf{x}-\mathbf{y}}%
                       =\norm{(-1)(\mathbf{y}-\mathbf{x})}%
                       =|-1|\norm{\mathbf{y}-\mathbf{x}}%
                       =\norm{\mathbf{y}-\mathbf{y}}%
                       =d(y,x)$
                \item The triangle inequality follows
                      from the triangle inequality that
                      norms have.
            \end{enumerate}
        \end{proof}
        There are metric spaces that have nothing to do
        with vector spaces or norms. Metric spaces are
        a more abstract object. Every normed space
        has an associated metric space since there
        is the ``induced'' metric.
        \begin{example}
            Let $X$ be a set and let
            $d(x,y)=\begin{cases}%
                        0,&x=y\\%
                        1,&{x}\ne{y}%
                    \end{cases}$
            This is the discrete metric on $X$.
        \end{example}
        \begin{example}
            Let $X=\{a,b,c\}$, and
            $d(a,b)=1$, $d(b,c)=2$. What value
            must $d(a,c)$ have if $d$ is a metric on $X$?
            We need $d(a,c)\leq{d(a,b)+d(b,c)}=1+2=3$.
            Also $d(a,b)\leq{d(a,c)+d(c,b)}=d(a,c)+2$, and
            therefore $-1\leq{d(a,c)}$. Finally, we need
            $d(b,c)\leq{d(b,a)+d(a,c)}=1+d(a,c)$. Together
            we have $d(a,c)\leq{3}$ and $1\leq{d(a,c)}$. So
            Pick $d(a,c)=2$.
            This makes $(X,d)$ a metric space.
        \end{example}
        \begin{example}
            Let $X=\mathbb{R}$ and $d(x,y)=|x-y|$.
            Then $(X,d)$ is a metric space.
        \end{example}
        \begin{example}
            $\mathbb{R}$ with
            $d(x,y)=|f(x)-f(y)|$, where
            $f$ is injective, is a metric space.
        \end{example}
        \begin{example}
            $\mathbb{R}$ with
            $d(x,y)=|\tan^{-1}(x)-\tan^{-1}(y)|$ is a
            metric. Moreover, $d(x,y)<\pi$ for all
            $x,y\in\mathbb{R}$. Thus, we have found
            a metric that makes $\mathbb{R}$ a bounded
            set. As a fun fact, $x_{n}=n$ is a Cauchy
            sequence in this metric space, but
            this sequence does not converge to anything.
            Thus we've found a metric on
            $\mathbb{R}$ such that
            $(\mathbb{R},d)$ is not complete.
        \end{example}
    \subsubsection{Topology}
        \begin{definition}
            The open ball of radius $r>0$
            about a point $x$ in a metric space
            $(X,d)$ is the set
            $B_{r}(x)=\{y\in{X}:d(x,y)<r\}$
        \end{definition}
        The picture for this is a ``circle'' around the
        point $x$ or radius $r$. However, this circle
        can look very strange for weird metrics.
        \begin{example}
            If $X$ is a set and $d$ is the discrete metric,
            then $B_{r}(x)$ is either the point $x$
            (If $r\leq{1}$), or it is the entire set $X$.
        \end{example}
        \begin{example}
            With $X=\mathbb{R}$ and $d$ the standard metric
            $d(x,y)=|x-y|$, we have $B_{r}(x)$ is simply
            the open interval $(x-r,x+r)$.
        \end{example}
        \begin{example}
            Let $X=\mathbb{R}^{2}$ and define
            $d_{p}(x,y)%
             =(|x_{1}-y_{1}|^{p}+|x_{2}-y_{2}|^{p})^{1/p}$.
            For $p=2$, an open ball is a circle around
            the point $(x,y)$ of radius $r$. For $p=1$,
            we have ``diamonds'' around the point $x$.
            And for $p=\infty$ we have a square
            around $x$.
        \end{example}
        If you have a vector space and a norm on it,
        then the open balls about a point will have the
        property of convexity. Convexity is a vector space
        property, given two points the ``line'' between the
        two remains in the set. Metric spaces have no such
        notion. Since the balls of $\norm{}_{p}$ are not
        convex with $p<1$, we have that $\norm{}_{p}$ is
        a metric on $\mathbb{R}^{n}$
        if and only if $p\geq{1}$.
        \begin{definition}
            We say that a subset of $X$ is open if
            for all $x\in{S}$ there is an $r>0$
            such that $B_{r}(x)\subset{S}$.
        \end{definition}
        \begin{example}
            If $(X,d)$ is a metric space, then
            $X$ is open, $\emptyset$ is open
            (Vacuously true), and if $x\in{X}$ and
            $r>0$, then $B_{r}(x)$ is open.
        \end{example}
        \begin{theorem}
            If $(X,d)$ is a metric space, $x\in{X}$,
            and $r>0$, then $B_{r}(x)$ is an open
            subset of $X$.
        \end{theorem}
        \begin{proof}
            If $z\in{B_{r}(x)}$, let $t=d(x,z)$.
            Then $0\leq{t}<r$. Let $r'=r-t$.
            But if $y\in{B_{r'}(z)}$, then
            $d(x,y)\leq{d(x,z)+d(y,z)}<t+r'=t+r-t=r$.
            Therefore $B_{r'}(z)\subset{B_{r}(x)}$.
        \end{proof}
        \begin{theorem}
            A finite intersection of open sets is open.
        \end{theorem}
        \begin{proof}
            If $\mathcal{U}_{1},\hdots,\mathcal{U}_{n}$
            are open and if
            $x\in\cap_{k=1}^{n}\mathcal{U}_{k}$, then there
            exists $r_{1},\hdots,r_{n}$ such that
            $B_{r_{i}}(x)\subset\mathcal{U}_{i}$. Let
            $r=\min\{r_{1},\hdots,r_{n}\}$. Then
            $B_{r}(x)\subset\cap_{k=1}^{n}\mathcal{U}_{i}$
        \end{proof}
        \begin{theorem}
            Arbitrary unions of open sets are open.
        \end{theorem}
        Infinite intersections need not be open.
        The proof above would fail since the
        $r_{i}$ can form a sequence tending to zero.
        But indeed, let $X=\mathbb{R}$ and let
        $d(x,y)=|x-y|$, and take
        $\mathcal{U}_{n}=(-\frac{1}{n},\frac{1}{n})$.
        Then all of the $\mathcal{U}_{n}$ are open,
        yet the intersection, which is the set $\{0\}$,
        is not open. All of this mumbo-jumbo creates
        the more general notion of a topological space.
        \begin{definition}
            A topological space is a set $X$ and a
            subset $\tau\subset\mathcal{P}(X)$ such that:
            \begin{enumerate}
                \item $\emptyset,X\in\tau$
                \item Finite intersections of sets in $\tau$
                      are also sets in $\tau$.
                \item Arbitrary unions of sets in $\tau$
                      are also sets in $\tau$.
            \end{enumerate}
        \end{definition}
        \begin{definition}
            An open subset of a topological space
            $(X,\tau)$ is a set $\mathcal{U}\in\tau$.
        \end{definition}
        Here, $\mathcal{P}(X)$ denotes the \textit{power set}
        of $X$. This is the set of all subsets of $X$.
        The notion of a topological space generalizes the
        notion of a metric space. There is no notion of
        distance in such spaces, and things can be weird.
        There are topological spaces that have no metric
        associated with them.
\end{document}