\documentclass[crop=false,class=article,oneside]{standalone}
%----------------------------Preamble-------------------------------%
\input{../../../../preamble.tex}
%--------------------------Main Document----------------------------%
\begin{document}
    \ifx\ifmathcoursessurgery\undefined
        \section*{Surgery Theory}
        \setcounter{section}{2}
        \renewcommand\thesubfigure{%
            \arabic{section}.\arabic{figure}.\arabic{subfigure}%
        }
    \fi
    \subsection{Lecture 1: Singular and Simplicial Homology}
        The fundamental group $\pi_{1}(X)$ is useful for
        studying low dimensional spaces. However, it is poor for
        studying higher dimensional spaces since, for example,
        it is unable to distinguish spheres of dimensions
        $n\geq 2$. The first solution to this is to study
        the homotopy groups $\pi_{n}(X)$. For this, we have
        that $\pi_{i}(X)=0$ for $i<n$, and $\mathbb{Z}$ for
        $i=n$. A drawback is that homotopy groups are
        difficult to compute. The problem of $\pi_{i}(S^{n})$
        is very difficult for when $i>n$. Homology groups,
        $H_{n}(X)$ are one such solution to this difficulty.
        Homology groups share some characteristics with
        homotopy groups. If $X$ is a CW complex, then $H_{n}(X)$
        depends only on the $(n+1)$-skeleton of $X$. Also,
        $H_{i}(S^{n})$ and $\pi_{i}(S^{n})$ are isomorphic for
        $1\leq i\leq n$. One benefit is that $H_{i}(S^{n})=0$
        for $i>n$.
        \subsubsection{Simplicial Homology}
            The torus, projective plane, and Klein bottle can
            be created from a square by identifying opposite
            edges in certain ways. We can divide the square
            into two triangles, meaning these surfaces can by
            built from two triangles and then identifying
            edges. This can be done for all closed polygons
            as well. We can generalize this to $n$ dimensions
            by considering the $n-\textrm{simplex}$, which is
            the convex hull of a set of $n+1$ points in
            $\mathbb{R}^{n}$ that do not lie in an
            $n-\textrm{dimensional}$ hyperplane.
            $n-\textrm{Simplexes}$ are denoted $\Delta^{n}$.
            The interior of $\Delta^{n}$ is denoted
            $\mathring{\Delta}^{n}$. A face of an
            $n-\textrm{simplex}$ is a simplex formed by
            removing one of the vertices from $\Delta^{n}$.
            \begin{definition}
                A $\Delta-\textrm{Complex}$ on a space $X$ is
                a set of maps
                $\sigma_{\alpha}:\Delta^{n}\rightarrow X$
                such that:
                \begin{enumerate}
                    \item The restriction
                        $\sigma_{\alpha}|\mathring{\Delta}^{n}$
                        is injected. Each point $x\in X$ is
                        in the image of only one such
                        $\mathring{\Delta}^{n}$.
                    \item Each restriction of $\sigma_{\alpha}$
                        to a face is equal to one of the maps
                        $\sigma_{\beta}:%
                         \Delta^{n-1}\rightarrow X$.
                    \item A set $A\subset X$ is open if and only
                        if $\sigma_{\alpha}^{-1}$ is open in
                        $\Delta^{n}$ for all $\sigma_{\alpha}$.
                \end{enumerate}
            \end{definition}
            Let $X$ be a $\Delta-\textrm{Complex}$, and let
            $\Delta_{n}(X)$ be the free abelian group whose
            basis is the open $n-\textrm{simplices}$ of $X$.
            Elements of $\Delta_{n}(X)$ are called
            $n-\textrm{chains}$ and can be written as
            $\sum_{\alpha}n_{\alpha}e_{\alpha}^{n}$, where
            $n_{\alpha}$ is an integer.
            \begin{definition}
                The Boundary Homomorphism
                $\partial_{n}:%
                 \Delta_{n}(X)\rightarrow\Delta_{n-1}(X)$
                is the map:
                \begin{equation*}
                    \partial_{n}(\sigma_{\alpha})=
                    \sum_{i}(-1)^{i}\sigma_{\alpha}|
                    (v_{0},\hdots,v_{i-1},v_{i+1},\hdots,v_{n})
                \end{equation*}
            \end{definition}
            \begin{theorem}
                The composition of
                $\Delta_{n}(X)%
                 \overset{\partial_{n}}{\longrightarrow}%
                 \Delta_{n-1}(X)%
                 \overset{\partial_{n-1}}{\longrightarrow}%
                 \Delta_{n-2}(X)$
                is zero.
            \end{theorem}
            \begin{definition}
                The $n^{th}$ simplicial homology group of
                $X$, denoted $H_{n}^{\Delta}(X)$,
                is the quotient group
                $\ker(\partial_{n})/\Ima(\partial_{n+1})$
                formed from the chain complex
                $\hdots\longrightarrow\Delta_{n}(X)%
                 \overset{\partial_{n}}{\longrightarrow}%
                 \Delta_{n-1}(X)%
                 \overset{\partial_{n-1}}{\longrightarrow}%
                 \Delta_{n-2}(X)\longrightarrow\hdots$
            \end{definition}
        \subsubsection{Singular Homology}
            Singular homology is formed in the same way that
            simplicial homology is, with the requirement
            that the chains be formed by $\Delta_{n}(X)$ being
            relaxed. Now, only the continuity of the $\sigma$
            are required. Therefore, when $X$ is a space that can
            be ``triangulated,'' we have that the simplicial
            and singular homologies are the same.
            Suppose X and Y are orientable mans f:X-Y continuous. Whats degree?
            Take the nth top homology, $h_n(Z)-h_n(Y,Z)$. This is the map
            $f^*$ which is induced by $f$. Each one of these is a copy of
            $\mathbb{Z}$. So each one of these is a homomorphism. So it has
            to send the number $1\in\mathbb{N}$ somewhere. So the image of
            $1$ is the degree of the map $f$. For example
            $f$ constant, the degree is 0. If $f$ is the identity,
            then the degree is 1. If you take a loop that wraps around
            $S^{1}$ twice then the degree is $2$.
            This looks like the winding number, but is not quite that.
\end{document}