\documentclass[crop=false,class=book]{standalone}
%---------------PREAMBLE------------%
\input{../../preamble.tex}
%---------------GLOSSARY------------%
\makeglossaries
\loadglsentries{../../glossary}
\loadglsentries{../../acronym}
%--------------Title Page-----------%
\begin{document}
\chapter{Mechanics}
\section{Some Notes on Lagrangian Mechanics}
The Lagrangian is defined as $\mathcal{L} = T-V$, where $T$ is the kinetic energy and $V$ is the potential energy. Hamilton's Principle, which we take upon as an axiom of nature, states that the action, $\int_{t_1}^{t_2} \mathcal{L}(x,\dot{x},t)dt$, is an extremum. This means that $\mathcal{L}$ satisfies the Euler-Lagrange equation:
\begin{equation} 
\nonumber \frac{\partial \mathcal{L}}{\partial x} - \frac{d}{dt}\big(\frac{\partial \mathcal{L}}{\partial \dot{q}}\big) = 0
\end{equation}
This is the equation of motion in a one-dimensional Cartesian system. We may use a generalized coordinate system to obtain:
\begin{equation}
\nonumber \frac{\partial \mathcal{L}}{\partial q} - \frac{d}{dt} \big(\frac{\partial \mathcal{L}}{\partial \dot{q}}\big) = 0.
\end{equation}
Let's suppose we have a nice "Physics I," style Lagrangian. By that I mean that $T = T(t)$, and $V \ne V(t)$. That is, the potential energy is a function of position, and not of time. Then the equation of motion simplifies to $\frac{\partial}{\partial q}(T-V) - \frac{d}{dt}\big(\frac{\partial}{\partial \dot{q}}(T-V)\big) = 0$, where $\frac{\partial T}{\partial q} = 0$, $\frac{\partial V}{\partial \dot{q}} = 0$, and therefore $\frac{\partial V}{\partial q} + \frac{d}{dt}\big(\frac{\partial T}{\partial \dot{q}}\big) = 0$. In a standard problem, $T = \frac{1}{2}m \dot{q}^2$. This is the kinetic energy one would find in such a "Physics I," problem. So we have that:
\begin{equation}
\nonumber m\ddot{q} = -\frac{\partial V}{\partial q}
\end{equation}
Recall that Newton's Second Law says that $m\ddot{x} = -\frac{\partial V}{\partial x}$. So this final result looks very much like Newton's Second law, except that $"x"$ is replaced with $"q"$. So, we defined the following:
\begin{definition}
The Generalized Momentum of a system is defined as $\frac{\partial \mathcal{L}}{\partial \dot{q}}$. The Generalized Force of a system is defined as $\frac{\partial \mathcal{L}}{\partial q}$.
\end{definition}
When $\mathcal{L}$ is the nice "Physics I," Lagrangian that we're familiar with, we see that Newton's Second Law appears. That is, the time derivative of momentum is equal to minus the gradient of the potential energy. For any Lagrangian, if we we generalized momentum and generalized force, then the mathematics becomes very similar to Newton's Second Law. We obtain the "Generalized," Newton's Second Law:
\begin{equation}
\nonumber Generalized\ Force = \frac{d}{dt}\big(Generalized\ Momentum\big)
\end{equation}
Let's consider the example $q = \theta$. That is, our generalized coordinate is the angle made between the particle and the $x-$axis. The generalized momentum is just angular momentum, and the generalized force is angular force (Also known as torque). Let's consider a system where $\frac{\partial \mathcal{L}}{\partial \theta} = mr^2 \ddot{\theta}$. This is particle going around in a circle. Then we have from the equation of motion that $\frac{d}{dt}\big(\frac{\partial \mathcal{L}}{\partial \dot{\theta}}\big) = mr^2 \ddot{\theta}$, and thus $\frac{\partial \mathcal{L}}{\partial \dot{\theta}} = mr^2\dot{\theta} +c$. So we arrive at $\mathcal{L} = \frac{1}{2}mr^2\dot{\theta} + g(\theta) + c\dot{\theta}$. Remember from calculus that since $\frac{\partial g(\theta)}{\partial \dot{\theta}} = 0$, we get a function of integration, and not a constant of integration. This function of integration is the $g(\theta)$ we have written down. Let's further add the requirement that $\ddot{\theta} = 0$. That is, there is no angular acceleration. This represent a particle going around in a circle at constant angular velocity. With this information, we can determine $g(\theta)$. We have that $\frac{\partial \mathcal{L}}{\partial \theta} = 0$, and thus $g'(\theta) = 0$, which means $g(\theta)$ is a constant. The Lagrangian of this problem is $\mathcal{L} = \frac{1}{2}mr^2 \dot{\theta}^2+ c_1 \dot{\theta}+c_2$. Now what of the generalized momentum? We have that $\frac{d}{dt}\big(\frac{\partial \mathcal{L}}{\partial \dot{\theta}}\big) = \frac{\partial \mathcal{L}}{\partial \theta} = 0$, and therefore $\frac{\partial \mathcal{L}}{\partial \dot{\theta}} = constant$. But our generalized momentum is simply the angular momentum. That is, we have shown that angular momentum is conserved.
\end{document}