\documentclass[12pt]{article}

\begin{document}
    \textbf{BEN}
    \begin{enumerate}
        \item Slide 1: introduce the four of us.
        \item Slides 2 and 3: just read off verbatim and ask if
            anyone has a question.
        \item Slide 4: give definition of graph, talk about picture, ask for questions.
        \item Slide 5: read from, ask if anything is confusing so far.
        \item Slide 6: read from.
        \item Slide 7: read from. Ask if the two drawings are simple or multigraphs.
            Ask if there are any cycles in either of the pictures.
        \item Slide 8 and 9: Read from, point out how one graph looks like a tree, the other doesn't.
        \item Slide 10: Bridges of Konigsberg. Describe the problem. Break out into groups for 10 minutes.
        \item Slide 11 and 12: Ask groups what they're solutions are. Present Euler's proof that there is no
            solution. Show how the bridges problem can be made into a graph one.
        \item Slide 13: Without breaking into groups, ask if any one can find an Eulerian path in the
            Haus vom Nikolaus graph. 5 minutes or so.
        \item Slide 14: Same, but with Annie Hope graph.
        \item Slide 15: Just read from it, nothing major here.
        \item Slide 16: Discuss irreducibility. Ask if there is any confusion.
        \item Slide 17: Try to solve the Good Will Hunting problem. Groups. 15 minutes.
        \item Slide 18: Present the 10 graphs.
        \item Slide 19, 20, 21, 22: Read from slides, ask for questions.
        \item Slide 23: Talk about what it means for the crossings in the graph to be irrelevant.
            Break into groups and try to draw $K_{4}$ planar, using straight lines, and same for $K_{5}$.
        \item Slide 24 and 25: Meet back and talk about solutions and near solutions. Ask students what they got.
    \end{enumerate}
    \textbf{RYAN}
    \begin{enumerate}
        \item 
    \end{enumerate}
    
\end{document}