\section{Groups}
    \begin{fdefinition}{Groups}{Groups}
        A group is a set $G$ with a binary operation $*$,
        denoted $(G,*)$, such that: 
        \begin{enumerate}
            \item There exists an identity element $e$.
            \item For every element $a\in{A}$, there is an inverse element.
            \item The binary operation $*$ is associative.
        \end{enumerate}
    \end{fdefinition}
    Note that it is not necessarily true that $a*b = b*a$.
    These are special groups that are called Abelian.
    \begin{theorem}
        If $(G,*)$ is a group and $e$ is the identity, then it is unique.
    \end{theorem}
    \begin{proof}
        For if $e$ and $e'$ are identities, then:
        \begin{equation}
            e'=e'*e=e
        \end{equation}
        Therefore, etc.
    \end{proof}
    \begin{theorem}
        \label{thm:Group_Theory_Inverses_Are_Unique}
        If $(G,*)$ is a group, $a\in{G}$, and if $a^{-1}$ and
        $a'^{-1}$ are inverses of $a$, then $a^{-1}=a'^{-1}$.
    \end{theorem}
    \begin{proof}
        For if $e$ is the identity, and
        $a^{-1}$ and $a'^{-1}$ are inverses of $a$, then:
        \begin{align}
            a^{-1}&=a^{-1}*e
            \tag{Identitive Property}\\
            &=a^{-1}*(a*a'^{-1})
            \tag{Inverse Property}\\
            &=(a^{-1}*a)*a'^{-1}
            \tag{Associative Property}\\
            &=e*a'^{-1}
            \tag{Inverse Property}\\
            &=a'^{-1}
            \tag{Identitive Property}
        \end{align}
        Therefore, etc.
    \end{proof}
    \begin{theorem}
        If $(G,*)$ is a group, and if $e\in{G}$ is the identity,
        then $e^{-1}=e$.
    \end{theorem}
    \begin{proof}
        For $e=e*e$, and by Thm.~\ref{thm:Group_Theory_Inverses_Are_Unique}
        inverses are unique. Therefore, etc.
    \end{proof}
    \begin{theorem}
        \label{thm:Group_Theory_Inverse_of_Product}
        If $(G,*)$ is a group and $a,b\in G$, then:
        \begin{equation}
            (a*b)^{-1} = b^{-1}*a^{-1}
        \end{equation}
    \end{theorem}
    \begin{proof}
        For:
        \begin{align}
            (a*b)*(b^{-1}*a^{-1})&=
            a*(b*b^{-1})*a^{-1}
            \tag{Associative Property}\\
            &=a*(e)*a^{-1}
            \tag{Inverse Property}\\
            &=a*a^{-1}
            \tag{Identitive Property}\\
            &=e
            \tag{Inverse Property}
        \end{align}
        Thus $b^{-1}*a^{-1}$ is a right-inverse of $a*b$.
        But since $(G,*)$ is a group, right-inverses are
        left-inverses, and therefore $b^{-1}*a^{-1}$ is
        an inverse of $a*b$. But by
        Thm.~\ref{thm:Group_Theory_Inverses_Are_Unique},
        inverses are unique. Therefore, etc.
    \end{proof}
    \begin{theorem}
        If $(G,*)$ is a group and $a\in{G}$, then:
        \begin{equation}
            (a^{-1})^{-1}=a
        \end{equation}
    \end{theorem}
    \begin{proof}
        For:
        \begin{align}
            a^{-1}*(a^{-1})^{-1}
            &=(a^{-1}* a)^{-1}
            \tag{Thm.~\ref{thm:Group_Theory_Inverse_of_Product}}\\
            &=e
            \tag{Inverse Property}
        \end{align}
        From uniqueness, $(a^{-1})^{-1}=a$.
    \end{proof}
    \begin{definition}
        If $(G,*)$ and $(G',\circ)$ are groups and
        $f:G\rightarrow G'$ is a bijective function, then $f$ is said to
        be an isomorphism between $(G,*)$ and $(G',\circ)$ if and only if
        for all $a,b\in{G}$, $f(a*b)=f(a)\circ{f}(b)$.
    \end{definition}
    \begin{theorem}
        If $(G,*)$ and $(G',\circ)$ are isomorphic with identities $e_{*}$
        and $e_{\circ}$ are the identities, then $f(e_{*})=e_{\circ}$.
    \end{theorem}
    \begin{proof}
        $\forall a\in G,\ f(a)=f(a* e_*) = f(a)\circ f(e_*)$ as $f$ is
        an isomorphism. As identities are unique, $f(e_*)=e_{\circ}$.
    \end{proof}
    \begin{theorem}
    If $\langle G, * \rangle$ and $\langle G', \circ \rangle$ are isomorphic, with isomorphism $f$, and if $a\in G$, then $f(a^{-1}) = f(a)^{-1}$.
    \end{theorem}
    \begin{proof}
    For $e_{\circ}=f(e_*) = f(a*a^{-1}) = f(a^{-1}*a) = f(a)\circ f(a^{-1})=f(a^{-1})\circ f(a)$. As inverses are unique, $f(a^{-1})=f(a)^{-1}$.
    \end{proof}
    \begin{definition}
    A binary operation $*$ on a set $A$ is said to be commutative if and only for all $a,b\in A$, $a*b = b*a$.
    \end{definition}
    \begin{definition}
    A field is a set $F$ with two operations $+$ and $\cdot$, denoted $\langle F, +,\cdot \rangle$, with the following properties:
    \begin{enumerate}
    \item $a+b=b+a$ \hfill [Addition is Commutative]
    \item $a+(b+c)=(a+b)+c$ \hfill [Addition is Associative]
    \item $a\cdot b = b\cdot a$ \hfill [Multiplication is Commutative]
    \item $a\cdot (b\cdot c) = (a\cdot b)\cdot c$ \hfill [Multiplication is Associative]
    \item There is a $0\in F$ such that $0+a=a$ for all $a\in F$ \hfill [Existence of Additive Identity]
    \item There is a $1\in F$ such that $1\cdot a = a$ for all $a\in F$ \hfill [Existence of Multiplicative Identity]
    \item For each $a\in F$ there is a $b\in F$ such that $a+b = 0$. $b$ is denoted $-a$ \hfill [Existence of Additive Inverses]
    \item For each $a\in F$, $a\ne 0$ there is a $b\in F$ such that $a\cdot b = 1$. $b$ is denoted $a^{-1}$. \hfill [Existence of Multiplicative Inverses]
    \item $a\cdot(b+c) = a\cdot b + a\cdot c$ \hfill [Distributive Property]
    \end{enumerate}
    \end{definition}
    \begin{definition}
    A subfield of a field $\langle F,+,\cdot \rangle$ is a set $K\subset F$, such that $\langle K, +,\cdot \rangle$ is a field.
    \end{definition}
    \begin{theorem}
    In a field, $0$ and $1$ are unique.
    \end{theorem}
    \begin{proof}
    For suppose not, and let $0'$ and $1'$ be other identities. Then $1'=1'\cdot 1 = 1$ and $0'=0'+0=0$.
    \end{proof}
    \begin{theorem}
    For any field $\langle{F},+,\cdot\rangle$ and $a\in{F}$,
    $a\cdot{0}=0$.
    \end{theorem}
    \begin{proof}
    For $0=a\cdot{0}+(-a\cdot 0)=a\cdot(0+0)+(-a\cdot 0)=a\cdot{0}+a\cdot 0 + (-a\cdot 0) = a\cdot 0$. Thus, $a\cdot 0 = 0$.
    \end{proof}
    If $1=0$, then $a=a\cdot{1}=a\cdot{0}=0$, and thus every element is
    zero. A very boring field.
    \begin{theorem}
        In a field $\langle F, +,\cdot \rangle$, if $0\ne 1$, then $0$
        has no inverse.
    \end{theorem}
    \begin{proof}
    For let $a$ be such an inverse. Then $a\cdot 0 = 1$. But for any element of $F$, $a \cdot 0 = 0$. But $0\ne 1$, a contradiction.
    \end{proof}
    \begin{theorem}
    If $a+b = 0$, then $b= (-1)\cdot a$ where $(-1)$ is the solution to $1+(-1)=0$.
    \end{theorem}
    \begin{proof}
    $a+(-1)a = a(1+(-1)) = a\cdot 0 = 0$. From uniqueness, $b=(-1)a$. We may thus write additive inverses as $-a$
    \end{proof}
    \begin{definition}
    Given two fields $\langle F,+,\cdot \rangle$ and $\langle F', +',\times \rangle$, a bijection function $f:F\rightarrow F'$ is said to be a field isomorphism if and only if for allelements $a,b\in F$, $f(a+b)=f(a)+'f(b)$, and $f(a\cdot b) = f(a)\times f(b)$
    \end{definition}
    \begin{definition}
    $\langle F,+,\cdot \rangle$ and $\langle F', +',\times \rangle$, are said to be isomorphic if and only if they have an isomorphism.
    \end{definition}
    \begin{theorem}
    Given an ismorphism between two fields $\langle F,+,\cdot \rangle$ and $\langle F', +',\times \rangle$, $f(1) = 1'$ and $f(0) = 0'$.
    \end{theorem}
    \begin{proof}
    For let $x\in F$. Then $f(x)=f(x\cdot 1) = f(x)\times f(1)$, and $f(x)=f(x+0) = f(x)+'f(0)$. Therefore, etc.
    \end{proof}
    \begin{theorem}
    In a field $\langle F,+,\cdot \rangle$, $(a+ b)^2 = a^2 + 2ab + b^2$ ($2$ being the solution to $1+1$).
    \end{theorem}
    \begin{proof}
    For $(a+b)^2 = (a+b)(a+b) = a(a+b)+b(a+b) = a^2 + ab + ba + b^2 = a^2 +ab(1+1)+b^2 = a^2 + 2ab + b^2$.
    \end{proof}
    \begin{definition}
        A group is a set $G$ and a binary relation $*$
        on $G$, denoted $(G,*)$, such that:
        \begin{enumerate}
            \item For all ${a,b,c}\in{G}$, $(a*b)*c=a*(b*c)$
            \item There is an ${e}\in{G}$ such that for all
                ${a}\in{G}$, $a*e=e*a=a$.
            \item For all ${a}\in{G}$ there is a ${b}\in{G}$
                such that $a*b=e$
        \end{enumerate}
    \end{definition}
    \begin{definition}
        An Abelian group is a group $(G,*)$ such that
        $*$ is commutative.
    \end{definition}
    \begin{example}
        $G=\{1\}$ is an Abelian group under multiplication.
        This is the trivial group.
    \end{example}
    \begin{theorem}
        If $(G,*)$ is a group, then the following are true:
        \begin{enumerate}
            \item The identity ${e}\in{G}$ is unique.
            \item If $a*b=a*c$, then $b=c$.
            \item If $b*a=c*a$, then $b=c$.
            \item Inverses $a^{-1}$ are unique.
            \item $\forall_{{a,b}\in{G}}\exists_{{x}\in{G}}:a*x=b$
            \item $(a*b)^{-1}=b^{-1}*a^{-1}$
        \end{enumerate}
    \end{theorem}
    \begin{definition}
        The order of a group is number of elements in the
        group.
    \end{definition}
    \begin{definition}
        A group of finite order, or a finite group,
        is a group with finitely many elements.
    \end{definition}
    \begin{definition}
        The direct product of two groups $(G,*)$ and
        $(H,\circ)$ is the group  $({G}\times{H},\star)$
        where $\star$ is the binary operation defined by
        $(g_{1},h_{1})\star(g_{2},h_{2})%
         =(g_{1}*g_{2},{h_{1}}\circ{h_{2}})$
    \end{definition}
    \begin{definition}
        A permutation group on $n$ elements is a
        group whose elements are permutations of
        $n$ elements.
    \end{definition}
    \begin{definition}
        The symmetric group on $n$ elements,
        denoted $S_{n}$, is the group formed by
        permuting $n$ elements.
    \end{definition}
    \begin{definition}
        A homomorphism from a group $(G,*)$ to
        a group $(H,\circ)$ is a function
        $h:{G}\rightarrow{H}$ such that for all
        ${a,b}\in{G}$, $h(a*b)={h(a)}\circ{h(b)}$
    \end{definition}
    \begin{definition}
        An epimorphism from a group $(G,*)$ to
        a group $(H,\circ)$ is a homomorphism
        $h:{G}\rightarrow{H}$ such that
        $h$ is surjective.
    \end{definition}
    \begin{definition}
        A monomorphism from a group $(G,*)$ to
        a group $(H,\circ)$ is a homomorphism
        $h:{G}\rightarrow{H}$ such that
        $h$ is injective.
    \end{definition}
    \begin{definition}
        An isomorphism from a group $(G,*)$ to
        a group $(H,\circ)$ is a homomorphism
        $h:{G}\rightarrow{H}$ such that
        $h$ is bijective.
    \end{definition}
    \begin{definition}
        A ring is a set $R$ and two binary operations
        on $R$, denoted $(R,\cdot,+)$, such that:
        \begin{enumerate}
            \item $(R,+)$ is an Abelian group.
            \item $a\cdot({b}\cdot{c})=({a}\cdot{b})\cdot{c}$
            \item ${a}\cdot(b+c)={a}\cdot{b}+{a}\cdot{c}$
        \end{enumerate}
    \end{definition}
    \begin{definition}
        A ring with identity is a ring $(R,\cdot,+)$
        such that there is a ${1}\in{R}$ such that for
        all ${a}\in{R}$, ${a}\cdot{1}={1}\cdot{a}=a$.
    \end{definition}
    Left and right identities are elements such that ${e_{L}}\cdot{a}=a$
    and ${e_{R}}\cdot{a}=a$. If inverses $a_{L}^{-1}$ and $a_{R}^{-1}$
    exist for $a$, then $a_{L}^{-1}=a_{R}^{-1}$. That is, the inverse
    is the same for both right and left identities.
    \begin{definition}
        A commutative ring is a ring $(R,\cdot,+)$ such that
        $\cdot$ is commutative.
    \end{definition}
    \begin{definition}
        A commutative ring with identity is a ring with identity such
        that $\cdot$ is commutative.
    \end{definition}
    \begin{definition}
        A Field is a commutative ring with identity $(F,\cdot,+)$ such
        that for all ${a}\in{F}$ such that $a$ is not an identity with
        respect to $+$, there is a $b\in{F}$ such that ${a}\cdot{b}=1$.
    \end{definition}
    \begin{definition}
        Equivalent sets are sets $A$ and $B$ such that there exists a
        bijective function $f:{A}\rightarrow{B}$
    \end{definition}
    \begin{definition}
        A finite set is a set $A$ such that there is an
        ${n}\in{\mathbb{N}}$ such that $A$ is equivalent to
        $\mathbb{Z}_{n}$.
    \end{definition}
    \begin{definition}
        A countable set (Or a denumerable set) is a set $A$ that is
        equivalent to $\mathbb{N}$.
    \end{definition}
    \begin{definition}
        An uncountable set is a set that is neither finite nor countable.
    \end{definition}
    \begin{theorem}
        Set Equivalence is an equivalence relation.
    \end{theorem}
    This equivalence allows to classify all sets by the
    number of elements they contain or, more generally,
    by their cardinality. We say that two sets $A$ and
    $B$ have the same cardinality, denoted
    $\Card(A)$, if and only if $A$ and $B$ are equivalent.
    \begin{theorem}
        The following are true:
        \begin{enumerate}
            \item $\Card(A)=0$ if and only if $A=\emptyset$.
            \item If ${A}\sim{\mathbb{Z}_{n}}$, then $\Card(A)=n$.
        \end{enumerate}
    \end{theorem}
    \begin{definition}
        A finite cardinal number is a cardinal
        number of a finite set.
    \end{definition}
    \begin{definition}
        The standard ordering on the finite cardinal
        number is $0<1<\hdots<n<n+1<\hdots$
    \end{definition}
    Thus, if $A$ and $B$ are finite sets, then we write
    $\Card(A)<\Card(B)$ if $A$ is equivalent to a
    subset of $B$ but not equivalent to $B$.
    We take this notion and generalize to
    all sets. For $A$ and $B$, we write
    $\Card(A)<\Card(B)$ if $A$ is equivalent to a subset
    of $B$ but is not equivalent to $B$. This is the
    same as saying $A$ is equivalent to a subset of $B$,
    but $B$ is not equivalent to a subset of $A$.
    We write that
    $\Card(A)\leq\Card(B)$ is $A$ is equivalent to a
    subset of $B$.
    \begin{theorem}[Schr\"{o}der-Bernstein Theorem]
        If $A$ and $B$ are sets such that
        $\Card(A)\leq\Card(B)$ and
        $\Card(B)\leq\Card(A)$, then
        $\Card(A)=\Card(B)$.
    \end{theorem}
    \begin{theorem}
        The following are true:
        \begin{enumerate}
            \item If $\Card(A)\leq\Card(B)$ and
                  $\Card(B)\leq\Card(A)$, then
                  $\Card(A)\leq\Card(C)$.
            \item If $\Card(A)\leq\Card(B)$, then
                  $\Card(A)+\Card(C)\leq\Card(B)+\Card(C)$
        \end{enumerate}
    \end{theorem}
    \begin{theorem}
        If ${A}\subset{B}\subset{C}$, and
        $\Card(A)=\Card(C)$, then $\Card(B)=\Card(C)$.
    \end{theorem}
    \begin{theorem}
        If $f:{X}\rightarrow{Y}$ is a function,
        then $\Card(f(X))\leq\Card(X)$.
    \end{theorem}
    \begin{proof}
        Note that $f^{-1}(\{y\})$ creates a set of mutually disjoint
        subsets of $X$. By the axiom of choice there is a function
        $F:{f(X)}\rightarrow{X}$ such that for all ${y}\in{f(X)}$,
        ${F(y)}\in{f^{-1}(\{y\})}$. But since these sets are disjoint,
        $F$ is injective. Thus, $f(X)$ is equivalent to a subset of $X$.
        Therefore, $\Card(f(X))\leq\Card(X)$.
    \end{proof}
    The Schr\"{o}der-Bernstein theorem can be restated equivalently as
    ``If $A$ is equivalent to a subset of $B$ and $B$ is equivalent to a
    subset of $A$, then $A$ is equivalent to $B$.'' Addition and
    multiplication of finite cardinals follows directly from the standard
    arithmetic for the natural numbers. For cardinals of infinite sets,
    the arithmetic becomes a little more complicated.
    \begin{definition}
        The sum of two cardinal numbers is the
        cardinality of the union of two disjoint sets $A$
        and $B$. That is, if ${A}\cap{B}=\emptyset$, then
        $\Card(A)+\Card(B)=\Card({A}\cup{B})$.
    \end{definition}
    \begin{theorem}
        If $a$ and $b$ are distinct cardinal numbers, then there exists
        sets $A$ and $B$ such that ${A}\cap{B}=\emptyset$, $\Card(A)=a$,
        and $\Card(B)=b$.
    \end{theorem}
    \begin{theorem}
        If $A,B,C,$ and $D$ are sets such that $\Card(A)=\Card(C)$,
        $\Card(B)=\Card(D)$, and if ${A}\cap{B}=\emptyset$ and
        ${C}\cap{D}=\emptyset$, then
        $\Card({A}\cup{B})=\Card({C}\cup{D})$.
    \end{theorem}
    \begin{theorem}
        If $x,y,$ and $z$ are cardinal numbers, then
        $x+y=y+x$ and $x+(y+z)=(x+y)+z$.
    \end{theorem}
    The carinality of the set of natural numbers is denoted $\aleph_{0}$.
    That is, $\Card(\mathbb{N})=\aleph_{0}$
    \begin{example}
        Find the cardinal sum of $2$ and $5$. Let
        $N_{2}=\{1,2\}$ and $N_{5}=\{3,4,5,6,7\}$.
        Then $N_{2}$ and $N_{5}$ are disjoint,
        $\Card(N_{2})=2$ and $\Card(N_{5})=5$.
        Therefore $2+5=\Card(N_{2}\cup{N_{5}})$.
        But ${N_{2}}\cup{N_{5}}$ is just $\mathbb{Z}_{7}$,
        and $\Card(\mathbb{Z}_{7})=7$. Thus, $2+5=7$.
    \end{example}
    \begin{theorem}
        If $n$ and $m$ are finite cardinalities, then the cardinal sum
        of $n$ and $m$ is the integer $n+m$, where $+$ is the usual
        arithmetic addition.
    \end{theorem}
    \begin{example}
        Compute the cardinal sum $\aleph_{0}+\aleph_{0}$. Let
        $\mathbb{N}_{e}$ be the set of even natural numbers, and let
        $\mathbb{N}_{o}$ be the set of odd natural numbers. Then
        $\Card(\mathbb{N}_{e})=\aleph_{0}$,
        $\Card(\mathbb{N}_{o})=\aleph_{0}$, and
        ${\mathbb{N}_{o}}\cap{\mathbb{N}_{e}}=\emptyset$.
        Thus:
        \begin{equation}
            \aleph_{0}+\aleph_{0}
            =\Card({\mathbb{N}_{o}}\cup{\mathbb{N}_{e}})
        \end{equation}
        But ${\mathbb{N}_{o}}\cup{\mathbb{N}_{e}}=\mathbb{N}$ and
        $\Card(\mathbb{N})=\aleph_{0}$. Therefore,
        $\aleph_{0}+\aleph_{0}=\aleph_{0}$.
    \end{example}
    \begin{example}
        Find $n+\aleph_{0}$, where $n\in\mathbb{N}$.
        We have that
        $\Card(\mathbb{Z}_{n}z)=n$ and
        $\Card(\mathbb{N}\setminus\mathbb{Z}_{n})%
         =\aleph_{0}$
        But then
        $n+\aleph_{0}=%
         \Card(\mathbb{Z}_{n}\cup%
         \mathbb{N}\setminus\mathbb{Z}_{n})%
         =\Card(\mathbb{N})=\aleph_{0}$.
        Therefore, $n+\aleph_{0}=\aleph_{0}$.
    \end{example}
    \begin{definition}
        The cardinality of the continuum,
        denoted $\mathfrak{c}$, is the
        cardinality of the set of real numbers.
        That is, $\mathfrak{c}=\Card(\mathbb{R})$.
    \end{definition}
    \begin{theorem}
        $\Card([0,1])=\mathfrak{c}$.
    \end{theorem}
    \begin{theorem}
        $\Card\big((0,1)\big)=\mathfrak{c}$.
    \end{theorem}
    \begin{theorem}
        $\mathbb{R}$ is uncountable. That is,
        $\mathfrak{c}>\aleph_{0}$.
    \end{theorem}
    \begin{theorem}
        $\mathfrak{c}+\aleph_{0}=\mathfrak{c}$.
    \end{theorem}
    \begin{proof}
        We have $\Card((0,1))=\mathfrak{c}$ and
        $\Card(\mathbb{N})=\aleph_{0}$. But
        $(0,1)\cap\mathbb{N}=\emptyset$, and thus
        $\aleph_{0}+\mathfrak{c}%
         =\Card((0,1)\cup\mathbb{N})$.
        But $\mathbb{R}\sim(0,1)$ and
        $\mathbb{N}\cup(0,1)\subset\mathbb{R}$.
        By the Schr\"{o}der-Bernstein theorem,
        $\mathbb{N}\cup(0,1)\sim\mathbb{R}$.
        Therefore, etc.
    \end{proof}
    \begin{definition}
        The product of two cardinal numbers $a$ and $b$
        is the cardinality of the cartesian product
        of two set $A$ and $B$ such that
        $\Card(A)=a$ and $\Card(B)=b$. That is,
        ${a}\times{b}=\Card({A}\times{B})$.
    \end{definition}
    \begin{theorem}
        The following are true of cardinal numbers:
        \begin{enumerate}
            \item $xy=yx$
            \item $x(yz)=(xy)z$
            \item $x(y+z)=xy+xz$
        \end{enumerate}
    \end{theorem}
    \begin{proof}[Proof of Part 3]
        Let $A,B,$ and $C$ be disjoint.
        Then
        ${A}\times{({B}\cup{C})}%
         =({A}\times{B})\cup({A}\times{C})$, and thus
        $\Card({A}\times{({B}\cup{C})})%
         =\Card(({A}\times{B})\cup({A}\times{C}))$.
        But ${A}\times{B}$ and ${A}\times{C}$ are disjoint.
        Thus we have
        $\Card(({A}\times{B})\cup({A}\times{C}))%
         =\Card({A}\times{B})+\Card({A}\times{C})$.
        Therefore, etc.
    \end{proof}
    \begin{theorem}
        If $\Card(T)=x$ and $F:{T}\rightarrow{\mathcal{P}(T)}$ is a
        set-valued mapping such that for all ${t}\in{T}$ we have that
        $\Card(F(t))=y$ and for all ${t}\ne{t}$,
        ${F(t)}\cap{F(t')}=\emptyset$, then $\Card(\cup_{t=1}^{N}F(t))=xy$
    \end{theorem}
    \begin{example}
        Let $f:{\mathbb{N}^{2}}\rightarrow{\mathbb{N}}$
        be defined by $f(n,m)=2^{n}3^{m}$.
        Then $f$ is injective, since $2$ and $3$
        are coprime. Therefore,
        $\aleph_{0}\times\aleph_{0}=\aleph_{0}$.
    \end{example}
    \begin{example}
        Show that $\mathbb{R}^{2}\sim\mathbb{R}$.
        Let $f:\mathbb{R}^{2}\rightarrow\mathbb{R}$
        be the rather bizarre function defined by the image
        $f(x_{0}.x_{1}x_{2}\hdots,y_{0}.y_{1}y_{2}\hdots)%
         =x_{0}y_{0}.x_{0}y_{0}x_{1}y_{1}\hdots$ Then
        $f$ is inective. But the mapping
        $g:\mathbb{R}\rightarrow\mathbb{R}^{2}$
        defined by $g(x)=(x,0)$ is also injective.
        By Schr\"{o}der-Bernstein,
        $\mathbb{R}^{2}\sim\mathbb{R}$.
    \end{example}
    \begin{definition}
       Order isomorphic set are two sets $A$ and $B$
       with well orders $<_{A}$ and $<_{B}$ such that
       there exists a bijection $f:{B}A\rightarrow{B}$
       such that for all $a_{1},a_{2}\in{A}$ such that
       $a_{1}<_{A}a_{2}$, $f(a_{1})<_{B}f(a_{2})$.
    \end{definition}
    \begin{theorem}
       Order-Isomorphism is an equivalence relation.
    \end{theorem}
    To every well ordered set, an ordinal number is
    assigned, denoted $\Ord(A,<_{A})$. Conversely,
    for every ordinal number there is a set with a
    well order corresponding to it. Two ordinal numbers
    are equal if and only if the well-ordered sets
    corresponding to them are order isomorphic.
    That is,
    $\Ord(A,<_{A})=\Ord(B,<_{B})$ if and only if
    $(A,<_{A})$ and $(B,<_{B})$ are order isomorphic.
    \begin{theorem}
       If $(A,<_{A})$ and $(B,<_{B})$ are well ordered
       sets, and if $\Card(A)=\Card(B)$, then
       $(A,<_{A})$ and $(B,<_{B})$ are order
       isomorphic.
    \end{theorem}
    The ordinal number of the empty set is $0$. The
    ordinal number of a finite set of $n$ elements with
    a well ordering is denoted $n\in\mathbb{N}$.
    The ordinal for the natural numbers $\mathbb{N}$
    with their usual well-ordering is denoted $\omega$.
    A given well-ordered set has only one cardinal number,
    but it is possible for it to have two ordinal numbers.
    \begin{definition}
        An ordinal number $\alpha$ is less than or equal to an ordinal
        number $\beta$ if there are well-ordered sets $(A,<_{A})$ and
        $(B,<_{B})$ such that $\alpha=\Ord((A,<_{A}))$ and
        $\beta=\Ord(B,<_{B})$, and $(A,<_{B})$ is order isomorphic to
        subset of $(B,<_{B})$.
    \end{definition}
    \begin{theorem}
        The only order isomorphism from a well ordered set $(A,<_{A})$ to
        itself is the identity isomorphism.
    \end{theorem}
    \begin{theorem}
        If $\alpha$ and $\beta$ are ordinal numbers and
        ${\alpha}\leq{\beta}$ and ${\beta}\leq{\alpha}$,
        then $\alpha=\beta$.
    \end{theorem}
    \begin{theorem}
        If $\alpha$ and $\beta$ are ordinal numbers, either
        ${\alpha}\leq{\beta}$, or ${\beta}\leq{\alpha}$.
    \end{theorem}
    \begin{theorem}
        If $\alpha$ and $\beta$ are ordinal numbers, either
        $\alpha<\beta$, $\beta<\alpha$, or $\alpha=\beta$.
    \end{theorem}
    \begin{definition}
        The total ordering relation of a well-ordered set $(A,<_{A})$
        with respect
       to a well-ordered set $(B,<_{B})$ is the ordering
       on the set ${A}\cup{B}$ defined as: For all
       $a_{1},a_{2}\in{A}$ such that $a_{1}<_{A}a_{2}$,
       $a_{1}<_{*}a_{2}$, for all $b_{1},b_{2}\in{B}$
       such that $b_{1}<_{B}b_{2}$, $b_{1}<_{*}b_{2}$,
       and for all ${a}\in{A}$ and ${b}\in{B}$,
       ${a}<_{*}{b}$.
    \end{definition}
    \begin{theorem}
       The total ordering relation $<_{*}$ on the set
       ${A}\cup{B}$ is a well-ordering.
    \end{theorem}
    \begin{definition}
        The ordinal sum of two ordinal numbers $\Ord((A,<_{A}))$ and
        $\Ord((B,<_{B}))$, where $A$ and $B$ are disjoint, is the ordinal
        number $\Ord(({A}\cup{B},<_{*}))$.
    \end{definition}
    \begin{theorem}
       The following are true of ordinal numbers:
       \begin{enumerate}
            \item $\alpha<\beta\Rightarrow\alpha+\gamma<\beta+\gamma$
            \item $(\alpha+\beta)+\gamma=\alpha+(\beta+\gamma)$
            \item $\alpha+\beta=\alpha+\gamma\Rightarrow\beta=\gamma$
       \end{enumerate}
    \end{theorem}
    \begin{definition}
        The lexicographic ordering on the cartesianproduct of well
        ordered set $(A,<_{A})$ and $(B,<_{B})$ is the ordering on
        ${A}\times{B}$ defined by: If ${a}<_{A}{x}$, then
        $(a,b)<_{*}(x,y)$ for all $b,y\in{B}$, and if $a=x$ and
        $b<_{B}y$, then $(a,b)<_{*}(x,y)$.
    \end{definition}
    \begin{theorem}
        If $(A,<_{A})$ and $(B,<_{B})$ are well ordered sets, then the
        lexicographic ordering on ${A}\times{B}$ is a well ordering.
    \end{theorem}
    \begin{definition}
        The ordinal product of two ordinal numbers
        $\Ord((A,<_{A}))$ and $\Ord((B,<_{B}))$,
        is $\Ord(({A}\times{B},<_{*}))$
    \end{definition}
    \begin{theorem}
        The following are true of ordinal numbers:
        \begin{enumerate}
            \item $\alpha(\beta\gamma)=(\alpha\beta)\gamma$
            \item $\alpha(\beta+\gamma)=\alpha\beta+\alpha\gamma$
        \end{enumerate}
    \end{theorem}
    \begin{definition}
       Relatively prime integers are integers
       $a,b\in\mathbb{N}$ such that $\gcd(a,b)=1$.
    \end{definition}
    \begin{theorem}
       If $p$ is prime and $a\in\mathbb{N}$ is
       such that $p$ does not divide $a$, then $a$ and $p$
       are relatively prime.
    \end{theorem}
    \begin{theorem}
       There are infinitely many prime numbers.
    \end{theorem}
    \begin{theorem}
       If $a\in\mathbb{N}$, $a>1$, then either
       $a$ is a prime number, or $a$ is the product
       of finitely many primes.
    \end{theorem}
    \begin{theorem}
       If $a\in\mathbb{N}$, $a>1$, and if $a$ is not
       prime, then the prime expansion of $a$ is
       unique.
    \end{theorem}
    \begin{definition}
       A diophantine equation is an equation whose
       solutions are required to be integers.
    \end{definition}
    \begin{definition}
       A linear diophantine equation in two variables
       $x$ and $y$ is an equation
       $ax+by=c$, where $a,b,c\in\mathbb{Z}$.
    \end{definition}
    \begin{theorem}
       If $a,b,c\in\mathbb{Z}$ $d=\gcd(a,b)$, and if $d$ does not
       divide $c$, then $ax+by=c$ has no integral solutions.
    \end{theorem}
    \begin{theorem}
       If $a,b,c\in\mathbb{Z}$ $d=\gcd(a,b)$, and if $d$ divides $c$,
       then $ax+by=c$ has infinitely many solutions.
    \end{theorem}