%------------------------------------------------------------------------------%
\documentclass[crop=false,class=article]{standalone}                           %
%------------------------------Preamble----------------------------------------%
\makeatletter                                                                  %
    \def\input@path{{../../../}}                                               %
\makeatother                                                                   %
\input{preamble.tex}                                                           %
%----------------------------Main Document-------------------------------------%
\begin{document}
    \title{Topics in Algebra}
    \author{Ryan Maguire}
    \date{\vspace{-5ex}}
    \maketitle
    \section{Homework IV}
        \begin{problem}
            Let $\varphi:\mathbb{Z}^{n}\rightarrow\mathbb{Z}^{n}$ be a
            $\mathbb{Z}\textrm{-Module}$ homomorphism such that the cokernel is
            finite. Let $\mathscr{E}$ by the standard basis of $\mathbb{Z}^{n}$
            and let $A=[\varphi]_{\mathscr{E}}^{\mathscr{E}}$ be the
            representing matrix of $\varphi$. Show that that cardinality of
            $\varphi$ is given by:
            \begin{equation}
                \textrm{Card}\big(\textrm{coker}(\varphi)\big)=|\textrm{det}(A)|
            \end{equation}
        \end{problem}
        \begin{solution}
            We prove by induction on $n$. If $n=1$ then for all $m\in\mathbb{Z}$
            we have:
            \begin{equation}
                \varphi(m)=\varphi(n\cdot{1})=m\varphi(1)
            \end{equation}
            Since the cokernel is finite, $\varphi(1)\ne{0}$. Otherwise the
            cokernel would be $\mathbb{Z}$, which is infinite. Let
            $k=\varphi(1)$. Then we have that the cokernel is isomorphic to
            $\mathbb{Z}_{k}$, and there are thus $k$ elements. Moreover the
            transformation matrix $[\varphi]_{\mathscr{B}}^{\mathscr{B}}$ is
            simply the singleton $[k]$. Thus
            $\textrm{det}([k])=\textrm{Card}(\mathbb{Z}_{k})=k$. Suppose the
            proposition is true for $n\in\mathbb{N}$. Let
            $\varphi:\mathbb{Z}^{n+1}\rightarrow\mathbb{Z}^{n+1}$ be a
            $\mathbb{Z}\textrm{-Module}$ homomorphism such that the cokernel is
            finite. But then the restriction $\varphi|_{\mathbb{Z}^{n}}$ is a
            $\mathbb{Z}\textrm{-Module}$ homomorphism from $\mathbb{Z}^{n}$ to
            itself and therefore:
            \begin{equation}
                \textrm{Card}\big(\textrm{coker}(\varphi|_{\mathbb{Z}^{n}})\big)
                =\big|\det\big([\varphi|_{\mathbb{Z}^{n}}
                    ]_{\mathscr{E}_{n}}^{\mathscr{E}_{n}}\big)\big|
            \end{equation}
            Doing this for every entry and the summing along, using the minor
            expansion formula, we get the end result.
        \end{solution}
        \begin{problem}
            Prove the short five-lemma.
        \end{problem}
        \begin{solution}
            It suffices to show that $f$ is bijective. That is, that $f$ is both
            injective and surjective. It is surjective for let $y\in{N}$. Since
            $f''$ is an isomorphism it is bijective, and thus there is an
            $m''\in{M}''$ such that $f''(m'')=h(y)$. But since the rows are
            short exact, $v$ is surjective and thus there is an $x\in{M}$ such
            that $v(x)=m''$. But then $f''(v(x))=f''(m'')=h(y)$. From the
            commutativity of the diagram we have that $h(f(x))=h(y)$. Let
            $\alpha=f(x)-y$. If $\alpha=0$ then we are done, if not then
            $\alpha$ is in the kernel of $h$ and is therefore in the image of
            $g$ since the sequence is exact. But then there is an $n'\in{N}'$
            such that $g(n')=\alpha$. But $f'$ is an isomorphism so there is
            an $m'\in{M}'$ such that $f'(m')=n'$. But $u$ is injective and thus
            there is a unique $m\in{M}$ such that $u(m')=m$. From commutativity
            we have that $f(u(m'))=\alpha$. But then $f(x-u(m'))=y$, and thus
            $f$ is surjective. In a similar manner it is injective. For suppose
            $f(x)=0$ for some $x\in{M}$. Then $f(x)$ is in the kernel of $h$
            and thus in the image of $g$. Therefore there is a unique
            $n'\in{N}'$ such that $g(n')=f(x)$. But $0$ is such that $g(0)=0$,
            and thus $n'=0$. Going back along $f'$, since it is bijective, we
            get a unique $m'$ such that $f(m')=0$. But again $0$ does this so
            $m'=0$. Going along $u$ we conclude that $x=0$, and thus $f$ is
            injective.
        \end{solution}
        \begin{problem}
            Let $M$ and $N$ be finitely generated Abelian group. If $M\oplus{M}$
            is isomorphic to $N\oplus{N}$, does it follow that $N$ is isomorphic
            to $N$?
        \end{problem}
        \begin{solution}
            Yes, for by the primary decomposition theorem we have that:
            \par
            \begin{subequations}
                \begin{minipage}[b]{0.49\textwidth}
                    \begin{equation}
                        M\simeq\mathbb{Z}^{m}
                        \bigoplus_{k=1}^{N}\mathbb{Z}_{q_{k}}
                    \end{equation}
                \end{minipage}
                \hfill
                \begin{minipage}[b]{0.49\textwidth}
                    \begin{equation}
                        N\simeq\mathbb{Z}^{n}
                        \bigoplus_{k=1}^{N}\mathbb{Z}_{p_{k}}
                    \end{equation}
                \end{minipage}
            \end{subequations}
            Where $q_{k}|q_{k+1}$ and $p_{k}|p_{k+1}$ are unique. From this we
            have:
            \begin{equation}
                M\oplus{M}\simeq
                \mathbb{Z}^{2m}\bigoplus_{k=1}^{N}
                \Big(\mathbb{Z}_{q_{k}}\oplus\mathbb{Z}_{q_{k}}\Big)
                \simeq
                \mathbb{Z}^{2n}\bigoplus_{k=1}^{N}
                \Big(\mathbb{Z}_{p_{k}}\oplus\mathbb{Z}_{p_{k}}\Big)
                \simeq{N}\oplus{N}
            \end{equation}
            By then this is a primary decomposition of both $M\oplus{M}$ and
            $N\oplus{N}$ and thus the sequence $q_{1},q_{1},q_{2},q_{2},\dots$
            all the way up to $q_{N},q_{N}$ is unique and so we conclude that
            $p_{k}=q_{k}$ for all $k\in\mathbb{Z}_{N}$. Lastly we conclude that
            $n=m$. Therefore, since $\simeq$ is an equivalence relation, we have
            that $N\simeq{M}$.
        \end{solution}
        \begin{problem}
            Let $R$ be a ring and let $M$ be and $R\textrm{-Module}$. $M$ is
            Noetherian if it satisfies the descending chain condition on
            submodules. That is, for any sequence of submodules $M_{n}$ such
            that $M_{n}\subseteq{M}_{n+1}$, there exists an $N\in\mathbb{N}$
            such that for all $n>N$, $M_{n}=M_{N}$.
        \end{problem}
        \begin{problem}
            Let $m$ and $n$ be positive integers. Show that as a $\mathbb{Z}$
            module:
            \begin{equation}
                \textrm{Hom}_{\mathbb{Z}}(\mathbb{Z}/n\mathbb{Z},
                                          \mathbb{Z}/m\mathbb{Z})
                \simeq\mathbb{Z}/\textrm{gcd}(n,m)\mathbb{Z}
            \end{equation}
        \end{problem}
\end{document}