%--------------------------------------------------------------------------%
\documentclass[crop=false,class=book,oneside]{standalone}                  %
%--------------------------Preamble----------------------------------------%
\input{preamble.tex}                                                       %
%------------------------Main Document-------------------------------------%
\begin{document}
        \pagenumbering{roman}
        \title{Topics in Algebra}
        \author{Ryan Maguire}
        \date{\vspace{-5ex}}
        \maketitle
        \tableofcontents
        \clearpage
        \chapter*{Topics in Algebra}
        \addcontentsline{toc}{chapter}{Topics in ALgebra}
        \markboth{}{SURGERY THEORY}
        \vspace{10ex}
        \setcounter{chapter}{1}
        \pagenumbering{arabic}
    \section{Modules}
        Let $R$ be a ring with identity. Ring homomorphisms are required to
        to preserve identities. The identity is idemptotent:
        $1^{2}=1$. In a group, if $x^{2}=x$ then $x=1$, by the cancellation
        laws. This is not necessary in a ring. Let $R=\mathbb{Z}^{2}$. Here,
        there are several idemptotent elements: $(0,1)$, $(1,0)$, and
        $(1,1)$. For a group, a homomorphism that preserves that product
        also preserves the identity and the inverses. For rings we must
        add that to the definition. Any ring without identity can be
        embedded into a ring with identity, so there's not much harm in
        assuming our rings have identity.
        \begin{ldefinition}{$R$ Modules}{R_Module}
            And $R$ module on a ring $R$ is a set $M$ with a function
            $\cdot:R\times{M}\rightarrow{M}$ with the following properties:
            \begin{enumerate}
                \item $r\cdot(m_{1}+m_{2})=r\cdot{m}_{1}+r\cdot{m}_{2}$
                \item $(r_{1}+r_{2})\cdot{m}=r_{1}\cdot{m}+r_{2}\cdot{m}$
                \item $r_{1}\cdot(r_{2}\cdot{m})=(r_{1}r_{2})\cdot{m}$
                \item $1\cdot{m}=m$
            \end{enumerate}
        \end{ldefinition}
        \begin{theorem}
            An $R$ module is an Abelian group $M$ equipped with a ring
            homomorphism $\lambda:R\rightarrow\textrm{End}(M)$, where
            $\textrm{End}(M)$ is the ring of endomorphisms.
        \end{theorem}
        The ring of endomorphisms is the set of all endomorphisms equipped
        with function addition and composition. That is,
        $f+g$ is the function defined by $(f+g)(x)=f(x)+g(x)$. The product
        is composition $(g\circ{f})(x)=g(f(x))$.
        Given an R module in the sense of the definition, we need to define
        a ring homomorphism $\lambda:R\rightarrow\textrm{End}(M)$.
        Let $(\lambda(r))(m)=r\cdot{m}$. Then $\lambda(r)\in\textrm{End}(M)$,
        by the first part of the definition of an $R$ module. By the second
        part, $\lambda(r_{1}+r_{2})=\lambda(r_{1})+\lambda(r_{2})$. By three,
        $\lambda(r_{1}r_{2})=\lambda(r_{1})\circ\lambda(r_{2})$. Finally, by
        the fourth portion of our definition,
        $\lambda(1_{R})=1_{\textrm{End}(M)}$.
        \begin{ldefinition}{Module Homomorphism}{Module_Homomorphism}
            For $R$ modules $M$ and $N$, a homomorphism is an Abelian group
            homomorphism $f:M\rightarrow{N}$ such that, for all $r,m$,
            $f(r\cdot{m})=r\cdot{f}(m)$.
        \end{ldefinition}
        \begin{ldefinition}{Module Isomorphism}{Module_Isomorphism}
            $f:M\rightarrow{N}$ is an isomorphism if there exists a
            homomorphism $g:N\rightarrow{M}$ such that
            $f\circ{g}=\textrm{id}_{N}$ and $g\circ{f}=\textrm{id}_{M}$.
        \end{ldefinition}
        \begin{example}
            Let $R$ be a field. Then any $R$ module is simply a vector space
            over $R$. If we let $R=\mathbb{Z}$, then a $\mathbb{Z}$ module
            is an Abelian group.
        \end{example}
        For any ring $E$ there exists a unique ring homomorphism
        $\mathbb{Z}\rightarrow{E}$,
        $\mathbb{Z}\overset{\lambda}{\rightarrow}\textrm{End}(M)$.
        From appearance, modules seem very similar to vector spaces, but
        structurally they are very difference. Every vector space has a
        basis, but this is not true for modules.
        \begin{lexample}{}{}
            If $k$ is a field and $V$ is a finite dimensional vector space
            over $k$, and if $T:V\rightarrow{V}$ is a linear operator. Make
            $V$ a $k[x]$ module by defining $f\cdot{r}=(f(T))(v)$. For
            example, $(2-x+3x^2)\cdot{v}=2v-T(v)+3T^{2}(v)$.
        \end{lexample}
        A subspace $W\subseteq{V}$ is a $k[X]$ submodule such that
        $T(W)\subseteq{W}$. That is, a $T$ invariant space. If $W$ is invariant
        under $T$, then it is invariant under $T^{2}$ and $T^{3}$, etc., and
        it is invariant under linear combinations. That is, it is invariant
        under polynomials.
        \begin{example}
            Let $\varphi:A\rightarrow{B}$ be a ring homomorphism. Then any
            $B$ module $M$ becomes an $A$ module by pullback along $\varphi$.
        \end{example}
        Special case, if $R$ is a ring and $I$ is a two-sided ideal of $R$,
        then $\pi:R\rightarrow{R}/I$. Any $R/I$ module $M$ becomes an
        $R$ module by pullback. $M$ is annihilated by $I$. An $R/I$ module is
        just an $R$ module annihilated by $I$. Let $M$ be an $R$ module
        annihilated by $I$. Then $\lambda(I)=0$.
        \begin{ldefinition}{Direct Sum of Modules}{Direct_Sum_of_Modules}
            The direct sum of two $R$ modules $M_{1}$ and $M_{2}$ is the abelian
            group $M_{1}\oplus{M}_{2}$ defined by $M_{1}\times{M}_{2}$ where
            $r\cdot(m_{1},m_{2})=(r\cdot{m_{1}},r\cdot{m_{2}})$.
        \end{ldefinition}
        \begin{ltheorem}{Recognition Principle for Direct Sums}
                        {Recognition_Principle_for_Direct_Sums}
            It's a very cool theorem.
        \end{ltheorem}
        \begin{ltheorem}{Primary Decomposition Theorem}
                        {Primary Decomposition_Theorem}
            If $R$ is a commutative ring and if $I$ and $J$ are coprime ideals
            of $R$ ($I+J=R$), and if $M$ is an R module annihilated by the
            product ideal $IJ$, then $M=_{I}M+_{J}M$, where
            $_{K}M$ is the set of all $m\in{M}$ such that $Km=0$.
        \end{ltheorem}
        \begin{proof}
            We need to show that the sum is everything and that the intersection
            is trivial.
        \end{proof}
        Let $V$ be a finite dimensional $k$ vector space and let
        $T:V\rightarrow{V}$ be a linear map. $T$ is diagonalizable if and only
        if it's minimal polynomial $\mu_{T}$ factors as
        $(x-\lambda_{1})\cdots(x-\lambda_{r})$ with distinct linear factors.
\end{document}