\documentclass[crop=false,class=article,oneside]{standalone}
%----------------------------Preamble-------------------------------%
\input{../../../../preamble.tex}
%--------------------------Main Document----------------------------%
\begin{document}
    \ifx\ifmathcoursesalgebraicgeometry\undefined
        \section*{Algebraic Geometry}
        \setcounter{section}{1}
    \fi
    \subsection{Groebner Bases}
        \begin{definition}
            A ring is a set $R$ with two binary operations $+$
            and $\cdot$, called addition and multiplication,
            such that the following are true:
            \begin{enumerate}
                \begin{multicols}{3}
                    \item $(R,+)$ is an Abelian Group
                    \item $(a\cdot{b})\cdot{c}=a\cdot(b\cdot{c})$
                    \item $a\cdot(b+c)=(a\cdot b)+(a\cdot c)$
                \end{multicols}
            \end{enumerate}
        \end{definition}
        \begin{definition}
            A commutative ring is a ring $R$ such that
            $\forall_{a,b\in R},a\cdot{b}=b\cdot{a}$
        \end{definition}
        \begin{definition}
            A ring with identity is a ring $R$ such that
            $\exists_{1_{R}\in R}:\forall_{a\in R}, 1_{R}\cdot a=a\cdot 1_{R}=a$
        \end{definition}
        \begin{definition}
            A subring of a ring with identity $R$ is a set
            $S\subset R$ such that $1_{R}\in S$, and $S$ is
            closed under the ring operations.
        \end{definition}
        \begin{remark}
            Any field is a ring.
        \end{remark}
        \begin{definition}
            A monomial in variables $x_1,\hdots, x_n$ over a
            ring $R$ is a product
            $x^\alpha=\prod_{k=1}^{n} x_1^{\alpha_1}$,
            where $(\alpha_1,\hdots,\alpha_n)\in \mathbb{N}^n$.
        \end{definition}
        \begin{notation}
            The set of monomials in $n$ variables over
            $R$ is denoted $\Mon_{R}(x_1,\hdots, x_n)$
        \end{notation}
        \begin{definition}
            If $\alpha,\beta \in \mathbb{N}^n$ such that
            $\alpha_i \leq \beta_i$, then $x^{\alpha}$ is said
            to divide $x^\beta$, denoted $x^\alpha \vert x^\beta$,
            if $x^\beta = x^\alpha \cdot x^\gamma$ for some
            $\gamma\in\mathbb{N}^n$.
        \end{definition}
        \begin{definition}
            A term is a monomial multiplied by a coefficient in $R$.
        \end{definition}
        \begin{definition}
            A polnyomial over $R$ is a finite $R-$linear
            combination of monomials,
            $f=\sum_{\alpha} a_{\alpha}\cdot x^{\alpha}$.
        \end{definition}
        \begin{notation}
            The set of all polynomials in $n$ variables over
            a ring $R$ is denoted $R[x_1,\hdots, x_n]$.
        \end{notation}
        \begin{theorem}
            If $R$ is a commutative ring with identity,
            then $R[x_1,\hdots, x_n]$ is a commutative
            ring with identity.
        \end{theorem}
        \begin{definition}
            A polynomial $f\in R[x_1,\hdots, x_n]$ is
            called a constant polynomial if $f\in R$.
        \end{definition}
        \begin{definition}
            A field $k$ is a commutative ring with identity
            such that for all $a\in k$, $a\ne 0$, there is a
            $b\in k$ such that $a\cdot b=1$
        \end{definition}
        \begin{remark}
            We usually work with fields and consider
            polynomial rings of the form $k[x_1,\hdots ,x_n]$.
        \end{remark}
        \begin{definition}
            A total ordering on a set $A$ is a relation
            $>$ such that $\forall_{a,b\in A}$, precisely one
            of the following truee:
            \begin{enumerate}
                \begin{multicols}{3}
                    \item $a<b$
                    \item $a=b$
                    \item $b<a$
                \end{multicols}
            \end{enumerate}
        \end{definition}
        \begin{definition}
            A relation $\sim$ on a set $A$ is said to be
            transitive if for all $a,b,c\in A$, if $a\sim b$ and
            $b\sim c$, then $a\sim c$.
        \end{definition}
        \begin{definition}
            A well ordering on a set $A$ is a relation $<$
            such that for every subset $E\subset A$, there is an
            element $x\in E$ such that for all $y\in E$, $y\ne x$,
            we have $x<y$.
        \end{definition}
        \begin{remark}
            Equivalently, a well ordering on a set $A$
            is a relation $<$ such that for every monotonically
            decreasing sequence $\alpha_n$, there is an
            $N\in \mathbb{N}$ such that for all $n>N$,
            $\alpha_n = \alpha_N$. That is,
            decreasing sequences terminate.
        \end{remark}
        \begin{definition}
            A monomial ordering on $\mathbb{N}^n$ is a relation
            $>$ such that $>$ is total, transitive, well
            ordering. A well ordering on $k[x_1,\hdots ,x_n]$
            is a well ordering on
            $\alpha=(\alpha_1,\hdots,\alpha_n)\in\mathbb{N}^n$.
        \end{definition}
        \begin{definition}
            The lexicographic ordering on $\mathbb{N}^n$ is
            defined as
            $(\alpha_1,\hdots,\alpha_n)\underset{Lex}{>}%
             (\beta_1,\hdots,\beta_n)$
            if the left-most non-zero entry of
            $(\alpha_1-\beta_1,\hdots, \alpha_n-\beta_n)$
            is positive.
        \end{definition}
        \begin{theorem}
            The lexicographic ordering is a monomial ordering.
        \end{theorem}
        \begin{definition}
            The graded lexicographic ordering is defined as
            $(\alpha_1,\hdots,\alpha_n)\underset{GrLex}{>}%
             (\beta_1,\hdots, \beta_n)$
            if $|\alpha|>|\beta|$ or $|\alpha|=|\beta|$
            and $\alpha\underset{Lex}{>}\beta$.
        \end{definition}
        \begin{theorem}
            The graded lexicographic ordering is a monomial ordering.
        \end{theorem}
        \begin{theorem}[The Division Algorithm]
            If $f_1,\hdots, f_s\in k[x_1,\hdots ,x_n]$ are
            non-zero polynomials and if $>$ is a monomial ordering,
            then there are $r,q_1,\hdots, q_n\in k[x_1,\hdots ,x_n]$
            such that the following are true:
            \begin{enumerate}
                \item $f=q_{1}f_{1}+\hdots+q_{s}f_{s}+r$
                \item No term of $r$ is divisible by
                      any of $\LT(f_{1}),\hdots,\LT(f_{s})$.
                \item $\LT(f)=\max_{>}\{\LT(q_{i})%
                       \cdot\LT(f_i):q_i\ne{0}\}$
            \end{enumerate}
        \end{theorem}
        \begin{definition}
            An ideal
            $I=\langle{x}^{\alpha}:\alpha\in{A}\rangle%
              =\{\sum_{\alpha}h_{\alpha}x^\alpha,h_{\alpha}%
               \in k[x_1,\hdots ,x_n]\}$
            is called a monomial ideal.
        \end{definition}
        \begin{theorem}
            If $I=\langle{x}^\alpha:\alpha\in{A}\rangle$
            is a monomial ideal,
            $\beta\in\mathbb{N}^n$, then $x^\beta\in{I}$
            if and only if there is an $\alpha\in{A}$
            such that $x^{\alpha}$ divides $x^{\beta}$.
        \end{theorem}
        \begin{theorem}
            If $I$ is a monomial ideal,
            $f\in{k}[x_1,\hdots ,x_n]$,
            then the following are equivalent:
            \begin{enumerate}
                \item $f\in I$
                \item Every term of $f$ lies in $I$.
                \item $f$ is a $k-$linear combination of
                      monomials in $I$.
            \end{enumerate}
        \end{theorem}
        \begin{theorem}[Dickson's Lemma]
            Every monomial ideal of $k[x_{1},\hdots,x_{n}]$
            is finitely generated.
        \end{theorem}
        \begin{theorem}[Hilbert's Basis Theorem]
            Every ideal $I\subset{k}[x_{1},\hdots,x_{n}]$
            is finitely generated.
        \end{theorem}
        \begin{definition}
            If $>$ is a monomial ordering on $k[x_{1},\hdots,x_{n}]$,
            then a Groebner Basis of $I\subset k[x_{1},\hdots,x_{n}]$
            is a set $G=\{g_{1},\hdots,g_{s}\}$ such that
            $\langle\LT(I)\rangle%
             =\langle \LT(g_1),\hdots,\LT(g_s)\rangle$
        \end{definition}
        \begin{theorem}
            Every non-zero ideal
            $I\subset{k}[x_{1},\hdots,x_{n}]$
            has a Groebner Basis.
        \end{theorem}
\end{document}