\documentclass[crop=false,class=article,oneside]{standalone}
%----------------------------Preamble-------------------------------%
\input{../../../../preamble.tex}
%--------------------------Main Document----------------------------%
\begin{document}
    \ifx\ifsub\undefined
        \section*{Algebraic Geometry}
        \setcounter{section}{1}
    \fi
    \subsection{The Zariski Topology}
        \subsubsection{The Zariski Topology}
            \begin{definition}
                A subset of $k^{n}$ is is closed in the
                Zariski Topology if it is an algebraic set.
                The Zariski Topology is formed by
                considering all such sets.
            \end{definition}
            \begin{definition}
                A topological space $X$ is called irreducible if
                for any closed subsets $X_1,X_2\subset X$ such that
                $X=X_{1}\cup{X_{2}}$, either $X=X_{1}$ or
                $X=X_{2}$. A topological space that is
                not irreducible is called reducible.
            \end{definition}
            \begin{definition}
                A subset $Y\subset X$ of a topological space
                is said to be irreducible if $Y$ is irreducible
                with respect to the inherited,
                or the induced topology.
            \end{definition}
            \begin{definition}
                A topological space $X$ is said to be disconnected
                if there are two non-empty closed subsets $X_1,X_2$
                such that $X=X_1\cup X_2$,
                and $X_1\cap X_2 = \emptyset$.
            \end{definition}
            \begin{theorem}
                If $X$ is disconnected, then it is reducible.
            \end{theorem}
            \begin{proof}
                For if $X$ is disconnected, there are two
                non-empty closed sets $X_1,X_2\subset X$ such
                that $X_1\cap X_2 = \emptyset$ and
                $X=X_1\cup X_2$. But if $X_1$ and $X_2$
                are non-empty and disjoint, then
                $X_1\ne X$ and $X_2 \ne X$.
                Therefore $X$ is reducible.
            \end{proof}
            \begin{definition}
                An algebraic affine variety is an
                irreducible closed subset of $k^n$.
            \end{definition}
            \begin{definition}
                An open subset of an affine variety
                is called a quasi-affine variety.
            \end{definition}
            \begin{definition}
                If $X\subset k^n$ is an algebraic set,
                then $k[x_1,\hdots ,x_n]/\mathbb{I}(X)$
                is called the coordinate ring of $X$.
            \end{definition}
            \begin{definition}
                A set $Y$ in a topological space $X$ is
                said to be dense in $X$ if for every
                non-empty open set $\mathcal{O}$,
                $\mathcal{O}\cap Y\ne \emptyset$.
            \end{definition}
            \begin{theorem}
                A topological space $X$ is irreducible if
                and only if every non-empty open set is dense.
            \end{theorem}
            \begin{definition}
                An irreducible component of $X$ is a
                maximal irreducible subset of $X$.
            \end{definition}
            \begin{theorem}
                If $X$ is a closed topological space,
                then any irreducible subset $Y\subset X$ is
                contained in a maximal component.
            \end{theorem}
            \begin{theorem}
                If $X$ is a topological space,
                then it is the union of irreducible components.
            \end{theorem}
            \begin{definition}
                A topological space $X$ is called Noetherian
                if every descending chain $X_n \subset X_{n+1}$
                of closed subsets stabilizes.
            \end{definition}
            \begin{theorem}
                If $X$ is a Noetherian Space,
                then every subset $Y\subset X$ can be
                written as a finite union of irreducible
                closed subsets.
            \end{theorem}
            \begin{theorem}
                Every algebraic set in $k^n$ can be expressed
                uniquely as a union of varieties.
            \end{theorem}
            \begin{theorem}
                If $R$ is an Noetherian ring,
                then $k[x_1,\hdots ,x_n]$ is Noetherian.
            \end{theorem}
            \begin{theorem}
                A ring $R$ is Noetherian if and only if every
                non-empty set of ideals in $R$ has a maximal element.
            \end{theorem}
            \begin{theorem}[Hilbert's Nullstellensats]
                If $k$ is an algebraically closed field,
                $I\subset R = k[x_1,\hdots ,x_n]$ is an ideal,
                and $f\in R$ is a polynomial which vanishes on
                $\mathbf{V}(I)$, then there is an $n\in \mathbb{N}$
                such that $f^{n}\in{I}$.
            \end{theorem}
            \begin{definition}
                The dimension of a topological space $X$ is the
                supremum of all $n\in \mathbb{N}$ such that
                there is a chain
                $Z_0\subset Z_1\subset\hdots\subset Z_n$
                of distinct irreducible closed
                subsets of $X$.
            \end{definition}
            \begin{theorem}
                If $k$ is a field, and $B$ is an integral domain
                which is finitely generated by a $k-$algebra,
                then the dimension of $B$ is equal to the
                transcendence degree of the quotient field $k(B)$
                of $B$ over $k$.
            \end{theorem}
            \begin{theorem}
                The dimension of $k^{n}$ is $n$.
            \end{theorem}
            \begin{theorem}
                If $Y$ is a quasi-affine variety,
                then $\dim(Y)=\dim(\overline{Y})$.
            \end{theorem}
        \subsubsection{Problems}
            \begin{problem}
                Let $f\in k[x]$ be a non-constant polynomial
                in one variable over a field $k$. $f$ is called
                irreducible if $f\notin k$ and if it is not
                the product of two polynomials of strictly smaller
                degree. Prove the following are equivalent:
                \begin{enumerate}
                    \item $k[x]/\langle f\rangle$ is a field.
                    \item $k[x]/\langle f\rangle$ is an
                          integral domain.
                    \item $f$ is irreducible.
                \end{enumerate}
            \end{problem}
            \begin{proof}[Solution]
                If $k[x]/\langle f\rangle$ is a field,
                then it is an integral domain. If $f$ is
                irreducible, then $\langle f\rangle$ is
                maximal and thus $k[x]/\langle f\rangle$ is
                a field. Finally, if $k[x]/\langle f\rangle$ is
                an integral domain, then $\langle f\rangle$ is
                prime. But if $\langle f\rangle$ is prime,
                then it is maximal. And if $\langle f\rangle$
                is maximal, then $f$ is irreducible. 
            \end{proof}
            \begin{problem}
                Show every prime ideal is radical.
            \end{problem}
            \begin{proof}[Solution]
                Let $I$ be a prime ideal. Then if $fg\in I$,
                either $f\in I$ or $g\in I$. Suppose $f^n \in I$
                for some $f\in R$. Then $f^{n-1}f \in R$.
                But then either $f^{n-1} \in I$ or $f\in I$.
                If $f\in I$, we are done. If not, by induction
                $f^{n-k} \in I$ and we obtain $f\in I$.
            \end{proof}
            \begin{problem}
                Show that any Noetherian
                Topological Space $X$ is compact.
            \end{problem}
            \begin{proof}[Solution]
                If $X$ is Noetherian, then every ascending
                chain terminates. Suppose $X$ is not compact.
                Then there is an open cover $\Delta$ with no
                finite subcover. Let $\mathcal{O}_1$ be a finite
                subcover. Then
                $\cup_{\mathcal{U}\in \mathcal{O}_1}\mathcal{U}$
                is not all of $X$, otherwise $X$ would be compact.
                Thus there is an open subcover $\mathcal{O}_2$
                such that $\mathcal{O}_1 \subset \mathcal{O}_2$.
                Inductively, we have a sequence
                $\mathcal{O}_n\subset \mathcal{O}_{n+1}$. Let
                $A_{n}=\cup_{k=1}^{n}\cup_{\mathcal{U}\in \mathcal{O}_k}\mathcal{U}$.
                Then $A_{n}\subset A_{n+1}$.
                But by the Noetherian property,
                this chain must stabilize.
                But then there is an $N\in \mathbb{N}$
                such that $\mathcal{O}_{N+1}=\mathcal{O}_N$,
                a contradiction as we said $X$ is not compact.
                Therefore, etc.
            \end{proof}
            \begin{remark}
                This proof subtly requires the axiom of
                choice in the construction of such
                $\mathcal{O}'s$.
            \end{remark}
\end{document}