%------------------------------------------------------------------------------%
\begingroup
    \ifcsname\PATH\endcsname
        \newcommand{\PATH}{books/Foundations/Logic}
        \newcommand{\OLDPATH}{\PATH}
    \else
        \newcommand{\OLDPATH}{\PATH}
        \renewcommand{\PATH}{books/Foundations/Logic}
    \fi
    \chapter{Logic}
        \label{chapt:Propositional_Logic}%
        We'll begin our discussion of logic with the most primitive kind:
        propositional logic\index{Logic!Propositional}. This form, also called
        \textit{sententially logic}\index{Logic!Sentential}, deals with the
        structure of sentences. That is, how do we use the English language to
        formulate arguments, and how can various arguments be used to deduce new
        facts. It is for this reason that one should start with the foundations
        of logic, for at the heart of mathematics is the concept of
        \textit{definition}, \textit{theorem}, and \textit{proof}. The word
        definition, it is hoped, is understood as a primitive word in the
        English language (much like the work \textit{the}), but theorem and
        proof need an explaination if we are to consistently use the notions.
        \par\hfill\par
        We'll build logic rather rapidly, starting with the concept of a
        \textit{proposition}\index{Proposition}, which will be
        another one of our primitive words. The development here will be self
        contained, but rather brief. Unlike other parts of this work, which
        contain theorems, examples, and discussions not for their usefulness,
        but for the sake of mathematics, this part on foundational logic will
        primarily develop what is needed to proceed on to set theory. This is
        not to say that mathematical logic\index{Mathematical Logic} will have
        no further part, on the contrary we will develop
        \textit{Boolean Algebras}\index{Boolean Algebra} later in
        Book~\ref{book:Foundations}, and in Book~\ref{book:Topology}, when
        discussing topology, we will discuss
        \textit{Stone Spaces}\index{Stone Space}, which are integral to one of
        the most fundamental theorems of mathematics: The
        \textit{Stone Representation Theorem}%
        \index{Theorem!Stone Representation Theorem}%
        \index{Stone Representation Theorem}, which connects logic, set theory,
        topology, and measure theory in a remarkable way. All that is meant is,
        in comparison to other areas, logic will be the most underdeveloped and
        the curious should consult the plethora of texts available.
        \input{\PATH/Propositional_Logic/Propositions.tex}
        \input{\PATH/Connectives.tex}
        \input{\PATH/Quantifiers.tex}
    \renewcommand{\PATH}{\OLDPATH}
\endgroup